
%%--------------------------------------------------
%% CPO: AMC Open Free Response Questions
%%--------------------------------------------------


%% Chapter 1: Describing the Physical Universe
%%--------------------------------------------------


%% CPO Short Answer Questions
%%--------------------------------------------------
\element{cpo-short}{
\begin{question}{ch01-short-q01}
    List three fundamental activities involved in the study of physics.
    \AMCOpen{lines=3}{
        \wrongchoice[W]{w}\scoring{0}
        \wrongchoice[P]{p}\scoring{1}
        \correctchoice[C]{c}\scoring{2}
    }
\end{question}
}

\element{cpo-short}{
\begin{question}{ch01-short-q02}
    Summarize the method for solving physics problems by listing
        the steps in the four-step technique:
    \AMCOpen{lines=3}{
        \wrongchoice[W]{w}\scoring{0}
        \wrongchoice[P]{p}\scoring{1}
        \correctchoice[C]{c}\scoring{2}
    }
    %% ANS: FGRS
\end{question}
}

\element{cpo-short}{
\begin{question}{ch01-short-q03}
    What two measurements do you need to know in order to determine
        the speed of something?
    \AMCOpen{lines=3}{
        \wrongchoice[W]{w}\scoring{0}
        \wrongchoice[P]{p}\scoring{1}
        \correctchoice[C]{c}\scoring{2}
    }
    %% ANS: distance and time
\end{question}
}


%% CPO Problem Questions
%%--------------------------------------------------
\element{cpo-problem}{
\begin{question}{ch01-problem-q01}
    Calculate the number of millimeters in 2.13 kilometers
    \AMCOpen{lines=3}{
        \wrongchoice[W]{w}\scoring{0}
        \wrongchoice[P]{p}\scoring{1}
        \correctchoice[C]{c}\scoring{2}
    }
    %% ANS: \SI{2.13e6}{\milli\meter}
\end{question}
}

\element{cpo-problem}{
\begin{question}{ch01-problem-q02}
    How many centimeters tall is a person who is 1.65 meters tall?
    \AMCOpen{lines=3}{
        \wrongchoice[W]{w}\scoring{0}
        \wrongchoice[P]{p}\scoring{1}
        \correctchoice[C]{c}\scoring{2}
    }
    %% ANS: \SI{165}{\centi\meter}
\end{question}
}

\element{cpo-problem}{
\begin{question}{ch01-problem-q03}
    Convert the following quantity of time to seconds. \textbf{3:45:12}
    \AMCOpen{lines=3}{
        \wrongchoice[W]{w}\scoring{0}
        \wrongchoice[P]{p}\scoring{1}
        \correctchoice[C]{c}\scoring{2}
    }
    %% ANS: \SI{13 512}{\second}
\end{question}
}

\element{cpo-problem}{
\begin{question}{ch01-problem-q04}
    A Canadian goose flies 150 kilometers in 2.2 hours.
    What is the speed of the goose?
    \AMCOpen{lines=3}{
        \wrongchoice[W]{w}\scoring{0}
        \wrongchoice[P]{p}\scoring{1}
        \correctchoice[C]{c}\scoring{2}
    }
    %% ANS: \SI{68}{\kilo\meter\per\hour}
\end{question}
}

\element{cpo-problem}{
\begin{question}{ch01-problem-q05}
    Arnold the astronaut sends a laser signal from his moon base headquarters to Earth.
    If the signal, traveling at \SI{186 000}{\mile\per\second} (the speed of light),
        is received on Earth \SI{1.280}{\second} after it is sent, what is the distance
        between Arnold's lunar headquarters and Earth?
    \AMCOpen{lines=3}{
        \wrongchoice[W]{w}\scoring{0}
        \wrongchoice[P]{p}\scoring{1}
        \correctchoice[C]{c}\scoring{2}
    }
    %% ANS: \SI{238 000}{\mile}
\end{question}
}

\element{cpo-problem}{
\begin{question}{ch01-problem-q06}
    Emma walks to school at a speed of \SI{3}{\mile\per\hour}.
    If it takes her 20 minutes to walk from home to school,
        how many miles away is the school from her hours?
    \AMCOpen{lines=3}{
        \wrongchoice[W]{w}\scoring{0}
        \wrongchoice[P]{p}\scoring{1}
        \correctchoice[C]{c}\scoring{2}
    }
    %% ANS: \SI{1}{\mile}
\end{question}
}

\element{cpo-problem}{
\begin{question}{ch01-problem-q07}
    If Lyda can run \SI{2}{\mile} in \SI{15}{\minute},
        what is her speed in miles per hour?
    \AMCOpen{lines=3}{
        \wrongchoice[W]{w}\scoring{0}
        \wrongchoice[P]{p}\scoring{1}
        \correctchoice[C]{c}\scoring{2}
    }
    %% ANS: \SI{8}{\mile\per\hour}
\end{question}
}

\element{cpo-problem}{
\begin{question}{ch01-problem-q08}
    A professional bicyclist rides a time trial in which
        he travels at 51.2 kilometers per hour for 55 minutes.
    How far does he travel?
    \AMCOpen{lines=3}{
        \wrongchoice[W]{w}\scoring{0}
        \wrongchoice[P]{p}\scoring{1}
        \correctchoice[C]{c}\scoring{2}
    }
    %% ANS: \SI{46.9}{\kilo\meter}
\end{question}
}

\element{cpo-problem}{
\begin{question}{ch01-problem-q09}
    Recently, the speed limit between Utica and Rome, New York
        was raised from \SI{55}{\milee\per\hour} to \SI{65}{\mile\per\hour}.
    If the distance from Utica to Rome is \SI{12}{\hour}, how many
        minutes are saved by traveling at the new speed limit?
    \AMCOpen{lines=3}{
        \wrongchoice[W]{w}\scoring{0}
        \wrongchoice[P]{p}\scoring{1}
        \correctchoice[C]{c}\scoring{2}
    }
    %% ANS: \SI{2}{\minute}
\end{question}
}


%% CPO Essay Questions
%%--------------------------------------------------
\element{cpo-essay}{
\begin{question}{ch01-essay-q01}
    A child's wagon rolls from the top of a hill to the bottom  
        of a hill.
    Discuss the changes in energy and the stability of the system
        of the wagon and the hill as a result of these energy changes.
    \AMCOpen{lines=3}{
        \wrongchoice[W]{w}\scoring{0}
        \wrongchoice[P]{p}\scoring{1}
        \correctchoice[C]{c}\scoring{2}
    }
    %% ANS: At the top of the hill the wagon has more energy and is less stable.
\end{question}
}

\element{cpo-essay}{
\begin{question}{ch01-essay-q02}
    Tell why it is important to include units whenever you describe a measurement.
    \AMCOpen{lines=3}{
        \wrongchoice[W]{w}\scoring{0}
        \wrongchoice[P]{p}\scoring{1}
        \correctchoice[C]{c}\scoring{2}
    }
\end{question}
}

\endinput


