
%%--------------------------------------------------
%% CPO: AMC Open Free Response Questions
%%--------------------------------------------------


%% Chapter 3: Conservation Laws
%%--------------------------------------------------


%% CPO Short Answer Questions
%%--------------------------------------------------
\element{cpo-short}{
\begin{question}{ch03-short-q01}
    A speeding truck makes contact with a bug on its windshield.
    Compare the force that the bug exerts on the truck to the force
        that the truck exerts on the bug.
    \AMCOpen{lines=3}{
        \wrongchoice[W]{w}\scoring{0}
        \wrongchoice[P]{p}\scoring{1}
        \correctchoice[C]{c}\scoring{2}
    }
\end{question}
}

\element{cpo-short}{
\begin{question}{ch03-short-q02}
    When you push on your friend who is seated in a wagon,
        the wagon moves.
    According to Newton's 1\textsuperscript{st} law of motion,
        the force you apply to your friend is equal but opposite
        to the force your friend applies to you.
    Explain why the two equal and opposite do not cancel one
        another with no resulting motion.
    Tell what force \emph{does} cause the motion.
    \AMCOpen{lines=3}{
        \wrongchoice[W]{w}\scoring{0}
        \wrongchoice[P]{p}\scoring{1}
        \correctchoice[C]{c}\scoring{2}
    }
\end{question}
}

\element{cpo-short}{
\begin{question}{ch03-short-q03}
    As a tennis player, golfer, baseball player or soccer player you might
        be told by your coach to ``follow through'' when striking the ball.
    Explain why.
    \AMCOpen{lines=3}{
        \wrongchoice[W]{w}\scoring{0}
        \wrongchoice[P]{p}\scoring{1}
        \correctchoice[C]{c}\scoring{2}
    }
    %% ANS: maintain contact for a longer period of time.
\end{question}
}

\element{cpo-short}{
\begin{question}{ch03-short-q04}
    A ball is thrown from position (1) to a height of \SI{5}{\meter}
        above at position (2), giving the ball potential energy.
    The ball then falls to position (3).
    Assuming there is no loss of energy due to friction:
    \begin{center}
    \begin{tikzpicture}
        %% NOTE: TODO: draw tikz
    \end{tikzpicture}
    \end{center}
    \begin{itemize}
        \item Name the height at which the kinetic energy of the ball would be exactly the same as its potential energy.
        \item Compare the potential energy at (3) to the kinetic energy at (2).
        \item Compare the kinetic energy at (1) to the potential energy at (2).
    \end{itemize}
    \AMCOpen{lines=3}{
        \wrongchoice[W]{w}\scoring{0}
        \wrongchoice[P]{p}\scoring{1}
        \correctchoice[C]{c}\scoring{2}
    }
    %% ANS: maintain contact for a longer period of time.
\end{question}
}


%% CPO Problem Questions
%%--------------------------------------------------
\element{cpo-problem}{
\begin{question}{ch03-problem-q01}
    Calculate the momentum of a \SI{30}{\kilo\gram} cart moving
        at a speed of \SI{2.0}{\meter\per\second}.
    \AMCOpen{lines=3}{
        \wrongchoice[W]{w}\scoring{0}
        \wrongchoice[P]{p}\scoring{1}
        \correctchoice[C]{c}\scoring{2}
    }
    %% ANS: \SI{60}{\kilo\gram\meter\per\second}
\end{question}
}

\element{cpo-problem}{
\begin{question}{ch03-problem-q02}
    While sitting motionless on a \SI{10}{\kilo\gram}, friction-free wagon,
        \SI{75}{\kilo\gram} ``Bozo, the human target'' catches an \SI{8}{\kilo\gram}
        cannonball moving at \SI{15}{\meter\per\second}.
    After catching the cannonball, at what speed do Bozo, the wagon
        and the cannonball move?
    \AMCOpen{lines=3}{
        \wrongchoice[W]{w}\scoring{0}
        \wrongchoice[P]{p}\scoring{1}
        \correctchoice[C]{c}\scoring{2}
    }
    %% ANS: \SI{1.3}{\meter\per\second}
\end{question}
}

\element{cpo-problem}{
\begin{question}{ch03-problem-q03}
    Calculate the size of the impulse that must be applied to stop
        a \SI{200}{\kilo\gram} wagon rolling on a flat path at a
        speed of \SI{4.5}{\meter\per\second}.
    \AMCOpen{lines=3}{
        \wrongchoice[W]{w}\scoring{0}
        \wrongchoice[P]{p}\scoring{1}
        \correctchoice[C]{c}\scoring{2}
    }
    %% ANS: \SI{13 512}{\second}
\end{question}
}

\element{cpo-problem}{
\begin{question}{ch03-problem-q04}
    Calculate the speed of a \SI{0.25}{\kilo\gram} water
        balloon propelled by a water balloon launcher applying
        an average force of \SI{20}{\newton} for \SI{0.75}{\second}.
    \AMCOpen{lines=3}{
        \wrongchoice[W]{w}\scoring{0}
        \wrongchoice[P]{p}\scoring{1}
        \correctchoice[C]{c}\scoring{2}
    }
    %% ANS: \SI{60}{\meter\per\hour}
\end{question}
}

\element{cpo-problem}{
\begin{question}{ch03-problem-q05}
    Calculate the maximum height a \SI{0.75}{\kilo\gram} ball will
        rise if it is kicked straight up with an initial speed of \SI{17}{\meter\per\second}.
    \AMCOpen{lines=3}{
        \wrongchoice[W]{w}\scoring{0}
        \wrongchoice[P]{p}\scoring{1}
        \correctchoice[C]{c}\scoring{2}
    }
    %% ANS: \SI{14.7}{\meter}
\end{question}
}


%% CPO Essay Questions
%%--------------------------------------------------
\element{cpo-essay}{
\begin{question}{ch03-essay-q01}
    Two forces act on you when you are standing motionless on the floor,
        the force due to gravity and the force of the floor.
    These two forces are equal and opposite.
    Are they the action-reaction forces that are referred to in Newton's
        third law?
    Explain your answer.
    \AMCOpen{lines=3}{
        \wrongchoice[W]{w}\scoring{0}
        \wrongchoice[P]{p}\scoring{1}
        \correctchoice[C]{c}\scoring{2}
    }
    %% ANS: At the top of the hill the wagon has more energy and is less stable.
\end{question}
}

\element{cpo-essay}{
\begin{question}{ch03-essay-q02}
    Explain why airbags in automobiles help to prevent injury.
    \AMCOpen{lines=3}{
        \wrongchoice[W]{w}\scoring{0}
        \wrongchoice[P]{p}\scoring{1}
        \correctchoice[C]{c}\scoring{2}
    }
\end{question}
}

\element{cpo-essay}{
\begin{question}{ch03-essay-q03}
    If you exert the same force on Earth exerts on your, why
        doesn't Earth move up to meet you when you jump off its surface?
    \AMCOpen{lines=3}{
        \wrongchoice[W]{w}\scoring{0}
        \wrongchoice[P]{p}\scoring{1}
        \correctchoice[C]{c}\scoring{2}
    }
\end{question}
}

%\element{cpo-essay}{
%\begin{question}{ch03-essay-q04}
%    A \SI{20}{\gram} ball of clay strikes a wooden block
%        (pictured in the diagram) at a speed of \SI{10}{\centi\meter\per\second}
%        and sticks to the block.
%    The block wiggles but does not tip over.
%    A \SI{20}{\gram} ``bouncy ball'' traveling at \SI{10}{\centi\meter\per\second}
%        strikes the same block and bounces off in the direction from which it came.
%    This time, the block tips over.
%    Explain why.
%    \begin{center}
%        %% NOTE: Add diagram
%    \end{center}
%    \AMCOpen{lines=3}{
%        \wrongchoice[W]{w}\scoring{0}
%        \wrongchoice[P]{p}\scoring{1}
%        \correctchoice[C]{c}\scoring{2}
%    }
%\end{question}
%}

\endinput


