
%%--------------------------------------------------
%% CPO: AMC Open Free Response Questions
%%--------------------------------------------------


%% Chapter 8: Physical Properties of Matter
%%--------------------------------------------------


%% CPO Short Answer Questions
%%--------------------------------------------------
\element{cpo-short}{
\begin{question}{ch08-short-q01}
    In general, how do densities of solids, liquids, and gases compare?
    \AMCOpen{lines=3}{
        \wrongchoice[W]{w}\scoring{0}
        \wrongchoice[P]{p}\scoring{1}
        \correctchoice[C]{c}\scoring{2}
    }
    %% ANS: solid > liquid > gas
\end{question}
}

\element{cpo-short}{
\begin{question}{ch08-short-q02}
    Name three factors that determine the viscosity of a fluid.
    \AMCOpen{lines=3}{
        \wrongchoice[W]{w}\scoring{0}
        \wrongchoice[P]{p}\scoring{1}
        \correctchoice[C]{c}\scoring{2}
    }
    %% ANS: molecule size, molecule shape, and temperature
\end{question}
}

\element{cpo-short}{
\begin{question}{ch08-short-q03}
    A cork with a volume of \SI{500}{\centi\meter\cubed} and a mass
        of \SI{60}{\gram} is floating in water.
    What is the weight of the water displaced by the cork?
    \AMCOpen{lines=3}{
        \wrongchoice[W]{w}\scoring{0}
        \wrongchoice[P]{p}\scoring{1}
        \correctchoice[C]{c}\scoring{2}
    }
    %% ANS: \SI{0.588}{\newton}
\end{question}
}

\element{cpo-short}{
\begin{question}{ch08-short-q04}
    If the temperature of a gas is held constant, what would
        happen to the volume of a gas if the pressure on the
        gas is increased to three times the original amount?
    \AMCOpen{lines=3}{
        \wrongchoice[W]{w}\scoring{0}
        \wrongchoice[P]{p}\scoring{1}
        \correctchoice[C]{c}\scoring{2}
    }
    %% ANS: the volume of gas would decrease by a factor of 3
\end{question}
}

\element{cpo-short}{
\begin{question}{ch08-short-q05}
    Describe the effect of increasing the temperature of a gas
        on the pressure exerted by the gas when a constant
        volume is maintained.
    \AMCOpen{lines=3}{
        \wrongchoice[W]{w}\scoring{0}
        \wrongchoice[P]{p}\scoring{1}
        \correctchoice[C]{c}\scoring{2}
    }
    %% ANS: PV/nrT = K
\end{question}
}


%% CPO Problem Questions
%%--------------------------------------------------
\element{cpo-problem}{
\begin{question}{ch08-problem-q01}
    Calculate the volume of a small iceberg with a mass of
        \SI{200 000}{\kilo\gram}.
        (density of ice = \SI{920}{\kilo\gram\per\meter\cubed})
    \AMCOpen{lines=3}{
        \wrongchoice[W]{w}\scoring{0}
        \wrongchoice[P]{p}\scoring{1}
        \correctchoice[C]{c}\scoring{2}
    }
    %% ANS: \SI{217}{\meter\cubed}
\end{question}
}

\element{cpo-problem}{
\begin{question}{ch08-problem-q02}
    Calculate the cross-section area needed using an oak beam
        to support a \SI{10 000}{\kilo\gram} mass.
    (tensile strength of oak = \SI{95e6}{\pascal})
    \AMCOpen{lines=3}{
        \wrongchoice[W]{w}\scoring{0}
        \wrongchoice[P]{p}\scoring{1}
        \correctchoice[C]{c}\scoring{2}
    }
    %% ANS: \SI{98 000}{\newton}
\end{question}
}

\element{cpo-problem}{
\begin{question}{ch08-problem-q03}
    A stone that weighs \SI{6.5}{\newton} in air weighs
        only \SI{5.0}{\newton} when submerged in water.
    What is the buoyant force exerted on the rock by the
        water?
    \AMCOpen{lines=3}{
        \wrongchoice[W]{w}\scoring{0}
        \wrongchoice[P]{p}\scoring{1}
        \correctchoice[C]{c}\scoring{2}
    }
    %% ANS: \SI{1.5}{\newton}
\end{question}
}

\element{cpo-problem}{
\begin{question}{ch08-problem-q04}
    Calculate the pressure at the bottom of a water-filled
        aquarium that is \SI{0.4}{\meter} deep.
    (density of water = \SI{1000}{\kilo\gram\per\meter\cubed})
    \AMCOpen{lines=3}{
        \wrongchoice[W]{w}\scoring{0}
        \wrongchoice[P]{p}\scoring{1}
        \correctchoice[C]{c}\scoring{2}
    }
    %% ANS: \SI{3920}{\pascal}
\end{question}
}

\element{cpo-problem}{
\begin{question}{ch08-problem-q05}
    Rita opened a \SI{500}{\centi\meter\cubed} bottle of water
        and drank half of it, leaving \SI{250}{\centi\meter\cubed}
        of air space at the top of the bottle.
    When she left the bottle with the cap in her car, the
        temperature was \SI{20}{\degreeCelsius}.
    When she came back to her car later in the day the temperature
        had risen to \SI{40}{\degreeCelsius}.
    What is the pressure of the air in the bottle?
    \AMCOpen{lines=3}{
        \wrongchoice[W]{w}\scoring{0}
        \wrongchoice[P]{p}\scoring{1}
        \correctchoice[C]{c}\scoring{2}
    }
    %% ANS: \SI{1.07}{\atm}
\end{question}
}


%% CPO Essay Questions
%%--------------------------------------------------
\element{cpo-essay}{
\begin{question}{ch08-essay-q01}
    Explain why the ability to withstand an applied force is not
        enough to describe the strength of a material.
    \AMCOpen{lines=3}{
        \wrongchoice[W]{w}\scoring{0}
        \wrongchoice[P]{p}\scoring{1}
        \correctchoice[C]{c}\scoring{2}
    }
\end{question}
}

\element{cpo-essay}{
\begin{question}{ch08-essay-q02}
    Jim and his friend Bill are building a small pond on their farm
        by piling rocks across the channel of a stream to make a dam.
    If they have difficulty lifting a rock out of the water to move
        it to the dam, they carry the rock more easily by keeping
        it under the surface of the water.
    Explain why this works.
    \AMCOpen{lines=3}{
        \wrongchoice[W]{w}\scoring{0}
        \wrongchoice[P]{p}\scoring{1}
        \correctchoice[C]{c}\scoring{2}
    }
\end{question}
}

\element{cpo-essay}{
\begin{question}{ch08-essay-q03}
    Describe how Newton's third law is related to fluid pressure.
    \AMCOpen{lines=3}{
        \wrongchoice[W]{w}\scoring{0}
        \wrongchoice[P]{p}\scoring{1}
        \correctchoice[C]{c}\scoring{2}
    }
\end{question}
}

\element{cpo-essay}{
\begin{question}{ch08-essay-q04}
    The density of steel is \SI{7800}{\kilo\gram\per\meter\cubed}.
    The density of water is \SI{1000}{\kilo\gram\per\meter\cubed}.
    Explain how steel ships are made to float in water.
    \AMCOpen{lines=3}{
        \wrongchoice[W]{w}\scoring{0}
        \wrongchoice[P]{p}\scoring{1}
        \correctchoice[C]{c}\scoring{2}
    }
\end{question}
}

\element{cpo-essay}{
\begin{question}{ch08-essay-q05}
    While pumping up the tire of her bicycle, Kortney feels the
        tire and finds it warmer to touch.
    What is the most likely cause for the increase in the temperature
        of the tire?
    \AMCOpen{lines=3}{
        \wrongchoice[W]{w}\scoring{0}
        \wrongchoice[P]{p}\scoring{1}
        \correctchoice[C]{c}\scoring{2}
    }
\end{question}
}

\endinput


