
%%--------------------------------------------------
%% CPO: AMC Open Free Response Questions
%%--------------------------------------------------


%% Chapter 12: Relativity
%%--------------------------------------------------


%% CPO Short Answer Questions
%%--------------------------------------------------
\element{cpo-short}{
\begin{question}{ch12-short-q01}
    Where does the energy released by a nuclear reaction come from?
    \AMCOpen{lines=3}{
        \wrongchoice[W]{w}\scoring{0}
        \wrongchoice[P]{p}\scoring{1}
        \correctchoice[C]{c}\scoring{2}
    }
    %% ANS: reactants: HCl and CaCO_3;
    %% ANS: products: CaCl_2 and H_2O
\end{question}
}

\element{cpo-short}{
\begin{question}{ch12-short-q02}
    What happens when antimatter meets an equal amount of normal matter?
    \AMCOpen{lines=3}{
        \wrongchoice[W]{w}\scoring{0}
        \wrongchoice[P]{p}\scoring{1}
        \correctchoice[C]{c}\scoring{2}
    }
\end{question}
}

\element{cpo-short}{
\begin{question}{ch12-short-q03}
    Which travels the fastest: light, gravity or radio waves?
    \AMCOpen{lines=3}{
        \wrongchoice[W]{w}\scoring{0}
        \wrongchoice[P]{p}\scoring{1}
        \correctchoice[C]{c}\scoring{2}
    }
\end{question}
}

\element{cpo-short}{
\begin{question}{ch12-short-q04}
    Energy is produced by the sun in fusion reactions.
    What does this say about the mass of the sun?
    \AMCOpen{lines=3}{
        \wrongchoice[W]{w}\scoring{0}
        \wrongchoice[P]{p}\scoring{1}
        \correctchoice[C]{c}\scoring{2}
    }
\end{question}
}

\element{cpo-short}{
\begin{question}{ch12-short-q05}
    What is ``relative'' about the theory of special relativity?
    \AMCOpen{lines=3}{
        \wrongchoice[W]{w}\scoring{0}
        \wrongchoice[P]{p}\scoring{1}
        \correctchoice[C]{c}\scoring{2}
    }
\end{question}
}

\element{cpo-short}{
\begin{question}{ch12-short-q06}
    Explain what the variables in the equation $E=mc^2$ represent
        and the meaning of the equation itself.
    \AMCOpen{lines=3}{
        \wrongchoice[W]{w}\scoring{0}
        \wrongchoice[P]{p}\scoring{1}
        \correctchoice[C]{c}\scoring{2}
    }
\end{question}
}

\element{cpo-short}{
\begin{question}{ch12-short-q07}
    You are traveling in a spaceship at \SI{5e7}{\meter\per\second}.
    You friend is standing on the ground observing as you travel by.
    Use this scenario to answer the following question.
    If you were to throw a ball at \SI{10}{\meter\per\second} in the
        same direction the rocketship is traveling, what speed would
        your friend on the ground see the ball traveling?
    What speed would you see the ball traveling from inside the rocketship?
    \AMCOpen{lines=3}{
        \wrongchoice[W]{w}\scoring{0}
        \wrongchoice[P]{p}\scoring{1}
        \correctchoice[C]{c}\scoring{2}
    }
\end{question}
}

\element{cpo-short}{
\begin{question}{ch12-short-q08}
    You are traveling in a spaceship at \SI{5e7}{\meter\per\second}.
    You friend is standing on the ground observing as you travel by.
    Use this scenario to answer the following question.
    If you were to shine a light in the same direction the
        rocketship is traveling, what speed would your friend
        on the ground see the light traveling?
    What speed would you see the light traveling from inside the rocketship?
    \AMCOpen{lines=3}{
        \wrongchoice[W]{w}\scoring{0}
        \wrongchoice[P]{p}\scoring{1}
        \correctchoice[C]{c}\scoring{2}
    }
\end{question}
}

\element{cpo-short}{
\begin{question}{ch12-short-q09}
    You are traveling in a spaceship at \SI{5e7}{\meter\per\second}.
    You friend is standing on the ground observing as you travel by.
    Use this scenario to answer the following question.
    If you were holding a meter stick in the rocketship, how would
        the meter stick look to your friend on the ground?
    How would the meter stick look to you from inside the rocketship?
    \AMCOpen{lines=3}{
        \wrongchoice[W]{w}\scoring{0}
        \wrongchoice[P]{p}\scoring{1}
        \correctchoice[C]{c}\scoring{2}
    }
    %% ANS: \SI{1}{\minute}
\end{question}
}


%% CPO Problem Questions
%%--------------------------------------------------
\element{cpo-problem}{
\begin{question}{ch12-problem-q01}
    If \SI{0.001}{\kilo\gram} of matter were completely converted
        into energy, how much energy would be created?
    \AMCOpen{lines=3}{
        \wrongchoice[W]{w}\scoring{0}
        \wrongchoice[P]{p}\scoring{1}
        \correctchoice[C]{c}\scoring{2}
    }
    %% ANS: \SI{9e13}{\joule}
\end{question}
}

\element{cpo-problem}{
\begin{question}{ch12-problem-q02}
    A nuclear power plant produces \SI{1e9}{\joule} of energy each
        second.
    How much mass is converted to energy each second?
    \AMCOpen{lines=3}{
        \wrongchoice[W]{w}\scoring{0}
        \wrongchoice[P]{p}\scoring{1}
        \correctchoice[C]{c}\scoring{2}
    }
    %% ANS: \SI{1e-8}{\kilo\gram}
\end{question}
}

\element{cpo-problem}{
\begin{question}{ch12-problem-q02}
    If \SI{1}{\micro\gram} (\SI{1e-9}{\kilo\gram}) of material is
        completely converted to pure energy, how long could the
        energy produced operate a \SI{100}{\watt} light-bulb?
    \AMCOpen{lines=3}{
        \wrongchoice[W]{w}\scoring{0}
        \wrongchoice[P]{p}\scoring{1}
        \correctchoice[C]{c}\scoring{2}
    }
    %% ANS: \SI{9e5}{\second}
\end{question}
}

\endinput


