
%%--------------------------------------------------
%% CPO: AMC Open Free Response Questions
%%--------------------------------------------------


%% Chapter 20: Waves
%%--------------------------------------------------


%% CPO Short Answer Questions
%%--------------------------------------------------
\element{cpo-short}{
\begin{question}{ch20-short-q01}
    List the following waves in order of their speeds from fastest to
        slowest and give their approximate speed.
    \begin{enumerate*}
        \item sound waves
        \item light waves
        \item water waves
    \end{enumerate*}
    \AMCOpen{lines=3}{
        \wrongchoice[W]{w}\scoring{0}
        \wrongchoice[P]{p}\scoring{1}
        \correctchoice[C]{c}\scoring{2}
    }
\end{question}
}

%\element{cpo-short}{
%\begin{question}{ch20-short-q02}
%    How many waves are represented in this diagram?
%    \begin{center}
%        %% NOTE: add diagram
%    \end{center}
%    \AMCOpen{lines=3}{
%        \wrongchoice[W]{w}\scoring{0}
%        \wrongchoice[P]{p}\scoring{1}
%        \correctchoice[C]{c}\scoring{2}
%    }
%    %% ANS: 4.5
%\end{question}
%}

\element{cpo-short}{
\begin{question}{ch20-short-q03}
    A vibrating string produces a standing wave of the 5\textsuperscript{th}
        harmonic.
    How many wavelengths are contained in this standing wave?
    \AMCOpen{lines=3}{
        \wrongchoice[W]{w}\scoring{0}
        \wrongchoice[P]{p}\scoring{1}
        \correctchoice[C]{c}\scoring{2}
    }
    %% ANS: 2.5
\end{question}
}

\element{cpo-short}{
\begin{question}{ch20-short-q04}
    List four things that may happen to a wave as it meets a boundary.
    \AMCOpen{lines=3}{
        \wrongchoice[W]{w}\scoring{0}
        \wrongchoice[P]{p}\scoring{1}
        \correctchoice[C]{c}\scoring{2}
    }
    %% ANS: reflection, refraction, diffraction, absorption
\end{question}
}


%% CPO Problem Questions
%%--------------------------------------------------
\element{cpo-problem}{
\begin{question}{ch20-problem-q01}
    Middle C on a piano has a frequency of about \SI{264}{\hertz}.
    If the wavelength in air of this note is \SI{1.31}{\meter},
        what is the speed of sound in air?
    \AMCOpen{lines=3}{
        \wrongchoice[W]{w}\scoring{0}
        \wrongchoice[P]{p}\scoring{1}
        \correctchoice[C]{c}\scoring{2}
    }
    %% ANS: \SI{346}{\meter\per\second}
\end{question}
}

\element{cpo-problem}{
\begin{question}{ch20-problem-q02}
    On a July day, the waves in the Outer Banks of North Carolina
        hit the beach every \SI{13}{\second}.
    If the distance between each wave crest is \SI{25}{\meter},
        what is the speed of the waves as they travel toward
        the beach?
    \AMCOpen{lines=3}{
        \wrongchoice[W]{w}\scoring{0}
        \wrongchoice[P]{p}\scoring{1}
        \correctchoice[C]{c}\scoring{2}
    }
    %% ANS: \SI{1.9}{\meter\hertz}
\end{question}
}

\element{cpo-problem}{
\begin{question}{ch20-problem-q03}
    The magnetron of a microwave oven produces a standing,
        electromagnetic wave with a frequency of \SI{2.4e9}{\hertz}.
    What is the length of one of these standing waves if the speed
        of an electromagnetic wave is \SI{3.0e8}{\meter\per\second}?
    \AMCOpen{lines=3}{
        \wrongchoice[W]{w}\scoring{0}
        \wrongchoice[P]{p}\scoring{1}
        \correctchoice[C]{c}\scoring{2}
    }
    %% ANS: \SI{1.25e-1}{\meter}
\end{question}
}

\element{cpo-problem}{
\begin{question}{ch20-problem-q04}
    A string \SI{3.0}{\meter} long is vibrating at \SI{50}{\hertz}
        at the 4\textsuperscript{th} harmonic.
    Calculate the speed of the wave on the string.
    \AMCOpen{lines=3}{
        \wrongchoice[W]{w}\scoring{0}
        \wrongchoice[P]{p}\scoring{1}
        \correctchoice[C]{c}\scoring{2}
    }
    %% ANS: \SI{75}{\meter\per\second}
\end{question}
}


%% CPO Essay Questions
%%--------------------------------------------------
\element{cpo-essay}{
\begin{question}{ch20-essay-q01}
    A string one meter long is being driven to vibrate at its
        fundamental frequency.
    The driver frequency is increased, causing the string to
        vibrate at its second harmonic.
    Explain what happens to the speed of the wave on the string
        when the frequency is increased.
    \AMCOpen{lines=3}{
        \wrongchoice[W]{w}\scoring{0}
        \wrongchoice[P]{p}\scoring{1}
        \correctchoice[C]{c}\scoring{2}
    }
    %% ANS: nothing, the changes cancel out
    %% ANS: v = \sqrt{ \frac{T}{\mu} }
\end{question}
}

\element{cpo-essay}{
\begin{question}{ch20-essay-q02}
    Describe each of the following using at least one complete sentence.
    \begin{enumerate*}
        \item reflection
        \item refraction
        \item diffraction
        \item absorption
    \end{enumerate*}
    \AMCOpen{lines=3}{
        \wrongchoice[W]{w}\scoring{0}
        \wrongchoice[P]{p}\scoring{1}
        \correctchoice[C]{c}\scoring{2}
    }
\end{question}
}

\element{cpo-essay}{
\begin{question}{ch20-essay-q03}
    Explain why a hot dog on a dry paper plate becomes hot in
        the microwave oven but the paper plate becomes hot
        only where it is in contact with the hot dog?
    \AMCOpen{lines=3}{
        \wrongchoice[W]{w}\scoring{0}
        \wrongchoice[P]{p}\scoring{1}
        \correctchoice[C]{c}\scoring{2}
    }
\end{question}
}

\endinput


