
%%--------------------------------------------------
%% CPO: AMC Open Free Response Questions
%%--------------------------------------------------


%% Chapter 22: Light and Color
%%--------------------------------------------------


%% CPO Short Answer Questions
%%--------------------------------------------------
\element{cpo-short}{
\begin{question}{ch22-short-q01}
    List three characteristics of light:
    \AMCOpen{lines=3}{
        \wrongchoice[W]{w}\scoring{0}
        \wrongchoice[P]{p}\scoring{1}
        \correctchoice[C]{c}\scoring{2}
    }
\end{question}
}


%% NOTE: light intensity is the candela?
%%       the question is using luminous flux
\element{cpo-short}{
\begin{question}{ch22-short-q02}
    Light intensity is the amount of light energy falling
        on a surface every second.
    Name a metric unit that could be used to measure light
        intensity?
    \AMCOpen{lines=3}{
        \wrongchoice[W]{w}\scoring{0}
        \wrongchoice[P]{p}\scoring{1}
        \correctchoice[C]{c}\scoring{2}
    }
    %% ANS: \si{\joule\per\second\per\meter\squared}
    %% ANS: \si{\watt\per\meter\squared}
    %% ANS: \si{\lumen}
\end{question}
}

\element{cpo-short}{
\begin{question}{ch22-short-q03}
    Another name for the subtractive color process is the CMYK
        color process.
    What do the letters CMYK represent?
    \AMCOpen{lines=3}{
        \wrongchoice[W]{w}\scoring{0}
        \wrongchoice[P]{p}\scoring{1}
        \correctchoice[C]{c}\scoring{2}
    }
\end{question}
}

\element{cpo-short}{
\begin{question}{ch22-short-q04}
    Indicate the color the apple appears for each of the following lights:
    \begin{enumerate*}
        \item A pure red apple illuminated by white light.
        \item A pure red apple illuminated by red light.
        \item A pure red apple illuminated by blue light.
    \end{enumerate*}
    \AMCOpen{lines=3}{
        \wrongchoice[W]{w}\scoring{0}
        \wrongchoice[P]{p}\scoring{1}
        \correctchoice[C]{c}\scoring{2}
    }
\end{question}
}


%% CPO Problem Questions
%%--------------------------------------------------
\element{cpo-problem}{
\begin{question}{ch22-problem-q01}
    The speed of light (\SI{3.00e8}{\meter\per\second})
        was determined by allowing light to travel \SI{40}{\kilo\meter}
        (\SI{40 000}{\meter}) and measuring the time for it to
        travel that distance.
    How much time was required for light to travel that distance?
    \AMCOpen{lines=3}{
        \wrongchoice[W]{w}\scoring{0}
        \wrongchoice[P]{p}\scoring{1}
        \correctchoice[C]{c}\scoring{2}
    }
    %% ANS: \SI{1.3e-4}{\second}
\end{question}
}

\element{cpo-problem}{
\begin{question}{ch22-problem-q02}
    A light year is the distance light travels in one year.
    What is the distance in meters?
    \AMCOpen{lines=3}{
        \wrongchoice[W]{w}\scoring{0}
        \wrongchoice[P]{p}\scoring{1}
        \correctchoice[C]{c}\scoring{2}
    }
    %% ANS: \SI{5 935}{\meter\hertz}
\end{question}
}

\element{cpo-problem}{
\begin{question}{ch22-problem-q03}
    A small light source located \SI{2}{\meter} from a
        wall illuminates the wall with an intensity of
        \SI{800}{\watt\per\square\meter}.
    Calculate the intensity of light illuminating the wall
        if the light source is moved to a distance of \SI{6}{\meter}
        from the wall.
    \AMCOpen{lines=3}{
        \wrongchoice[W]{w}\scoring{0}
        \wrongchoice[P]{p}\scoring{1}
        \correctchoice[C]{c}\scoring{2}
    }
    %% ANS: \SI{88.9}{\watt\per\meter\squared}
\end{question}
}


%% CPO Essay Questions
%%--------------------------------------------------
\element{cpo-essay}{
\begin{question}{ch22-essay-q01}
    The starter at a track meet shoots a blank pistol to start
        a \SI{100}{\meter} race.
    The timers at the other end of the track are told to start
        their watched when they see the smoke from the pistol,
        not when they hear the discharge.
    Explain why they should be given this instruction.
    \AMCOpen{lines=3}{
        \wrongchoice[W]{w}\scoring{0}
        \wrongchoice[P]{p}\scoring{1}
        \correctchoice[C]{c}\scoring{2}
    }
\end{question}
}

\element{cpo-essay}{
\begin{question}{ch22-essay-q02}
    Why are fluorescent lights considered more efficient
        than incandescent lights?
    \AMCOpen{lines=3}{
        \wrongchoice[W]{w}\scoring{0}
        \wrongchoice[P]{p}\scoring{1}
        \correctchoice[C]{c}\scoring{2}
    }
\end{question}
}

\element{cpo-essay}{
\begin{question}{ch22-essay-q03}
    Describe the basic difference between the operation
        of a video camera and a television.
    \AMCOpen{lines=3}{
        \wrongchoice[W]{w}\scoring{0}
        \wrongchoice[P]{p}\scoring{1}
        \correctchoice[C]{c}\scoring{2}
    }
\end{question}
}

\element{cpo-essay}{
\begin{question}{ch22-essay-q04}
    Explain the difference between the image of a yellow
        banana on a computer screen and an image of the
        banana on a piece of paper.
    \AMCOpen{lines=3}{
        \wrongchoice[W]{w}\scoring{0}
        \wrongchoice[P]{p}\scoring{1}
        \correctchoice[C]{c}\scoring{2}
    }
\end{question}
}

\element{cpo-essay}{
\begin{question}{ch22-essay-q05}
    A computer monitor screen is capable of producing million
        of colors.
    Explain how that may be done using only three colors:
        red, blue and green.
    \AMCOpen{lines=3}{
        \wrongchoice[W]{w}\scoring{0}
        \wrongchoice[P]{p}\scoring{1}
        \correctchoice[C]{c}\scoring{2}
    }
    %% ANS: \SIRange{20}{20 000}{\hertz}
\end{question}
}

\endinput


