
%%--------------------------------------------------
%% CPO: Multiple Choice Questions
%%--------------------------------------------------


%% Chapter 22: Light and Color
%%--------------------------------------------------


%% Learning Objectives
%%--------------------------------------------------

%% Describe the properties of light. 
%% Review the term light intensity.
%% Learn about the speed of light. 
%% Compare light and sound waves.
%% Describe white light and color. 
%% Learn how our eyes see light and interpret color. 
%% Explain the additive color process. 
%% Describe light as both a wave and a particle. 
%% Explain the subtractive color process.
%% Compare the CMYK and RGB processes. 
%% Explain the reasons behind color blindness. 
%% Describe how plants use light and color to grow.


%% CPO Multiple Choice Questions
%%--------------------------------------------------
\element{cpo-mc}{
\begin{question}{cpo-ch22-q01}
    All of the following are characteristics of light
        \emph{except} that light:
    \begin{choices}
        \wrongchoice{has color}
      \correctchoice{has mass}
        \wrongchoice{can travel \num{7.5} times around the Earth in one second}
        \wrongchoice{travel in straight lines}
    \end{choices}
\end{question}
}

\element{cpo-mc}{
\begin{question}{cpo-ch22-q02}
    The process of making light with heat is called.
    \begin{multicols}{2}
    \begin{choices}
        \wrongchoice{photoluminescence}
        \wrongchoice{photosynthesis}
      \correctchoice{incandescence}
        \wrongchoice{refraction}
    \end{choices}
    \end{multicols}
\end{question}
}

\element{cpo-mc}{
\begin{question}{cpo-ch22-q03}
    The speed of light is:
    \begin{multicols}{2}
    \begin{choices}
        \wrongchoice{\SI{300}{\meter\per\second}}
        \wrongchoice{\SI{30 00}{\meter\per\second}}
        \wrongchoice{\SI{300 000}{\meter\per\second}}
      \correctchoice{\SI{300 000 000}{\meter\per\second}}
    \end{choices}
    \end{multicols}
\end{question}
}

\element{cpo-mc}{
\begin{question}{cpo-ch22-q04}
    The use of fluorescent lights is more economical than
        incandescent bulbs because fluorescent bulbs:
    \begin{choices}
        \wrongchoice{produce more heat than light.}
      \correctchoice{emit four times more light from the same amount of electricity.}
        \wrongchoice{emit light from a hot, wire filament.}
        \wrongchoice{can be used for hatching baby chicks as well as for lighting.}
    \end{choices}
\end{question}
}

\element{cpo-mc}{
\begin{question}{cpo-ch22-q05}
    The speed of light is such an important speed it is represented by its own ``symbol''.
    The symbol used to represent the speed of light is:
    \begin{multicols}{4}
    \begin{choices}
        \wrongchoice{$L$}
        \wrongchoice{$v$}
      \correctchoice{$c$}
        \wrongchoice{$@$}
    \end{choices}
    \end{multicols}
\end{question}
}

\element{cpo-mc}{
\begin{question}{cpo-ch22-q06}
    Light travels in straight lines in a medium.
    Physicists call imaginary lines used to represent light in optical diagrams.
    \begin{multicols}{2}
    \begin{choices}
        \wrongchoice{light beams}
        \wrongchoice{sunbeams}
      \correctchoice{light rays}
        \wrongchoice{spectral lines}
    \end{choices}
    \end{multicols}
\end{question}
}

\element{cpo-mc}{
\begin{question}{cpo-ch22-q07}
    If light bounces off the surface of a material,
        the change in direction is called:
    \begin{multicols}{2}
    \begin{choices}
        \wrongchoice{refraction}
      \correctchoice{reflection}
        \wrongchoice{diffusion}
        \wrongchoice{interference}
    \end{choices}
    \end{multicols}
\end{question}
}

\element{cpo-mc}{
\begin{question}{cpo-ch22-q08}
    Light shining through a bottle of water is often bent.
    This change in direction is called:
    \begin{multicols}{2}
    \begin{choices}
        \wrongchoice{refraction}
        \wrongchoice{reflection}
      \correctchoice{diffusion}
        \wrongchoice{interference}
    \end{choices}
    \end{multicols}
\end{question}
}

\element{cpo-mc}{
\begin{question}{cpo-ch22-q09}
    Of the objects listed, the one that you do \emph{not}
        see because of reflected light is:
    \begin{choices}
        \wrongchoice{a painting}
        \wrongchoice{the moon}
      \correctchoice{the sun}
        \wrongchoice{the wall of your home}
    \end{choices}
\end{question}
}

\element{cpo-mc}{
\begin{question}{cpo-ch22-q10}
    A straw will appear broken in a glass of water because light traveling from air to water is:
    \begin{multicols}{2}
    \begin{choices}
        \wrongchoice{reflected}
      \correctchoice{refracted}
        \wrongchoice{diffused}
        \wrongchoice{diffracted}
    \end{choices}
    \end{multicols}
\end{question}
}

\element{cpo-mc}{
\begin{question}{cpo-ch22-q11}
    Which of the following colors of light has the highest energy?
    \begin{multicols}{2}
    \begin{choices}
        \wrongchoice{Red}
        \wrongchoice{Yellow}
        \wrongchoice{Blue}
      \correctchoice{Violet}
    \end{choices}
    \end{multicols}
\end{question}
}

\element{cpo-mc}{
\begin{question}{cpo-ch22-q12}
    During an electrical storm,
        thunder associated with a distant lightning strike is heard:
    \begin{choices}
      \correctchoice{after the lightning is seen because sound travels slower than light.}
        \wrongchoice{at the same time as the lightning because they occur at the same time.}
        \wrongchoice{before the lightning is seen because sound travels faster than light.}
        \wrongchoice{at the same time as the lightning because they travel at the same speed.}
    \end{choices}
\end{question}
}

\element{cpo-mc}{
\begin{question}{cpo-ch22-q13}
    Most of the objects that we see are visible to us because they:
    \begin{multicols}{2}
    \begin{choices}
        \wrongchoice{refract light}
        \wrongchoice{diffract light}
      \correctchoice{reflect light}
        \wrongchoice{emit light}
    \end{choices}
    \end{multicols}
\end{question}
}

\element{cpo-mc}{
\begin{question}{cpo-ch22-q14}
    When a light beam travels from a light source to your eyes,
        we know it:
    \begin{choices}
      \correctchoice{travels in a straight line}
        \wrongchoice{follows a zigzag path}
        \wrongchoice{moves very slowly}
        \wrongchoice{slows down and speeds up}
    \end{choices}
\end{question}
}

\element{cpo-mc}{
\begin{question}{cpo-ch22-q15}
    Sound travels \SI{0.2}{\mile} in one second.
    Lightning is seen to strike in the distance.
    Thunder associated with the strike is heard \SI{10}{\second} later.
    The lightning occurred at a distance of:
    \begin{multicols}{2}
    \begin{choices}
        \wrongchoice{\SI{10}{\mile}}
        \wrongchoice{\SI{5}{\mile}}
      \correctchoice{\SI{2}{\mile}}
        \wrongchoice{\SI{0.2}{\mile}}
    \end{choices}
    \end{multicols}
\end{question}
}

\element{cpo-mc}{
\begin{question}{cpo-ch22-q16}
    If the distance between a small light source and a screen
        is doubled, the intensity of light on the screen
        \rule[-0.1pt]{4em}{0.1pt} by \rule[-0.1pt]{4em}{0.1pt} times. 
    \begin{multicols}{2}
    \begin{choices}
        \wrongchoice{increases, two}
        \wrongchoice{decreases, two}
        \wrongchoice{increases, four}
        \wrongchoice{decreases, four}
    \end{choices}
    \end{multicols}
\end{question}
}

\element{cpo-mc}{
\begin{question}{cpo-ch22-q17}
    If the sun, which is located approximately \SI{1.49e11}{\meter} from Earth,
        were to suddenly stop emitting light,
        how much time would pass before people on Earth saw no sunlight?
    \begin{multicols}{2}
    \begin{choices}
        \wrongchoice{\SI{1.49e11}{\second}}
        \wrongchoice{\SI{0}{\second}}
      \correctchoice{\SI{4.96e2}{\second}}
        \wrongchoice{\SI{400}{\minute}}
    \end{choices}
    \end{multicols}
\end{question}
}

%% NOTE: These questions are technically incorrect.
%\element{cpo-mc}{
%\begin{question}{cpo-ch22-q18}
%    Photoreceptors commonly called cone cells respond to:
%    \begin{choices}
%      \correctchoice{red, blue, and green}
%        \wrongchoice{yellow, cyan, and magenta.}
%        \wrongchoice{black, white, and gray.}
%        \wrongchoice{yellow, cyan, magenta, and black.}
%    \end{choices}
%\end{question}
%}

%\element{cpo-mc}{
%\begin{question}{cpo-ch22-q19}
%    Rod cells respond to:
%    \begin{choices}
%      \correctchoice{white, black and gray.}
%        \wrongchoice{red, white, and blue.}
%        \wrongchoice{red, green, and blue.}
%        \wrongchoice{red, yellow, and blue.}
%    \end{choices}
%\end{question}
%}

\element{cpo-mc}{
\begin{question}{cpo-ch22-q20}
    The additive primary colors are:
    \begin{choices}
        \wrongchoice{red, white, and blue}
        \wrongchoice{cyan, magenta, and yellow}
        \wrongchoice{red, yellow, and blue}
      \correctchoice{red, green, and blue}
    \end{choices}
\end{question}
}

\element{cpo-mc}{
\begin{question}{cpo-ch22-q21}
    The color of a light source is related to its:
    \begin{choices}
        \wrongchoice{speed}
      \correctchoice{energy}
        \wrongchoice{amplitude}
        \wrongchoice{frequency multiplied by its wavelength}
    \end{choices}
\end{question}
}

\element{cpo-mc}{
\begin{question}{cpo-ch22-q22}
    When cone cells are stimulated by equal amounts of red, green, and blue light, we see:
    \begin{choices}
        \wrongchoice{no light}
      \correctchoice{white light}
        \wrongchoice{red light because it is the dominant color}
        \wrongchoice{orange light}
    \end{choices}
\end{question}
}

\element{cpo-mc}{
\begin{question}{cpo-ch22-q23}
    The portion of the electromagnetic spectrum most useful to living things is:
    \begin{choices}
        \wrongchoice{microwave radiation}
        \wrongchoice{infrared radiation}
        \wrongchoice{ultraviolet radiation}
      \correctchoice{visible light}
    \end{choices}
\end{question}
}

\element{cpo-mc}{
\begin{question}{cpo-ch22-q24}
    Color blindness is a condition that affects:
    \begin{multicols}{2}
    \begin{choices}
        \wrongchoice{the retina}
        \wrongchoice{rod cells}
      \correctchoice{cone cells}
        \wrongchoice{the optic nerve}
    \end{choices}
    \end{multicols}
\end{question}
}

\element{cpo-mc}{
\begin{question}{cpo-ch22-q25}
    Color televisions produce images by mixing dots of:
    \begin{choices}
        \wrongchoice{red, white, and blue}
        \wrongchoice{red, yellow, and blue}
      \correctchoice{red, green, and blue}
        \wrongchoice{magenta, yellow, and cyan}
    \end{choices}
\end{question}
}

\element{cpo-mc}{
\begin{question}{cpo-ch22-q26}
    The subtractive primary colors are:
    \begin{choices}
        \wrongchoice{red, white, and blue}
      \correctchoice{cyan, magenta, and yellow}
        \wrongchoice{red, yellow and blue}
        \wrongchoice{red, green, and blue}
    \end{choices}
\end{question}
}

\element{cpo-mc}{
\begin{question}{cpo-ch22-q27}
    An object that appears red in sunlight is illuminated only by blue light.
    It will appear to be:
    \begin{multicols}{2}
    \begin{choices}
      \correctchoice{black}
        \wrongchoice{white}
        \wrongchoice{red}
        \wrongchoice{violet}
    \end{choices}
    \end{multicols}
\end{question}
}

\element{cpo-mc}{
\begin{question}{cpo-ch22-q28}
    When white light illuminates a green leaf, \rule[-0.1pt]{4em}{0.1pt}
        are the two colors of light that are mainly absorbed.
    \begin{multicols}{2}
    \begin{choices}
        \wrongchoice{green and yellow}
        \wrongchoice{green and red}
      \correctchoice{red and blue}
        \wrongchoice{blue and yellow}
    \end{choices}
    \end{multicols}
\end{question}
}

\element{cpo-mc}{
\begin{question}{cpo-ch22-q29}
    The color of light that is \emph{least} useful for the growth of green plants is:
    \begin{multicols}{2}
    \begin{choices}
        \wrongchoice{red}
      \correctchoice{green}
        \wrongchoice{blue}
        \wrongchoice{white}
    \end{choices}
    \end{multicols}
\end{question}
}

\element{cpo-mc}{
\begin{question}{cpo-ch22-q30}
    Our vision is based on:
    \begin{choices}
      \correctchoice{the CMYK color process}
        \wrongchoice{the additive color process}
        \wrongchoice{the subtractive color process}
        \wrongchoice{constructive interference}
    \end{choices}
\end{question}
}

\element{cpo-mc}{
\begin{question}{cpo-ch22-q31}
    Compared to the best video equipment available,
        the human eye can detect \rule[-0.1pt]{4em}{0.1pt} from light.
    \begin{choices}
        \wrongchoice{a little more information}
        \wrongchoice{the same amount of information}
      \correctchoice{much more information}
        \wrongchoice{much less information}
    \end{choices}
\end{question}
}

\endinput

