
%%--------------------------------------------------
%% CPO: AMC Open Free Response Questions
%%--------------------------------------------------


%% Chapter 24: The Physical Nature of Light
%%--------------------------------------------------


%% CPO Short Answer Questions
%%--------------------------------------------------
\element{cpo-short}{
\begin{question}{ch24-short-Q01}
    Why is the speed of light in a vacuum considered to be a special speed?
    \AMCOpen{lines=3}{
        \wrongchoice[W]{w}\scoring{0}
        \wrongchoice[P]{p}\scoring{1}
        \correctchoice[C]{c}\scoring{2}
    }
\end{question}
}

\element{cpo-short}{
\begin{question}{ch24-short-Q02}
    As light passes from a vacuum into a material,
        how are the speed, frequency, and wavelength affected?
    \AMCOpen{lines=3}{
        \wrongchoice[W]{w}\scoring{0}
        \wrongchoice[P]{p}\scoring{1}
        \correctchoice[C]{c}\scoring{2}
    }
\end{question}
}

\element{cpo-short}{
\begin{question}{ch24-short-Q03}
    State the relationship between frequency of a light soucr
        and its energy.
    \AMCOpen{lines=3}{
        \wrongchoice[W]{w}\scoring{0}
        \wrongchoice[P]{p}\scoring{1}
        \correctchoice[C]{c}\scoring{2}
    }
\end{question}
}

\element{cpo-short}{
\begin{question}{ch24-short-Q04}
    How are electromagnetic waves created?
    \AMCOpen{lines=3}{
        \wrongchoice[W]{w}\scoring{0}
        \wrongchoice[P]{p}\scoring{1}
        \correctchoice[C]{c}\scoring{2}
    }
\end{question}
}

\element{cpo-short}{
\begin{question}{ch24-short-Q05}
    When the wavelength and frequency for each of the colors
        (lists in the table below) is multiplied, each product
        yields approximately the same answer.
    What is the significance of this ``coincidence''?
    In what units does the answer appear?
    \begin{center}
        \begin{tabulary}{\columnwidth}{RCC}
            Color   &
            Wavelength (\si{\nano\meter})   &
            Frequency (\si{\tera\hertz}) \\
            Red     & 650 & 462 \\
            Orange  & 600 & 500 \\
            Yellow  & 580 & 517 \\
            Green   & 530 & 566 \\
            Blue    & 470 & 638 \\
            Violet  & 400 & 750 \\
        \end{tabulary}
    \end{center}
    \AMCOpen{lines=3}{
        \wrongchoice[W]{w}\scoring{0}
        \wrongchoice[P]{p}\scoring{1}
        \correctchoice[C]{c}\scoring{2}
    }
\end{question}
}

\element{cpo-short}{
\begin{question}{ch24-short-Q06}
    Explain the importance of Thomas Young' experiments
        the produced interference patterns.
    \AMCOpen{lines=3}{
        \wrongchoice[W]{w}\scoring{0}
        \wrongchoice[P]{p}\scoring{1}
        \correctchoice[C]{c}\scoring{2}
    }
\end{question}
}


%% CPO Problem Questions
%%--------------------------------------------------
\element{cpo-problem}{
\begin{question}{ch24-problem-Q01}
    Light travels through the transparent material lucite
        at a speed of \SI{2.0e8}{\meter\per\second}.
    What is the index of refration?
    \AMCOpen{lines=3}{
        \wrongchoice[W]{w}\scoring{0}
        \wrongchoice[P]{p}\scoring{1}
        \correctchoice[C]{c}\scoring{2}
    }
    %% ANS: \num{1.5}
\end{question}
}

\element{cpo-problem}{
\begin{question}{ch24-problem-Q02}
    The wavelength of a certain frequency of green light is \SI{5.3e-7}{\meter}.
    What is the frequency of this green light?
    \AMCOpen{lines=3}{
        \wrongchoice[W]{w}\scoring{0}
        \wrongchoice[P]{p}\scoring{1}
        \correctchoice[C]{c}\scoring{2}
    }
    %% ANS: \SI{5.66e14}{\hertz}
\end{question}
}

\element{cpo-problem}{
\begin{question}{ch24-problem-Q03}
    The light from Samantha's flashlight travels in air at a speed
        of about \SI{3.0e8}{\meter\per\second}.
    The index of refraction for water is \num{1.33}.
    If she shines the flashlight into her family's swimming pool,
        what is the speed of the light in the water?
    \AMCOpen{lines=3}{
        \wrongchoice[W]{w}\scoring{0}
        \wrongchoice[P]{p}\scoring{1}
        \correctchoice[C]{c}\scoring{2}
    }
    %% ANS: \SI{2.26e8}{\meter\per\second}
\end{question}
}


% CPO Essay Questions
%--------------------------------------------------
\element{cpo-essay}{
\begin{question}{ch24-essay-Q01}
    What experimental proof is there to support the theory that
        light is a wave?
    \AMCOpen{lines=3}{
        \wrongchoice[W]{w}\scoring{0}
        \wrongchoice[P]{p}\scoring{1}
        \correctchoice[C]{c}\scoring{2}
    }
    %% ANS: ex. Thomas Young
\end{question}
}

\element{cpo-essay}{
\begin{question}{ch24-essay-Q02}
    Describe the appearance of an interference pattern.
    Explain how an interfence pattern is created.
    \AMCOpen{lines=3}{
        \wrongchoice[W]{w}\scoring{0}
        \wrongchoice[P]{p}\scoring{1}
        \correctchoice[C]{c}\scoring{2}
    }
\end{question}
}

\element{cpo-essay}{
\begin{question}{ch24-essay-Q03}
    Explain how glow-in-the-dark plastic provides evidence to verify the theory
        that photon emission is caused by the ineraction between a single
        electron and a single photon.
    \AMCOpen{lines=3}{
        \wrongchoice[W]{w}\scoring{0}
        \wrongchoice[P]{p}\scoring{1}
        \correctchoice[C]{c}\scoring{2}
    }
\end{question}
}

