%% http://www.bestsamplequestions.com/gre-questions/reading-comprehension/reading-comprehension.html


%% page 1 1


Though cynics like to see the government’s strategy for women in terms of the party’s inner power efforts, it will, on the other hand be impolite to reject that it symbolized a revolutionary effort designed at bringing about sweeping social improvements. In its language a scope of understanding of woman requirements, which is uncommon in government pronouncements? This is due in large part to the participatory procedure that marked its formulation, looking for the active participation right from the start of women’s groups, educational institution and non-government association with grass roots knowledge. The consequence is not just a haughty announcement of principles but a blueprint of a sensible programmed of action. The strategy delineates a sequence of existing measures to deal women a choice making role in the political area and greater power over their economic position. Of especially far reaching contact are the decentralization of control of financial communications to women, notably at the gram panchayat level, and the improvement planned in the Hindu progression Act of 1956 to give women coparceners their rights.

A progressive aspect of the policy is its gratitude that actual modify in the position of women cannot be brought about by the simple ratification of socially progressive legislation. As a result, it focuses on reorienting growth programmer and sensitizing management to address precise situations, as for example, the rising number of family headed by women, which is a result of rural and urban relocation. The proposal to generate an equal prospect police force and give women better control of police station is an acknowledgement of the bias and callousness displayed by the usually all male commandment enforcement authorities in cases of household violence. While the mere enunciation of such a strategy has the useful effect of sensitizing the management as a whole, it does not make the job of its execution any easier. This is because the changes it predicts in the political and financial status of a woman strike at the root of power arrangement in the society and the basis of man woman connection. There is also the danger that reservation of women in civic life, while necessary of their greater visibility, could tumble into tokenism or become a means in the hands of vote seeking politicians. Much will depend on the propagation of the strategy and the ability of the chosen representatives and government organization to reorder their priority.

    According to the passage, which of the following feature has been recognized as, it alone would not bring change in the position of women?
        Coparcenary rights of women
        Judgment making role in political area
        Enactment of socially progressive legislation
        Greater control over financial status
        Creating equal prospect in police force 

    Ans : C
    According to the comprehension, which of the following is a consequence of rural and urban migration?
        Growth programs are not effective
        Legislation is not enforced properly
        Industries do not get adequate man power in rural areas
        Many women voyage to urban areas leaving their family in the rural areas
        None of the above 

    Ans : E
    Which of the following can be inferred from the passage?
        Domestic violence is on the rise
        Women already have coparcenaries rights
        There is a need for stricter legislation
        Most of the government policies are formulated through participatory process
        The policy recommends reservation for women 

    Ans : E
    According to the comprehension which of the following is not correct?
        The policy gives a blueprint for program me of action
        For effective implementation, the government agencies will have to reorder their priorities
        There is no law enforcement bias in cases of domestic violence
        The woman should be given greater control of police stations
        The policy based on the perceptive of the requirements of women 

    Ans : C
    Which of the following is true about the policy?
        In its formulation participatory loom was not followed
        This is a new assertion by the government
        It has made several big announcement
        It is a revolutionary effort
        It is not based on perceptive of women requirements 

    Ans : D 


%% page 2 

A leading Indian manufacturer in a current article one ways to reinforce India’s economy has drained notice to the tribulations of price rises and industrial illness among other things. One of the major reasons for industrial illness in our country has been the truth that the business and manufacturing managers, have not been able to look further than the instantaneous future. They have been too anxious with their effort to report positive results for the recent year, higher income and larger payment to the share holders. The preparation horizon has barely over exceeded five years. Savings have been insufficient for new plants and towards diversification and development, transformation and benefit creation has badly lagged behind.

In business, development is required for endurance; one has to develop if one does not desire to be wiped out. This is mainly right today with liberalization of importation and increasing antagonism. Moreover, growth and higher competence create service and higher service creates better markets both for manufacturing and consumers goods. It was Henry ford who brought home the requirement for the formation of a better and a steadier middle class that is a better number of people who can have enough money more and more of goods and services. Even after forty years of sovereignty our manufacturers have not been able to shack the petty shopkeeper’s state of mind and our highly knowledgeable management has tagged along joyfully and without worry.

    According to the comprehension, development and rising production lead to
        Unequal superfluous of supplies
        Service and thus offer an opening to manufacturing and purchaser products
        Support to sell to other countries of surplus customer goods
        Obligation of constraint on importation
        None of the above 

    Ans : B
    Why did Henry Ford pressurize the requirements for a steadier middle class?
        Middle class people are generally service tilting
        People in that class can have enough money to buy more and more luxurious goods
        Middle class people are most wobbly
        Middle class people do not have shopkeeper state of mind
        None of the above 

    Ans : B
    The planning horizon has barely ever exceeded five years implies
        Planning should take care of all likely ups and downs in the next five-year time
        Planning must not be for a time of less than five years
        Five year period is too short for successful implementation of plans
        The planning procedure is very time consuming
        The planners are not prone to think of upcoming 

    Ans : C
    In order to develop the situation of Indian industries, the entrepreneur should do all of the following apart from
        Giving up the narrow state of mind which very small shopkeepers usually have
        Adopting policies for diversification and transformation
        Cheering antagonism from industrialists with in the country and from overseas
        Resorting to long term planning for industrial development and growth in varied fields
        Determined to make long term profits 

    Ans : E
    Which of the following shortcoming of Indian manufacturer has been pointed by the author of the comprehension?
        They are less worried for expense of payments to shareholders
        They spend irrational high sum on diversification and development
        They are unwilling to preserve the storekeeper state of mind
        They are more worried for instant net growth than for development activities
        None of the above 

    Ans : D 

%% page 3

Since the most prehistoric times India has been not only occasionally attacked by voracious hordes, but also visited by tradesmen and explorers, researchers and tourists. Some of them have printed books. The books of these writers became all the more significant because there were not too many of them, and they have served as prosperous sources of the historians. It is particularly in this background that surveillance provided by the grand Chinese writer Hiuen Tsand became very applicable. Already in the 7th century, Buddhism was an influential enlightening force amongst the sophisticated classes of China. It was universal for Chinese pilgrims to come to India, the native land of the Buddha, to pay their respects to the founder in their religion. Perhaps the most famous of them all was this gengle observer who has studied and travelled extensively in China before entering the Indian subcontinent. Being both scholar and sophisticated, he was not given to easy praise. With in India itself he travelled desserts and climbed mountains, stayed in villages and lived in capitals, practiced in monasteries and studied in universities and spent time in some royal courts as well.

He went to Mathura and Ayodhya, to Prayag and Patliputra, to Gaya and Kamarupa. He premeditated Sanskrit and Pali to research more into Buddhist philosophy and Hindu society. Most significant of all, he wrote down in detail his many practices and impressions.

    Which of the subsequent has been regarded as the real involvement of Hiuen Tsang?
        He pointed out the collision of Hinduism on Buddhism
        He scrupulously recorded his knowledge and feelings
        He prejudiced elites to China to visit India
        He visited and spent time in several places in India
        He loyally wrote about the invaders who assaulted India in the past 

    Ans : B
    Why the writing of prehistoric writers is measured as very significant?
        They are printed by renowned people
        We get an account about the reason of the attackers
        They have studied and travelled comprehensively
        They are amongst the few sources of chronological significance
        It gives quintessence of Buddhists beliefs and Hindu belief 

    Ans : D
    The writing of Hiuen Tsang emerge to be purpose because
        He had visited China and could evaluate it with India
        He was mainly a historian
        Of pressure of Buddhist viewpoint
        He was learned and refined
        None of the above 

    Ans : D
    Why did Hiuen Tsang study Sanskrit and Pali?
        To converse with neighboring people
        To write his autobiography in these languages
        To interpret writing from Chinese into these languages
        To educate this language in China
        None of the above 

    Ans : E
    Why the writings of Hiuen Tsang are regarded as appropriate?
        He had spent a little time in some noble courts
        He was a kind spectator
        He visited India as dealer and tourist
        He had travelled to several Asian countries
        None of the above 

%% page 4

According to a few economists swadeshi does not mean insulating India’s financial system from the world economy. The fundamental thought of swadeshi is to have all the segments which enabled to complete with the best in the world after going through extreme internal rivalry leading to amalgamation, acquisitions and purging. This is how Japan has urbanized its industry and the whole economy. However, under the current world circumstances and the requirement of migrating circumstances of scarcity in the country, the government has to make a decision as to how much of free of charge trade is to be permitted in the different sections of financial system in order to attain the rate of development planned for the financial system through the period of Ninth plan. All over the world, our nation has been found to be divided on crucial question of defense and free trade. A latest study has found that the protectionist in the world outnumber free buyers and showing more increase in their number.

The research has been made for The Economist by the Augus-Reild assembly, a Canadian pollster. It is based on a view poll approved among 12.750 adults spread over 23 vital countries of the world. The main important question asked in the poll was to which of the next two approaches do you consider would be the finest way to progress the economic and service situation in this country:
(a) Defending our local industries by checking imports
(b) Removing imports checking to raise our worldwide trade

Reply received to this question showed that:
(1) Protectionist global outnumber free traders is: 47% to 42%
(2) Percentage of people supporting free of charge trade has reduced from 43% in 1997 to 42% in 1998

In 14 out of the 22 countries, protectionists have outnumbered the free of charge traders and another four countries had revealed a fall in the number of the buyers, which means a swing towards protectionism. The development for a fall in the number of free of charge traders and a increase in the number of protectionists has been called as astonishing in the research because it has revealed a harmful result for the astonishing global efforts of the WTO, The World Bank, the IMF and the most powerful G-7 countries for the propagation and promotion of free trade and globalization in the world. It is interesting to note that America, Australia, UK, Canada and Italy, who are strong champions of free trade in the world, have a large majority of their own people still supporting protection. The study says: A clear majority of Americans 56% to 37% are protectionist even today. And over the past one year the number of free traders in America had declined by 5%. Such decline was much higher in Italy 22%, Canada 14% and UK 15%.

    What according to the author is amazing as per the report of the study?
        Decrease in the number of protectionist
        Increase and decrease in the numbers of protectionist and free traders respectively
        The trend for increase in the number of free traders
        The inconclusive finds of survey
        None of the above 

    Ans : B
    It can be inferred from the last paragraph of the last passage that
        Most of the people in the countries who are champions of free trade are in favor of free trade
        There is a swing of public opinion in favor of free trade
        Results of protectionism are not positive
        Advocates of free trade are gradually outnumbering protectionists
        None of the above 

    Ans : D
    The author suggest the government to
        Give a preferential treatment to local industries
        Judiciously decide the extents of protection and free trade
        Mitigate conditions of poverty in the country
        Allow free trade without restriction
        None of the above 

    Ans : B
    The study undertaken by Augus Reild group was with a view to find out
        (a) How people know different countries differ an economic issues (b) The implication of restricting imports (c) Various measures to improve the economic situation (d) The result of increase in international trade (e) Viewpoint of people on free trade versus protectionism Answer (e)
        The implication of restricting imports
        Various measures to improve the economic situation
        The result of increase in international trade
        Viewpoint of people on free trade versus protectionism 

    Ans : E
    The credit of Japan’s industrial and economic development goes to the strategy of
        Merging its industries with those of foreign players
        Isolating its own economy from the world economy
        Elimination of loss making industries and acquisition of profit making ones
        Effectively facing internal and external economic competition
        None of the above 

    Ans : D 

%% page 56

There is a quite common sentiment that the use of nuclear arms is obviously different to morality and that it’s making probably so, does not go far sufficient. These activities are not only conflicting to ethics but also to law and if the lawful objection can be added to the ethical, the argument beside the use and the produce of these weapons will significantly be unbreakable. Now the time is ripe to estimate the duty of scientist who intentionally uses their proficiency for the creation of such weapons which has deterious result on mankind. To this should be added to the fact that more than 50% of the trained scientific manpower on the earth is now busy in the armaments business. Now it is suitable that manufacture of arms of death in a world of scarcity is a question that must lay a hand on the scientific conscience.

A gathering of biologists on the Long term wide-reaching Biological cost of Nuclear War added scary dimensions to those biological affects consequential from weather changes may at least be as severe as the direct ones. Sub cold temperature , low light levels and high dose of ionizing and ultra violet rays expanding for many months after a huge scale nuclear nation , at least in the northern hemisphere. Efficiency in usual and agricultural eco systems could be ruthlessly constrained for a year or more. Post war survivors would face malnourishment as well as chilly condition in the dark and be bare to near lethal dose of rays. If, as now seems possible, the southern hemisphere were exaggerated also, worldwide disruption of the bio sphere could result. In any event there could be stern consequences, even in the areas not exaggerated directly, because of the inter trust of the world financial system. In either case the extermination of a large fraction of the earth’s animals, plants and microorganisms seems probable. The inhabitant’s size of Hemo sapiens possibly could be condensed to pre historic levels or below and annihilation of the human genus itself cannot be debarred.

    The author of the passage seems to be of the view that
        Utilization of valuable knowledge for manufacture of lethal weapons is inhuman
        Utilization of scientific skills in manufacture of weapons is appropriate
        Manufacture of weapons of death would help eradication of poverty
        Spending money on manufacture of weapons may be justified subject to availability of funds
        The evaluation of the scientist expertise show their incompetence 

    Ans : A
    The author’s most important objective of writing the above passage seems to------
        Explain scientifically the climate changes resulting from use of nuclear weapons
        Highlight the use of nuclear weapons as an effective population control measures
        Duly highlight the supremacy of the nations which possess nuclear weapons
        Illustrate the devastating effects of use of nuclear weapons on mankind
        Summarize the long biological effects of use of nuclear weapons 

    Ans : E
    Which of the following is one of the consequences of nuclear war?
        Southern hemisphere would remain quite safe in the post war period
        Post war survivors being very few will have abundant food
        Fertility of land will last only for a year or so
        Lights would be cooler and more comfortable
        None of the above 

    Ans : C
    According to the passage the argument against the use and manufacture of nuclear weapons
        Becomes stronger if legal and moral consideration are combined
        Does not stand the test of legality
        Is acceptable only on moral grounds
        Possesses legal strength although it does not have moral standing
        None of the above 

    Ans : A
    It appears from the passage that the use of nuclear weapons is considered against morality by
        Most of the scientist who devote their valuable skills to manufactures nuclear weapons (
        Almost all the nations who cannot afford to manufacture and sell weapons
        A minority group of scientist who have the necessary skills and competence
        Only the superpowers who can afford the manufacture and sell weapons
        Only such of those nation who cannot afford to manufacture and sell weapons 

    Ans : B 

%% page 6

It is to growth in the human sciences that we should look to open the tribulations which have resulted from facts of the material world hastily and apparently obtained by populations unaware of the changes in them that the new facts has made very important. The road to a more contented world than any known in the history lies open before us if atavistic unhelpful passion can be kept in restraint while the essential adaptation are made. Fears are predictable in our time, but hopes are similarly balanced and far more probable to bear fine fruit. We should study to believe rather less of the hazard to be avoided than of the superior that will lie inside our grasp if we can consider in it and let it control our feelings. Science, anything obnoxious cost it may have by the way, is in its very temperament a liberator, a liberator of repression to physical personality and in time to come, a liberator from the burden of unhelpful passion. We are on the doorsill of thorough tragedy or unprecedentedly magnificent attainment. No earlier age has been burdened with troubles so important, and it is to knowledge that we should look to for a content future.



    If man’s bestial yearning is controlled
        The present will be brighter than the future
        The future will be tolerable
        The present will become tolerable
        The future will be brighter than the present
        None of the above 

    Ans : D
    Should human sciences be developed because they will?
        Eliminate the destruction caused by a superficial knowledge of the physical world
        Make us conscious of the changing world
        Provide more knowledge of the physical world
        Make us conscious of the changes in ourselves
        None of the above 

    Ans : A
    What does science liberate us from? It liberates us from
        Idealistic hopes of a glorious future
        Fears and destructive passion
        Bondage to physical nature and from passions
        Slavery to physical nature and from passions
        None of the above 

    Ans : D
    Fears and hopes according to the author
        Are irrational
        Can bear fruit.
        Are closely linked with the life of modern man
        Can yield good results
        None of the above 

    Ans : C
    To carve out a bright future man should
        Analyze dangers that lie ahead
        Try to avoid dangers
        Cultivate to positive outlook
        Overcome fears and dangers
        None of the above 

    Ans : C 

%% page 7

The work of the heart can by no means be intervallic. The heart’s job is to keep oxygen rich blood flowing throughout the body. All the body cell needs a regular supply of oxygen, particularly those in the brain. The brain cells exist only four to six minutes after their oxygen is cut off and death comes into the entire body. The heart is a specialized muscle that serves as a pump. This pump is alienated into four chambers linked by tiny door known valves. The chambers job to keep the blood flowing round the body in a loop. At the end of every circuit, veins transmit the blood to the right atrium, the first of the four chambers, its oxygen has been used up and it is on its way back to the lung to pick up a clean supply and to give up the carbon dioxide it has gathered. From the right atrium the blood run through the tricuspid valve into the second chamber, this is known as the right ventricle. The right ventricle pacts when it is filled pushing the blood in the course of the pulmonary artery, which leads to the lungs. In the lungs the blood gives up its carbon dioxide and picks up clean oxygen. Then it moves to the third chamber, the left atrium. At this time chamber is full it forces the blood all the way through the mitral valve to the left ventricles. At this time it is pushed into a big blood vessel known aorta and sent round the body by way of arteries

Heart sickness cans consequence from injure to the heart muscle, the valves or the pacemaker. If the muscle is injured, the heart is not capable to pump suitably. If the valves are injured, blood cannot flow usually and simply from one chamber to one more chamber, and if the pacemaker is faulty, the reduction of the chambers will become ungainly. Until the twentieth century, few health centers challenged to pouch the heart. In 1954, all this tainted. After twenty years of labor, Dr.John Gibson of U.S.A had invented a machine that could take over momentarily from the heart and lungs. Blood might be in retreat through the machine that could take over provisionally from your heart and lungs. Blood could be routed throughout the machine, bypassing the heart so that doctors could work within it and see what they were doing. The age of open-heart operation had begun. In the working theatre, it gives doctors the chance to mend or restore a faulty heart. Many patients have had artificial valves put in in their hearts, when their own liability. Many natives are being kept active with small battery operated pacemaker; none of these conservation could have been completed with no the heart lung appliance. But expensive as it is to the doctors, the heart lung machine has definite restrictions. It can be used merely for a few hours at a time for the reason that it’s pumping slowly damages your blood cells.

    Who had developed a machine that could take over temporarily from the heart and the lungs?
        Dr. Robert willson
        Dr. John Gibbson
        Dr. Steven
        None of the above 

    Ans : B
    What should be the ideal title for the passage?
        Working for the heart
        Heart is life
        Heat
        None of the above 

    Ans : A
    The heart is a specialized muscle which serves as a -- -- --?
        Blood vessel
        Pump
        Chambers
        None of the above 

    Ans : B
    The pump is divided into -- -- -- chambers
        Five
        Three
        Four
        None of the above

    Ans : C
    Which is the main organ of our body?
        Leg
        Hand
        Heart
        None of the above 

    Ans : C 

%% page 8

The worldwide notice in power issues triggered off by the jagged increases in oil cost in1973 and 1979 has since waned. With the dramatic fall in oil prices in the late 1980, there is a euphoric emotion the world over that power is no longer a difficulty. Dynamic policy institute in the 1970 to include the development of energy command have been terminating in many countries. In common, the approach is one of trade as natural. India is no omission. There is no proof of approval at the rule level of the fact that for India the power future is probable to be bleak, and that ensuring sufficient energy accessibility to maintain even an unassuming rate of financial development will be a main test.

Energy consumption is not end in itself. Its importance lies in the fact that it is an essential overhead for economic development. Energy plays an overhead for economic development. Energy plays a dual role. It is an input towards the productive sectors of the economy, namely agricultural and industry and the supporting infrastructure of transport. It is also a consumer good, energy consumed in house hold has a direct impact on the quality of life. It is not surprising therefore those studies of energy consumption patterns across countries and over periods of time clearly establish a correlation between per capita energy consumption and per capita income. Even with in a country, the affluent sections of society consume larger amounts of energy per capita than the poorer sections. The extents of access to energy at affordable prices have distributive implications. The equity aspect must therefore figure as an element of energy policy.

The fundamental features of India’s power circumstances are well recognized and do not need amplification. Per capita expenditure of power is low, about one fourth of the world standard and about one twenty fifth that of the U.S.A and imitate the gathering scarcity still ubiquitous in the country. Long-established fuels like fuel wood, animal dung and crop remains account, even now for as much as 35% to 40% of the total energy consumption in the country.

    Energy consumption has direct impact on quality of life means
        More energy consumption helps people raise their social status
        Rich people can afford to pay more than the poor can for comparable consumption
        Quality of life can be improved by more energy consumption
        Poor people have to consume less energy due to the high cost involved
        None of the above 

    Ans : C
    The energy policy makers, according to the passage, should take due cognizance of the fact that
        The energy requirement of the rich in India does not differ from that of the poor
        India’s energy situation is sound and there will be no shortage in the next future
        India’s energy requirement is far less than that of the Americans
        Access to energy and availability therefore are in proportion to financial status
        None of the above 

    Ans : D
    Author of the passage is of the view that the policy makers in India
        Are showing challenge of energy shortage probable challenge of energy shortage
        Are duly aware of the probably energy crisis in near future
        Are unreasonably alarmed by the challenge posed by energy shortage
        Have not taken due cognizance of the threat posed by energy shortage
        None of the above 

    Ans : B
    According to the passage the low per capita energy consumption in India is an indicator of
        (a) Lack of technological information to have an easy access to energy resource (b) Awareness of Indian masses of the energy situation in the country (c) Inadequate energy generation and supply in the country (d) Measures adopted by people for fuel economy (e) None of the above Answer (c)
        Awareness of Indian masses of the energy situation in the country
        Inadequate energy generation and supply in the country
        Measures adopted by people for fuel economy
        None of the above 

    Ans : C
    Energy plays a duel role in which of the following pair of aspects.
        Industrial and household consumption
        Political, economic and social development
        Agricultural, Industrial production, transport and consumers goods
        Agriculture and Industrial production
        None of the above 

    Ans : C 

%% page 9

Everyone conforms to infancy, infancy conforms to nobody, so that one babe commonly makes four or five out of the adults who prattle and play to it. So God has armed youth and puberty and manhood no less with its own piquancy and charm, and made it enviable and gracious and its claims not to be put by, if it will stand by itself. Do not think the youth has no force, because he cannot speak to you and me. Hark! In the next room his voice is sufficiently clear and emphatic. It seems he knows how to speak to his contemporaries. Bashful or bold, then, he will know how to make us seniors very unnecessary.

The healthy attitude of human nature can be seen in the nonchalance of boys who are sure of a dinner, and would disdain as much as a lord to do or say aught to conciliate one. A boy is in the parlor what the pit is in the playhouse; independent, irresponsible, looking out from his corner on such people and facts as pass by, he tries and sentences them on their merits, in the swift, summary way of boys, as good, bad, interesting, silly, eloquent, troublesome. He never cumbers himself regarding consequences, about interests and he gives an independent, genuine verdict. You should court him: he will not court you. But the man is, as it were, clapped into jail by his consciousness. As soon as he has once acted or spoken with eclat, he is a committed person, watched by the sympathy or the hatred of hundreds, whose affections must now enter into his account. There is no Lethe for this. Ah, that he could pass again into his neutrality.

These are the voices, which we hear in solitude, but they grow faint and inaudible as we enter into the world. Everywhere society is conspiring against the manhood of every one of its members. Society is joint - stock company, in which members agree, for the better securing of his bread to each shareholder, to surrender the liberty and culture of the eater. The virtue in most request is conformity. It is averse to self-reliance. What it loves is names and customs and not realities and creators.

Whosoever is a man has to be a nonconformist. He who would gather immortal palms must not be hindered by the name of goodness, but must explore if it be goodness. Nothing is at last sacred but the integrity of your own mind.

No law can be sacred to me but that of my nature. Good and bad are but names very readily transferable to that to this; the only right is what is after my constitution, the only right is what is after me constitution, the only wrong what is against it. A man is to carry himself in the presence of all opposition as if every thing were titular and ephemeral but he. I am ashamed to think how easily we capitulate to badges and names, to large societies and dead institutions. Every decent and well-spoken individual affects and sways me more than is right. I ought to go upright and vital, and speak the rude truth in all ways.

I shun father and mother and wife and brother, when my genius calls me. I would write on the lintels of the doorpost, whim. I hope it is somewhat better than whim at last, but we cannot spend the day in explanation. Except me not to show cause why I seek or why I exclude company. Then, again, do not tell me, as a good man did not to-day, of my obligation to put all poor men in good situations. Are they my poor? I tell thee, thou foolish philanthropist, that I grudge the dollar, the time, the cent, I give to such men as do not belong to me and to whom I do not belong. There is a class of person to whom by all spiritual affinity I am bought and sold; for them I will go to prison, if need be; but your miscellaneous popular charities; the education at collage of fools; the building of meeting - house to the vain end to which many now stand; alms to sots; and the thousandfold Relief Societies; - though I confess with shame I sometimes succumb and give the dollar, it is a wicked dollar which by and by I shall have the manhood to withhold.

If you refuse to conform, you can experience the displeasure of the world. Hence, a man should know how to estimate a sour face. The by - standers look askance on him in the public street or in the friend's parlor. In case this aversion originates from contempt and resistance similar to his own, it might result in a sad countenance; but the sour faces of the multitude, like their sweet faces, have no deep cause, but are caused by reasons as diverse as the direction of the wind and what he reads in the newspapers. Yet is the discontent of the multitude more formidable than that of the senate and the collage.

Another factor, which frightens us from self - trust in our consistency; a reverence for our past act or word, because the eyes of others have no other data for computing our orbit than our past acts, and we are loath to disappoint them.

But why should you keep your head over your shoulder? Why drag about this corpse of your memory, lest you contradict somewhat you have stated in this or that public place? Suppose you should contradict yourself; what then?

This is a rather silly consistency in our minds, which is adored by little statesmen and philosophers and divines. Uniformly a great soul has almost nothing to do, he could just occupy himself with his shadow on the wall. Speak what you think now in hard words; and to-morrow speak what tomorrow thinks in hard words again, though it contradict everything you said to-day. - ''Ah, so you shall be sure to be misunderstood.'' - Is it so bad, then, to be misunderstood? Pythagoras was misunderstood, and Socrates, and Jesus, and Luther, and Copernicus, and Galileo, and Newton, and every pure and wise spirit that ever took flesh. What can be considered to be truly great is to be misunderstood.

    Which of the following statements would best describe the main theme of the above passage?
        "A foolish consistency is the hobgoblin of little mind."
        "Eternal youth means eternal independence."
        "Whoso would be a man must be a nonconformist."
        "Colleges are designed to educate fools."
        "Infancy conforms to nobody." 

    Ans : C
    When is the period during which we are most nonconformist?
        infancy
        puberty
        youth
        manhood
        old age 

    Ans : A
    In his statement ''What can be considered to be truly great is to be misunderstood'' the author means:
        One should refrain from saying, what one exactly means
        Being misunderstood, equals being great
        All great man have always been misunderstood
        Even though a person might be considered inconsistent, he shouldn't hesitate to change his mind if he feels the need to.
        It is seldom, that nice people succeed 

    Ans : D
    As inferred from the passage, the refusal of young people to cater to accept public opinion is:
        A feature of the rebelliousness of youth
        A healthy attitude of human nature
        A manifestation of deep - seated immaturity
        Simply bad manners
        Part of growing up 

    Ans : B
    "Society is a joint-stock company etc." is one way which the author shows
        The anti-culture attitude of the public
        Society is highly organized and structured
        The self-rejection of society
        The lack of room for solitude in our world
        The public's interest in the stock market 

    Ans : C
    " I would write on the lintels of the doorpost, whim." What does the author mean by this statement:
        That one should renounce his immediate family
        That signposts have an important educational function in our society
        That an impulsive action may have a subsequent rational explanation
        That one must never be held responsible for what one says and does
        That everyone should do foolish things occasionally 

    Ans : C
    Which of the following statements best summarizes the spirit and sense of the above passage?
        "Nothing is at last sacred but the integrity of your own mind."
        "With consistency, a great soul; has simply nothing to do."
        "Do not think the youth has no force, because cannot speak to you and me."
        "The virtue in most request is conformity."
        "A man must know how to estimate a sour force." 

    Ans : A 

%% page 10

The budget for 1993-1994 has set the stage for a greater inflow of resources into the farm sector. A part from errant monsoons, one reason why this sector has remained sluggish in recent years is the trend of falling investments in agriculture. At a time when shortage of cultivable land means that growth has to come mainly through increases in productivity, the pace of investment is crucial to raising farm production. During the eighties, while public investment has fallen in real terms, private investment has remained stagnant. Since agriculture is a state subject, the fall in public investment reflects the dwindling ability of state government to find more resources. Therefore while central budget cannot do much to stimulate public investment in the farm sector, it can surely create condition for increased investment by farmers themselves. And this is precisely what the latest budget seeks to do. Since then brought year of 1987 to 88, the tardy pace of credit flow to agriculture has affected investment. By promising a 20% increase in institutional credit to farmers during the coming year, the budget expects that term loans for minor irrigation will help sink 3.70 lakh wells and install more as the cuts in customs duties on farm machinery will now make it cheaper.

In fact, the reductions in customs tariffs have the potential of generating more investible resources for farmers. This is because high rates of tariff protection hitherto accorded to Indian industry have allowed the latter to sell industrial goods to farmers at much higher prices than those at which they are sold internationally. Indirectly, high customs duties have thus imposed a tax on farmers and transferred resources away from rural areas to the industrial sectors. The latest budget takes the correct initiative to arrest this trend. It is true that the government policy of raising administered prices to reduce subsidies will raise the prices of inputs like power, fertilizer and diesel use in farm operation. However apart from the usually simultaneous and compensatory increase in procurement prices, farmers stand to gain the most through in increase in public investment made possibly by reduction in subsides. The central budget has shown that subsidy reduction mean more plan investment. If the state government can follow this example, than a package comprising cuts in customs tariffs, increases in public investments and higher credit flows to formers, holds the potential or revalorizing Indian agriculture.

    Which of the following statements is true in the context of the passage?
        Since 1987-88 government as provided substantial credit to agricultural sector
        There is a steady increase in cultivable land over the years
        During the eighties public investment had increased in real terms
        Monsoon has been regular and timely in the recent years
        The budget for 1993-94 has been favorable for Indian agriculture 

    Ans : E
    According to the passage what will be the effect of governmentâ€™s policy of raising administered prices to reduce subsidies
        It will raise the prices of important inputs used in farm sectors
        It will reduce the procurement prices of farm products
        It will divert flow of resources from industrial sector to farm sector
        It will automatically result in reduction of custom tariffs
        None of the above 

    Ans : A
    Reduction in customs tariffs will result in generation of more resources for farmers because
        More and more term loan will be available to them
        State government will come forward to provide them with credit facilities
        They will get higher prices for their products
        They will get industrial goods at much lower prices
        They will divert resources from farm sectors to industrial sector 

    Ans : D
    Which of the following statements is not true in the context of the passage?
        High custom duty resulted in transforming resources away from rural areas to industrial sector
        So far Indian industry had low rate of tariff protection
        Central budget can create favorable conditions for increased in vestments
        Reduction in customs tariffs can help generate more resources
        During eighties private investments had remained stagnant 

    Ans : B
    Which of the following is most nearly the same in meaning as the word ERRANT as used in the
        Unblemished
        Circuitous
        Erroneous
        Deviating
        Deviating 

    Ans : D 

%% page 11

Read the following comprehension and answer the following question.

    One of the most fascinating stories of the Russian revolt concerns the uniqueness of Anastasia, the smallest daughter of Czar Nicholas II. Throughout his sovereignty over Russia, the Czar had intended to repeal many of the inconsiderate laws recognized by earlier czars. Some staff and peasants, though, screamed for more quick social transformation. In 1918 a cluster of these groups, popularly known as Bolsheviks, conquer the regime. On July 18 or 19, they killed the Czar and what was believed to be his complete family.

    Even though spectators vouched that all the associates of the Czar's family had been executed, there were reports signifying that Anastasia had continue to exist. After many years, a number of women declared to be magnificent Duchess Anastasia. Possibly the top known petitioner was Anastasia Tschaikovsky, who was also recognized as Anna Anderson.

    In 1920, eighteen months later the Czar's implementation, this frightened young woman and was saved from sinking in a Berlin river. She spends two years in a hospital, where she attempted to reclaim her health and shattered mind. The doctors and nurses thought that she resembled Anastasia and questioned her about her conditions. She denies any association with the Czar's family.

    Eight years later on, although, she declares that she was Anastasia. She said that she had been saved by two Russian armed forces following the Czar and the rest of her relatives had been murdered. Two brothers known as Tschaikovsky had accepted her into Romania. She had wedded one of his brothers, who had taken her to Berlin and made her left there, bankrupt and devoid of a job. Incapable to raise the help of her mother's relatives in Germany, she had tried to kill herself. For the period of the coming few years, scores of the Czar's family, ex-servants, and associates had been discussed with her. Lot of these people thought that her appearance and gesture were redolent of the Anastasia that they had identified. Her grandmother and other relations deprived of that she was the real Anastasia, though. Tired of being blamed of hoax, Anastasia went back to the United States in the year 1928 and took the name of Anna Anderson. She still desired to show that she was Anastasia, although, and came back to Germany in the year 1933 to take suit beside her mother's relatives. There she proclaimed to the court, declaring that she was really Anastasia and ought to have her legacy.

    In 1957, the court determined that it could neither verify nor contradict Anastasia's individuality. Even though we will most likely never know whether this lady was the Grand Duchess Anastasia, her hunt to create her individuality has been the topic of several books, theaters, and cinema

        Some Russian peasants and workers------for social reform.
            begged
            hoped
            longed
            thought much
            cried out 

        Ans : A
        Witnesses------ that all members of the Czar's family had been executed.
            hoped
            thought
            gave assurance
            convinced some
            answer not stated 

        Ans : B
        Tschaikovsky------any connection with the Czar's family.
            stopped
            denied
            justified
            noted
            answer not stated 

        Ans : B
        She was unable to------the aid of her relative.
            speak about
            know
            identify
            locate
            call upon 

        Ans : D
        In court she------ maintaining that she was Anastasia and deserved her inheritance.
            testified
            finally appeared
            gave evidence
            spoke forcedly
            answer not stated 

        Ans : A 

%% page 12



Read the following comprehension and answer the following question.

    The train was on correct time. Mrs Tickoo picked up her baggage and got into a first class compartment. There was a lady with a kid in the compartment. Mrs. Tickoo put her luggages where beneath the seat and she sat close to the window. Just then a boy and a girl hurried up. The girl cried saying “We truly missed telling send-off to you!” The boy said “Our car crashed down fifty yards from the local station and we ran all the way. Where is your mom? Asked Mrs. Tickoo , “She can’t run like we do”, said the boy. At that minute, the guard blows his whistle and wields his green flag. “Thanks a lot for seeing me off”, said Mrs. Tickoo, “but why did you run all the way. Say adieu to your mother for me!” Bye! cried the kids, as the train ran out of the station.



        From the comprehension, we assembled that the children
            Detested Mrs. Tickoo a bat
            Were affectionate towards Mrs. Tckoo
            Were joyful that Mrs. Tickoo was parting
            Did not care much for Mrs. Tickoo (e) None of the above

        Ans : B
        The kids had come to the station
            To give a present to Mrs. Tickoo
            To meet up Mrs. Tickoo
            To collect Mrs. Tickoo
            To say send-off to Mrs. Tickoo 

        Ans : D
        The kids mother were deferred because
            Their car had gradually developed some problem
            They had to walk all the way to the station
            They had started behind schedule from home
            The train had come late
            None of the above 

        Ans : A
        The train runs out of the station- means
            The train formed stream but did not go
            The train formed a lot of stream
            The train came at the station
            The train gradually moved out of the station
            None of the above 

        Ans : B
        The kids were late because
            They had started moving late from home
            They have walk all their way to the station
            Their car had developed some problem
            The train had came late
            None of the above 

        Ans : C 

%% page 13



Read the following comprehension and answer the following question.

    Amnesty global charge that ten thousands of political prisoners, which consist of prisoners of ethics, are sufferers in the Indian jails and those captive are usually agonized in this country has to be seen in a much huge context than the association yearly report cares to do. In its on the whole reviews of 151 countries, Amnesty has charged 112 torturing captives, 63 for dock prisoners of ethics, 61 for resorting to political murder and 53 for captured people without a examination. Of these it seems that partly cover categories, India seems to have been disqualified from the list of the 61 which assume following killings. The description has on the other hand pointed out that achievement of people in India pass away of agony in police and armed forces custody and that many also just vanish. Obviously, only a thin line divides the 61 charges with the political killings from the rest. Before coming to such termination, on the other hand it may also be essential to their political systems. Torment by the refuge forces and murdering at the behest of the administration makes no disparity to the victim’s whether they are in a self-governing country or authoritarian one. It is also nobody’s case that a self-ruled country is less responsible than totalitarianism in the event of human rights abuse. But the point that still requires to be made perhaps is that anguish or vanishing symbolizes a breakdown of the system in a social equality in distinction to being an essential part of state rules in a country lined by a dictator who is responsible to no one.

    India may be culpable of keeping ten thousand at the back bars and of the other human being rights violence mentioned by Amnesty, but it yet remains a qualitatively special place from an authoritarian country. It is in this admiration that Amnesty has been less than reasonable. It has selected to pay no attention to the difference between the superior, the bad and the repulsive. The honesty of Indian civilization will be obvious to anyone who wishes to spend half an hour in one of its muddled market places or visits the commandment courts or watches a political meeting or reads a paper or strikes up a protection with any person on the roads.

    There is no logic of fear in India, as in totalitarianism. There is also a capacity for securing liberation from the heavy handed behaviors of the establishment, even if the human rights charge has not yet lived up to the opportunity. Unless such points are known, Amnesty evaluation will seem to be a dry performance of statistics which may brand India merely because of its bigger population. Thankfully, Amnesty these days at least notes that the revolutionary also treat in human rights desecration and that India has to cope with a number of insurgencies fermented by a country where the armed does not always seem to be under the power of the chosen administration. True there is much that is incorrect in India’s jail system and with the way the terrorist challenge is sometimes met, but the pressure must be on activating the self correcting device with in a democratic organization and not just on painting a bleak, even partial picture.

        Which of the following is not true in the context of the passage?
            The report notes that the terrorist also violate human rights
            There is over lapping of cases in the categories of human right abuses
            Amnesty International appraised all the democratic countries
            India was one of the countries appraised by amnesty international
            India is guilty of some human rights abuses 

        Ans : C
        Which of the following is true according to the passage?
            India is not at all guilty of human rights violation
            The human rights commission has done commendable services
            There is a need to improve India’s prison system
            There is a need to check political killings in India
            None of the above 

        Ans : C
        In the report Indian has been excluded from which of the following categories of human rights violation?
            Harboring prisoner of conscience
            Political killings
            Detaining without trial
            Torturing prisoners
            None of the above 

        Ans : B
        Which of the following seems to be the main purpose of writing this passage?
            To condemn political killings
            To highlight the role of Amnesty international
            To highlight the suffering of prisoners
            To further the cause of human rights
            None of the above 

        Ans : C
        Which of the following human rights violation is most prevalent among the countries?
            Harboring prisoners of conscience
            Torturing prisoners
            Killing the political motives
            Detaining without trial
            None of the above 

        Ans : B 

%% page 14



Read the following comprehension and answer the following question.

    Nehru was a many sided character. He used to take pleasure in reading and writing books as much as he took pleasure in struggle political and community ills or resisting dictatorship. In him, the scientist and the humanist were held in wonderful balance. While he kept looking at extraordinary troubles from a logical point of view, he by no means forgets that we must endorse the total man. As a scientist, he declined to believe in a kind power interested in men’s matter, but as a self-proclaimed non-believer, he loved affirming his faith in life and the beauty of nature. Children he respected. Unlike Wordsworth, he did not see those sprawling smoke of beauty from their current sojourn in paradise. He saw them as bloom of pledge and rejuvenation the only optimism of mankind.



        Nehru thought that children
            Held no hope for mankind
            Were trailing clouds of glory
            Were like flowers to be loved and admired
            Held promise for a better future
            None of the above 

        Ans : D
        A many side personality means
            A capable person
            A complex personality
            A person having varied interests
            A secretive person
            None of the above 

        Ans : C
        In this passage, a benevolent power interested in men’s affair means
            Were like flowers to be loved and admire
            Were trailing clouds of glory
            Held no hope for mankind
            Held promise for a better future
            None of the above 

        Ans : B
        Nehru enjoyed
            Resisting tyranny
            Reading and writing books
            Fighting political and social evils
            Doing all the above and much more
            None of the above 

        Ans : D
        Which of the following statements reflects Nehru’s point of view?
            (a) There is no common ground between science and humanism (b) Humanism is more important than science (c) Science and humanism are equally important (d) Science is supreme and humanities is subordinate to it (e) None of the above Answer (c)
            Humanism is more important than science
            Science and humanism are equally important
            Science is supreme and humanities is subordinate to it
            None of the above 

        Ans : C 

%% page 15



Read the following comprehension and answer the following question.

    The villager has usually been very conventional in his thoughts and approach. He is unenthusiastic to modify his customary way of belief and doing things. His approach in many compliments is homemade is most excellent. For example more farm animal’s farmers in villages favor to nourish their cows and buffaloes with a habitat mix concession of home oil cakes like pulses, mustard or cottonseeds, jiggery, salt etc. It takes a lot of time, which is hard to believe, every day trial and research to persuade the countryside cattle farmer that mix feeds, systematically formulated, develop the production of milk, without any incremental price. The age old principles and approach towards social group, belief, women, time and funds take time to alter. The villager has conventionally been a supporter in the values of karma or destiny. He has found it more suitable to charge his financial hardship, underprivileged living condition and straitened community position on bhagya (Karma or Destiny). The safety that the villagers find in the position quo, act as a deterrent to alter and test in the short run. Many of this old-fashioned approach, price system and out looks are altering, due to advance level of alertness and teaching. On the other hand the rate of alter is lethargic. Attitudes that have fossilized over the centuries, do take time to modify.



        Why does a villager feel secure in maintaining status quo?
            Because of the imagined risk involved in trying a new approach
            Because whatever is known should be the best
            Because too many people go about advising him
            Because change is seldom for the better
            None of the above 

        Ans : B
        When will you call a person conservative in his attitude and approach?
            When he solves his problem through tried out methods
            When he sticks to old ways of thinking and doing
            When he imputes motives to change agents
            When he would like to try out every new idea before accepting it
            None of the above 

        Ans : B
        What is the best method to convince? The average Indian villager about supervisory of the new cattle feed?
            Field demonstration
            Home visits
            Discussion
            Distribution of related literature
            None of the above 

        Ans : E
        Which one of the following is not the usual reason offered by an average Indian villager for his poverty?
            It is because of his resistance to new ideas
            It is God will
            It is his destiny
            It is a result of some of his bad deeds committed in this or the previous birth
            None of the above 

        Ans : D
        What does the phrase “home-made is best” imply?
            (a) Change for the sake of change is no good
            The best should not be discarded
            People should go in for the swadeshi because it is home made
            Whatever is being practiced is better than what is new
            None of the above 

        Ans : D 

%% page 16

Read the following comprehension and answer the following question.

    Galileo Galilee was born in the year 1564 in Europe wracked by enriching havoc and spiritual disagreement. The father and popes of the Roman extensive Church, influential in their roles as both spiritual and worldly leaders, had established defenseless to the experienced and immoral spirit of the age, and their private dissipation brought the status of the papacy to momentous lows. In 1517, Martin Luther, an earlier priest, shows aggression Catholicism for having become too grown-up and politically crooked and for incomprehensible the basics of Christianity with pagan essentials. His improvement zeal, which requested to a concept of an unusual, “cleaned” Christianity, set in motion the Protestant restoration and divides European Christianity in two sections. In answer, Roman Catholicism strengthens itself for conflict and begins with the Counter improvement, which highlighted convention and loyalty to the right church. The Counter improvement reinvigorated the church and, to some point, eliminates its immoderation. But the Counter restoration also give to the turn down of the Italian rebirth, a recovery of arts and letters that required to get well and revise the traditional talent and beliefs of prehistoric Greece and Rome.

    The priest and popes had once been big clientele of regeneration skill and sciences but the Counter restoration put an ending to the church’s liberal leniency in this region. In addition, the church’s latest stress on spiritual belief would soon conflict with the up-and-coming systematic rebellion. Galileo, with his learning of astronomy, establishes himself at the middle of this conflict. Conventional astronomers of Galileo’s era, working with no telescopes, attributed without digression to the prehistoric speculation of self-absorption. This assumption of astronomy detained that the earth lay at the middle of the planetary system, scoped by equally the sun and the further planets. Certainly, to the informal spectator, it seemed common intellect that as the sun “rise” in the daybreak and “set” at nighttime, it should have circled in the region of the earth. Prehistoric establishment like the Roman and Aristotle astronomer Ptolemy had won this point of view, and the idea also agreed with the extensive Church’s sight of the world, which located mankind, God’s major formation, at the middle of the universe. Supported by common intellect, the prehistoric logician, and the church, the geocentric replica of the world seemed protected in its influence. The Ptolemaic assumption, on the other hand, was not impermeable to show aggression.

    In the 16th century, astronomers stressed to create new explanation fit Ptolemy’s geocentric replica of the world. More and more compound arithmetical systems were required to settle these latest clarification with Ptolemy’s structure of joining path. Nicholas Copernicus, a good astronomer, explicitly questioned the Ptolemaic scheme and anticipated a heliocentric scheme in which the planets which consists of Earth tracked the sun which is also known as Helios. This precisely pleasing way of placing the planetary system did not draw many followers at first, since the obtainable data did not yet hold up an extensive desertion of Ptolemy’s scheme. By the end of the 16th century, on the other hand, astronomers like Johannes Kepler (1571–1630) had also started to hold Copernicus’s assumption. In the end, Galileo’s telescope strikes a deadly drive to the Ptolemaic scheme. But, in a common sense, the telescope was also almost deadly to Galileo himself. The extensive Church, to a great extent trying to grasp the Protestant heresy at inlet, could not recognize a systematic beating on its own theory of the world. The stress of the age set in suggestion a momentous argument between belief and science, one which would conclude in 1633 when the church put Galileo on test, forced him to take back his stated and in print scientific viewpoint, and put him below enduring house capture.

        During the Renaissance, the extensive Church was
            saw little clash between its own objective and those of the arts and sciences
            focused on holiness as conflicting to worldly matters
            supported Martin Luther’s views on religion and the church
            had limited contact with the spiritual affairs of the commoners
            promoted the arts as a way to limit the public influence of scientists 

        Ans : A
        Which of the following best states the major thought of the comprehension?
            Science always clash with faith
            Science is defenseless to outer social forces
            Preferably, scientific assumption should strengthen religious policy
            Science operates in a vacuum
            A higher machine is the only way to fine scientific theories 

        Ans : B
        Which of the subsequent was not a cause for Martin Luther’s assault on the extensive Church?
            Pagan elements in its performance
            the amorality of its management
            its unnecessary attention to piety
            its dishonesty and worldliness
            the political participation of the popes 

        Ans : C
        The author’s tone in this comprehension can best be explained as
            analytical
            troubled
            cynical
            theatrical
            deferential 

        Ans : A
        Which of the following best elucidate why the extensive Church started the Counter restoration?
            to clash systematic heresy
            to fresh out its own ranks
            to revive artists and thinkers
            to choose a new pope
            to counter Protestant dispute 

        Ans : E 

%% page 17



Read the following comprehension and answer the following question.

    A few minutes ago, when I was coming back from lunch, and when I began to walk on the street when I heard the noise of a coin tumbling. It wasn't much but, as I bowed, my eyes trapped the heads of numerous other people turning too. A woman had dropped what come out to be a dime. The chinking sound of a coin tumbling on street is a notice getter. It can be nothing more than a penny. Whatever the coin is, no one ignores the sound of it. It got me thinking about sounds again. We are overwhelmed by so many noises that draw the most awareness. Citizens in New York City hardly ever turn to come across when a blaze engine, a police vehicle or an ambulance comes blaring along the road. When I’m New York, I called myself as a New Yorker. I don't turn moreover. Like the inhabitants. I barely hear an alarm bell there.

    At residence in my small town in Connecticut, it's unusual. The far-off wail of a police vehicle, an urgent situation car or a fire alarm bell brings me to my foot if I'm seated and brings me to the windowpane if I'm in bed. It's the silent noises that have most consequence on us, not the loudest. In the mid of the nighttime, I can listen to a drenched tap a hundred yard away all the way through three clogged doors. I have been hearing little squeaking sounds and sounds which my mind turns onto the footpath in the mid of the nighttime for twenty five years in our home. How come I by no means listen to those noises in the daylight? I'm pretty sure in my mind what the ideal noises are and what the terrible noise are.
    I have turned next to shrieking, for example. I used to believe of it as the blot of a joyful employee but recently I've been connecting the whistler with an anxious person creating obsessive sounds. The tapping sound, my typewriter as the keys strike the paper is a beautiful noise to me. I frequently like the sound of what I write improved than the looks of it.

        People in New York
            Are used to alarms
            Don’t listen to loud sounds
            Don’t care about emergencies
            Are fascinated by sounds
            None of the above 

        Ans : C
        How does the author narrate to sounds at night?
            He thinks taps must be turned off
            He visualizes sounds that do not live
            He believes it's quite quiet at nighttime
            He overstresses quiet noise
            None of the above 

        Ans : D
        What kind of sound does he find pleasant?
            tapping of his typewriter
            tinkling sound of a coin dropping
            creaking sounds
            clinking sound of keys
            None of the above 

        Ans : A
        The noise of a coin dropping makes people
            Stop crossing the road
            Look at each other
            Think of cash
            Pay notice to it
            None of the above 

        Ans : D
        He dislikes whistle for the reason that
            It reminds him of anxious people
            He is exhausted of it
            He doesn't like workforce
            He used to be more contented
            None of the above 

        Ans : A 

%% page 18



Read the following comprehension and answer the following question.

    The new day we heard somebody cheery refer to poets as visionary. No it is precise to pass on to poets as visionary but it is not discriminating to deduce as this human being did, that the dreams of writer are just as practical as nation who make bridges or glance into microscopes are now as close to actuality and fact. Where they vary from the theorist and the scientist is in the chronological sense alone, they are at the forefront of their time, while logicians and scientist are side by side of their time. We must not be outward that we not succeed to distinguish the practicableness of thoughts. Dreams are the daylight streamers sign of a new day of scientific development another forward pitch.

    Every onward step man takes in any ground of life is first taken along the pensive paths of thoughts. Robert Foulton did not find out his steamboat and then scientific knowledge improved a picture in the mind into an actuality of steel and wood. The vehicle was not dug out of the earth like a hunk of gold, first men dreamed the auto and afterwards, the sensible minded engineers fixed up with what had been shaped by winging dream. He looks intensely and with a considering eye into the poetry of the past finds there all the cold scientific delightful of today and much we shall not take pleasure in until some tomorrow. If the poet does not vision so evidently that blue print of this dream can right away be haggard and the sensible discussion right away effected, he should not for that cause be smiled upon as just the cerebral host for a sort of safe madness. For the poet, like the engineer is an expert. His being turned to the verve to tomorrow, cannot be turned concurrently to the life of nowadays. To the scientist, he says, “Here I offer you a flash of the outlook”. The shrewd scientist thanks him and takes that spark of the outlook and makes it over into a fiber of nowadays.

        What should be the ideal title for the passage?
            Dreamers of coming Reality
            Dreamers
            Reality
            None of the above 

        Ans : A
        Dreams are the -- -- -- streamers sign of a new day of scientific development another forward pitch.
            Night
            Daylight
            Light of day
            None of the above 

        Ans : B
        Scientist say Here I offer you a flash of the -- -- --
            (a) Outlook (b) Attitude (c) Position (d) None of the above Answer (a)
            Attitude
            Position
            None of the above 

        Ans : A
        ------ did not find out his steamboat
            (a) David
            Renaldo
            Robert Foulton
            None of the above 

        Ans : C
        Robert Foulton did not find out his -- -- -- and then scientific knowledge improved a picture in the mind into a actuality of steel and wood
            Steamboat
            Boat
            Ship
            None of the above 

        Ans : A 

%% page 19



Read the following comprehension and answer the following question.

    The question whether law and liberty are antithetical or friendly to each other has baffled the scholars for a long time. Diametrically opposite views have been expressed on these issues. On one hand the idealist holds that the state is an embodiment of reason justice and its laws promotes and strengthen individual liberty. Laws not only protect the rights and liberties of the people but also provide conditions for the development of human faculties. The state by enacting laws for compulsory education, regulation of working hours etc. tries to protect and promote the interest of the children and weaker sections. No doubt the state is a useful institution and aims at general welfare, but it would be wrong to categorically own position, such laws shall certainly lead to curtailment of liberty and may even result in a type of bondage. Usually the laws made by the despotic rules human liberty and blind obedience. To such laws is suicidal for human development. According to the other views expressed by the individualist and Anarchists, the law and the liberty are antithesis to each other. Each law puts certain restrictions on every individual’s liberty and the more of one leads to the less of the other. In other words they assert the law and liberty are always in inverse ratio. The individualists consider the state as a necessary evil. It is necessary because of the selfish nature of man and the existence of crime. But it is nonetheless an evil because every action of the state implies a restriction on the liberty of the individual. The Anarchists go a step further and assert that the state is an unnecessary evil. They consider that the state as a positive instrument of oppression and want to do away with it at the earliest. They believe that the individual shall be able to enjoy real liberty only when the state disappears.

    The view of the individualist and Anarchists seem to be incorrect in so far as they take liberty in absolute terms and envisage the absence of all restrains on the conduct of the individual. Actually the laws are enacted to regulate the social behaviors of the people and they invariably impose certain restraints in the larger interest of the society. In the absence of such laws or restraints liberty and give rise to would means merely the liberty of the strong and give rise to chaos and disorder. As liberty is meant for all the sections of society restrictions are essential for its enjoyment by all. Thus both views are not fully correct. We cannot say for certain that all laws promote liberty as we cannot say that all laws curtail liberty. In fact much depends on the nature and the contents of the laws. Generally, the laws made by democratic bodies promote liberty because the extended representatives of the people give due consideration to the wishes and interests of the people while enacting this laws with a view to provide facilities for the maximum development of the members of society. With a view to provide equal facilities to all the sections, it has to impose certain restraints on the liberty of the stronger people. In the absence of such restraints will be fully dependent on the will of the strong. Viewed in this sense, law promotes liberty.

        Which two groups of people are nearest in agreement in regard to the need of the state?
            Individualist and Anarchist
            Idealists and Anarchists
            The author and the Anarchista
            Idealists and Individualists
            None of the above 

        Ans : D
        The view with which Idealists are not likely to agree is
            Laws provide conditions for the promotion of human faculties
            Many of the laws enacted by the state are not useful for the citizens
            Since a state is an embodiment of reason and justice, a citizen must implicitly obey the laws made by it
            The children and weaker sections have to be protected through laws which may seem to curtail individual liberty
            None of the above 

        Ans : B
        Which of the following laws will be author not support?
            Compelling parents to send their children to school
            Compulsory hanging of a murderer
            Detention of a person who lectures against a prime minister
            Law fixing minimum age of factory workers
            None of the above 

        Ans : C
        The individualist consider the state a necessary evil because
            It provides compulsory education
            It protects them against Anarchists
            Man is basically selfish and, if unchecked is likely to indulge in crimes
            It provides job to many
            None of the above 

        Ans : C
        In this passage, the author is trying to
            Argue for the abolition of the state
            Widen the gap between the views of various groups
            Distort the views of various groups
            Reconcile the views of various groups
            None of the above 

        Ans : D 
