%% http://www.bestsamplequestions.com/gre-questions/sentence-completions/sentence-completions.html

%%--------------------------------------------------
%% GRE: Sentence Completion
%%--------------------------------------------------


%% Directions:
%% Every sentence given below has one or may be two blanks; every blank point out that there is something that has been erased. Beneath the sentence are set of words or five options given. Select the particular word or set of words from every blank that perfectly fits the meaning of the sentence as a whole.


%% GRE Multiple Choice Questions
%%--------------------------------------------------
\element{gre-mc}{
\begin{question}{gre-sentence-completion-q01}
    Hoping to \rule[-0.1pt]{4em}{0.1pt} the clash,
        negotiators suggest a negotiation that they felt would be \rule[-0.1pt]{4em}{0.1pt} to both policies and legislation.
    \begin{choices}
        \wrongchoice{Manage---Resolving}
        \wrongchoice{Solve---Divisive}
        \wrongchoice{Extend---Detrimental}
      \correctchoice{Resolve---Acceptable}
        \wrongchoice{End---Likely}
    \end{choices}
\end{question}
}

\element{gre-mc}{
\begin{question}{gre-sentence-completion-q02}
    In spite of her age, she has a childish and \rule[-0.1pt]{4em}{0.1pt} sense of humor.
    \begin{choices}
        \wrongchoice{Adolescent}
        \wrongchoice{Trivial}
        \wrongchoice{Mature}
      \correctchoice{Asinine}
        \wrongchoice{Youthful}
    \end{choices}
\end{question}
}

    At the cutting edge of research, scientists are developing new sunscreens to protect people from harmful-- -- --
        UV rays
        Pollution
        Environment
        Atmosphere
        None of the above 

    Ans :A
    Knowing Julian was outshined by many other performers, she knew she was pampering in a bit of -- -- -- when she speculated whether Julian was the supreme living performer ever.
        Hyperbole
        Injustice
        Understatement
        Irony
        Overemphasis 

    Ans :B
    In spite of mixed effusion to the divergent, there is no required link between technical skill and humanism, and quite probably, there may be a little of a -- -- --between them.
        Dichotomy
        Congruity
        Reciprocity
        Union
        Generosity 

    Ans :E
    Simply paying a judgment or tax won’t -- -- -- improve your credit score. It will however, start the clock ticking so that item will -- -- -- get removed.
        Likely- Eventually
        Possible- Finally
        Promising – Lastly
        Capable – Last of all
        Potentially – At last 

    Ans :A
    Bankruptcy can offer a fresh start from debts it does not -- -- -- out the -- -- -- accounts that appeared on your report.
        Wash – Unique
        Wipe – Original
        Dab – Inventive
        Blob – Creative
        Splash – Artistic 

    Ans :B
    Your credit cards however will be closed during the program so it will be -- -- -- you can get new loans.
        Similarly
        Likely
        Probably
        Unlikely
        Doubtful 

    Ans :D
    There are lenders, though, that understand the value of credit counseling and will be willing to finance a loan once you have been -- -- -- paying on your program for -- -- -- one or two years, provided you meet their
        Profitably - Slightest
        Successfully - At least
        Beneficially – Least
        Usefully – Smallest amount
        None of the above 

    Ans :B
    If you had joint accounts with -- -- -- who died, then you will be responsible for the bills
        Someone
        Any one
        Every one
        Everybody
        Each one 

    Ans : A 


%% page 2 11


    If you have an account that was charged off, it may show a balance -- -- -- it is paid or settled.

        Pending
        Unless
        Except
        If not
        Until 

    Ans : E
    Don’t be pressured into paying those bills directly, -- -- -- if it will hurt your family financially
        Particularly
        Especially
        Mainly
        Mostly
        Typically 

    Ans : B
    It’s feasible that during a bank merger or the sale of a few accounts, your account went to a latest lender and you just don’t -- -- -- the name of the latest lender.
        Recognize
        Distinguish
        Discern
        Discriminate
        Classify 

    Ans :A
    If your bankruptcies may be reported for ten years from the date you filed, -- -- -- credit bureaus will remove chapter 13 bankruptcies seven years from the filling date.
        Minor
        Small
        Major
        Important
        Particular 

    Ans :C
    The students have been complaining about the assigned novel, which is hard to -- -- --.
        Understand
        Remember
        Know
        Consider
        Believe 

    Ans :A
    Some drugs are -- -- -- to children, and such medicines should be kept locked up.
        Useful
        Harmful
        Helpful
        Valuable
        Profitable 

    Ans :B
    Physical needs are unsatisfied, they take first place, but when they are satisfied, emotions unconnected with them become -- -- -- in deciding whether a man is to be happy or unhappy.
        Significant
        Important
        Vital
        Main
        Major 

    Ans :B
    Millions of people struggle for bare -- -- -- in every country and we don’t have -- -- -- medical facilities in this hospital.
        Existence – Adequate
        Life – Sufficient
        Living – Ample
        Livelihood – Plenty
        Existing – Plenty 

    Ans :A
    The master tells the upset workers that machines have -- -- -- their earning, buying power and hence, happiness.
        Amplified
        Increased
        Enlarged
        Inflated
        Magnified 

    Ans :B
    Workers who operate the machines in dark, dirty and noisy work places complain that the machine affect their health badly.
        Criticize – Distress
        Complain – Affect
        Condemn – Sorrow
        Attack – Grief
        Harass – Influence 

    Ans :B 

%% page 3 21


    The people wish to be rich not in order to -- -- -- luxury goods so much as to feel superior to their neighbors.

        Sell
        Buy
        Advertise
        Publicize
        Announce 

    Ans :B
    The master -- -- -- naturally admires the machines because they will serve him sincerely. But he admires their look -- -- -- they are actually operated
        Quiet – Before
        Bit – Previous to
        Little – Prior
        Slight – Former
        Minor – Past 

    Ans :A
    The rich are -- -- -- fortunate than their neighbors or relations. This is their competitive -- -- -- over others.
        More – Advantage
        Less – Gain
        Little- Profit
        Slight – Yield
        Small – Expand 

    Ans :A
    The state can provide some -- -- -- sport facilities to satisfy men inherit ant desire for -- -- -- and action.
        Daring – Gratify
        Adventurous – Thrill
        Bold – Indulge
        Brave – Spoil
        Heroic – Ruin 

    Ans :B
    The two other factors which play -- -- -- part in -- -- -- poverty is density of population and political condition.
        Major – Increasing
        Chief – Rising
        Principle – Growing
        Main – Budding
        Important – Emergent 

    Ans :A
    Machines demand regularity and they -- -- -- to be operated regularly and continually. But human emotions do not follow any set course and they are -- -- -- and spontaneous.
        Required – Unequal
        Compulsory - Imbalanced
        Need – irregular
        Vital – Lopsided
        Obligatory – Extreme 

    Ans :C
    The -- -- -- praise given to a person who is a sincere tireless worker is that he has the qualities of a machine. He is -- -- --, punctual and accurate
        Highest – Dependable
        Good – Silly
        Bad – Stupid
        Nice – Brainless
        Polite – Mindless 

    Ans :A
    The art collector -- -- -- pleasure from the thought that others know how much he has spent on -- -- -- painting
        Attain – Every
        Derives – Each
        Accomplish – All
        Achieve – Everyone
        Do – Everything 

    Ans :B
    The author wants to -- -- -- those machines have the -- -- -- attraction for the young and the old alike
        Show – Huge
        Explain – Big
        Prove – Great
        Establish – Vast
        Found – Immense 

    Ans :C
    Machines are worshipped because they are beautiful, and valued because they -- -- -- power; they are hated because they are hideous and loathed because they -- -- -- slavery.
        Confer – Impose
        Grant – Impress
        Allowance – Astonish
        Payment – Daze
        Contribution - Stun 

    Ans :A 

%% page 4 31


    The master of the machine, it is true, lives at a -- -- -- from it where he cannot hear its noise or see its unsightly heaps of slag or smell it’s -- -- -- fumes.

        Distance – Noxious
        Aloofness – Deadly
        Coldness – Toxic
        Iciness – Noxious
        Frostiness – Injurious 

    Ans :A
    David complains that his room is -- -- -- filled with tobacco smoke.
        Frequently
        Regularly
        Habitually
        Often
        Commonly 

    Ans :D
    His hairs are cut too -- -- --. It -- -- -- that he has been given a hair cut for the army.
        Short – Seems
        Tiny - As if
        Little – Since
        Slight – When
        Minor – While 

    Ans :A
    The -- -- -- percentage for admission to this course is 95%
        Initial
        Primary
        Starting
        Cut off
        Main 

    Ans :D
    How did they -- -- --the flight for California?
        Board
        Took
        Went
        Taken
        Gone 

    Ans :A
    How many persons were to be hanged to -- -- -- and how did they behave before their death?
        Decrease
        Death
        Murder
        Killed
        Demise 

    Ans :B
    The islands -- -- -- rains for more than six or seven months
        Get
        Obtain
        Acquire
        Receive
        Got 

    Ans :D
    Poetry and Philosophy take -- -- -- forms in the times of struggle for freedom or revolution.
        Recent
        Latest
        Fresh
        New
        Modern 

    Ans :D
    The author’s mother died and his father -- -- -- lonely and sad.
        Experienced
        Feel
        Feeling
        Felt
        Touch 

    Ans :D
    He didn’t feel the -- -- -- of his mother because his father was both father and mother to him.
        Lack
        Absence
        Need
        Want
        Requirement 

    Ans :B 

%% page 5 41



    The lake was not a -- -- -- once but a man made reservoir.

        Normal
        Natural
        Ordinary
        Usual
        Normal 

    Ans :B
    I -- -- -- a car the day after landing and brought a comprehensive book of maps, which I found most helpful on the cross country voyage, but which I did not believe I should -- -- -- on the last stage.
        Brought – Require
        Hired – Need
        Bring – Involve
        Booked – Should
        Taken – Requirement 

    Ans :B
    We have been -- -- -- about the evils of child labor for the last 15 years in this country.
        Talking
        Speaking
        Communicating
        Language
        Talk 

    Ans :A
    A successful man is able to -- -- -- his ideas in a way that he can sell them to others.
        Speak
        Talking
        Telling
        Communicate
        Communication 

    Ans :D
    David knows how to influence people and win friends so as to -- -- -- them for a purpose.
        Motivate
        Encourage
        Knowledge
        Training
        Information 

    Ans :A
    Education does not seem to have played a -- -- -- role in making our life successful.
        Affective
        Great
        Huge
        Small
        Little 

    Ans :B
    After thirty years of work, Dr. John Gibbon of U.S.A had -- -- -- a machine that could take over temporarily from the heart and lungs.
        Developed
        Invented
        Made up
        Urbanized
        Imaginary 

    Ans :A
    Medical experts have cautioned against -- -- -- use of aluminum cookware and foils, especially for acidic food preparations -- -- --tamarind, tomatoes and green leafy vegetables which could lead to aluminum toxicity and consequent nerve disorders.
        Wide – Have
        Extensive – Containing
        Ample- Contain
        Plentiful – Enclose
        Abundant – Surround 

    Ans :B
    Chronic exposure of high levels of aluminum -- -- -- food and water could lead to nerve and brain disorders such as Alzheimer’s and Parkinson’s disease, they say.
        Through
        During
        Throughout
        All over
        For the duration of 

    Ans :A
    NIN Scientist says in a statement that they have also -- -- -- regular monitoring of aluminum in blood for dialysis victims. Patients with kidney disorders are -- -- -- susceptible to aluminum toxicity as their excretion of aluminum is affected.
        Suggested – Chiefly
        Advised – Particularly
        Recommended – Mostly
        Optional – Mainly
        Not compulsory – Chiefly 

    Ans :B 

%% page 6 51


    With the exposure of human beings to aluminum increasing markedly in recent years, they are more prone to absorbing excessive amount of this metal, the report warns.

        Current – Too much
        Recent – Excessive
        Modern – Extreme
        Present - Severe
        Fresh – Harsh 

    Ans :B
    Aluminum is -- -- -- in water, spoil, plants and cooking utensils. It is added to drinking water as aluminum sulphate at the treatment plants, while soil contamination with it leads to its -- -- -- in vegetables.
        Present- Accumulation
        There – Buildup
        Nearby - Increase
        Close by – Boost
        Close at hand – Improve 

    Ans :A
    Beggars almost sell themselves as human beings to -- -- -- the pity of passersby.
        Stimulate
        Arouse
        Kindle
        Promote
        Support 

    Ans :B
    A tramp may ask you for money, but he will never ask you to feel sorry for him.
        Bad
        Worst
        Sorry
        Good
        Best 

    Ans :C
    Teachers sell knowledge, philosophers wisdom and priests spiritual comforts. Value of material goods can be measured in terms of money but not the value of the services.
        Religious – Calculated
        Spiritual- Measured
        Dutiful – Planned
        Loyal – Intended
        Reliable – Projected 

    Ans :B
    Continuity of purpose is one of the most -- -- -- ingredients of happiness and that come chiefly through their work.
        Important
        Particular
        Significant
        Essential
        Useless 

    Ans :D
    Work, therefore is desirable first and -- -- -- as a preventive of boredom, for the boredom that a man feels when he is doing something out of -- -- --, through uninteresting work is as boring as having nothing to do.
        Foremost – Compulsion
        Primary – Obligation
        Prime – Responsibility
        Main – Blame
        Chief – Duty 

    Ans :A
    Clever advertising, aimed at chronic sufferers who will try anything because doctors have not been able to cure them, can induce such faith in a preparation, particularly if sleepy priced that it will produce by suggestion a very real effect in some people.
        Heal – Especially
        Cure – Particularly
        Mend – Above all
        Fix – Mainly
        Make well – Chiefly 

    Ans :B
    The topic of thought is one area of Psychology and many observers have considered these aspects in connection with robots and computers, some of the old worries about artificial intelligence were closely linked to the question of whether computers could think.
        Directly
        Closely
        Very much
        Strongly
        Honestly 

    Ans :B
    Another disadvantage is that television -- -- -- causes people to become dissatisfied with their own lives.
        Frequently
        Often
        Regularly
        Normally
        Commonly 

    Ans :B 

%% page 7 61


    Penguin became a different company in the year 1936 and set up -- -- -- -- -- in the Crypt of the Holy Trinity Church on Marylebone Road, using a fairground glide to obtain deliveries from the street above. In twelve months, it had sold an incredible 3 million paperbacks. Customary publishers tended to view Penguin with misgiving and -- -- -- -- --, as did some authors.

        Premises – Uncertainty
        Ground – Doubt
        Location – hesitation
        Place - Indecision
        Position – Hesitancy 

    Ans :A
    The planets, the majority of the satellites of the planets and the asteroids -- -- -- -- -- around the Sun in the similar direction, in almost spherical orbits. When looking down from on top of the Sun's North Pole, the planets -- -- -- -- -- contradict in a clockwise direction. The planets orbit the Sun in or close to the similar plane, called the ecliptic.
        Rotate – Track
        Revolve – Orbit
        Spin – Path
        Circle – Range
        Encircle – Lane 

    Ans :B
    The term volcano came from the Vulcano desert island, which had been named after Vulcan, the Roman god of fire. There are many -- -- -- -- -- kinds of volcanoes as well as composite volcanoes, shelter volcanoes, clinker cones, splash cones, and compound or complex volcano. These dissimilar types of volcanoes come in unusual shapes and -- -- -- -- -- in various ways.
        Dissimilar – Explode
        Unlike – Blow up
        Distinct – Burst
        Disparate – Rapture
        Unrelated – delight 

    Ans :A
    Kiwifruit is the most vitamin and nutrient rich of the top 27 fruits eaten in the world nowadays. It also has the -- -- -- -- -- compactness of any fruit which is rich in vitamin C and magnesium limited mineral in the food delivered of wealthy countries and a nutrient useful for cardiovascular physical condition. Amongst the top three high potassium low sodium fruits, kiwi fruit is regarded as the one of the -- -- -- -- -- fruit, having a large amount of potassium compared to banana or any other citrus fruits.
        Maximum – Best
        Great – Most excellent
        Grand – Finest
        Impressive – Premium
        Imposing – Quality 

    Ans :A
    It’s alluring to blame fruit growers, sellers and wholesalers for making the pear a substandard eating experience but in -- -- -- -- --, pear is a very complicated fruit to trade. They ripen from the inside out and the only sign that they are ready to eat is a slight give or smoothness around the stem. Eat them -- -- -- -- -- and they will be dry and tasteless. Leave them too long and they may become brown and soft in the middle.
        Actually – Fast
        Really – Quick
        Truly – Speedy
        Reality – Quickly
        Certainly – Rapid 

    Ans :D
    Diamond is the strongest and hardest natural metal. The Mohs solidity scale, on which diamond is 10 and sapphire is 9, doesn't sufficiently attest to this -- -- -- -- -- solidity, as diamond is exponentially stronger compared to corundum. Diamond is very least compressible and -- -- -- -- -- substance.
        Unbelievable – Strongest
        Incredible – Hard
        Absurd – strong
        Illogical – Stiff
        Irrational – Rigid 

    Ans :A
    More than \$50 billion of people are blown on cosmetics -- -- -- -- -- every year and hundreds of hours are spent using creams, powders and lotions. Even with the current downturn in the country, makeup fans have basically turned to drugstores, instead of -- -- -- -- -- cosmetics boutiques, to holdup their tonics, wands and face cosmetics, according to a current consumer details by Euro monitor International.
        Universal – Small
        Widespread – Low- priced
        Extensive – Posh
        General - Cheap
        Worldwide – Expensive 

    Ans :E
    Starfish are also -- -- -- -- -- as sea stars and are not actually fish in spite of the name been given to them because of its shape. These are known as echinoderms, which are found plentiful in the deep Oceans and low waters as well. If you have ever bumped into a starfish and turned it over, you will find bulges on the base. These are called as tube feet, which have basically two functions - one being able to travel around the -- -- -- -- -- floor and the other to open up a clam or scallop.
        Identified - Deep Sea
        Branded – Pond water
        Famous – Shallow water
        Famed – River water
        Celebrated – Water 

    Ans :A
    All stars starts from clouds of freezing molecular hydrogen that -- -- -- -- -- fall down. As they cloud crumples, it wreckage into many pieces that will go on to form alone stars. The objects collect into a ball that persists to fall down under its individual gravity until it can -- -- -- -- -- fire nuclear fusion at its main core. This original gas was formed throughout the Big Bang, and is always about 75% hydrogen gas and 24% helium.
        Gravitationally – Catches
        Automatically – Hold
        Mechanically – Grab
        Involuntarily – Clutch
        Unwillingly – Grasp 

    Ans :A
    Venus is like the Earth’s wicked twin. Although it’s alike in -- -- -- -- -- and weight to the Earth, the environment of Venus sets it separately. The mass of the environment is 95 times that of the Earth’s environment. If you could stand on the plane of Venus, you would actually -- -- -- -- -- 92 times the force you have on Earth. This is the similar as going almost a kilometer beneath the surface of the ocean.
        Dimension – Experience
        Length – Feel
        Height – Know
        Size – Experience
        Altitude – Skill 

    Ans :D 


