%%
%% Copyright (C) 2014 Jeffrey P. Hafner <jphafner@buffalo.edu>
%%
%%  This program is free software: you can redistribute it and/or modify
%%  it under the terms of the GNU General Public License as published by
%%  the Free Software Foundation, either version 3 of the License, or
%%  (at your option) any later version.
%%
%%  This program is distributed in the hope that it will be useful,
%%  but WITHOUT ANY WARRANTY; without even the implied warranty of
%%  MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
%%  GNU General Public License for more details.
%%
%%  You should have received a copy of the GNU General Public License
%%  along with this program.  If not, see <http://www.gnu.org/licenses/>.
%%

\documentclass[
    11pt,
    titlepage,
]{scrartcl}

\usepackage{AMCexam}

%% Begin Definitions
%%------------------------------------------------
\newlength{\mylen}
%% I use these for space saving
\setlength{\parskip}{0pt} % 1ex plus 0.5ex minus 0.2ex}
\setlength{\parindent}{0pt}

\titlehead{Title Head}
\subject{Subject or Class Name}
\title{Examination Title}
\subtitle{Examination Subtitle \textnumero{}\serialnum}
\author{Dr. Jeffrey Hafner}
\date{\today}
%% Thanks is not used in my template
%\thanks{}
\publishers{
    %% This is used for exam instructions
    %% Feel free to change this however you want
    The possession or use of \emph{any} electronic device is strictly
        prohibited when taking this examination.
    If you use any electronic device, no matter how briefly,
        your examination will be invalidated and no score will be given.

    Use a ruler of any scale,
        any writing utensil, and a protractor are permitted.
    The use of any external reference material is strictly prohibited.
    You will be provided with scrap paper by the proctor,
        you may request more at any time.

    For each statement or question, choose the word or expression that,
        of those given, best completes the statement or answers the question.
    Some questions may require the use of the provided reference tables.
    Record your answers on the provided response sheet
        located on the last page of this booklet.

    %% Necessay if you include any questionmult items
    Questions using the sign \multiSymbole{} may have zero,
        one or several correct answers.
    All other questions have one correct answer.

    You may write in this booklet as only your response sheet will be collected.
    You may \emph{only} use either an HB or \textnumero{}2 graphite pencil,
        or a black ink pen on the response sheet.
    Make no stray marks on the response sheet!

    %% As defined in AMCexam
    All questions are weighted evenly for grading purposes.
    Each correct response is worth $+4$ points,
        and each incorrect response is worth $-1$ point.
    Questions using the sign \multiSymbole{} are worth $+4$ or $0$,
        and nothing in-between.
    Points awarded will be the geometric mean of the
        points earned and points available.
    
    This booklet has printed material on the recto and verso side of each page.
    \emph{Good Luck!}
}

%% Needed for includegraphic commands
\graphicspath{{./qbank/halliday/gfx/}{./qbank/serway/gfx/}{./qbank/aapt/gfx/}}

%% Begin Document
%%------------------------------------------------
\begin{document}

%% 319 Questions

%% NYSED
\input{./qbank/nysed/NYSED-sound.tex}
\input{./qbank/nysed/NYSED-waves.tex}

%% AAPT 52Q
\input{./qbank/aapt/Bowl-A3.tex}

%% Lua
%\directlua{dofile("./qbank/lua/common.lua")}
%\input{./qbank/lua/wrong.tex}
%\input{./qbank/lua/units.tex}


%% Begin Question Sheet
%%------------------------------------------------
\begin{examcopy}[1]
    \begin{titlepage}
        \titleAMC
        \newpage
    \end{titlepage}

    %% Section: question or questionmult
    %\section{Multiple Choice Questions}
    \begin{multicols}{2}
        \cleargroup{all}

        \shufflegroup{nysed}
        \copygroup[40]{nysed}{all}
        
        \shufflegroup{all}
        \insertgroup{all}
    \end{multicols}

    \begin{center}
    \fbox{
        \begin{minipage}{0.618\linewidth}
            When you finish this exam,
            you should go back and reexamine your work,
            both on the earlier part of this exam and in your life up until the day of this exam,
            for any errors that you may have made.
        \end{minipage}
    }
    \end{center}
    
    \AMCcleardoublepage

    %% Begin Answer Sheet
    %%------------------------------------------------

    %% Must use to begin answer sheet
    \AMCformBegin

    \setlength{\mylen}{\linewidth}
    \addtolength{\mylen}{-17em}
    \begin{minipage}{\linewidth}
        \centering
        \begin{minipage}{15.5em}
            \centering
            Student Number \\
            %% Change this to match student nuber size
            %% I personally use 3 digits
            \AMCcodeH{StudentNum}{3}
        \end{minipage}
        \begin{minipage}{\mylen}
            \centering
            \titleHeader \\
            \namefield{\fbox{
                \begin{minipage}{\linewidth}
                    Last and First Name: \hfill Today's Date:
                    \vspace*{3em}
                \end{minipage}
            }}
        \end{minipage}
    \end{minipage}

    \null\hfill\parbox[c]{0.9\linewidth}{
        %% Response Sheet instructions
        %% Feel free to change how you want
        Print your last and first name in the box provided above.
        Enter your course student ID number by filling in
            the appropriate boxes to the left.
        %% It is important to remind to fill completely!!
        Enter your chosen selection for each question on this
            %% ovals, plural, as some may have more than one answer
            form by filling in completely your selected oval(s) for each question.
        \emph{Good Luck!!}
    }\hfill\null

    \rule[0pt]{\linewidth}{0.5pt}

    %%% end of the answer sheet header
    \begin{multicols}{3}
        \columnseprule=.4pt
        %% prevent broken paragraphs
        \widowpenalties 1 10000
        \AMCform
        %\AMCformS
    \end{multicols}
    %% NOTE: Place Reference sheet here
    \clearpage
    \input{./qbank/REF.tex}
    %\input{./Slide_rule.pdf}
    %% NOTE: This is needed for mass printing
    \AMCcleardoublepage
\end{examcopy}
\end{document}

