
%% This defines the lua function mycommand()
%\directlua{require('./qbank/lua/common.lua')}


%% Numeric Difficulty A
%%--------------------------------------
\element{numeric}{
\begin{questionmultx}{horizontal-A-Q01}
\luaexec{
    %% Question
    local Q = [[
        An ogre stands on the top of a
            \string\SI{\%d}{\string\meter}
            high bridge and kicks a rock horizontally off of the bridge.
        The rocks lands in the water below,
            \string\SI{\%d}{\string\meter}
            down range of the bridge.
        What is the velocity of the rock as it enters the water
            divided by \string\SI{1}{\string\meter\string\per\string\second}?
    ]]
    %% Random Values
    local h = math.random(10,40)
    local d = math.random(10,40)
    %% Print Question
    local v = 
    local ans = dis/1000
    tex.print( string.format(Q, vel, tim0, acc, tim1, -1*dec ))
    %tex.print( ans )
    %% Print AMCnumeric
    options = [[ digits=4, decimals=1, sign=True, approx=1 ]]
    tex.print( BeginCenter )
    tex.print( string.format(AMCnumeric, ans, options ) )
    tex.print( EndCenter )
}
\end{questionmultx}
}


\begin{question}[ID=horizontal-A-Q02,topic=projectiles,difficulty=easy]
    An evil overlord stands on the top of his evil perch
        \SI{47}{\meter} above his evil minions.
    He casually throws a spear horizontally at a speed of
        \SI{3.2}{\meter\per\second} and watches as it
        sticks in the ground at the feet of his evil
        workers.
    At what angle does the spear stick out of the ground and
        at what speed does it hit the ground?
\end{question}
\begin{solution}
    N/A
\end{solution}


\begin{question}[ID=horizontal-A-Q03,topic=projectiles,difficulty=A]
    An evil overlord stands on the top of his evil perch and
        throws his spear horizontally at his evil minions.
    He casually tosses a spear horizontally at a speed of
        \SI{7.3}{\meter\per\second} and watches as it sticks
        in the ground at the feet of his evil workers.
    The spear makes an angle of \SI{62}{\degree} with respect
        to the ground.
    How high is the evil overlord's perch?
\end{question}
\begin{solution}
    N/A
\end{solution}


\begin{question}[ID=horizontal-A-Q04,topic=projectiles,difficulty=A]
    An evil overlord stands on the top of his evil perch and
        throws his spear horizontally at a height of \SI{33}{\meter}
        and watches it land at the feet of his evil minions
        at an angle of \ang{58} with respect to the ground.
    At what speed did he throw his spear?
\end{question}
\begin{solution}
    N/A
\end{solution}


\begin{question}[ID=horizontal-A-Q05,topic=projectiles,difficulty=A]
    The evil overlord stands on top of his evil perch
        \SI{36}{\meter} above his evil minions.
    He casually tosses a spear horizontally at a speed
        of \SI{4.1}{\meter\per\second} and watches as it
        sticks in the ground at the feet of his evil workers.
    At what angle does the spear stick out of the ground and
        at what speed does it hit the ground?
\end{question}
\begin{solution}
    N/A
\end{solution}


\begin{question}[ID=horizontal-B-Q01,topic=projectiles,difficulty=easy]
    The bad guys in Car A are chasing the good guys in Car B
        as they come around the turn and approach a cliff.
    Car B is moving at \SI{31.7}{\meter\per\second} and 
        Car A is moving at \SI{35.2}{\meter\per\second}.
    They both go horizontally off of the \SI{17}{\meter}
        high cliff.
    Which car lands first and how far apart do they land?
\end{question}
\begin{solution}
    N/A
\end{solution}


\begin{question}[ID=horizontal-B-Q02,topic=projectiles,difficulty=B]
    An archer and a pistol marksman are standing side-by-side
        on a hill.
    The both fire their weapons horizontally at the same instant
        from a height of \SI{2.5}{\meter} above the ground.
    The arrow travels at a speed of \SI{65}{\meter\per\second}
        and the bullet travels at a speed of \SI{140}{\meter\per\second}.
    Which projectile hits the ground first and how far apart do they land?
\end{question}
\begin{solution}
    N/A
\end{solution}


\begin{question}[ID=horizontal-B-Q03,topic=projectiles,difficulty=B]
    A sniper is on the roof of a \SI{22}{\meter} high building
        standing next to a cannon.
    The sniper fires his rifle horizontally at the same
        time the cannon is also fired horizontally.
    The sniper's bullet leaves the rifle at a speed of 
        \SI{750}{\meter\per\second} and the cannonball
        leaves the cannon at \SI{220}{\meter\per\second}.
    Which projectile hits the ground first and how far
        apart do they land?
    (Ignore air resistance)
\end{question}
\begin{solution}
    N/A
\end{solution}


\begin{question}[ID=horizontal-B-Q04,topic=projectiles,difficulty=easy]
    The bad guys in Car A are chasing the good guys in Car B
        as they come around the turn and approach a cliff.
    Car B is moving at \SI{33.5}{\meter\per\second} and 
        Car A is moving at \SI{45.6}{\meter\per\second}.
    They both go horizontally off of the \SI{13}{\meter}
        high cliff.
    How far apart do they land?
\end{question}
\begin{solution}
    N/A
\end{solution}


\begin{question}[ID=horizontal-C-Q01,topic=projectiles,difficulty=C]
    A rock is kicked horizontally at a speed of \SI{13.5}{\meter\per\second}
        from teh top of a \SI{142}{\meter} high cliff.
    How far down range does the rock travel?
\end{question}
\begin{solution}
    N/A
\end{solution}


\begin{question}[ID=horizontal-C-Q03,topic=projectiles,difficulty=C]
    A woman stands on the top of a \SI{112}{\meter} bridge
        and kicks a rock horizontally off of the bridge.
    The rock lands in the water below, \SI{88}{\meter}
        down range of the bridge.
    What was the initial velocity of the rock that she
        kicked?
\end{question}
\begin{solution}
    N/A
\end{solution}


\begin{question}[ID=horizontal-C-Q04,topic=projectiles,difficulty=C]
    A ball is kicked horizontally off of a \SI{78}{\meter}
        high bridge at a speed of \SI{6.3}{\meter\per\second}.
    How far down range down the ball land?
\end{question}
\begin{solution}
    N/A
\end{solution}


\begin{question}[ID=horizontal-C-Q05,topic=projectiles,difficulty=C]
    A ball is kicked horizontally off a cliff at a speed of
        \SI{9.12}{\meter\per\second} and lands
        \SI{43.7}{\meter\per\second} down range.
    How high is the cliff?
\end{question}
\begin{solution}
    N/A
\end{solution}


\begin{question}[ID=horizontal-C-Q06,topic=projectiles,difficulty=C]
    A golfer stands on a cliff \SI{72}{\meter} high and
        hits a gold ball horizontally off the cliff.
    The ball lands on the green \SI{575}{\meter} away.
    What was the initial velocity of the gold ball?
\end{question}
\begin{solution}
    N/A
\end{solution}


\endinput

