

%% Relative Motion
%%------------------------------------------------

\begin{question}[ID=relative-A-Q01,topic=relative-motion,difficulty=A]
    An archer is riding in the back of a pick-up truck.
    The pick-up truck is traveling at \SI{15}{\meter\per\secodn}
        relative to the earth.
    The archer shoots an arrow directly forward with respect to the truck
        with an initial velocity of \SI{65}{\meter\per\second} and
        at an angle of \ang{25}.
    What is the range of the arrow?
\end{question}
\begin{solution}
    N/A
\end{solution}


\begin{question}[ID=relative-A-Q02,topic=relative-motion,difficulty=A]
    A boy is riding in the back of a wagon that is traveling
        forward at \SI{5.0}{\meter\per\second} relative to the Earth.
    The boy throws a ball directly out the back of the vehicle
        with an initial velocity of \SI{35}{\meter\per\second}
        and at an angle of \SI{45}{\degree} with respect to
        the wagon.
    How far does the ball travel down range from the point of
        its release?
\end{question}
\begin{solution}
    N/A
\end{solution}


\begin{question}[ID=relative-A-Q03,topic=relative-motion,difficulty=A]
    A man with a potato cannon is riding in the back of a pick-up truck.
    The pick-up truck is traveling at \SI{25}{\meter\per\second}
        relative to the earth.
    The potato cannon shoots a projectile directly forward with
        respect to the truck at an initial velocity of
        \SI{52}{\meter\per\second} and at an angle of \SI{45}{\degree}.
    What is the range of the potato?
\end{question}
\begin{solution}
    N/A
\end{solution}


\begin{question}[ID=relative-A-Q04,topic=relative-motion,difficulty=A]
    An archer is riding in the back of a pick-up truck.
    The pick-up truck is traveling at \SI{23}{\meter\per\secodn}
        relative to the earth.
    The archer shoots an arrow straight up with an initial velocity
        of \SI{80}{\meter\per\second}.
    What is the range of the arrow?
\end{question}
\begin{solution}
    N/A
\end{solution}


\begin{question}[ID=relative-B-Q01,topic=relative-motion,difficulty=B]
    An aircraft carrier is moving due east at a velocity of
        \SI{18}{\meter\per\second} relative to the water.
    A jet takes off at a speed of \SI{42}{\meter\per\second}
        at an angle of \SI{10}{\degree} north of east relative
        to the aircraft carrier.
    What is the velocity of the jet relative to the water?
\end{question}
\begin{solution}
    N/A
\end{solution}


\begin{question}[ID=relative-B-Q02,topic=relative-motion,difficulty=B]
    A truck is moving due north at a velocity of \SI{24}{\meter\per\second}
        relative to the earth.
    A boy on the back of the truck throws a ball \SI{20}{\degree}
        south of east at a speed of \SI{15}{\meter\per\second}.
    There is an observer on the side of the road.
    What is the velocity of the ball relative to the observer?
\end{question}
\begin{solution}
    N/A
\end{solution}


\begin{question}[ID=relative-B-Q03,topic=relative-motion,difficulty=B]
    An aircraft carrier is moving due east at a velocity of
        \SI{18}{\meter\per\second} relative to the water.
    A dog is walking \SI{8.0}{\meter\per\second} on the deck
        \SI{25}{\degree} north of east.
    What is the velocity of the dog relative to the water?
\end{question}
\begin{solution}
    N/A
\end{solution}


\begin{question}[ID=relative-B-Q04,topic=relative-motion,difficulty=B]
    A truck is moving due east at a velocity of \SI{33}{\meter\per\second}
        relative to the earth.
    A boy on the back of the truck throws a ball \SI{20}{\degree}
        south of east at a speed of \SI{15}{\meter\per\second}.
    There is an observer on the side of the road.
    What is the velocity of the ball relative to the observer?
\end{question}
\begin{solution}
    N/A
\end{solution}


\begin{question}[ID=relative-B-Q05,topic=relative-motion,difficulty=B]
    A train is heading due west at a speed of
        \SI{34}{\meter\per\second} relative to the Earth.
    A man throws a rock out of the window at a speed of
        \SI{11}{\meter\per\second} and at an angle of
        \SI{15}{\degree} north of west.
    What is the velocity of the rock relative to the Earth?
\end{question}
\begin{solution}
    N/A
\end{solution}


\begin{question}[ID=relative-B-Q06,topic=relative-motion,difficulty=B]
    A truck is moving due west at a velocity of \SI{44}{\meter\per\second}
        relative to the earth.
    A boy on the back of the truck throws a ball \SI{65}{\degree}
        south of east at a speed of \SI{15}{\meter\per\second}.
    There is an observer on the side of the road.
    What is the velocity of the ball relative to the observer?
\end{question}
\begin{solution}
    N/A
\end{solution}


\begin{question}[ID=relative-C-Q01,topic=relative-motion,difficulty=C]
    A dog is riding on the back of his owner's pickup truck which is
        heading due north at a speed of \SI{22}{\meter\per\second}.
    The dog sees a cat sitting on the side of the road and throws his
        bone at the cat by throwing itdue east at a speed of
        \SI{15}{\meter\per\second}.
    What is the velocity of the bone as relative to the cat?
\end{question}
\begin{solution}
    N/A
\end{solution}


\begin{question}[ID=relative-C-Q02,topic=relative-motion,difficulty=C]
    A boat is heading north across a river at a velocity of
        \SI{18}{\meter\per\second} relative to the water.
    The river has a uniform velocity of \SI{6.0}{\meter\per\second}
        due east.
    Determine the boat's velocity relative to an observer on the shore.
\end{question}
\begin{solution}
    N/A
\end{solution}


\begin{question}[ID=relative-C-Q03,topic=relative-motion,difficulty=C]
    A plane is heading  due south at a velocity of
        \SI{110}{\meter\per\second} relative to the air.
    There is a wind heading due north at a velocity of
        \SI{25}{\meter\per\second} with respect to the earth.
    Determine the plane's velocity relative to the earth.
\end{question}
\begin{solution}
    N/A
\end{solution}


\begin{question}[ID=relative-C-Q04,topic=relative-motion,difficulty=C]
    A cannibal is floating down the river in his canoe at a velocity
        of \SI{7.05}{\meter\per\second} due north.
    He shoots a poison dart from his blowgun at a rabbit on the river
        bank.
    The shot is due west at a speed of \SI{31.0}{\meter\per\second}
        with respect to the boat.
    Relative to the rabbit that is about to die, what is the
        velocity of the blowgun dark?
\end{question}
\begin{solution}
    N/A
\end{solution}


\endinput

