

%% Free Fall
%%------------------------------------------------
    
%% NOTE: Check that displacement of air is non-neglible

\begin{question}[ID=falling-A-Q01,topic=kinematics,difficulty=A]
    A man is standing on top of a \SI{64}{\meter} tower.
    He throws a baseball straight up at a speed of
        \SI{21.0}{\meter\per\second}.
    How long does it take to reach the ground and how fast
        is it going when it it hits the ground?
    (Ignore air resistance)
\end{question}
\begin{solution}
    \begin{enumerate*}
        \item \SI{6.34}{\second}
        \item \SI{41.2}{\meter\per\second}
    \end{enumerate*}
\end{solution}


\begin{question}[ID=falling-A-Q02,topic=kinematics,difficulty=A]
    A woman is standing on top of a \SI{110}{\meter} cliff.
    She throws a rock straight down at a speed of
        \SI{8.5}{\meter\per\second}.
    How long does it take to reach the ground and how fast
        is it going when it hits the ground?
\end{question}
\begin{solution}
    \begin{enumerate*}
        \item \SI{3.95}{\second}
        \item \SI{47.2}{\meter\per\second}
    \end{enumerate*}
\end{solution}


\begin{question}[ID=falling-A-Q03,topic=kinematics,difficulty=A]
    A man is sitting on top of a large palm tree that is
        \SI{21.0}{\meter} high.
    He throws a coconut straight down at a passing tourist
        at a speed of \SI{17.5}{\meter\per\second}.
    How long does it take to reach the ground and how fast
        is it going when it hits the ground?
    (Ignore air resistance)
\end{question}
\begin{solution}
    \begin{enumerate*}
        \item \SI{0.95}{\second}
        \item \SI{26.8}{\meter\per\second}
    \end{enumerate*}
\end{solution}

\begin{question}[ID=falling-B-Q01,topic=kinematics,difficulty=B]
    A water balloon is dropped from the top of a
        \SI{1000}{\meter} tower.
    How fast is it going when it is exactly
        \SI{250}{\meter} above the ground?
    (Ignore air resistance)
\end{question}
\begin{solution}
    \SI{121}{\meter\per\second}
\end{solution}


\begin{question}[ID=falling-B-Q02,topic=kinematics,difficulty=B]
    A hot air balloon is at a height of \SI{1370}{\meter}
        and descending at a constant rate of \SI{520}{\meter\per\minute}
        when a water balloon is dropped from the basket of the balloon.
    How long does it take the water balloon to hit the ground
        and how fast is it going when it hits?
\end{question}
\begin{solution}
    \begin{enumerate*}
        \item \SI{15.8}{\second}
        \item \SI{164}{\meter\per\second}
    \end{enumerate*}
\end{solution}


\begin{question}[ID=falling-B-Q03,topic=kinematics,difficulty=B]
    A skydiver at \SI{1250}{\meter} is falling at a terminal velocity
        of \SI{56}{\meter\per\second} when he retrieves a rock from
        his back and throws it straight down at \SI{11}{\meter\per\second}.
    Assume the rock never reaches terminal velocity.
    How long does it take the rock to hit the ground and how fast
        is the rock going when it hits?
\end{question}
\begin{solution}
    \begin{enumerate*}
        \item \SI{10.5}{\second}
        \item \SI{170}{\meter\per\second}
    \end{enumerate*}
\end{solution}

\begin{question}[ID=falling-B-Q04,topic=kinematics,difficulty=B]
    %% Breaking sound barrier
    A jet plane launches a weapon by flying straight up at a speed
        of \SI{330}{\meter\per\second}.
    When it reaches an altitude of \SI{3200}{\meter}, the bomb
        is released and the jet flies off.
    How long does it take the bomb to hit the ground and how
        fast is it going at the moment of impact.
\end{question}
\begin{solution}
    \begin{enumerate*}
        \item \SI{75.9}{\second}
        \item \SI{414}{\meter\per\second}
    \end{enumerate*}
\end{solution}


\begin{question}[ID=falling-C-Q01,topic=kinematics,difficulty=C]
    A rock is dropped from the top of a \SI{68.4}{\meter} tall
        building.
    How long does it take to hit the ground and what is the
        velocity of the rock as it strikes the ground?
\end{question}
\begin{solution}
    \begin{enumerate*}
        \item \SI{3.7}{\second}
        \item \SI{36.6}{\meter\per\second}
    \end{enumerate*}
\end{solution}


\begin{question}[ID=falling-C-Q02,topic=kinematics,difficulty=C]
    A bowling balling ball is dropped from a helicopter hovering
        at \SI{2500}{\meter}.
    How long does it take the bowling ball to hit the ground
        and what is the velocity as it strikes the ground?
\end{question}
\begin{solution}
    \begin{enumerate*}
        \item \SI{22.6}{\second}
        \item \SI{221}{\meter\per\second}
    \end{enumerate*}
\end{solution}


\begin{question}[ID=falling-C-Q03,topic=kinematics,difficulty=C]
    A rock is dropped from the edge of a cliff.
    It takes the rock exactly \SI{2.88}{\second}    
        to hit the water below.
    How high is the cliff and how fast is the rock going
        when it hits the water?
\end{question}
\begin{solution}
    \begin{enumerate*}
        \item \SI{40.6}{\meter}
        \item \SI{28.2}{\meter\per\second}
    \end{enumerate*}
\end{solution}


\begin{question}[ID=falling-C-Q04,topic=kinematics,difficulty=C]
    A rock is dropped from the edge of a cliff.
    When it hits the water, it is traveling at
        \SI{-67.0}{\meter\per\second}.
    How high is the cliff and how long does it take
        the rock to hit the water?
\end{question}
\begin{solution}
    \begin{enumerate*}
        \item \SI{228}{\meter}
        \item \SI{6.8}{\second}
    \end{enumerate*}
\end{solution}


\endinput

