

%% Impulse
%%------------------------------------------------

%% NOTE: ballistic pendulum by Benjamin Robins

\begin{question}[ID=impulse-A-Q01,topic=impulse,difficulty=A]
    An \SI{8.0}{\gram} bullet is fired into a
        \SI{2.5}{\kilo\gram} pendulum bob,
        which is initially at rest and becomes
        embedded in the bob.
    The pendulum then rises a vertical distance of
        \SI{6.0}{\centi\meter}.
    What was the initial speed of the bullet?
\end{question}
\begin{solution}
    N/A
\end{solution}


\begin{question}[ID=impulse-A-Q02,topic=impulse,difficulty=A]
    A \SI{5.5}{\gram} dart is fired into a block of wood with
        a mass of \SI{22.6}{\gram}.
    The wood block is initially at rest on a \SI{1.5}{\meter}
        tall post.
    After the collision, the wood block and dart land 
        \SI{2.5}{\meter} from the base of the post.
    Find the initial speed of the dart.
\end{question}
\begin{solution}
    N/A
\end{solution}


\begin{question}[ID=impulse-A-Q03,topic=impulse,difficulty=A]
    A \SI{1400}{\kilo\gram} car, heading north at
        \SI{\kilo\meter\per\hour}, collides inelastically with
        a \SI{2500}{\kilo\gram} truck traveling east at
        \SI{33}{\kilo\meter\per\hour}.
    What is the vehicles final velocity?
\end{question}
\begin{solution}
    N/A
\end{solution}


\begin{question}[ID=impulse-A-Q04,topic=impulse,difficulty=A]
    A \SI{2.0}{\kilo\gram} block moving at \SI{8.0}{\meter\per\second}
        on a frictionless surface collides elastically with a block
        at rest.
    The first block moves in the same direction at
        \SI{2.0}{\meter\per\second}.
    What is the second block's mass?
\end{question}
\begin{solution}
    N/A
\end{solution}


\begin{question}[ID=impulse-B-Q01,topic=impulse,difficulty=B]
    Two carts with masses of \SI{4.0}{\kilo\gram} and 
        \SI{3.0}{\kilo\gram} move towards each other on
        a frictionless track with speeds of
        \SI{5.0}{\meter\per\second} and
        \SI{4.0}{\meter\per\second} respectively.
    The cars stick together after colliding head-on.
    Find the final speed.
\end{question}
\begin{solution}
    N/A
\end{solution}


\begin{question}[ID=impulse-B-Q02,topic=impulse,difficulty=B]
    A \SI{25.0}{\kilo\gram} bumper car moving to the right
        at \SI{5.00}{\meter\per\second} overtakes and collides
        with a \SI{25.0}{\kilo\gram} bumper car moving to the
        right.
    After the collision, the \SI{25.0}{\kilo\gram} bumper
        car slows to \SI{1.50}{\meter\per\second} to
        the right, and the \SI{35.0}{\kilo\gram} car
        moves at \SI{4.5}{\meter\per\second} to the right.
    Find the velocity of the \SI{35.0}{\kilo\gram} bumper
        car before the collision.
\end{question}
\begin{solution}
    N/A
\end{solution}


\begin{question}[ID=impulse-B-Q03,topic=impulse,difficulty=B]
    An \SI{8500}{\kilo\gram} railway car moves right at
        \SI{45}{\meter\per\second}, and a \SI{9800}{\kilo\gram}
        railway car moves left at \SI{3.9}{\meter\per\second}.
    The cars collide and stick together.
    \begin{enumerate*}[label=\arabic*)]
        \item What is the final velocity of the system?
        \item What is the change in kinetic energy for the two railway cars?
    \end{enumerate*}
\end{question}
\begin{solution}
    N/A
\end{solution}


\begin{question}[ID=impulse-B-Q04,topic=impulse,difficulty=B]
    An \SI{88}{\kilo\gram} fullback moving east with a speed
        of \SI{5.0}{\meter\per\second} is tackled by a
        \SI{97}{\kilo\gram} opponent running west at
        \SI{3.0}{\meter\per\second}.
    %% NOTE: You would only use the term perfect for elastic?
    The collision is perfect inelastic.
    \begin{enumerate*}[label=\arabic*)]
        \item Calculate the velocity of the players just after the tackle.
        \item Calculate the decrease in kinetic energy during the collision.
    \end{enumerate*}
\end{question}
\begin{solution}
    N/A
\end{solution}


\begin{question}[ID=impulse-B-Q05,topic=impulse,difficulty=B]
    A \SI{16.2}{\gram} bullet is fired from a \num{45} caliber
        handgun at a speed of \SI{270}{\meter\per\second} into
        a \SI{1.10}{\kilo\gram} block of wood.
    The bullet is embedded in the wood and the wood and bullet
        fly off the table.
    How fast is the block of wood and bullet moving as a result
        of the collision?
\end{question}
\begin{solution}
    N/A
\end{solution}


\begin{question}[ID=impulse-B-Q06,topic=impulse,difficulty=B]
    Two cars with masses of \SI{4.0}{\kilo\gram} and
        \SI{3.0}{\kilo\gram} move towards each other on
        a frictionless track with speeds of
        \SI{5.0}{\meter\per\second} and
        \SI{4.0}{\meter\per\second} respectively.
    The cars stick together after colliding head-on.
    Find the final speed.
\end{question}
\begin{solution}
    N/A
\end{solution}


\begin{question}[ID=impulse-C-Q01,topic=impulse,difficulty=C]
    A \SI{1350}{\kilo\gram} car is moving east with velocity of
        \SI{22}{\meter\per\second} when it collides with a wall
        and is brought to rest in \SI{0.28}{\second}.
    Find the force exerted on the car during the collision.
\end{question}
\begin{solution}
    N/A
\end{solution}


\begin{question}[ID=impulse-C-Q02,topic=impulse,difficulty=C]
    A \SI{0.50}{\kilo\gram} object is at rest.
    A \SI{3.00}{\newton} force to the right acts on 
        the object during a time interval of \SI{1.50}{\second}.
    What is the velocity of the object at the end of the interval?
\end{question}
\begin{solution}
    N/A
\end{solution}


\begin{question}[ID=impulse-C-Q03,topic=impulse,difficulty=C]
    A \SI{0.15}{\kilo\gram} baseball moving at
        \SI{26}{\meter\per\second} is slowed to a stop
        by a catcher who exerts a constant force of
        \SI{-390}{\newton}.
    How long does it take this force to stop the ball.
\end{question}
\begin{solution}
    N/A
\end{solution}


\begin{question}[ID=impulse-C-Q04,topic=impulse,difficulty=C]
    A \SI{50}{\gram} shell fired from a \SI{3.00}{\kilo\gram} rifle
        has a speed of \SI{400}{\meter\per\second}.
    With what velocity does the rifle recoil in the opposite direction?
\end{question}
\begin{solution}
    N/A
\end{solution}


\endinput

