

%% Torque
%%------------------------------------------------

\begin{question}[ID=torque-A-Q01,topic=torque,difficulty=A]
    A uniform \SI{5.00}{\meter} long horizontal beam that
        weights \SI{445}{\newton} is attached to a wall
        by a pin connection that allows the beam to rotate.
    Its far end is supported by a cable that makes an angle
        of \ang{35} with the horizontal, and a \SI{625}{\newton}
        person is standing \SI{1.10}{\meter} from the pin.
    Find the force in the cable, FT, and the force exerted
        on the beam by the wall, R, if the beam is in equilibrium.
\end{question}
\begin{solution}
    \SI{133}{\meter} \ang{2} west of north.
\end{solution}


\begin{question}[ID=torque-A-Q02,topic=torque,difficulty=A]
    A floodlight with a mass of \SI{20.0}{\kilo\gram} is supported
        at the end of a horizontal beam that is hinged to a vertical pole.
    A cable that makes an angle of \ang{30} with the beam is attached to
        the pole to help support the floorlight.
    Find the force provided by the cable and the horizontal and vertical
        forces exerted on the beam by the pole.
    %% tikz diagram
\end{question}
\begin{solution}
    N/A
\end{solution}


\begin{question}[ID=torque-A-Q03,topic=torque,difficulty=A]
    A uniform \SI{10.0}{\newton} frame is supported as shown in the
        figure to the right.
    Find the force in the two cords ($T_1$ and $T_2$) and the magnitude
        of the horizontal force at $P$ that are required to hold the frame
        in this position.
    %% tikz diagram
\end{question}
\begin{solution}
    N/A
\end{solution}


\begin{question}[ID=torque-B-Q01,topic=torque,difficulty=B]
    A wooden bucket filled with water has a mass of \SI{75}{\kilo\gram}
        and is attached to a rope that is wound around a cylinder with
        a radius of \SI{0.075}{\meter}.
    A crank with a turning radius of \SI{0.25}{\meter} is attached to
        the end of the cylinder.
    What minimum force directed perpendicularly to the crank handle
        is require to raise the bucket?
\end{question}
\begin{solution}
    N/A
\end{solution}


\begin{question}[ID=torque-B-Q02,topic=torque,difficulty=B]
    The bolts on the cylinder head of an engine require tightening to
        a torque of \SI{88}{\newton\meter}.
    \begin{enumerate*}[label=\arabic*)]
        \item If a wrench is \SI{28}{\centi\meter} long, what
            force perpendicular to the wrench must the mechanic
            exert at its end?
        \item What force is generated at at the ends if it has
            a diameter of \SI{15}{\milli\meter}?
    \end{enumerate*}
    %% Tikz diagram
\end{question}
\begin{solution}
    N/A
\end{solution}


\begin{question}[ID=torque-B-Q03,topic=torque,difficulty=B]
    To loosen the bolts on a tire, you can use a tire iron
        and jump on the tire iron to loosen the bolts.
    It requires a \SI{75}{\kilo\gram} person jumping on the
        iron \SI{25}{\centi\meter} from the center of the bolt.
    Instead of this method, your physics teacher recommended carrying
        a piece of pipe in the trunk.
    This piece fits over the tire iron and extends the handle.
    If you can loosen the bolts by pushing at an angle of \ang{80}
        on the pipe a distance of \SI{85}{\centi\meter} the bolt,
        how much force is needed?
\end{question}
\begin{solution}
    N/A
\end{solution}


\begin{question}[ID=torque-B-Q04,topic=torque,difficulty=B]
    A window washer is standing on a scaffold supported by a vertical
        rope at each end.
    The scaffold weighs \SI{245}{\newton} and is \SI{3.20}{\meter} long.
    What is the force each rope exerts on teh scaffold when the
        \SI{715}{\newton} worker stands \SI{1.20}{\meter} from
        one end of the scaffold?
\end{question}
\begin{solution}
    N/A
\end{solution}


\begin{question}[ID=torque-B-Q05,topic=torque,difficulty=B]
    A uniform bridge \SI{20.0}{\meter} long and weighing \SI{4.00e5}{\newton}
        is supported by two pillars located \SI{3.00}{\meter} from each end.
    If a \SI{1.96e4}{\newton} is parked \SI{8.00}{\meter} from one end of
        the bridge, how much force does each pillar exert?
\end{question}
\begin{solution}
    N/A
\end{solution}


\begin{question}[ID=torque-C-Q01,topic=torque,difficulty=C]
    A perfectly balanced meter stick is hanging from a string
        at the \SI{50.0}{\centi\meter} mark.
    You place a \SI{250}{\gram} mass at the \SI{72.4}{\centi\meter} mark.
    \begin{enumerate*}[label=\arabic*)]
        \item What is the torque generated by the mass (in \si{\newton\meter})?
        \item Where on the meter stick do you need to hang a \SI{350}{\gram}
            mass to bring the meter stick back into perfect balance?
    \end{enumerate*}
\end{question}
\begin{solution}
    N/A
\end{solution}


\begin{question}[ID=torque-C-Q02,topic=torque,difficulty=C]
    A perfectly balanced meter stick has a mass of \SI{94.2}{\gram}.
    You hang the meter stick at the \SI{30.0}{\meter} mark by a thin string.
    Where do you need to hang a \SI{200}{\gram} mass to bring the meter
        stick into equilibrium?
\end{question}
\begin{solution}
    N/A
\end{solution}


\begin{question}[ID=torque-C-Q03,topic=torque,difficulty=C]
    A perfectly balanced meter stick is hanging from a string at
        the \SI{50.0}{\centi\meter} mark.
    You place a \SI{125}{\gram} mass at the \SI{90.0}{\centi\meter} mark
        and a \SI{250}{\gram} mass at the \SI{75.0}{\centi\meter} mark.
    Where do you need to hang a \SI{500}{\gram} mass to bring the meter
        stick into equilibrium?
\end{question}
\begin{solution}
    N/A
\end{solution}


\begin{question}[ID=torque-C-Q04,topic=torque,difficulty=C]
    A non-uniformly dense meter stick has mass of \SI{95.4}{\gram}.
    The center of gravity of the meter stick is at
        the \SI{51.1}{\centi\meter} mark.
    You hang the meter stick at the \SI{35.0}{\centi\meter} mark
        a thin string.
    Where do you need to hang a \SI{75.0}{\gram} mass to bring
        the meter stick into equilibrium?
\end{question}
\begin{solution}
    N/A
\end{solution}


\begin{question}[ID=torque-C-Q04,topic=torque,difficulty=C]
    Tweedle-Dee, who has a mass of \SI{75}{\kilo\gram}, sits
        at the end of a \SI{4}{\meter} long seesaw, \SI{2}{\meter}
        from the fulcrum.
    Tweedle-Dum sits \SI{1.80}{\meter} from the fulcrum
        on the other side and brings the seesaw into perfect balance.
    What is Tweedle-Dum's mass?
\end{question}
\begin{solution}
    N/A
\end{solution}


\endinput

