

\sisetup{separate-uncertainty,bracket-numbers = false}

%% Basic Error Analysis
%%------------------------------------------------

\begin{question}[ID=EA01,topic=units,difficulty=easy]
    A rectangular plate has a length of \SI{21.3\pm 0.2}{\centi\meter}
        and a width of \SI{9.8\pm 0.1}{\centi\meter}
    Calculate the area of the plate, including its uncertainty.
\end{question}
\begin{solution}
    \SI{208.7 \pm 2.9 }{\centi\meter\squared}
\end{solution}

\begin{question}[ID=EA02,topic=units,difficulty=easy]
    A farmer measures the perimeter of a rectangular field.
    The length of each long side of the rectangle is found to be \SI{38.44\pm 0.4}{\meter}
        and the length of each short side is found to be \SI{19.5\pm 0.8}{\meter}.
    Calculate the perimeter and area of the field, including its uncertainty.
\end{question}
\begin{solution}
    $C = \SI{115.9 \pm 1.3}{\meter}$,
    $A = \SI{750 \pm 32 }{\meter\squared}$
\end{solution}

\begin{question}[ID=EA03,topic=units,difficulty=easy]
    The radius of a circle is measured to be \SI{10.5\pm 0.2}{\meter}.
    Calculate the area and circumference of the circle, including their uncertainty.
\end{question}
\begin{solution}
    $A = \SI{346.4 \pm 9.3 }{\meter\squared}$
    $C = \SI{66.0 \pm 0.5}{\meter}$
\end{solution}

%% Apply in unique manner
%%------------------------------------------------
\begin{question}[ID=EA04,topic=units,difficulty=easy]
    The fine structure constant represents the most
        accurate measurement in human history and has
        been measured to 0.32 parts per billion.
    The city of Baltimore is approximately
        \SI{60}{\kilo\meter} from Washington D.C.
    If you were to measure the distance from Baltimore to
        Washington D.C. to the same level of uncertainty as
        the fine structure constant, what would the uncertainty be?
    Is this even possible?
\end{question}
\begin{solution}
    \SI{1.92e-5}{\meter} or approx. \SI{20}{\micro\meter}
\end{solution}

\endinput

