

%% Introductory Material
%%------------------------------------------------

\begin{question}[ID=IM-Q01,topic=intro,difficulty=C]
    Give two examples of ways that physicists model the physical world.
\end{question}
\begin{solution}
    N/A
\end{solution}


\begin{question}[ID=IM-Q02,topic=intro,difficulty=C]
    What is the difference between a vector and a scalar?
    Give an example of each.
\end{question}
\begin{solution}
    N/A
\end{solution}


\begin{question}[ID=IM-Q03,topic=intro,difficulty=C]
    Define accuracy and precision and explain the difference between the two.
\end{question}
\begin{solution}
    N/A
\end{solution}


\begin{question}[ID=IM-Q04,topic=intro,difficulty=C]
    What are guard digits and why do we use them?
\end{question}
\begin{solution}
    N/A
\end{solution}


\begin{question}[ID=IM-Q05,topic=intro,difficulty=C]
    What are the seven base units in the International System of Units?
\end{question}
\begin{solution}
    meter (\si{\meter}), kilogram (\si{\kilo\gram}),
    second (\si{\second}), mole (\si{\mole}),
    kelvin (\si{\kelvin}), candela (\si{\candela}),
    ampere (\si{\ampere})
\end{solution}


\begin{question}[ID=IM-Q06,topic=intro,difficulty=C]
    Why should we do an order-of-magnitude estimation when
        doing a math-based problem?
\end{question}
\begin{solution}
    N/A
\end{solution}


\begin{question}[ID=IM-Q07,topic=intro,difficulty=C]
    When we solve a physics problem, we work through 5 steps.
    What are those 5 steps?
\end{question}
\begin{solution}
    N/A
\end{solution}


\begin{question}[ID=IM-Q08,topic=intro,difficulty=C]
    What is a controlled experiment?
    Explain how controls are used in such an experiment?
\end{question}
\begin{solution}
    N/A
\end{solution}


\endinput

