

%% Vectors
%%------------------------------------------------

\begin{question}[ID=vectors-A-Q01,topic=vectors,difficulty=A]
    A plane takes off at an angle of \ang{35}
        at a speed of \SI{120}{\meter\per\second}.
    It travels at that speed and angle for \SI{4}{\minute}.
    The plane then changes to an angle of \ang{15}
        and continues for another \SI{7}{\minute} at the
        same speed.
    What is the displacement of the plane at the end of
        the \SI{11}{\minute}.
\end{question}
\begin{solution}
    N/A
\end{solution}


\begin{question}[ID=vectors-A-Q02,topic=vectors,difficulty=A]
    A man drives his car heading \ang{65} north of east
        at a speed of \SI{22}{\meter\per\second} for 
        \SI{80}{\minute}.
    The man stops to fill up the gas tank for \SI{10}{\minute}.
    He gets back in the car and makes a turn and drives due east
        at a speed of \SI{26}{\meter\per\second} for
        \SI{90}{\minute}.
    What is the displacement of the car and driver?
\end{question}
\begin{solution}
    N/A
\end{solution}


\begin{question}[ID=vectors-A-Q03,difficulty=A]
    A helicopter ascends at a rate of \SI{85}{\kilo\meter\per\hour}
        at an angle of \ang{35} with respect to the ground
        for \SI{12}{\minute}.
    It then converts to level flight and travels at
        \SI{110}{\kilo\meter\per\hour} for another
        \SI{32}{\minute}.
    What is the displacement of the helicopter after this
        \SI{44}{\minute} trip?
\end{question}
\begin{solution}
    N/A
\end{solution}

\begin{question}[ID=vectors-B-Q01,topic=vectors,difficulty=B]
    A hiker walks \SI{702}{\meter} due north and then turns
        \ang{45.0} to the right and continues for
        another \SI{407}{\meter}.
    He then turns due west and walks another \SI{505}{\meter}.
    What is the displacement of the hiker?
\end{question}
\begin{solution}
    N/A
\end{solution}


\begin{question}[ID=vectors-B-Q02,topic=vectors,difficulty=B]
    A hiker walks \SI{500}{\meter} at an angle of \ang{30}
        north of east.
    He then turns due north and continues for \SI{800}{\meter}.
    He then turns \ang{45} to the left and continues for
        another \SI{400}{\meter}.
    Finally, he turns due west and walks another \SI{200}{\meter}.
    What is the displacement of the hiker?
\end{question}
\begin{solution}
    \SI{133}{\meter} \ang{2} west of north.
\end{solution}


\begin{question}[ID=vectors-B-Q03,topic=vectors,difficulty=B]
    A dog runs \SI{1500}{\meter} due west.
    She then turns due north and runs another \SI{2200}{\meter}.
    The dog then turns \ang{35} south of east and
        continues for another \SI{1100}{\meter}.
    What is the displacement of the dog?
\end{question}
\begin{solution}
    N/A
\end{solution}


\begin{question}[ID=vectors-B-Q04,topic=vectors,difficulty=B]
    A hiker walks \SI{575}{\meter} due west and then turns
        \ang{30} to the right and continues for another
        \SI{815}{\meter}.
    He then turns due north and continues for \SI{745}{\meter}.
    What is the displacement of the hiker?
\end{question}
\begin{solution}
\end{solution}


\begin{question}[ID=vectors-C-Q01,topic=vectors,difficulty=C]
    A car drives under a helicopter that is flying at
        \SI{75}{\kilo\meter\per\hour} and rising at
        an angle of \ang{25} with respect to the ground.
    How fast must the car drive to keep directly underneath
        the helicopter?
\end{question}
\begin{solution}
    \SI{68}{\kilo\meter\per\hour}
\end{solution}


\begin{question}[ID=vectors-C-Q02,topic=vectors,difficulty=C]
    A tiger leaps into the air with a speed of
        \SI{24.6}{\meter\per\second} at an angle
        of \ang{35}.
    What are the horizontal and vertical components of
        the rocket's velocity?
\end{question}
\begin{solution}
    $v_{x} = \SI{20.3}{\meter\per\second}$,
    $v_{y} = \SI{12.3}{\meter\per\second}$
\end{solution}


\begin{question}[ID=vectors-C-Q03,topic=vectors,difficulty=C]
    A rocket is launched into the air with a velocity of
        \SI{220}{\meter\per\second} at an angle of \ang{75}.
    What are the horizontal and vertical components of
        the rocket's velocity?
\end{question}
\begin{solution}
    $v_{x} = \SI{57}{\meter\per\second}$,
    $v_{y} = \SI{213}{\meter\per\second}$
\end{solution}


\endinput

