

%% Energy
%%------------------------------------------------

\begin{question}[ID=energy-A-Q01,topic=energy,difficulty=A]
    Tarzan and Jane, whose total mass is \SI{130}{\kilo\gram},
        start their swing on a \SI{5.0}{\meter} long vine when
        the vine is at an angle of \SI{30}{\degree} with the
        horizontal.
    At the bottom of the arc, Jane, whose mass is \SI{50}{\kilo\gram}
        releases the vine.
    What is the maximum height at which Tarzan can land on a branch
        after his swing continues?
\end{question}
\begin{solution}
    N/A
\end{solution}


\begin{question}[ID=energy-A-Q02,topic=energy,difficulty=A]
    A ball of mass \SI{522}{\kilo\gram} starts at rest down a
        frictionless track, as shown.
    It leaves the track horizontally, striking the ground.
    \begin{enumerate*}[label=\arabic*)]
        \item What is the speed of the ball when it leaves the track?
        \item What is the height, $h$, of the ball when it is released?
    \end{enumerate*}
    %\begin{tikzpicture}
    % use graph to draw track, anchor a filled circle
    % with mass label, place labels for top and bottom of slide
    % and where the ball lands (use parabola).
    % show dotted line for path of ball
    %\end{tikzpicture}
\end{question}
\begin{solution}
    N/A
\end{solution}


\begin{question}[ID=energy-A-Q03,topic=energy,difficulty=A]
    A \SI{25}{\kilo\gram} child on a \SI{2}{\meter} long swing
        is released from rest when the swing supports makes an
        angle of \SI{30}{\degree} with the vertical.
    \begin{enumerate*}[label=\arabic*)]
        \item What is the maximum potential energy
            associated with the child?
        \item What is the child's total mechanical energy?
        \item If the speed of the child at the lowest position
            is \SI{2.00}{\meter\per\second}, what is the change
            in mechanical energy due to friction?
    \end{enumerate*}
\end{question}
\begin{solution}
    N/A
\end{solution}


\begin{question}[ID=energy-A-Q04,topic=energy,difficulty=A]
    A student wearing frictionless in-line skates on a horizontal
        surface is pushed by a friend with a constant force
        of \SI{45}{\newton}.
    How far must the student be pushed, starting from rest, so that
        her final kinetic energy is \SI{352}{\joule}?
\end{question}
\begin{solution}
    N/A
\end{solution}


\begin{question}[ID=energy-A-Q05,topic=energy,difficulty=A]
    Tarzan is \SI{15}{\meter} above the ground in a tree
        holding onto a \SI{5.0}{\meter} long vine.
    The vine makes an angle of \SI{30}{\degree} with
        the horizontal.
    Tarzan drops from the tree and swings from the vine.
    At the bottom of the arc, Tarzan, whose mass is
        \SI{77}{\kilo\gram}, releases the vine.
    How far does he travel horizontally from where he released
        the vine when he hits the jungle floor?
\end{question}
\begin{solution}
    N/A
\end{solution}


\begin{question}[ID=energy-B-Q01,topic=energy,difficulty=B]
    A bike rider approaches a hill with speed
        of \SI{8.5}{\meter\per\second}.
    The total mass of the bike and rider is
        \SI{85}{\kilo\gram}.
    Assuming there is no friction, at what
        height will the bike and rider come
        to a stop?
\end{question}
\begin{solution}
    N/A
\end{solution}


\begin{question}[ID=energy-B-Q02,topic=energy,difficulty=B]
    A \SI{100}{\gram} arrow is pulled back \SI{30.0}{\centi\meter}
        against a bowstring.
    The bowstring's force constant is \SI{1250}{\newton\per\meter}.
    What speed will the arrow leave the bow?
\end{question}
\begin{solution}
    N/A
\end{solution}


\begin{question}[ID=energy-B-Q03,topic=energy,difficulty=B]
    A \SI{3.0}{\kilo\gram} rock is high enough above the ground
        to have \SI{175}{\joule} of potential energy when it
        is dropped from rest.
    How fast is the rock going when it is exactly \SI{1.0}{\meter}
        above the ground?
\end{question}
\begin{solution}
    N/A
\end{solution}


\begin{question}[ID=energy-B-Q04,topic=energy,difficulty=B]
    A dart of mass \SI{0.100}{\kilo\gram} is pressed against the spring
        of a toy dark gun.
    The spring has a spring constant of \SI{250}{\newton\per\meter}.
    The spring is compressed \SI{0.60}{\centi\meter} and released.
    If the dart detaches from the spring when the spring reaches
        its natural length, what speed does the dart acquire?
\end{question}
\begin{solution}
    N/A
\end{solution}


\begin{question}[ID=energy-B-Q05,topic=energy,difficulty=B]
    A \SI{0.250}{\kilo\gram} block on a vertical spring with a
        spring constant of \SI{5000}{\newton\per\meter} is pushed
        downward, compressing the spring \SI{0.100}{\meter}.
    When released, the block leaves the spring and travels upward
        vertically.
    How high does it rise above the points of release?
\end{question}
\begin{solution}
    N/A
\end{solution}


\begin{question}[ID=energy-B-Q06,topic=energy,difficulty=B]
    Initially sliding with a speed of \SI{2.2}{\meter\per\second},
        a \SI{1.8}{\kilo\gram} block collides with a spring and
        compresses it \SI{0.31}{\meter} before coming to a rest.
    What is the force constant of the spring?
\end{question}
\begin{solution}
    N/A
\end{solution}


\begin{question}[ID=energy-C-Q01,topic=energy,difficulty=C]
    A ball starts from rest at the top of a ramp that
        is \SI{3.0}{\meter}.
    The ball has a mass of \SI{0.60}{\kilo\gram}.
    \begin{enumerate*}[label=\arabic*)]
        \item What is the potential energy of the ball at the top of the ramp?
        \item What is the speed of the ball at the bottom of the ramp?
    \end{enumerate*}
\end{question}
\begin{solution}
    N/A
\end{solution}


\begin{question}[ID=energy-C-Q02,topic=energy,difficulty=C]
    A spring has a force constant of \SI{420}{\newton\per\meter}.
    What is the potential energy stored in the spring when the
        spring is stretched \SI{4.00}{\centi\meter}?
\end{question}
\begin{solution}
    N/A
\end{solution}


\begin{question}[ID=energy-C-Q03,topic=energy,difficulty=C]
    What is the total mechanical energy of a ball that has a mass
        of \SI{0.45}{\kilo\gram} and that is \SI{2.3}{\meter}
        above the ground and falling at a speed
        of \SI{8.5}{\meter\per\second}.
\end{question}
\begin{solution}
    N/A
\end{solution}


\begin{question}[ID=energy-C-Q04,topic=energy,difficulty=C]
    A \SI{5.5}{\kilo\gram} block is attached to a bungee cord
        that has a spring coefficient of \SI{44.1}{\newton\per\meter}.
    When the bungee hangs from a pole, it stretches \SI{2.45}{\meter}
        and is \SI{1.55}{\meter} off the ground.
    What is the block's total potential energy?
\end{question}
\begin{solution}
    N/A
\end{solution}


\begin{question}[ID=energy-C-Q05,topic=energy,difficulty=C]
    A \SI{1.20}{\kilo\gram} ball sits on the top of a bridge that
        is \SI{18}{\meter} above the ground below.
    The ball is dropped off of the bridge.
    What is the total mechanical energy of the ball when it is
        \SI{12}{\meter} above the ground?
\end{question}
\begin{solution}
    N/A
\end{solution}


\endinput

