

%% Frictional forces
%%------------------------------------------------

\begin{question}[ID=friction-A-Q01,topic=friction,difficulty=A]
    Consider the two-body situation below.
    A \SI{3.5e2}{\kilo\gram} crate, $m_1$, rests on an inclined
        plane and is connected by a light string to a
        \SI{1.00e2}{\kilo\gram} mass, $m_2$.
    This second mass, $m_2$, is suspended over a frictionless
        pulley.
    The incline angle is \SI{30}{\degree} and the surface has a
        coefficient of friction of \num{0.210}.
    Determine the acceleration of the system and the tension
        in the string.
    %\begin{tikzpicture}
    % draw atwood on incline plane and one free hanging
    %\end{tikzpicture}
\end{question}
\begin{solution}
    N/A
\end{solution}


\begin{question}[ID=friction-A-Q02,topic=friction,difficulty=A]
    The coefficient of static friction between the \SI{3.00}{\kilo\gram}
        crate and the \SI{35}{\degree} incline shown is \num{0.300}.
    What is the magnitude of the minimum force, $F$, that must
        be applied to the perpendicularly to the incline to
        prevent the crate from sliding down the incline?
    %\begin{tikzpicture}
    % draw box on incline with additional normal force vector
    %\end{tikzpicture}
\end{question}
\begin{solution}
    N/A
\end{solution}


\begin{question}[ID=friction-A-Q03,topic=friction,difficulty=A]
    Consider the two-body situation below.
    A \SI{1.00}{\kilo\gram} hanging mass, $m_2$, is attached to
        a \SI{3.25}{\kilo\gram} mass, $m_1$, at rest on the table.
    The coefficient of friction between the \SI{3.25}{\kilo\gram}
        mass and the table is \num{0.215}.
    Determine the acceleration of the system and the tension
        in the string.
    %\begin{tikzpicture}
    % draw atwood with one mass on flat surface, second free hanging
    %\end{tikzpicture}
\end{question}
\begin{solution}
    N/A
\end{solution}


\begin{question}[ID=friction-A-Q05,topic=friction,difficulty=A]
    Three objects are connected as shown.
    The coefficient of kinetic friction between the block
        $m_2$ and the table is \num{0.350}.
    The objects have masses $m_1=\SI{4.00}{\kilo\gram}$,
        $m_2=\SI{1.00}{\kilo\gram}$, and
        $m_3=\SI{2.00}{\kilo\gram}$.
    \begin{enumerate*}[label=\arabic*)]
        \item Draw a free body diagram of the forces on each object.
        \item Determine the acceleration of each object, including its direction
    \end{enumerate*}
    %\begin{tikzpicture}
    %% table with two masses hanging freely and one mass on table
    %\end{tikzpicture}
\end{question}
\begin{solution}
    N/A
\end{solution}


\begin{question}[ID=friction-A-Q06,topic=friction,difficulty=A]
    Two packing crates of masses \SI{5.00}{\kilo\gram}
        and \SI{10.0}{\kilo\gram} are connect with a light
        string that passes over a frictionless pulley.
    The \SI{5.00}{\kilo\gram} crate lies on a frictionless
        incline of angle \SI{40}{\degree}.
    Find:
    \begin{enumerate*}[label=\arabic*)]
        \item the acceleration of the \SI{5.00}{\kilo\gram} crate
        \item the tension in the string
    \end{enumerate*}
    %\begin{tikzpicture}
    %% atwood machine with inclined plane
    %\end{tikzpicture}
\end{question}
\begin{solution}
    N/A
\end{solution}


\begin{question}[ID=friction-B-Q01,topic=friction,difficulty=B]
    A \SI{12}{\kilo\gram} box sits on an inclined plane that
        is at an angle of \SI{38}{\degree} with the horizontal.
    The coefficient of friction between the box and the plane
        is \num{0.455}.
    \begin{enumerate*}[label=\arabic*)]
        \item Draw a free-body diagram of all the forces acting on the box.
        \item Calculate the frictional force on the box and then,
            if it is moving, calculate the acceleration of the box.
    \end{enumerate*}
\end{question}
\begin{solution}
    N/A
\end{solution}


\begin{question}[ID=friction-B-Q02,topic=friction,difficulty=B]
    A \SI{30}{\kilo\gram} boy sits on an \SI{8}{\kilo\gram} sled
        on a snow covered hill.
    The hill is \SI{40}{\meter} long and makes an angle of
        \SI{24}{\degree} with the horizontal.
    The coefficient of friction between the sled and the snow is
        \num{0.12}.
    Assuming he starts from rest, how fast is the boy going at
        the bottom of the hill?
\end{question}
\begin{solution}
    N/A
\end{solution}


\begin{question}[ID=friction-B-Q03,topic=friction,difficulty=B]
    A \SI{3.2}{\kilo\gram} book sits on a ramp which is at an
        angle of \SI{35}{\degree} with the horizontal.
    It turns out that the ramp is at a point where the book
        will slide if it is raised any amount.
    Knowing this, calculate the coefficient of friction between the
        book and the ramp.
\end{question}
\begin{solution}
    N/A
\end{solution}


\begin{question}[ID=friction-C-Q01,topic=friction,difficulty=C]
    An almost dead, partially decaying zombie has a
        mass of \SI{54}{\kilo\gram}.
    You wrap a rope around its foot and drag it with
        a force of \SI{260}{\newton} at an angle
        of \SI{34}{\degree} to the horizontal.
    The asphalt has a coefficient of friction of \num{0.38}.
    \begin{enumerate*}[label=\arabic*)]
        \item Draw a free-body diagram of the forces acting on the zombie.
        \item Calculate the frictional force on the zombie, and then if it
            is moving, calculate the acceleration of the zombie.
    \end{enumerate*}
\end{question}
\begin{solution}
    N/A
\end{solution}


\begin{question}[ID=friction-C-Q02,topic=friction,difficulty=C]
    You drag a crate with a mass of \SI{25}{\kilo\gram} by pulling
        on a rope with a force of \SI{210}{\newton} at an angle of
        \SI{50}{\degree} with the horizontal.
    The coefficient of static friction between the crate and the
        floor is \num{0.500}.
    \begin{enumerate*}[label=\arabic*)]
        \item Draw a free-body diagram of the forces acting on the crate.
        \item Calculate the frictional force on the crate and then, it
            is moving, calculate the acceleration of the crate.
    \end{enumerate*}
\end{question}
\begin{solution}
    N/A
\end{solution}


\begin{question}[ID=friction-C-Q03,topic=friction,difficulty=C]
    Cave man Fred wants to drag his cave wife Wilma by her hair.
    (I don't know why, it's what cave people did)
    Wilma is a petite \SI{48}{\kilo\gram}.
    Fred pulls Wilma with a force of \SI{205}{\newton} and Wilma's
        hair makes an angle of \SI{45}{\degree} with the cave
        floor and the coefficient of friction between cave woman
        and cave floor is \num{0.430}.
    \begin{enumerate*}[label=\arabic*)]
        \item Draw a free-body diagram of the forces acting on Wilma.
        \item Calculate the frictional force on Wilma and then,
            if she is moving, calculate her acceleration.
    \end{enumerate*}
\end{question}
\begin{solution}
    N/A
\end{solution}


\begin{question}[ID=friction-C-Q04,topic=friction,difficulty=C]
    You drag a crate with a mass of \SI{30}{\kilo\gram} by pulling
        on a rope with a force of \SI{170}{\newton} at an angle
        of \SI{40}{\degree} with the horizontal.
    The coefficient of static friction between the crate and the
        floor is \num{0.460}.
    \begin{enumerate*}[label=\arabic*)]
        \item Draw a free-body diagram of the forces acting on the crate.
        \item Calculate the frictional force on the crate and then,
            if it is moving, calculate the acceleration of the crate.
    \end{enumerate*}
\end{question}
\begin{solution}
    N/A
\end{solution}


\endinput

