

%% Torque
%%------------------------------------------------

\begin{question}[ID=rotational-A-Q01,topic=rotational,difficulty=A]
    A regulation basketball has a \SI{25}{\centi\meter} diameter and may be
        approximated as a thin spherical shell ($I=\frac{2}{3}mR^2$).
    How long will it take a basketball starting from rest to roll
        without slipping \SI{4.0}{\meter} down an incline that makes
        an angle of \ang{30.0} with the horizontal?
\end{question}
\begin{solution}
    N/A
\end{solution}


\begin{question}[ID=rotational-B-Q01,topic=rotational,difficulty=B]
    A \SI{1.5}{\kilo\gram} bicycle tire of radius \SI{0.33}{\meter} starts
        from rest and rolls down from the top of a hill that is \SI{14.8}{\meter} high.
    What is the translational speed of the tire when it reaches the bottom of the hill?
    (Assume that the tire is a hoop with $I=mr^2$.)
\end{question}
\begin{solution}
    N/A
\end{solution}


\begin{question}[ID=rotational-B-Q02,topic=rotational,difficulty=B]
    As part of a kinetic sculpture, a \SI{5.0}{\kilo\gram} hoop with a radius
        of \SI{3.0}{\meter} rolls without slipping.
    If the hoop is given an angular speed of \SI{3.0}{\radian\per\second}
        while rolling on the horizontal and then rolls up a ramp inclined
        at \ang{20.0} with the horizontal, how far does the hoop roll along the incline?
    (Moment of inertia of a hoop is $I=mr^2$.)
\end{question}
\begin{solution}
    N/A
\end{solution}


\begin{question}[ID=rotational-B-Q03,topic=rotational,difficulty=B]
    A coin with a diameter of \SI{3.00}{\centi\meter} rolls up a \ang{30.0} incline.
    The coin starts with an initial angular speed of \SI{60.0}{\radian\per\second}
        and rolls in a straight line without slipping.
    How far does it roll up the inclined plane?
    (Moment of inertia of a disk is $I=\frac{1}{2}mr^2$.)
\end{question}
\begin{solution}
    N/A
\end{solution}


\begin{question}[ID=rotational-C-Q01,topic=rotational,difficulty=C]
    A potter’s wheel of radius \SI{0.50}{\meter} and mass
        \SI{100.0}{\kilo\gram} is freely rotating at \SI{50.0}{rev\per\minute}.
    The potter can stop the wheel in \SI{6.0}{\second} by pressing a
        wet rag against the rim.
    \begin{enumerate*}
        \item What is the angular acceleration of the wheel?
        \item How much torque does the potter apply to the wheel?
    \end{enumerate*}
\end{question}
\begin{solution}
    N/A
\end{solution}


\begin{question}[ID=rotational-C-Q02,topic=rotational,difficulty=C]
    A \SI{30.0}{\kilo\gram} uniform solid cylinder has a radius of \SI{0.180}{\meter}.
    If the cylinder accelerates at \SI{2.30e-2}{\radian\per\second\squared}
        as it rotates about an axis through its center,
        what is the magnitude of the torque acting on the cylinder?
\end{question}
\begin{solution}
    N/A
\end{solution}


\begin{question}[ID=rotational-C-Q03,topic=rotational,difficulty=C]
    The net work done in accelerating a propeller from rest to an
        angular speed of \SI{220}{\radian\per\second} is \SI{3250.0}{\joule}.
    What is the moment of inertial of the propeller?
\end{question}
\begin{solution}
    N/A
\end{solution}


\begin{question}[ID=rotational-C-Q04,topic=rotational,difficulty=C]
    A bicycle tire of radius \SI{0.33}{\meter} and mass \SI{1.5}{\kilo\gram}
        is rotating at \SI{98.7}{\radian\per\second}.
    What torque is necessary to stop the tire in \SI{2.0}{\second}? 
    (moment of inertia for a ring is $I=mR^2$)
\end{question}
\begin{solution}
    N/A
\end{solution}


\endinput

