

%% Power
%%------------------------------------------------

\begin{question}[ID=power-A-Q01,topic=power,difficulty=A]
    What minimum horsepower ($\SI{1}{hp} = \SI{746}{\watt}$)
        must a motor have to be able to drag a
        \SI{310}{\kilo\gram} box along a level floor
        at a speed of \SI{1.20}{\meter\per\second}
        if the coefficient of friction is \num{0.45}?
\end{question}
\begin{solution}
    \SI{164}{\watt} or \SI{3.0}{hp}
\end{solution}


\begin{question}[ID=power-A-Q02,topic=power,difficulty=A]
    You push a \SI{67}{\kilo\gram} box across a floor where the
        coefficient of kinetic friction is \num{0.55}.
    The force you exert is horizontal.
    How much power is needed to push the box at a speed
        of \SI{0.50}{\meter\per\second}?
\end{question}
\begin{solution}
    \SI{181}{\watt}
\end{solution}


\begin{question}[ID=power-A-Q03,topic=power,difficulty=A]
    How much power is needed to drag a \SI{85}{\kilo\gram} box
        across a level floor if you are pulling the box at
        a constant \SI[2.67}{\meter\per\second} and the coefficient
        of kinetic friction is \num{0.475}.
\end{question}
\begin{solution}
    \SI{1056}{\watt}
\end{solution}


\begin{question}[ID=power-B-Q01,topic=power,difficulty=B]
    A \SI{1400}{\kilo\gram} sports car accelerates from rest
        to \SI{95}{\kilo\gram\per\hour} in \SI{7.4}{\second}.
    What is the average power delivered by the engine?
\end{question}
\begin{solution}
    \SI{6.6e4}{\watt}
\end{solution}


\begin{question}[ID=power-B-Q02,topic=power,difficulty=B]
    A shot-putter accelerates a \SI{7.3}{\kilo\gram} shot from
        rest to \SI{14}{\meter\per\second}.
    If this motion takes \SI{1.5}{\second}, what average
        power was developed?
\end{question}
\begin{solution}
    \SI{477}{\watt}
\end{solution}


\begin{question}[ID=power-B-Q03,topic=power,difficulty=B]
    During a workout, a football player ran up the stadium
        stairs in \SI{66}{\second}
    The stairs are \SI{140}{\meter} long and inclined at
        an angle of \SI{32}{\degree}.
    If a typical player has a mass of \SI{95}{\kilo\gram},
        estimate the average power output on the way up.
    Ignore friction and air resistance.
\end{question}
\begin{solution}
    N/A
\end{solution}


\begin{question}[ID=power-B-Q04,topic=power,difficulty=B]
    During a workout, a football player ran up the stadium
        stairs in \SI{66}{\second}.
    The stairs are \SI{140}{\meter} long and inclined at
        an angle of \SI{32}{\degree}
    If a typical player has a mass of \SI{95}{\kilo\gram},
        estimate the average power output on the way up.
    Ignore friction and air resistance.
\end{question}
\begin{solution}
    N/A
\end{solution}


\begin{question}[ID=power-B-Q05,topic=power,difficulty=B]
    A \SI{740}{\kilo\gram} dragster accelerates from rest
        to \SI{24}{\meter\per\second} in \SI{4.5}{\second}.
    What is the average power that was developed in that run?
\end{question}
\begin{solution}
    N/A
\end{solution}


\begin{question}[ID=power-B-Q06,topic=power,difficulty=B]
    A compound bow can accelerate an arrow with a mass of
        \SI{52}{\gram} from rest to \SI{35}{\meter\per\second}
        in \SI{0.44}{\second}.
    How much power is developed launching this arrow?
\end{question}
\begin{solution}
    N/A
\end{solution}


\begin{question}[ID=power-C-Q01,topic=power,difficulty=C]
    How long does is take for \SI{4.5e6}{\joule} of work to be
        done by a \SI{380}{\kilo\watt} engine?
\end{question}
\begin{solution}
    N/A
\end{solution}


\begin{question}[ID=power-C-Q02,topic=power,difficulty=C]
    A ship's engine has a power output of \SI{13.0}{\mega\watts}.
    How much work can it do in \SI{15.0}{\minute}?
\end{question}
\begin{solution}
    N/A
\end{solution}


\begin{question}[ID=power-C-Q03,topic=power,difficulty=C]
    A spacecraft's engines do \SI{1.4e13}{\joule} of work in
        \SI{8.5}{\minute}.
    What is the power output of these engines?
\end{question}
\begin{solution}
    N/A
\end{solution}


\begin{question}[ID=power-C-Q04,topic=power,difficulty=C]
    How much work can a \SI{3.0}{hp} motor do in \SI{1}{\hour}?
    ($\SI{1}{hp} = \SI{746}{\watt}$)
\end{question}
\begin{solution}
    N/A
\end{solution}


\begin{question}[ID=power-C-Q05,topic=power,difficulty=C]
    A pump lifts \SI{18}{\kilo\gram} of water per minute through
        a height of \SI{3.60}{\meter}.
    What minimum power output rating should the pump motor have?
\end{question}
\begin{solution}
    N/A
\end{solution}


\endinput

