
%% university of northern iowa
%%  morgans astronomy exams
%%--------------------------------------------------

%% this section contains 20 problems

\element{morgans}{
\begin{question}{test4B-q01}
    Which planet's orbital and physical characteristics differ the most from all the other planets?
    \begin{choices}
        \wrongchoice{Mercury}
        \wrongchoice{Earth}
        \wrongchoice{Uranus}
      \correctchoice{Pluto}
    \end{choices}
\end{question}
}

\element{morgans}{
\begin{question}{test4B-q02}
    What are the cores of the terrestrial planets primarily composed of?
    \begin{choices}
        \wrongchoice{silicates}
        \wrongchoice{iron and magnesium}
      \correctchoice{iron and nickel}
        \wrongchoice{lead and uranium}
    \end{choices}
\end{question}
}

\element{morgans}{
\begin{question}{test4B-q03}
    The Earth's early atmosphere was dominated by:
    \begin{choices}
        \wrongchoice{oxygen-bearing compounds.}
      \correctchoice{hydrogen-bearing compounds.}
        \wrongchoice{water.}
        \wrongchoice{nitrogen.}
        \wrongchoice{carbon dioxide.}
    \end{choices}
\end{question}
}

\element{morgans}{
\begin{question}{test4B-q04}
    Large scale changes on the surface of the Earth are probably caused by:
    \begin{choices}
        \wrongchoice{wind erosion.}
      \correctchoice{continental drift.}
        \wrongchoice{glaciation.}
        \wrongchoice{water erosion.}
        \wrongchoice{micrometeoroid impact.}
    \end{choices}
\end{question}
}

\element{morgans}{
\begin{question}{test4B-q05}
    The strong lunar magnetic field is evidence for:
    \begin{choices}
        \wrongchoice{a molten core.}
        \wrongchoice{rapid rotation of the core.}
        \wrongchoice{present day volcanic activity.}
        \wrongchoice{the fission theory of lunar formation.}
      \correctchoice{nothing, since the Moon does not have a stong magnetic field.}
    \end{choices}
\end{question}
}

\element{morgans}{
\begin{question}{test4B-q06}
    Mercury is expected to have a weak magnetic field because of its:
    \begin{choices}
      \correctchoice{slow rotation.}
        \wrongchoice{high surface temperature.}
        \wrongchoice{high density.}
        \wrongchoice{spin-orbit coupling.}
    \end{choices}
\end{question}
}

\element{morgans}{
\begin{question}{test4B-q07}
    Which of the following is not a surface feature on Venus?
    \begin{choices}
        \wrongchoice{Arachnids}
        \wrongchoice{Pancakes}
      \correctchoice{Blueberries}
        \wrongchoice{Coronae}
    \end{choices}
\end{question}
}

\element{morgans}{
\begin{question}{test4B-q08}
    Venus' magnetic field produces which of the following?
    \begin{choices}
        \wrongchoice{strong lightning discharges}
        \wrongchoice{strong auroral activity}
        \wrongchoice{a connection between the surface of Venus and that of its satellite}
        \wrongchoice{a magnetosphere larger than the Earth's}
      \correctchoice{none of the provided, since Venus has no significant magnetic field}
    \end{choices}
\end{question}
}

\element{morgans}{
\begin{question}{test4B-q09}
    Which of the following is NOT a feature of Mars?
    \begin{choices}
        \wrongchoice{frost}
        \wrongchoice{clouds}
        \wrongchoice{dust storms}
        \wrongchoice{melting ice caps}
      \correctchoice{spring floods}
    \end{choices}
\end{question}
}

\element{morgans}{
\begin{question}{test4B-q10}
    Which one of the following statements about the Martian satellites is true?
    \begin{choices}
        \wrongchoice{both are large satellites (nearly the size of the Earth's moon)}
      \correctchoice{both are small satellites}
        \wrongchoice{one is large, while the other is small}
        \wrongchoice{Mars has only one small satellite}
    \end{choices}
\end{question}
}

\element{morgans}{
\begin{question}{test4B-q11}
    Which of the following planets has the strongest magnetic field?
    \begin{choices}
        \wrongchoice{Mercury}
        \wrongchoice{Venus}
      \correctchoice{Earth}
        \wrongchoice{Mars}
    \end{choices}
\end{question}
}

\element{morgans}{
\begin{question}{test4B-q12}
    What is the name of the probe that most recently was in orbit about Jupiter?
    \begin{choices}
        \wrongchoice{Huygens}
        \wrongchoice{Cassini}
        \wrongchoice{Herschel}
      \correctchoice{Galileo}
    \end{choices}
\end{question}
}

\element{morgans}{
\begin{question}{test4B-q13}
    The Great Red Spot on Jupiter is caused by:
    \begin{choices}
        \wrongchoice{volcanic activity below the cloud tops.}
        \wrongchoice{the interaction of the atmosphere with a tall mountain on the surface underneath the spot.}
        \wrongchoice{the infall of a large asteroid.}
      \correctchoice{meteorological conditions in the atmosphere (a storm).}
        \wrongchoice{a region having a different chemical composition than the surrounding area.}
    \end{choices}
\end{question}
}

\element{morgans}{
\begin{question}{test4B-q14}
    Io is known to have a warm interior because:
    \begin{choices}
      \correctchoice{it has active volcanos.}
        \wrongchoice{it shows continental drift.}
        \wrongchoice{it has a hot atmosphere.}
        \wrongchoice{of its strong interaction with the solar wind.}
        \wrongchoice{of its strong magnetic field.}
    \end{choices}
\end{question}
}

\element{morgans}{
\begin{question}{test4B-q15}
    Uranus is peculiar because its:
    \begin{choices}
        \wrongchoice{orbit is highly eccentric.}
        \wrongchoice{orbit is strongly inclined to the ecliptic plane.}
        \wrongchoice{satellites are in polar, rather than equatorial, orbits.}
      \correctchoice{axis of rotation is in the ecliptic plane.}
        \wrongchoice{moons revolve in the same direction the planet rotates.}
    \end{choices}
\end{question}
}

\element{morgans}{
\begin{question}{test4B-q16}
    Neptune has how many known satellites?
    \begin{choices}
        \wrongchoice{none}
        \wrongchoice{two}
        \wrongchoice{four}
        \wrongchoice{six}
      \correctchoice{more than six}
    \end{choices}
\end{question}
}

\element{morgans}{
\begin{question}{test4B-q17}
    Which of the following statements about Pluto is \emph{false}?
    \begin{choices}
        \wrongchoice{it is composed mainly of rocks and metals}
        \wrongchoice{it is currently further from the Sun than Neptune}
        \wrongchoice{it has a methane atmosphere}
        \wrongchoice{it is tilted more than 100° on its side}
    \end{choices}
\end{question}
}

\element{morgans}{
\begin{question}{test4B-q18}
    What does N.E.A. stand for? 
    \begin{choices}
        \wrongchoice{New England Astronomers}
        \wrongchoice{Northern Earth Anglers}
        \wrongchoice{Nasty, Evil Astronomers}
      \correctchoice{Near Earth Asteroids}
    \end{choices}
\end{question}
}

\element{morgans}{
\begin{question}{test4B-q19}
    Which of the following was found to be the most abundant material in a comet such as Halley's comet?
    \begin{choices}
      \correctchoice{water}
        \wrongchoice{carbon dioxide}
        \wrongchoice{carbon monoxide}
        \wrongchoice{ammonia}
        \wrongchoice{methane}
    \end{choices}
\end{question}
}

\element{morgans}{
\begin{question}{test4B-q20}
    Which of the following characterizes terrestrial planets?
    \begin{choices}
      \correctchoice{rocky composition}
        \wrongchoice{low density}
        \wrongchoice{rapid rotation}
        \wrongchoice{large size}
    \end{choices}
\end{question}
}

\begin{comment}
    Fill In
    Place the most appropriate word or words in the blank. You may have to click on the blank to activate it before you start typing in your answer.
    Relative to the Jovian planets, the size of the terrestrial planets is .

    are rocks formed from impact events.

    is the age of the Earth.

    The crust is composed of granitic material and has a relatively low density.

    In addition to the half-life of the material in a rock, must be known to determine a rock's age.

    The rotation of Venus may be characterized as .

    Martian volcanos are the size they are because of an absence of .

    Neptune has known satellites.

    Pluto's satellite is known as .

    The straight tail of a comet is called the tail.
\end{comment}


\endinput



