
%% university of northern iowa
%%  morgans astronomy exams
%%--------------------------------------------------

%% this section contains 20 problems

\element{morgans}{
\begin{question}{test4H-q01}
    Which planet has not yet been visited by a probe from the Earth?
    \begin{choices}
        \wrongchoice{Mercury}
        \wrongchoice{Saturn}
        \wrongchoice{Neptune}
      \correctchoice{Pluto}
    \end{choices}
\end{question}
}

\element{morgans}{
\begin{question}{test4H-q02}
    Which one of the following does \emph{not} contribute to modifying the Earth's surface?
    \begin{choices}
        \wrongchoice{wind}
        \wrongchoice{chemical processes}
      \correctchoice{magnetic fields}
        \wrongchoice{water}
        \wrongchoice{tectonic activity}
    \end{choices}
\end{question}
}

\element{morgans}{
\begin{question}{test4H-q03}
    Which of the following lists gives the various layers of the Earth in the correct order from the center going outwards?
    \begin{choices}
        \wrongchoice{liquid nickel/iron core, solid nickel/iron core, mantle.}
      \correctchoice{solid nickel/iron core, liquid nickel/iron core, mantle.}
        \wrongchoice{solid nickel/iron core, mantle.}
        \wrongchoice{there are no layers, it is a uniform composition.}
    \end{choices}
\end{question}
}

\element{morgans}{
\begin{question}{test4H-q04}
    Which lunar surface features best indicate past fluid flow on the lunar surface?
    \begin{choices}
        \wrongchoice{craters}
      \correctchoice{maria}
        \wrongchoice{rays}
        \wrongchoice{mountain ranges}
    \end{choices}
\end{question}
}

\element{morgans}{
\begin{question}{test4H-q05}
    Which one of the following is \emph{not} true about Mercury? 
    \begin{choices}
        \wrongchoice{highly eccentric orbit}
        \wrongchoice{orbital period of 88 days}
      \correctchoice{orbit is retrograde}
        \wrongchoice{orbit shows large (7 degrees) tilt to ecliptic}
        \wrongchoice{average distance from the Sun is 0.4 A.U.}
    \end{choices}
\end{question}
}

\element{morgans}{
\begin{question}{test4H-q06}
    The scarps on Mercury were caused by:
    \begin{choices}
        \wrongchoice{volcanic activity.}
        \wrongchoice{continental drift.}
        \wrongchoice{expansion of the surface due to intense solar heating.}
      \correctchoice{shrinking of the surface after cooling of the interior.}
        \wrongchoice{water erosion.}
    \end{choices}
\end{question}
}

\element{morgans}{
\begin{question}{test4H-q07}
    What type of radiation is able to penetrate Venus' clouds and thus allow us to study its surface?
    \begin{choices}
        \wrongchoice{X rays}
        \wrongchoice{ultraviolet radiation}
        \wrongchoice{visual radiation}
        \wrongchoice{infrared waves}
      \correctchoice{radio waves}
    \end{choices}
\end{question}
}

\element{morgans}{
\begin{question}{test4H-q08}
    Modern data indicate that Venus:
    \begin{choices}
        \wrongchoice{shows extensive, rapid, and current continental drift.}
        \wrongchoice{is as bright at the surface as is the Earth.}
        \wrongchoice{has never had volcanic activity.}
      \correctchoice{may have recent volcanic activity.}
    \end{choices}
\end{question}
}

\element{morgans}{
\begin{question}{test4H-q09}
    Which one of the following best describes Olympus Mons?
    \begin{choices}
      \correctchoice{700 mile diameter base, 90,000 feet high}
        \wrongchoice{70 mile diameter base, 15,000 feet high}
        \wrongchoice{10 mile diameter base, 5,000 feet high}
        \wrongchoice{1,000 mile diameter base, 100,000 feet high}
    \end{choices}
\end{question}
}

\element{morgans}{
\begin{question}{test4H-q10}
    Which planet is the most geologically active?
    \begin{choices}
        \wrongchoice{Mercury}
        \wrongchoice{Venus}
      \correctchoice{Earth}
        \wrongchoice{Mars}
    \end{choices}
\end{question}
}

\element{morgans}{
\begin{question}{test4H-q11}
    Who discovered Uranus?
    \begin{choices}
      \correctchoice{William Herschel}
        \wrongchoice{Clyde Tombaugh}
        \wrongchoice{Urbain Leverrier}
        \wrongchoice{Johann Galle}
        \wrongchoice{John C. Adams}
    \end{choices}
\end{question}
}

\element{morgans}{
\begin{question}{test4H-q12}
    The chemical composition of Jupiter is most similar to that of:
    \begin{choices}
        \wrongchoice{the Earth.}
      \correctchoice{the Sun.}
        \wrongchoice{Mars.}
        \wrongchoice{the Moon.}
        \wrongchoice{Venus.}
    \end{choices}
\end{question}
}

\element{morgans}{
\begin{question}{test4H-q13}
    Which Jovian satellite has the fewest impact craters?
    \begin{choices}
        \wrongchoice{Callisto}
      \correctchoice{Io}
        \wrongchoice{Europa}
        \wrongchoice{Ganymede}
        \wrongchoice{Titan}
    \end{choices}
\end{question}
}

\element{morgans}{
\begin{question}{test4H-q14}
    Saturn's rings are found:
    \begin{choices}
      \correctchoice{inside the Roche limit.}
        \wrongchoice{at the Roche limit.}
        \wrongchoice{outside the Roche limit.}
        \wrongchoice{in a location that has nothing to do with the Roche limit.}
    \end{choices}
\end{question}
}

\element{morgans}{
\begin{question}{test4H-q15}
    Uranus' magnetic field is:
    \begin{choices}
        \wrongchoice{not known to exist.}
        \wrongchoice{in the planet's equatorial plane.}
        \wrongchoice{in the planet's polar plane.}
        \wrongchoice{tipped 60° with respect to the rotation axis.}
        \wrongchoice{caused by a core of molten iron.}
    \end{choices}
\end{question}
}

\element{morgans}{
\begin{question}{test4H-q16}
    Triton's atmosphere is composed of:
    \begin{choices}
        \wrongchoice{carbon dioxide and water.}
        \wrongchoice{oxygen and ammonia.}
        \wrongchoice{water and methane.}
      \correctchoice{nitrogen and methane.}
        \wrongchoice{none---there is no atmosphere.}
    \end{choices}
\end{question}
}

\element{morgans}{
\begin{question}{test4H-q17}
    The largest asteroid has a diameter of roughly:
    \begin{choices}
        \wrongchoice{10 km.}
        \wrongchoice{100 km.}
        \wrongchoice{1,000 km.}
        \wrongchoice{10,000 km.}
        \wrongchoice{100,000 km.}
    \end{choices}
\end{question}
}

\element{morgans}{
\begin{question}{test4H-q18}
    How is it possible for a comet originating in the Oort cloud to become a short-period comet?
    \begin{choices}
      \correctchoice{its path would have to be altered by the gravitational pull of a large planet, such as Jupiter}
        \wrongchoice{its path must travel very close to the Sun, so that the solar winds would alter its path}
        \wrongchoice{it must collide with another object in the inner solar system}
        \wrongchoice{nothing needs to occur, since all comets from the Oort cloud are short-period comets}
    \end{choices}
\end{question}
}

\element{morgans}{
\begin{question}{test4H-q19}
    The most common type of meteorite is:
    \begin{choices}
      \correctchoice{stony.}
        \wrongchoice{stony-irons.}
        \wrongchoice{irons.}
        \wrongchoice{gaseous.}
    \end{choices}
\end{question}
}

\element{morgans}{
\begin{question}{test4H-q20}
    Why are large satellites spherical?
    \begin{choices}
        \wrongchoice{tidal forces from the planet they orbit force them to be spherical}
        \wrongchoice{the impact of meteoroids removes irregularities}
        \wrongchoice{strong magnetic fields}
      \correctchoice{gravitational compression}
    \end{choices}
\end{question}
}

\begin{comment}
    Fill In
    Place the most appropriate word or words in the blank. You may have to click on the blank to activate it before you start typing in your answer.
    The force which makes planets generally round is .

    is the term for the churning of material inside the Earth.

    can exist as a gas, liquid or solid on Titan.

    The region of the Earth's interior, known as the , is liquid.

    The rippled appearance directly opposite Caloris Basin was probably caused by produced at the time Caloris Basin was formed.

    was the name of the the Martian orbiter/lander which investigated the possibility of life on Mars.

    The satellite of Saturn known to have a substantial atmosphere is .

    The strangest of Uranus' moons is .

    The main part of a comet is called the .

    The group of planets having a low density are called the .
\end{comment}


\endinput



