

%% Physics 101 Sample Test Questions by Dr. James Pierce
%%------------------------------------------------------------


%% Exam #5 ---- (light, optics, electric charge, electric current, etc.)
%%----------------------------------------------------------------------
\element{cpo-mc}{
\begin{question}{exam05-Q96}
    A capacitor is a device used to
    \begin{choices}
        \wrongchoice{convert electricity into light.}
        \wrongchoice{convert electricity into heat.}
        \wrongchoice{force current through a wire.}
      \correctchoice{store separated electrical charges.}
        \wrongchoice{measure the volume of a glass container.}
    \end{choices}
\end{question}
}

\element{cpo-mc}{
\begin{question}{exam05-Q97}
    A positively charged object
    \begin{choices}
        \wrongchoice{has a deficiency of protons.}
        \wrongchoice{has a deficiency of neutrons.}
      \correctchoice{has a deficiency of electrons.}
        \wrongchoice{has an excess of electrons.}
        \wrongchoice{has an excess of neutrons.}
    \end{choices}
\end{question}
}

\element{cpo-mc}{
\begin{question}{exam05-Q98}
    Good electrical insulators are usually
    \begin{choices}
        \wrongchoice{good thermal conductors.}
      \correctchoice{poor thermal conductors.}
        \wrongchoice{good electical conductors.}
        \wrongchoice{poor thermal insulators.}
        \wrongchoice{opaque to light.}
    \end{choices}
\end{question}
}

\element{cpo-mc}{
\begin{question}{exam05-Q99}
    The lines of force for a point charge
    \begin{choices}
        \wrongchoice{form concentric circles about it.}
      \correctchoice{extend radially outward from it.}
        \wrongchoice{connect points of equal electric potential.}
        \wrongchoice{connect points of equal charge.}
        \wrongchoice{indicate the direction of motion of the point charge.}
    \end{choices}
\end{question}
}

\element{cpo-mc}{
\begin{question}{exam05-Q100}
    According to Coulomb's law, if the distance between two charges is doubled,
        the force each charge exerts on the other will be \rule[-0.1pt]{4em}{0.1pt} its previous value.
    \begin{multicols}{2}
    \begin{choices}
        \wrongchoice{the same as}
        \wrongchoice{double}
        \wrongchoice{one half of}
        \wrongchoice{four times}
      \correctchoice{one fourth of}
    \end{choices}
    \end{multicols}
\end{question}
}

\element{cpo-mc}{
\begin{question}{exam05-Q101}
    If the charges in an electrical circuit always flow in the same direction,
        the current is called
    \begin{choices}
        \wrongchoice{an alternating current.}
        \wrongchoice{a constant current.}
      \correctchoice{a direct current.}
        \wrongchoice{an oscillating current.}
        \wrongchoice{a basic current.}
    \end{choices}
\end{question}
}

\element{cpo-mc}{
\begin{question}{exam05-Q102}
    If the current in a wire is \SI{6}{\ampere},
        how much charge will flow through it in \SI{2}{\second}?
    \begin{multicols}{2}
    \begin{choices}
      \correctchoice{\SI{12 coulombs}}
        \wrongchoice{\SI{2 coulombs}}
        \wrongchoice{\SI{8 coulombs}}
        \wrongchoice{\SI{6 coulombs}}
        \wrongchoice{\SI{3 coulombs}}
    \end{choices}
    \end{multicols}
\end{question}
}

\element{cpo-mc}{
\begin{question}{exam05-Q103}
    If a voltage of \SI{110}{\volt} produces a current of \SI{2}{\ampere} in an electrical device,
        the resistance must be
    \begin{multicols}{2}
    \begin{choices}
        \wrongchoice{\SI{110}{\ohm}}
        \wrongchoice{\SI{2}{\ohm}}
        \wrongchoice{\SI{108}{\ohm}}
      \correctchoice{\SI{55}{\ohm}}
        \wrongchoice{\SI{220}{\ohm}}
    \end{choices}
    \end{multicols}
\end{question}
}

\element{cpo-mc}{
\begin{question}{exam05-Q104}
    If \SI{120}{\volt} are used to light a \SI{30}{\watt} light bulb,
        the current in the bulb will be
    \begin{multicols}{2}
    \begin{choices}
        \wrongchoice{\SI{120}{\ampere}}
        \wrongchoice{\SI{30}{\ampere}}
        \wrongchoice{\SI{150}{\ampere}}
      \correctchoice{\SI{0.25}{\ampere}}
        \wrongchoice{\SI{4}{\ampere}}
    \end{choices}
    \end{multicols}
\end{question}
}

\element{cpo-mc}{
\begin{question}{exam05-Q105}
    Wires that are \rule[-0.1pt]{4em}{0.1pt} have lower resistance.
    \begin{choices}
        \wrongchoice{longer and thicker}
        \wrongchoice{longer and thinner}
      \correctchoice{shorter and thicker}
        \wrongchoice{shorter and thinner}
        \wrongchoice{straight}
    \end{choices}
\end{question}
}

\element{cpo-mc}{
\begin{question}{exam05-Q106}
    If light bulb $A$ has four times the resistance of light bulb $B$
        and the same current passes through each bulb,
        the voltage across bulb $A$ will be \rule[-0.1pt]{4em}{0.1pt} the
        voltage across bulb $B$.
    \begin{multicols}{2}
    \begin{choices}
        \wrongchoice{two times}
        \wrongchoice{equal to}
        \wrongchoice{one half of}
        \wrongchoice{one fourth of}
      \correctchoice{four times}
    \end{choices}
    \end{multicols}
\end{question}
}

\element{cpo-mc}{
\begin{question}{exam05-Q107}
    If three light bulbs of different wattage are connected in series to a battery,
    \begin{choices}
        \wrongchoice{the voltage drop across each bulb will be the same.}
        \wrongchoice{the current in each light bulb will be the same.}
        \wrongchoice{the resistance in each light bulb will be the same.}
        \wrongchoice{the power consumed by each light bulb will be the same.}
        \wrongchoice{the light output of each bulb will be the same.}
    \end{choices}
\end{question}
}

\element{cpo-mc}{
\begin{question}{exam05-Q108}
    The speed of light in a vacuum
    \begin{choices}
        \wrongchoice{is found by averaging the different speeds of all the different colors of light.}
        \wrongchoice{is higher for blue light than for red light.}
        \wrongchoice{is higher for green light than for violet light.}
      \correctchoice{is the same for all the different colors of light.}
        \wrongchoice{is chosen to be equal to the speed of yellow light, which moves faster than any other color.}
    \end{choices}
\end{question}
}

\element{cpo-mc}{
\begin{question}{exam05-Q109}
    A material is said to be transparent if
    \begin{choices}
      \correctchoice{light can pass freely through it in a straight line.}
        \wrongchoice{it absorbs light and redistributes the energy as thermal energy.}
        \wrongchoice{it reflects light.}
        \wrongchoice{it can vibrate at a resonant frequency to match the frequency of the light.}
        \wrongchoice{it cannot emit any light.}
    \end{choices}
\end{question}
}

\element{cpo-mc}{
\begin{question}{exam05-Q110}
    Of all the electromagnetic waves,
        those with highest energy are \rule[-0.1pt]{4em}{0.1pt} and
        those with lowest energy are \rule[-0.1pt]{4em}{0.1pt}.
    \begin{choices}
      \correctchoice{gamma rays; radio waves}
        \wrongchoice{radio waves; x-rays}
        \wrongchoice{x-rays; microwaves}
        \wrongchoice{microwaves; ultraviolet}
        \wrongchoice{visible light; infrared}
    \end{choices}
\end{question}
}

\element{cpo-mc}{
\begin{question}{exam05-Q111}
    Which of the following is true?
    \begin{choices}
        \wrongchoice{Only virtual images can be projected on a screen.}
        \wrongchoice{A light ray passing through the center of a converging lens will be bent to pass through the focus.}
        \wrongchoice{A virtual image is formed where the rays from an object meet after passing through a lens.}
      \correctchoice{The image seen in a plane mirror is a virtual image.}
        \wrongchoice{A virtual image is always upside down.}
    \end{choices}
\end{question}
}

\element{cpo-mc}{
\begin{question}{exam05-Q112}
    When a converging lens is used as a magnifying glass,
        the image produced is
    \begin{choices}
        \wrongchoice{real and inverted.}
        \wrongchoice{real and upright.}
        \wrongchoice{virtual and inverted.}
      \correctchoice{virtual and upright.}
        \wrongchoice{none of the provided---a converging lens cannot be used as a magnifying glass.}
    \end{choices}
\end{question}
}

\element{cpo-mc}{
\begin{question}{exam05-Q113}
    Which of the following is true? 
    When used alone,
    \begin{choices}
        \wrongchoice{converging lenses can form only real images.}
        \wrongchoice{converging lenses can form only virtual images.}
        \wrongchoice{converging lenses can form only inverted images.}
        \wrongchoice{diverging lenses can form only real images.}
      \correctchoice{diverging lenses can form only virtual images.}
    \end{choices}
\end{question}
}

\element{cpo-mc}{
\begin{question}{exam05-Q114}
    The colors seen in a rainbow
    \begin{choices}
        \wrongchoice{are produced by raindrops of different colors.}
        \wrongchoice{are produced by raindrops of different shapes.}
        \wrongchoice{are the colors of the different atoms that make up water.}
        \wrongchoice{are the colors of the different molecules that make up water.}
      \correctchoice{are produced when sunlight is refracted by raindrops.}
    \end{choices}
\end{question}
}

\element{cpo-mc}{
\begin{question}{exam05-Q115}
    The law of reflection says
    \begin{choices}
        \wrongchoice{all reflected rays are perpendicular to the incident ray.}
        \wrongchoice{all reflected rays are parallel to the incident ray.}
        \wrongchoice{all reflected rays are parallel to each other.}
      \correctchoice{the angle of reflection equals the angle of incidence.}
        \wrongchoice{the angle of reflection equals the angle of refraction.}
    \end{choices}
\end{question}
}

\element{cpo-mc}{
\begin{question}{exam05-Q116}
    A light ray passing from air into water at an angle of \ang{30} from the normal in air
    \begin{choices}
        \wrongchoice{would make an angle of \ang{30} from the normal in water.}
        \wrongchoice{would make an angle greater than \ang{30} from the normal in water.}
      \correctchoice{would make an angle less than \ang{30} from the normal in water.}
        \wrongchoice{would be completely reflected by the water surface.}
        \wrongchoice{would be completely absorbed by the water surface.}
    \end{choices}
\end{question}
}

\element{cpo-mc}{
\begin{question}{exam05-Q117}
    The critical angle is
    \begin{choices}
        \wrongchoice{the angle of incidence for which the angle of the refracted beam is \ang{0}.}
      \correctchoice{the angle of incidence for which the angle of the refracted beam is \ang{90}.}
        \wrongchoice{the angle of incidence for which the angle of the refracted beam is the same.}
        \wrongchoice{the angle of incidence for which the angle of the reflected beam is the same.}
        \wrongchoice{the angular radius of the arc of a rainbow.}
    \end{choices}
\end{question}
}

\endinput


