

%% AP Physics MC Questions Archive
%%----------------------------------------


%% Work and Energy with Calculus
%%----------------------------------------
\element{ap}{
\begin{question}{work-calculus-q01}
    The position of a vehicle of mass \SI{1000}{\kilo\gram} moving on a straight track along the $x$-axis is given by the equation $x(t) = t^3-t^2-6t$,
        where $x$ is in meters and $t$ is in seconds.
    What is the instantaneous force acting on the vehicle at $t=\SI{3}{\second}$?
    \begin{multicols}{3}
    \begin{choices}
        \wrongchoice{Zero}
        \wrongchoice{\SI{3000}{\newton}}
        \wrongchoice{\SI{6000}{\newton}}
        \wrongchoice{\SI{12000}{\newton}}
      \correctchoice{\SI{16000}{\newton}}
    \end{choices}
    \end{multicols}
\end{question}
}

\element{ap}{
\begin{question}{work-calculus-q02}
    A force given by $F(x) = 6x + 3x^2$ acts upon a projectile that starts from rest at the origin.
    How much work is done on the \SI{5}{\kilo\gram} projectile if it travels \SI{5}{\meter}?
    \begin{multicols}{3}
    \begin{choices}
        \wrongchoice{\SI{155}{\joule}}
        \wrongchoice{\SI{175}{\joule}}
      \correctchoice{\SI{200}{\joule}}
        \wrongchoice{\SI{225}{\joule}}
        \wrongchoice{\SI{400}{\joule}}
    \end{choices}
    \end{multicols}
\end{question}
}

\element{ap}{
\begin{question}{work-calculus-q03}
    A \SI{50}{\kilo\gram} car travels along a straight track along the $x$-axis according to the equation $x(t) = t^2+4t+5$,
        where $x$ is in meters and $t$ is in seconds.
    What is the car's kinetic energy after \SI{1}{\second}?
    \begin{multicols}{3}
    \begin{choices}
      \correctchoice{\SI{900}{\joule}}
        \wrongchoice{\SI{1000}{\joule}}
        \wrongchoice{\SI{1500}{\joule}}
        \wrongchoice{\SI{2000}{\joule}}
        \wrongchoice{\SI{2705}{\joule}}
    \end{choices}
    \end{multicols}
\end{question}
}

\element{ap}{
\begin{question}{work-calculus-q04}
    The potential energy of an object is given by $U(x) = 0.5kx^2+3kx$,
        where $U$ is in joules, $x$ is in meters and $k$ is a constant.
    What is the force acting on the object when $x=0$?
    \begin{multicols}{3}
    \begin{choices}
      \correctchoice{$-3k$}
        \wrongchoice{$-k$}
        \wrongchoice{Zero}
        \wrongchoice{$k$}
        \wrongchoice{$3k$}
    \end{choices}
    \end{multicols}
\end{question}
}

\element{ap}{
\begin{question}{work-calculus-q05}
    A force acting on an object given by the function $F(x) = 3x^2+4$,
        where $F$ is in Newtons and $x$ is in meters.
    What is the change in the object's kinetic energy as it moves from $x=\SI{1}{\meter}$ to $x=\SI{3}{\meter}$?
    \begin{multicols}{3}
    \begin{choices}
        \wrongchoice{\SI{26}{\joule}}
        \wrongchoice{\SI{27}{\joule}}
        \wrongchoice{\SI{31}{\joule}}
      \correctchoice{\SI{34}{\joule}}
        \wrongchoice{\SI{36}{\joule}}
    \end{choices}
    \end{multicols}
\end{question}
}

\element{ap}{
\begin{question}{work-calculus-q06}
    A \SI{10}{\kilo\gram} particle's acceleration is given by the equation $a(t)=4t$,
        where $a$ is in \si{\meter\per\second\squared} and $t$ is in seconds.
    The particle is initially at rest at the origin.
    What is the particle's kinetic energy at $t=\SI{5}{\second}$?
    \begin{multicols}{3}
    \begin{choices}
        \wrongchoice{\SI{2.5}{\kilo\joule}}
        \wrongchoice{\SI{5}{\kilo\joule}}
      \correctchoice{\SI{12.5}{\kilo\joule}}
        \wrongchoice{\SI{125}{\kilo\joule}}
        \wrongchoice{\SI{250}{\kilo\joule}}
    \end{choices}
    \end{multicols}
\end{question}
}

\element{ap}{
\begin{question}{work-calculus-q07}
    A force acting on an object of mass \SI{3}{\kilo\gram} is given by the equation $F(x)=6x+2,$ where $F$ is in Newtons and $x$ is in meters.
    If the object starts at rest,
         what is the final velocity of the object as it travels from $x=0$ to $x=\SI{4}{\meter}$?
    \begin{multicols}{3}
    \begin{choices}
        \wrongchoice{\SI{2}{\meter\per\second}}
        \wrongchoice{\SI{4}{\meter\per\second}}
      \correctchoice{\SI{6}{\meter\per\second}}
        \wrongchoice{\SI{8}{\meter\per\second}}
        \wrongchoice{\SI{12}{\meter\per\second}}
    \end{choices}
    \end{multicols}
\end{question}
}

\element{ap}{
\begin{question}{work-calculus-q08}
    The velocity of an object of mass $m$ is given by the equation $v=2x+4$.
    What is an expression for the kinetic energy of the object?
    \begin{multicols}{2}
    \begin{choices}
        \wrongchoice{$2m$}
        \wrongchoice{$m\left(2 + x\right)$}
        \wrongchoice{$m\left(4x + x^2\right)$}
      \correctchoice{$m\left(2x^2 + 8x + 8\right)$}
        \wrongchoice{$m\left(8x^2 + 4x^3 + \dfrac{x^4}{2}\right)$}
    \end{choices}
    \end{multicols}
\end{question}
}

\element{ap}{
\begin{question}{work-calculus-q09}
    An object is pushed by a force given by $F(x)=6x-4$.
    What is the amount of work done to push the object \SI{4}{\meter}.
    \begin{multicols}{3}
    \begin{choices}
        \wrongchoice{\SI{16}{\joule}}
        \wrongchoice{\SI{20}{\joule}}
      \correctchoice{\SI{32}{\joule}}
        \wrongchoice{\SI{44}{\joule}}
        \wrongchoice{\SI{80}{\joule}}
    \end{choices}
    \end{multicols}
\end{question}
}

\element{ap}{
\begin{question}{work-calculus-q10}
    An object with an initial potential energy $k$ experiences a conservative force given by $F(x)=x^2+2$ over the interval $0<×<2$.
    What is the equation for the potential energy $U$ of this object?
    \begin{choices}
        \wrongchoice{$U(x) = \dfrac{x^3}{3} + 2x + k$}
        \wrongchoice{$U(x) = -\dfrac{x^3}{3} - 2x - k$}
      \correctchoice{$U(x) = -\dfrac{x^3}{3} - 2x + k$}
        \wrongchoice{$U(x) = -\dfrac{x^3}{3} - 2x$}
        \wrongchoice{$U(x) = \dfrac{x^3}{3} + 2x$}
    \end{choices}
\end{question}
}

\element{ap}{
\begin{question}{work-calculus-q11}
    What is the expression of the kinetic energy of an object of mass \SI{5}{\kilo\gram}
        whose acceleration is given by $a(t)=4t-5$ and that is initially at rest?
    \begin{multicols}{2}
    \begin{choices}
        \wrongchoice{$5\left(4t - 5\right)$}
        \wrongchoice{$5\left(2t^2 - 5t\right)$}
        \wrongchoice{$5\left(2t^2 - 5t\right)^2$}
      \correctchoice{$\dfrac{5}{2}\left(2t^2 - 5t\right)^2$}
        \wrongchoice{$\dfrac{5}{2}\left(4t - 5\right)^2$}
    \end{choices}
    \end{multicols}
\end{question}
}

\element{ap}{
\begin{question}{work-calculus-q12}
    If a force moves an object of mass $m$ so that its velocity is given by $v(t)=4t-2$,
        what is the power exerted by that force?
    \begin{multicols}{2}
    \begin{choices}
        \wrongchoice{$\dfrac{m}{2}\left(4t - 2\right)^2$}
      \correctchoice{$4m\left(4t - 2\right)$}
        \wrongchoice{$4m\left(2t^2 - 2t\right)$}
        \wrongchoice{$4m$}
        \wrongchoice{$m\left(4t - 2\right)$}
    \end{choices}
    \end{multicols}
\end{question}
}

\element{ap}{
\begin{question}{work-calculus-q13}
    If the power delivered to an object by a force acting on it is given by $P(t)=t^3-2t$ and the velocity of the object is given by $v(t) = 2t$,
        what is the force acting on the object in terms of $t$?
    \begin{choices}
        \wrongchoice{$F(t) = t^3 - 4t$}
        \wrongchoice{$F(t) = t^3$}
      \correctchoice{$F(t) = \dfrac{t^2}{2} - 1$}
        \wrongchoice{$F(t) = 3t^2 - 2 $}
        \wrongchoice{More information is needed to determine the force}
    \end{choices}
\end{question}
}

\element{ap}{
\begin{question}{work-calculus-q14}
    An object that starts at rest from the origin is pushed by a constant force of \SI{10}{\newton} has a position given by $x(t)=5t^2$.
    What is the power delivered to the object by the force at time $t=\SI{1}{\second}$?
    \begin{multicols}{3}
    \begin{choices}
        \wrongchoice{\SI{50}{\joule}}
        \wrongchoice{\SI{50}{\watt}}
        \wrongchoice{\SI{100}{\joule}}
        \wrongchoice{\SI{100}{\watt}}
      \correctchoice{\SI{125}{\watt}}
    \end{choices}
    \end{multicols}
\end{question}
}


\endinput


