
%%--------------------------------------------------
%% SAT Practice Test One
%%--------------------------------------------------

%% https://collegereadiness.collegeboard.org/pdf/sat-practice-test-1.pdf

%% Directions
%%--------------------------------------------------

%% For questions 1-15, solve each problem, choose the best answer from the choices provided, and fill in the corresponding circle on your answer sheet. 
%% For questions 16-20, solve the problem and enter your answer in the grid on the answer sheet. 
%% Please refer to the directions before question 16 on how to enter your answers in the grid. 
%% You may use any available space in your test booklet for scratch work.

%% Notes
%%--------------------------------------------------

%% 1. The use of a calculator is not permitted.
%% 2. All variables and expressions used represent real numbers unless otherwise indicated.
%% 3. Figures provided in this test are drawn to scale unless otherwise indicated.
%% 4. All figures lie in a plane unless otherwise indicated.
%% 5. Unless otherwise indicated, the domain of a given function f is the set of all real numbers x for which f(x) is a real number.


%% NOTE: Unauthorized copying or reuse of any part of this page is illegal.


%% SAT Writing and Language Test
%%--------------------------------------------------
\element{sat-mc}{
\begin{question}{math-t01-q01}
    If $\dfrac{x-1}{3} = k$ and $k=3$, what is the value of $x$?
    \begin{multicols}{2}
    \begin{choices}
        \wrongchoice{2}
        \wrongchoice{4}
        \wrongchoice{9}
     \correctchoice{10}
    \end{choices}
    \end{multicols}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t01-q02}
    For $i=\sqrt{-1}$, what is the sum of $\left(7+3i\right) + \left(-8+9i\right)$?
    \begin{multicols}{2}
    \begin{choices}
     \correctgchoice{$-1 + 12i$}
        \wrongchoice{$-1 - 6i$}
        \wrongchoice{$15 + 12i$}
        \wrongchoice{$15 - 6i$}
    \end{choices}
    \end{multicols}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t01-q03}
    On Saturday afternoon, Armand sent $m$ text messages each hour for 5 hours,
        and Tyrone sent $p$ text messages each hour for 4 hours.
    Which of the following represents the total number of messages sent by Armand and Tyrone on Saturday afternoon?
    \begin{multicols}{2}
    \begin{choices}
        \wrongchoice{$9 mp$}
        \wrongchoice{$20 mp$}
      \correctchoice{$5m + 4p$}
        \wrongchoice{$4m + 5p$}
    \end{choices}
    \end{multicols}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t01-q04}
    Kathy is a repair technician for a phone company.
    Each week, she receives a batch of phone that need repairs.
    The number of phones that she has left to fix at the end of each day can be estimated with the equation $P = 108-23d$,
        where $P$ is the number of phones left and $d$ is the number of days she has worked that week.
    What is the meaning of the value $108$ in this equation?
    \begin{choices}
        \wrongchoice{Kathy will complete the repairs within 108 days.}
      \correctchoice{Kathy starts each week with 108 phone to fix.}
        \wrongchoice{Kathy repairs phones at a rate of 108 per hour.}
        \wrongchoice{Kathy repairs phones at a rate of 108 per day.}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t01-q05}
    \begin{equation}
        \left( x^2y - 3y^2 + 5xy^2) - (-x^2y + 3xy^2 - 3y^2 \right)
    \begin{equation}
    Which of the following is equivalent to the expression above?
    \begin{choices}
        \wrongchoice{$4 x^2 y^2$}
        \wrongchoice{$8xy^2 - 6y^2$}
      \correctchoice{$2x^2y + 2xy^2$}
        \wrongchoice{$2x^2y + 8xy^2 - 6y^2$}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t01-q06}
    \begin{equation}
        h = 3a + 28.6
    \begin{equation}
    A pediatrician uses the model above to estimate the height $h$ of a boy, in inches,
        in terms of the boys age $a$, in years, between the ages of 2 and 5.
    Based on the model, what is the estimated increase, in inches,
        of a boy's height each year?
    \begin{choices}
      \correctchoice{$3$}
        \wrongchoice{$5.7$}
        \wrongchoice{$9.5$}
        \wrongchoice{$14.3$}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t01-q07}
    \begin{equation}
        m = \frac{ \left( \frac{r}{1,200} \right) \left(1 + \frac{r}{1200} \right)^N }
                 {\left(1 + \frac{r}{1200}\right)^N - 1}
    \begin{equation}
    The formuula above gives the monthly payment $m$ needed to pay off a loan of $P$ dollars at $r$ percent annual interest over $n$ months.
    Which of the following gives $P$ in terms of $m$, $r$, and $N$?
    \begin{choices}
        \wrongchoice{$P = \frac{\left(\frac{r}{1200}\right) \left(1+\frac{r}{1200}\right)^N}
                               {\left(1+\frac{r}{1200}\right)^N - 1} m$}
      \correctchoice{$P = \frac{\left(\left(1+\frac{r}{1200}\right)^N -1}
                               {\left(\frac{r}{1200}\right) \left(1+\frac{r}{1200}\right)^N - 1} m$}
        \wrongchoice{$P = \frac{\left(\frac{r}{1200}\right)m}$}
        \wrongchoice{$P = \frac{\left(\frac{1200}{r}\right)m}$}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t01-q08}
    if $\dfrac{a}{b}$ = 2, what if the value of $\dfrac{4b}{a}$?
    \begin{choices}
        \wrongchoice{$0$}
        \wrongchoice{$1$}
      \correctchoice{$2$}
        \wrongchoice{$4$}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t01-q09}
    \begin{equation}
        3x + 4y &= -23
        2y - x  = -19
    \end{equation}
    What is the solution $(x,y)$ to the system of equation above?
    \begin{choices}
        \wrongchoice{$(-5, -2)$}
        \wrongchoice{$(3, -8)$}
        \wrongchoice{$(4, -6)$}
        \wrongchoice{$(9, -6)$}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t01-q10}
    \begin{equation}
        g(x) = ax^2 + 24 
    \end{equation}
    For the function $g$ defined above, $a$ is a constant and $g(4)=8$.
    What is the value of $g(-4)$?
    \begin{choices}
      \correctchoice{$8$}
        \wrongchoice{$0$}
        \wrongchoice{$-1$}
        \wrongchoice{$-8$}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t01-q11}
    \begin{equation}
        b = 2.35 + 0.25x
        c = 1.75 + 0.40x
    \end{equation}
    In the equations above, $b$ and $c$ represent the price per pound,
         in dollars, of beef and chicken,
        respectively, $x$ weeks after July 1 during last summer.
    What was the price per pound of beef when it was equal to the price per pound of chicken?
    \begin{choices}
      \correctchoice{$\$ 2.60$}
        \wrongchoice{$\$ 2.85$}
        \wrongchoice{$\$ 2.95$}
        \wrongchoice{$\$ 3.35$}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t01-q12}
    A line in the $xy$-plane passes through the origin has a slope of $\dfrac{1}{7}$.
    Which of the following points lies on the line?
    \begin{choices}
        \wrongchoice{$\left( 0, 7 \right)$}
        \wrongchoice{$\left( 1, 7 \right)$}
        \wrongchoice{$\left( 7, 7 \right)$}
      \correctchoice{$\left( 14, 2 \right)$}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t01-q13}
    If $x>3$, which of the following is equivalent:
    \begin{choices}
        \wrongchoice{$\frac{1}{\frac{1}{x+2}+\frac{1}{x+3}}$}
        \wrongchoice{$\frac{2x+5}{x^2 + 5x + 6}$}
        \wrongchoice{$\frac{x^2 + 5x + 6}{2x+5}$}
        \wrongchoice{$2x+5$}
        \wrongchoice{$x^2 + 5x + 6$}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t01-q14}
    If $3x - y = 12$,
        what is the value of $\dfrac{8^x}{2^y}$?
    \begin{choices}
        \wrongchoice{$2^12$}
        \wrongchoice{$4^4$}
      \correctchoice{$8^2$}
        \wrongchoice{The value cannot be determined from the information given}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t01-q15}
    If $(ax + 2)(bx + 7) = 15x^2 + cx + 14$ for all values of $x$,
        and $a+b=8$, what are the two possible values for $c$?
    \begin{choices}
        \wrongchoice{3 and 5}
        \wrongchoice{6 and 35}
        \wrongchoice{10 and 21}
        \wrongchoice{31 and 41}
    \end{choices}
\end{question}
}


%% https://collegereadiness.collegeboard.org/pdf/sat-practice-test-2.pdf

\element{sat-mc}{
\begin{question}{math-t02-q01}
    If $5x + 6 = 10$, what is the value of $10x + 3$ ?
    \begin{choices}
        \wrongchoice{4}
        \wrongchoice{9}
      \correctchoice{11}
        \wrongchoice{20}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t02-q02}
    \begin{equation}
        x  +  y &= 0
        3x - 2y &= 10
    \end{equation}
    Which of the following orderd pairs $(x,y)$ satisfies the system of equation above?
    \begin{choices}
        \wrongchoice{$\left(3,-2\right)$}
        \wrongchoice{$\left(2,-2\right)$}
        \wrongchoice{$\left(-2,2\right)$}
        \wrongchoice{$\left(-2,-2\right)$}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t02-q03}
    A landscaping company estimates the price of a job in dollars,
    using the expression $60+12nh$, where $n$ is the  number of landscapers who will be working
        and $h$ is the total number of hours the job will take using $n$ landscapers.
   Which of the following is the best interpretation of the number 12 in the expression?
    \begin{choices}
        \wrongchoice{The company charges $12 per hours for each landscaper.}
        \wrongchoice{A minimum of 12 landscapers will work on each job.}
        \wrongchoice{the price of every job inncreases by $12 every hour.}
        \wrongchoice{Each landscaper works 12 hours a day.}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t02-q04}
        \begin{equation}
            9a^4 + 12a^2b^2 + 4b^4
        \end{equation}
        Which one of the following is equivalent to the expression shown above?
    \begin{choices}
        \wrongchoice{$\left( 3a^2 + 2b^2 \right)^2$}
        \wrongchoice{$\left( 3a + 2b \right)^4$}
        \wrongchoice{$\left( 9a^2 + 4b^2 \right)^2$}
        \wrongchoice{$\left( 9a + 4b \right)^4$}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t02-q05}
        \begin{equation}
            \sqrt{2k^2+17} -x = 0
        \end{equation}
        If $k>0$ and $x=7$ in the equation above,
            what is the value of $k$?
    \begin{choices}
        \wrongchoice{2}
        \wrongchoice{3}
      \correctchoice{4}
        \wrongchoice{5}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t02-q06}
    \begin{center}
    \begin{tikzpicture}

    \end{tikzpicture}
    \end{center}
    In the $xy$-plane above, line $l$ is parallel to the line $k$.
    What is the value of $p$?
    \begin{choices}
        \wrongchoice{4}
        \wrongchoice{5}
        \wrongchoice{8}
        \wrongchoice{10}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t02-q07}
    If $\dfrac{x^a^2}{x^b^2} = x^{16}$, $x>1$, and $a+b=2$,
        what is the value of $a-b$?
    \begin{choices}
        \wrongchoice{8}
        \wrongchoice{14}
        \wrongchoice{16}
        \wrongchoice{18}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t02-q08}
    \begin{equation}
        nA = 360
    \end{equation}
    The measure $A$, in degrees,
        of an exterior angle of a regular polygon is related to the number of sides,
        $n$, of a polygon by the formula above.
    If the measure of an exterior angle of a regular polygon is greater than \ang{50},
        what is the greatest number of sides it can have?
    \begin{choices}
        \wrongchoice{5}
        \wrongchoice{6}
        \wrongchoice{7}
        \wrongchoice{8}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t02-q09}
    The graph of a line in the $xy$-plane has slope 2 and contains the point $(1,8)$.
    The graph of a second  line passes through the points $(1,2)$ and $(2,1)$.
    If the two lines intersect at the point $(a,b)$,
        what is the value of $a+b$?
    \begin{choices}
        \wrongchoice{4}
        \wrongchoice{3}
        \wrongchoice{$-1$}
        \wrongchoice{$-4$}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t02-q10}
    Which of the following equations has a graph in the $xy$-plane
        for which $y$ is always greater than or equal to $-1$?
    \begin{choices}
        \wrongchoice{$y = \left|x\right| - 2$}
      \correctchoice{$y = x^2 - 2$}
        \wrongchoice{$y = \left( x - 2 \right)^2$}
        \wrongchoice{$y = x^3 - 2$}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t02-q11}
    Which of the following complex numbers is
        equivalent to $\dfrac{3-5i}{8+2i} ?
    Note: $\left(i = \sqrt(-1) \right)$
    \begin{choices}
        \wrongchoice{$\dfrac{3}{8} - \dfrac{5i}{2}$}
        \wrongchoice{$\dfrac{3}{8} + \dfrac{5i}{2}$}
        \wrongchoice{$\dfrac{7}{34} - \dfrac{23i}{34}$}
        \wrongchoice{$\dfrac{7}{34} + \dfrac{23i}{34}$}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t02-q12}
    \begin{equation}
        R = \frac{F}{N+F}
    \end{equation}
    A website uses the formula above to calculate a seller's rating,
        $R$, based on the number of favorable reviews,
        $F$, and unfavorable reviews, $N$.
    Which of the following expresses the number of favorable reviews in terms of the other variables?

    \begin{choices}
        \wrongchoice{$F = \frac{RN}{R-1}$}
        \wrongchoice{$F = \frac{RN}{1-R}$}
        \wrongchoice{$F = \frac{N}{1-R}$}
        \wrongchoice{$F = \frac{N}{R-1}$}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t02-q13}
    What is the sum of all values of $m$ that satisfy $2m^2 - 16m + 8 = 0$?
    \begin{choices}
        \wrongchoice{$-8$}
        \wrongchoice{$-4\sqrt{3}$}
        \wrongchoice{$4\sqrt{3}$}
        \wrongchoice{$8$}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t02-q14}
    A radioactive substance decays at an annual rate of 13 percent.
    If the initial amount of the substance is 325 grams,
        which of the following functions $f$ models the remaining amount of the substance,
        in grams, $t$ years later?
    \begin{choices}
        \wrongchoice{$f(t) = 325\left(0.87\right)^t$}
        \wrongchoice{$f(t) = 325\left(0.13\right)^t$}
        \wrongchoice{$f(t) = 0.87\left(325\right)^t$}
        \wrongchoice{$f(t) = 0.13\left(325\right)^t$}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t02-q15}
    The expression $\dfrac{5x-2}{x+3}$ is equivalent to which of the following?
    \begin{choices}
        \wrongchoice{$\dfrac{5-2}{3}$}
        \wrongchoice{$5 - \dfrac{2}{3}$}
        \wrongchoice{$5 - \dfrac{2}{x+3}$}
        \wrongchoice{$5 - \dfrac{17}{x+3}$}
    \end{choices}
\end{question}
}

%% https://collegereadiness.collegeboard.org/pdf/sat-practice-test-3.pdf


\element{sat-mc}{
\begin{question}{math-t03-q01}
    A painter will paint $n$ walls with the same size and shape in a building using a specific brand of paint.
    The painter's fee can be calculated by the expressino $nKlh$,
        where $n$ is the number of walls,
        $K$ is a constant with units of dollars per square foot, 
        $l$  is the length of each wall in feet, and $h$ is the height of each wall in feet.
    If the customer asks the painters to use a more expensive brand of paint,
        which of the factors in the expression would change?
    \begin{choices}
        \wrongchoice{$h$}
        \wrongchoice{$l$}
      \correctchoice{$K$}
        \wrongchoice{$n$}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t03-q02}
    If $3r=18$, what is the value of $6r+3$?
    \begin{choices}
        \wrongchoice{6}
        \wrongchoice{27}
        \wrongchoice{36}
      \correctchoice{39}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t03-q03}
    Which of the following is equal to $a^3$,
        for all value of $a$?
    \begin{choices}
        \wrongchoice{$\sqrt{a^{\dfrac{1}{3}}}$}
        \wrongchoice{$\sqrt{a^{3}}$}
        \wrongchoice{$\sqrt{a^{\dfrac{1}{2}}}{3}$}
        \wrongchoice{$\sqrt{a^2}{3}$}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t03-q04}
    The number of states that joined the United States between 1775 and 1849
        is twice the number of states that joined between 1776 and 1849 and $x$ states joined between 1850 and 1900,
        which of the following equations is true?
    \begin{choices}
        \wrongchoice{$30x = 2$}
        \wrongchoice{$2x = 30$}
        \wrongchoice{$\dfrac{x}{2} = 30$}
        \wrongchoice{$x +30 = 2$}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t03-q05}
    if $\dfrac{5}{x} = \dfrac{15}{x+20}$, what is the value of $\dfrac{x}{5}$
    \begin{choices}
        \wrongchoice{$10$}
        \wrongchoice{$5$}
        \wrongchoice{$2$}
        \wrongchoice{$\dfrac{1}{2}$}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t03-q06}
    If $(x,y)$ is a solution to the system of equations above,
        what is the value of $x-y$?
    \begin{choices}
        \wrongchoice{$-20$}
        \wrongchoice{$-8$}
        \wrongchoice{$-4$}
        \wrongchoice{$8$}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t03-q07}
    \begin{center}
    \begin{tabu}[XX]
        $x$ & $f(x)$ \\
        \hline
        0 & 3 \\
        2 & 1 \\
        4 & 0 \\
        5 & -2 \\
    \end{tabu}
    \end{center}
    The function $f$ is defined by a polynomial.
    Some values of $x$ and $f(x)$ are shown in the table above.
    Which of the following must be a factor of $f(x)$?
    \begin{choices}
        \wrongchoice{$x-2$}
        \wrongchoice{$x-3$}
        \wrongchoice{$x-4$}
        \wrongchoice{$x-5$}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t03-q08}
    The line $y=kx+4$, where $k$ is a constant if,
        is graphed in the $xy$-plane.
    If the lnie contains the point $(c,d)$, 
        where $c\neq 0$ and $d\neq 0$,
        what is the slope of the lnie ni terms of $c$ and $d$?
    \begin{choices}
        \wrongchoice{$\dfrac{d-4}{c}$}
        \wrongchoice{$\dfrac{c-4}{d}$}
        \wrongchoice{$\dfrac{4-d}{c}$}
        \wrongchoice{$\dfrac{4-c}{d}$}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t03-q09}
    \begin{equation}
        kx - 3y &= 4 \\
        4x - 5y &= y
    \end{equation}
    In the system of equations above, $k$ is a constant
        and $x$ and $y$ are variables.
    For what value of $k$ will the system of equations have no solution?
    \begin{choices}
        \wrongchoice{$\dfrac{12}{5}$}
        \wrongchoice{$\dfrac{16}{7}$}
        \wrongchoice{$-\dfrac{16}{7}$}
        \wrongchoice{$-\dfrac{12}{5}$}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t03-q10}
    In the $xy$-plane, the parabola with equations $y=\left( x-11 \right)^2$
        intersect the lnie with equation $y=25$ at two points,
        $A$ and $B$.
    what is the length of $\bar{AB}$?
    \begin{choices}
        \wrongchoice{10}
        \wrongchoice{12}
        \wrongchoice{14}
        \wrongchoice{16}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t03-q11}
    \begin{center}
    \begin{tikzpicture}

    \end{tikzpicture}
    \end{center}
    In the figure above, lines $k$, $l$, and $m$ intersect at a point.
    If $x+y = u+W$, which of the following must be true?
    \begin{center}
        \begin{tabu}
            I &   $x=z$ \\
            II &  $y=w$ \\
            III & $z=t$ \\
        \begin{tabu}
    \end{center}
    \begin{choices}
        \wrongchoice{I and II only}
        \wrongchoice{I and III only}
        \wrongchoice{II and III only}
        \wrongchoice{I, II and III}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t03-q12}
    \begin{equation} 
        y = a \left(x-2\right) \left(x+4\right)
    \end{equation} 
    In the quadratic equation above, $a$ is a nonzero constant.
    The graph of the equatino in the $xy$-plane is a parabola with vertex $(c,d)$.
    Which of the following is equal to $d$?
    \begin{choices}
        \wrongchoice{$-9a$}
        \wrongchoice{$-8a$}
        \wrongchoice{$-5a$}
        \wrongchoice{$-2a$}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t03-q13}
    The equation
    \begin{equation}
        \frac{24x^2 + 25x - 47}{ax-2} = -8x -3 - \frac{53}{ax-2}
    \end{equation} 
    is true for all values of $x\neq \dfrac{2}{a}$,
    where $a$ is a constant.
    What is the value of $a$ ?
    \begin{choices}
        \wrongchoice{$-16$}
        \wrongchoice{$-3$}
        \wrongchoice{$3$}
        \wrongchoice{$16$}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t03-q14}
    What are the solutions to $3x^2+12x+6=0$ ?
    The equation
    \begin{choices}
        \wrongchoice{$x = -2 \pm \sqrt{2}$}
        \wrongchoice{$x = -2 \pm \frac{\sqrt{30}}{3}$}
        \wrongchoice{$x = -6 \pm \sqrt{2}$}
        \wrongchoice{$x = -6 \pm 6\sqrt{2}$}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t03-q15}
    \begin{equation}
        C = \frac{5}{9} \left( F-32 \right)
    \end{equation}
    The equation above show how a temperature $F$,
        measured in degrees Fahrenheit,
        relates to a temperature $C$,
        measured in degree Celsius.
    Which of the following must be true?
    \begin{center}
    \begin{tabu}
        I & A temperature increase of 1 degree Fahrenheit is equavalent to a temperature increase of $\dfac{5}{9}$ degree Celsius. \\
       II & A temperature increase of 1 degree Celsius is equivalent to a temperature increase of 1.8 degrees Fahrenheit.
      III & A temperature increase of $\dfrac{5}{9}$ degree Fahrenheit is equivalent to a temperature increase of 1 degree Celsius.
    \end{tabu}
    \end{center}
    \begin{choices}
        \wrongchoice{I only}
        \wrongchoice{II only}
        \wrongchoice{III only}
        \wrongchoice{I and II only}
    \end{choices}
\end{question}
}


%% https://collegereadiness.collegeboard.org/pdf/sat-practice-test-4.pdf


\element{sat-mc}{
\begin{question}{math-t04-q01}
    Which of the following expressions is equal to $0$ for some value of $x$ ?
    \begin{choices}
        \wrongchoice{$\left| x-1 \right| - 1$}
        \wrongchoice{$\left| x+1 \right| + 1$}
        \wrongchoice{$\left| 1-x \right| + 1$}
        \wrongchoice{$\left| x-1 \right| + 1$}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t04-q02}
    \begin{equation}
        f(x) = \frac{3}{2} x + b
    \end{equation}
    In the function above, $b$ is a constant.
    If $f(6) = 7$, 
        What is the value of $f(-2)$?
    \begin{choices}
        \wrongchoice{$-5$}
        \wrongchoice{$-2$}
        \wrongchoice{$1$}
        \wrongchoice{$7$}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t04-q03}
    \begin{equation}
        \frac{x}{y} = 6 \\
        4 (y+1) = x \\
    \end{equation}
    If $(x,y)$ is the solution to the system of equations above,
        what is the value of $y$ ?
    \begin{choices}
        \wrongchoice{2}
        \wrongchoice{4}
        \wrongchoice{12}
        \wrongchoice{24}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t04-q04}
    If $f(x) = -2x + 5$, what if $f(-3x)$ equal to ?
    \begin{choices}
        \wrongchoice{$-6x-5$}
        \wrongchoice{$6x+5$}
        \wrongchoice{$6x+5$}
        \wrongchoice{$6x^2-15x$}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t04-q05}
    \begin{equation}
        3 \left(2x+1\right) \left(4x+2\right)
    \end{equation}
    Which of the following is equivalent to the expression above?
    \begin{choices}
        \wrongchoice{$45x$}
        \wrongchoice{$24x^2 +3$}
        \wrongchoice{$24x^2 +18x +3$}
        \wrongchoice{$18x^2 +6$}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t04-q06}
    If $\dfrac{a-b}{b} = \dfrac{3}{7}$,
        which of the following must also be true?
    \begin{choices}
        \wrongchoice{$\dfrac{a}{b} = -\dfrac{4}{7}$}
        \wrongchoice{$\dfrac{a}{b} = \dfrac{10}{7}$}
        \wrongchoice{$\dfrac{a+b}{b} = \dfrac{10}{7}$}
        \wrongchoice{$\dfrac{a-2b}{b} = -\dfrac{11}{7}$}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t04-q07}
    While preparing to run a marathon, Amelia created a training schedule in which the distance of her longer run every week increase by a constant amount.
    If Amelia's training schedule required that her longest run in week 4 is a distnace 8 mjiles and her longest run in week 16 is a distance of 26 miles,
    which of the following best describes how the distance Amelias runs changes between week 4 and week 16 of her training schedule?
    \begin{choices}
        \wrongchoice{Amelia increases the distance of her longest run by 0.5 miles each week.}
        \wrongchoice{Amelia increases the distance of her longest run by 2 miles each week.}
        \wrongchoice{Amelia increases the distance of her longest run by 2 miles each 3 weeks.}
        \wrongchoice{Amelia increases the distance of her longest run by 1.5 miles each 3 week.}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t04-q08}
    Which of the following equations represents a line that is parallel to the line with equation $y=-3x+4$.
    \begin{choices}
        \wrongchoice{$6x + 2y = 15$}
        \wrongchoice{$3x - y = 7$}
        \wrongchoice{$2x - 3y = 6$}
        \wrongchoice{$x + 3y = 1$}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t04-q09}
    \begin{equations}
        \sqrt{x-a} = x-4
    \end{equations}
    If $a=2$, what is the solution  set of the equation above?
    \begin{choices}
        \wrongchoice{$\left{ 3,7 \right}$}
        \wrongchoice{$\left{ 2 \right}$}
        \wrongchoice{$\left{ 3 \right}$}
        \wrongchoice{$\left{ 6 \right}$}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t04-q10}
    If $\dfrac{t+5}{t-5} = 10$,
        what is the value of $t$?
    \begin{choices}
        \wrongchoice{$\dfrac{45}{11}$}
        \wrongchoice{$5$}
        \wrongchoice{$\dfrac{11}{2}$}
        \wrongchoice{$\dfrac{55}{9}$}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t04-q11}
    \begin{equation}
        x = 2y + 5 \\
        y = \left(2x -3\right) \left(x+9\right)
    \end{equation}
    How many order pairs $(x,y)$ satisfy system of equations show above?
    \begin{choices}
        \wrongchoice{$0$}
        \wrongchoice{$1$}
        \wrongchoice{$2$}
        \wrongchoice{Infinitely many}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t04-q12}
    Ken and Pual each ordered a sandwich at a restaurant.
    The price of Ken's sanwich was $x$ dollars,
        and the price of Paul's sandwich was \$1 more than the price of Ken's sandwich.
    If Ken and Paul split the cost of the sandwiches event and paid a 20\% tip,
        which of the following expressoing represents the amount, in dollars, each of them paid?
    (Assume there is no sales tax.)
    \begin{choices}
        \wrongchoice{$0.2 x + 0.2$}
        \wrongchoice{$0.5 x + 0.1$}
        \wrongchoice{$1.2 x + 0.6$}
        \wrongchoice{$2.4 x + 1.2$}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t04-q13}
    \begin{center}
    \begin{tikzpicture}
        % pgfplots 
    \end{tikzpicture}
    \end{center}
    The functions $f$ and $g$,
    defined by $f(x)=8x^2 -2$ and $g(x)=-ix^2+2$,
        are graphed in the $xy$-plane above.
    The graphs of $f$ and $g$ intersect at the points $(k,0)$ and $(-k,0)$.
    What is the value of $k$?
    \begin{choices}
        \wrongchoice{$\dfrac{1}{4}$}
        \wrongchoice{$\dfrac{1}{2}$}
        \wrongchoice{$1$}
        \wrongchoice{$2$}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t04-q14}
    \begin{equation}
        \frac{8-i}{3-2i}
    \end{equation}
    If the expression above is rewritten in the form $a+bi$,
        where $a$ and $b$ are real numbers,
        what is the value of $a$? (Note: $i=\sqrt{-1}$
    \begin{choices}
        \wrongchoice{$2$}
        \wrongchoice{$\frac{8}{3}$}
        \wrongchoice{$3$}
        \wrongchoice{$\frac{11}{3}$}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t04-q15}
    \begin{equation}
        x^2 - \frac{k}{2} x = 2p
    \end{equation}
    In the quadratic equation above, $k$ and $p$ are constants.
    What are the solutions for $x$?
    \begin{choices}
        \wrongchoice{$x = \frac{k}{4}\pm \frac{\sqrt{k^2+2p}}{4}$}
        \wrongchoice{$x = \frac{k}{4}\pm \frac{\sqrt{k^2+32p}}{4}$}
        \wrongchoice{$x = \frac{k}{2}\pm \frac{\sqrt{k^2+2p}}{4}$}
        \wrongchoice{$x = \frac{k}{2}\pm \frac{\sqrt{k^2+32p}}{4}$}
    \end{choices}
\end{question}
}


%% https://collegereadiness.collegeboard.org/pdf/sat-practice-test-5.pdf

\element{sat-mc}{
\begin{question}{math-t05-q01}
    \begin{center}
    \begin{tikzpicture}

    \end{tikzpicture}
    \end{center}
    Which os the following is an equation of line $l$ in the $xy$-plane above?
    \begin{choices}
        \wrongchoice{$x=1$}
        \wrongchoice{$y=1$}
        \wrongchoice{$y=x$}
        \wrongchoice{$y=x+1$}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t05-q02}
    \begin{center}
    \begin{tikzpicture}

    \end{tikzpicture}
    \end{center}
    The circle above with center $O$ has circumference of $36$.
    What is the length of minor arc $\ovarbar AC$?
    \begin{choices}
        \wrongchoice{$x=1$}
        \wrongchoice{$y=1$}
        \wrongchoice{$y=x$}
        \wrongchoice{$y=x+1$}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t05-q03}
    what are the solutions of the quadratic equation
        $4x^2 - 8x - 12=0$ ?
    \begin{choices}
        \wrongchoice{$x=-1$ and $x=-3$}
        \wrongchoice{$x=-1$ and $x=3$}
        \wrongchoice{$x=1$ and $x=-3$}
        \wrongchoice{$x=1$ and $x=3$}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t05-q04}
    Which of teh following is an example of a function whose graph in $xy$-plane has no $x$-intercepts?
    \begin{choices}
        \wrongchoice{A linear function whose rate of change is not zero}
        \wrongchoice{A quadratic function with real zeros}
        \wrongchoice{A quadratic function with no real zeros}
        \wrongchoice{A cubic polynomial with at least one real zero}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t05-q05}
    \begin{equation}
        \sqrt{k+2}-x = 0
    \end{equation}
    In the equation above, $k$ is a constant.
    If $x=9$, what is the value of $k$?
    \begin{choices}
        \wrongchoice{1}
        \wrongchoice{7}
        \wrongchoice{16}
        \wrongchoice{79}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t05-q06}
    Which of the following is equivalent to the sum of the expressions $a^2-1$ and $a+1$?
    \begin{choices}
        \wrongchoice{$a^2 + a$}
        \wrongchoice{$a^3 - 1$}
        \wrongchoice{$2a^2$}
        \wrongchoice{$a^3$}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t05-q07}
    Jackie has two summer jobs.
    She works as a tutor,
        which pays \$12 per hour, and she works as a lifeguard,
        which pays \$9.50 per hour.
    She can work no more than 20 hours per week,
        but she want to earn at least \$220 per week.
    Which of the following systems of inequalities represents this situation in terms of $x$ and $y$,
        where $x$ is the number of hours she tutors and $y$ is the number of hours she works as a lifegaurd?
    \begin{choices}
        \wrongchoice{$12x + 9.5y \leq 220$}
        Think about best practices
        \wrongchoice{$12x + 9.5y \leq 220$}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t05-q08}
    In air, the speed of sound $S$, in meters per second,
        is a linear function os the air temperature $T$,
        in degrees Celsius, and is given by $S(T) = 0.6T+331.4$.
    Which of the following statement is the best interpretation of the number $331.4$ in this contex?
    \begin{choices}
        \wrongchoice{The speed of sound, in meters per second, at \SI{0}{\degreeCelsius}}
        \wrongchoice{The speed of sound, in meters per second, at \SI{0.6}{\degreeCelsius}}
        \wrongchoice{The increase of the speed of sound, in meters per second,
            that corresponds to an increase of \SI{1}{\degreeCelsiu}}
        \wrongchoice{The increase in the speed of sound, in meters per second,
            that correspond to an increase of \SI{0.6}{\degreeCelsius}}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t05-q09}
    \begin{equation}
        y      &= x^2 \\
        2y + 6 &= 2\left(x+3\right)
    \end{equation}
    If $(x,y)$ is a solution of the system of equations above and $x>0$,
        what is the value of $xy$?
    \begin{choices}
        \wrongchoice{1}
        \wrongchoice{2}
        \wrongchoice{3}
        \wrongchoice{9}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t05-q10}
    If $a^2+b^2=z$ and $ab=y$, which of the following is equivalent to $4z+8y$?
    \begin{choices}
        \wrongchoice{$\left(  a + 2b \right)^2$}
        \wrongchoice{$\left( 2a + 2b \right)^2$}
        \wrongchoice{$\left( 4a + 4b \right)^2$}
        \wrongchoice{$\left( 4a + 8b \right)^2$}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t05-q11}
    The volume of a right circular cylinder $A$ is 22 cubic centimeters.
    What is the volume, in cubic centimeters, of a right circular cylinder with twice the radius and half the height of cylinder $A$?
    \begin{choices}
        \wrongchoice{$11$}
        \wrongchoice{$22$}
        \wrongchoice{$44$}
        \wrongchoice{$66$}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t05-q12}
    Which of the following is equivalent to $9^{\dfrac{3}{4}}$ ?
    \begin{choices}
        \wrongchoice{$\sqrt[3]{9}$}
        \wrongchoice{$\sqrt[4]{9}$}
        \wrongchoice{$\sqrt{3}$}
        \wrongchoice{$3\sqrt{3}$}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t05-q13}
    At a restaurant, $n$ cups of tea are made by adding $t$ tea bags to hot water.
    If $t-n+2$, how many additinoal tea bags are needed to make each additional cup of tea?
    \begin{choices}
        \wrongchoice{None}
        \wrongchoice{One}
        \wrongchoice{Two}
        \wrongchoice{Three}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t05-q14}
    \begin{equation}
        f(x) = 2^x + 1
    \end{equation}
    The function $f$ is defined by the equation above.
    Which of the following is the graph of $y=-f(x)$ in the $xy$-plane?
    If $t-n+2$, how many additinoal tea bags are needed to make each additional cup of tea?
    \begin{choices}
        \wrongchoice{
            \begin{tikzpicture}
                %% pgfplots
            \end{tikzpicture}
        }
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t05-q15}
    Alan drives an average of 100 miles each week.
    His car can travel an average of 25 miles per gallon of gasoline.
    Alan would like to reduce his weekly expenditure on gasoline by \$5.
    Assuming gasoline costs \$4 per gallon, which equation can Alan use to determine how many fewer average miles, $m$ he should drive each week.
    \begin{choices}
        \wrongchoice{$\dfrac{25}{4}m = 95$}
        \wrongchoice{$\dfrac{25}{4}m = 5$}
        \wrongchoice{$\dfrac{4}{25}m = 95$}
        \wrongchoice{$\dfrac{4}{25}m = 5$}
    \end{choices}
\end{question}
}

%% https://collegereadiness.collegeboard.org/pdf/sat-practice-test-6.pdf

\element{sat-mc}{
\begin{question}{math-t06-q01}
    Salim wants to purchase tickets from a vendor to watch a tennis match.
    The vendor charges a one-time service fee for processing the purchase of the tickets.
    The equation $t=15n=12$ represents the total amount $T$, in dollars, Salime will pay for $n$ tickets.
    What does 12 represent in the equation?
    \begin{choices}
        \wrongchoice{The price of one ticket, in dollars}
        \wrongchoice{The amount of the service fee, in dollars}
        \wrongchoice{The total amount, in dollars, Salim will pay for one ticket}
        \wrongchoice{The total amount, in dollars, Salim will pay for any number of tickets}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t06-q02}
    A gardener buys two kinds of fertilizer.
    Fertizilizer $A$ contain 60\% filler materials by weight
        and Fertilizer $B$ contains 40\% filler material by weight.
    Together, the fertilizers bought by the gardener contain a total of 240 pounds of filler materials.
    Which equation models this relationship,
        where $x$ is the number of pounts of Fertilizer $A$
            and $y$ is the number of pounds of Fertilizer $B$?
    \begin{choices}
        \wrongchoice{$0.4x = 0.6y = 240$}
        \wrongchoice{$0.6x = 0.4y = 240$}
        \wrongchoice{$40x = 60y = 240$}
        \wrongchoice{$60x = 40y = 240$}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t06-q03}
    What is the sum of the complex numbers $2+3i$ and $4+8i$,   
        what $i=\sqrt{-1}$?
    \begin{choices}
        \wrongchoice{17}
        \wrongchoice{17i}
        \wrongchoice{$6 + 11i$}
        \wrongchoice{$8 + 24i$}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t06-q04}
    \begin{equation}
        4x^2 - 9 = \left(px+t\right)\left(px-t\left)
    \end{equation}
    In the equation above, $p$ and $t$ are constants.
    Which of the following could be the value of $p$?
    \begin{choices}
        \wrongchoice{2}
        \wrongchoice{3}
        \wrongchoice{4}
        \wrongchoice{9}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t06-q05}
    Which of the following is the graph of the equation $y-2x-5$ in the $xy$-plane?
    \begin{choices}
        \wrongchoice{
            \begin{tikzpicture}
                %% pgfplots
            \end{tikzpicture}
        }
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t06-q06}
    If $x=\dfrac{2}{3}y$ and $y=18$, what is the value of $2x-3$?
    \begin{choices}
        \wrongchoice{21}
        \wrongchoice{15}
        \wrongchoice{12}
        \wrongchoice{10}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t06-q07}
    A bricklayer uses the formula $n=7lh$ to estimate the number of bricks, $n$,
        need to build a wall that is $l$ feet long and $h$ feet high.
    Which of the following terms correctly expresses $l$ in terms of $n$ and $h$?
    \begin{choices}
        \wrongchoice{$l = \dfrac{7}{nh}$}
        \wrongchoice{$l = \dfrac{h}{7n}$}
        \wrongchoice{$l = \dfrac{n}{7h}$}
        \wrongchoice{$l = \dfrac{n}{7+h}$}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t06-q08}
    \begin{center}
    \begin{tabu}[XXX]
        $x$ & $w(x)$ & $t(x)$ \\
        $1$ & $-1$   & $-3$   \\
        $2$ & $ 3$   & $-1$   \\
        $3$ & $ 4$   & $ 1$   \\
        $4$ & $ 3$   & $ 3$   \\
        $5$ & $-1$   & $ 5$   \\
    \end{tabu}
    \end{center}
    The table above shows some values of the functoins $w$ and $t$.
    For which value of $x$ is $w(x) + t(x) = x$?
    \begin{choices}
        \wrongchoice{1}
        \wrongchoice{2}
        \wrongchoice{3}
        \wrongchoice{4}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t06-q09}
    If $\sqrt{x} + \sqrt{9} = \sqrt{64}$, what is the value of $x$?
    \begin{choices}
        \wrongchoice{$\sqrt{5}$}
        \wrongchoice{$5$}
        \wrongchoice{$25$}
        \wrongchoice{$55$}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t06-q10}
    Jaime is preparing for a bicyle race.
    His goal is to bicyle an average of at least 280 miles per week for 4 weeks.
    He bicycle 240 miles the first week,
        310 miles the second week,
        and 320 miles the third week.
    Which inequality can be used to represent the number of miles, $x$,
        Jaime could biclce on the 4th week to meet his goal?
    \begin{choices}
        \wrongchoice{$\dfrac{240+310+320}{3} + x \geq 280$}
        \wrongchoice{$240+310+320 \geq x \left(280\right)_$}
        \wrongchoice{$\dfrac{240}{4} + \dfrac{310}{4} + \dfrac{320}{4} + x \geq 280$}
        \wrongchoice{$240+310+320 + x \geq 4\left(280\right)$}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t06-q11}
    \begin{center}
    \begin{tikzpicture}
        %% PGFPLOTS
    \end{tikzpicture}
    \end{center}
    The vertex of the parabola in the $xy$-plane above is $(0,c)$.
    Which of the following is true about the parabola with the equation $y=-a\left(x-b\right)^2 + c$?
    \begin{choices}
        \wrongchoice{The vertex if $(b,c)$ and the graph opens upward.}
        \wrongchoice{The vertex if $(b,c)$ and the graph opens downward.}
        \wrongchoice{The vertex if $(-b,c)$ and the graph opens upward.}
        \wrongchoice{The vertex if $(-b,c)$ and the graph opens downward.}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t06-q12}
    Which of the following is equivalent to $\dfrac{4x^2 = 6x}{4x+2}$ ?
    \begin{choices}
        \wrongchoice{$x$}
        \wrongchoice{$x+4$}
        \wrongchoice{$x - \dfrac{2}{4x+2}$}
        \wrongchoice{$x+1 - \dfrac{2}{4x+2}$}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t06-q13}
    \begin{equation}
        2x^2 - 4x = t
    \end{equation}
    In the equation above, $t$ is a constant.
    If the equation has no real solutions, 
        which of the following could be the value of $t$?
    \begin{choices}
        \wrongchoice{$-3$}
        \wrongchoice{$-1$}
        \wrongchoice{$1$}
        \wrongchoice{$3$}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t06-q14}
    A laundry server is buying detergent and fabric softener for it supplier.
    The supplier will deliver no more than 300 pounds in a shipment.
    Each container of detergent weighs 7.35 pounds,
        and each container of fabric softener weight 6.2 pounds.
    The server want to buy at least twice as many container of detergent as containers of fabric softener.
    Let $d$ represent the number of containers of fabric software, where $d$ and $s$ are nonnegative integers.
    Which of the following system of inequalities best represents this situation?
    \begin{choices}
        \wrongchoice{$7.35d + 6.2s \leq 300$
                     $d \leq 2s$
        }
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t06-q15}
    Which of the following is equivalent to $\left( a + \dfrac{b}{2} \right) ^2$
    \begin{choices}
        \wrongchoice{$a^2 + \dfrac{b^2}{2}$}
        \wrongchoice{$a^2 + \dfrac{b^2}{4}$}
        \wrongchoice{$a^2 + \dfrac{ab}{2} + \dfrac{b^2}{2}$}
        \wrongchoice{$a^2 + ab + \dfrac{b^2}{4}$}
    \end{choices}
\end{question}
}


%% https://collegereadiness.collegeboard.org/pdf/sat-practice-test-7.pdf


\element{sat-mc}{
\begin{question}{math-t07-q01}
    \begin{equation}
        x + y = 75
    \end{equation}
    The equation above relates the number of minutes, $x$,
        Maria spends running each day and the number of minutes, $y$,
        she spend biking each day.
    In the equation, what does the number 75 represent?
    \begin{choices}
        \wrongchoice{The number of minutes spend running each day}
        \wrongchoice{The number of minutes spend biking each day}
        \wrongchoice{The total number of minutes spend running and biking each day}
        \wrongchoice{The number of minutes spend biking for each minutes spend running}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t07-q02}
    Which of the following is equivalent to $3(x+5)-6$
    \begin{choices}
        \wrongchoice{$3x - 3$}
        \wrongchoice{$3x - 1$}
        \wrongchoice{$3x + 9$}
        \wrongchoice{$15x - 6$}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t07-q03}
    \begin{equation}
        x = y-3 \\
        \frac{x}{2} + 2y = 6
    \end{equation}
    Which ordered pair $(x,y)$ satisfied the system of equations shown above?
    \begin{choices}
        \wrongchoice{$(-3,0)$}
        \wrongchoice{$(0,3)$}
        \wrongchoice{$(6,-3)$}
        \wrongchoice{$(36,-6)$}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t07-q04}
    Which of the following complex numbers is equal to
    \begin{equation}
        \left(5+12i\right) - \left(9i^2-6i\right),
    \end{equation}
    for $i=\sqrt(-1)$ ?
    \begin{choices}
        \wrongchoice{$-14 - 18i$}
        \wrongchoice{$-4 - 6i$}
        \wrongchoice{$ 4 + 6i$}
        \wrongchoice{$14 + 18i$}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t07-q05}
    If $f(x) = \frac{x^2-6x+3}{x-1}$, what is $f(-1)$ ?
    \begin{choices}
        \wrongchoice{$-5$}
        \wrongchoice{$-2$}
        \wrongchoice{$2$}
        \wrongchoice{$5$}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t07-q06}
    A company that makes wilflife videos purchases camera equipment for \$32,400.
    The equipment depreciates in value at constant rate for 12 years,
        after which it is consider to have no monitary value.
    How much is the camer camera equipment worth 4 years after it is purchased?
    \begin{choices}
        \wrongchoice{\$10,800}
        \wrongchoice{\$16,200}
        \wrongchoice{\$21,600}
        \wrongchoice{\$29,700}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t07-q07}
    \begin{equation}
        X^2 + 6x + 4
    \end{equation}
    Which of the following is equivalent to the expression above?
    \begin{choices}
        \wrongchoice{$\left( x+3 \right)^2 + 5$}
        \wrongchoice{$\left( x+3 \right)^2 - 5$}
        \wrongchoice{$\left( x-3 \right)^2 + 5$}
        \wrongchoice{$\left( x-3 \right)^2 - 5$}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t07-q08}
    Ken is working this summer as part of a crew on a farm.
    He earned \$8 per hour for the first 10 hours he worked this week.
    Because of his performance,
        his crew leader raise his salary to \$10 per hour for the reest of the week.
    When is the least number of hours he must work the rest of the week to save at least \$270 for the week?
    \begin{choices}
        \wrongchoice{38}
        \wrongchoice{33}
        \wrongchoice{22}
        \wrongchoice{16}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t07-q09}
    Marisa need to hire at least 10 staff members for an upcoming project.
    The staff members will be made up of junior director, who will be paid \$640 per week,
        and senior directors,
        who will be paid \$880 per week.
    Her budget for paying the staff members is no more than \$9,700 per week.
    She must hire at least 3 junior directors and at least 1 senior director.
    Which of the following systems of inequalities represents the conditions described if $x$ is the number of junior directors and $y$ is the number of senior directors?
    \begin{choices}
        \wrongchoice{
            \begin{equation}
                640x + 880y \geq 9,7000 \\
                x + y \leq 10 \\
                x \geq 3 \\
                y \geq 1 \\
            \end{equation}
        }
        \wrongchoice{}
    \end{choices}
\end{question}
}


\element{sat-mc}{
\begin{question}{math-t07-q10}
    \begin{equation}
        ax^3 + bx^2 + cx + d = 0
    \end{equation}
    In the equation above, $a$, $b$, $c$, and $d$ are constants.
    If the equation has roots $-1$, $-3$, and $5$, which of the following factors of $ax^3 + bx^2 +cx + d$?
    \begin{choices}
        \wrongchoice{$x-1$}
        \wrongchoice{$x+1$}
        \wrongchoice{$x-3$}
        \wrongchoice{$x+5$}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t07-q11}
    The expression $\dfrac{x^{-2}y^{\dfrac{1}{2}}}{x^{\dfrac{1}{3}}y^{-1}}$,
        where $x>1$ and $y>1$, is equivalent to which of the following?
    \begin{choices}
        \wrongchoice{$\dfrac{\sqrt{y}}{\sqrt[3]{x^2}}$}
        \wrongchoice{$\dfrac{y\sqrt{y}}{\sqrt[3]{x^2}}$}
        \wrongchoice{$\dfrac{y\sqrt{y}}{x\sqrt{x}}$}
        \wrongchoice{$\dfrac{y\sqrt{y}}{x^2\sqrt[3]{x}$}}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t07-q12}
    The function $f$ is defined by $f(x)=\left(x+3\right)\left(x+1\right)$.
    The graph of $f$ in the $xy$-plane is a parabola.
    Which of the following intervals contain the $x$-coordinate of the vertex of the graph of $f$?
    \begin{choices}
        \wrongchoice{$-4 < x < -3$}
        \wrongchoice{$-3 < x <  1$}
        \wrongchoice{$ 1 < x <  3$}
        \wrongchoice{$ 3 < x <  4$}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t07-q13}
    Which of the following expressions is equivalent to
    \begin{equation}
        \frac{x^2 - 2x -5}{x-3}
    \end{equation}
    \begin{choices}
        \wrongchoice{$x - 5 - \dfrac{20}{x-3}$}
        \wrongchoice{$x - 5 - \dfrac{20}{x-3}$}
        \wrongchoice{$x + 1 - \dfrac{8}{x-3}$}
        \wrongchoice{$x + 1 - \dfrac{2}{x-3}$}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t07-q14}
    A shipping service restricts the dimensions of the boxes it will ship for a certain type of service.
    The restriction states that for boxes shaped like rectangular prisms,
        the sum of the perimeter of the base of the box and height of the box cannot exceed 130 inches.
    The perimeter of the base is determined using with width and length of the box.
    if a box has a height of 60 inches and its length if 2.5 times the width,
        which inequaltiy shows the allowable width $x$, in inches, of the box?
    \begin{choices}
        \wrongchoice{$0 < x \leq 10$}
        \wrongchoice{$0 < x \leq 11\dfrac{2}{3}$}
        \wrongchoice{$0 < x \leq 17\dfrac{1}{2}$}
        \wrongchoice{$0 < x \leq 20$}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t07-q15}
    The expression $\dfrac{1}{3}x^2 - 2$ can be rewritten as
         $\dfrac{1}{3}\left(x-k\right)\left(x+k\right)$, where $k$ is a positive contant.
    What is the value of $k$?
    \begin{choices}
        \wrongchoice{$2$}
        \wrongchoice{$6$}
        \wrongchoice{$\sqrt{2}$}
        \wrongchoice{$\sqrt{5}$}
    \end{choices}
\end{question}
}

%% https://collegereadiness.collegeboard.org/pdf/sat-practice-test-8.pdf

\element{sat-mc}{
\begin{question}{math-t08-q01}
    One pound of grapes costs \$2.
    At this rate,
        how many dollars will $c$ pounds of grapes cost?    
    \begin{choices}
        \wrongchoice{$2c$}
        \wrongchoice{$2+c$}
        \wrongchoice{$\dfrac{2}{c}$}
        \wrongchoice{$\dfrac{c}{2}$}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t08-q02}
    Tracey collects, sells, and trades figurines,
         and she tracks the number of figurines in her collection on the graph below.
    \begin{center}
    \begin{tikzpicture}
        %% pdfplots
    \end{tikzpicture}
    \end{center}
    On what interval did the number of figurines decrease the fastest?
    \begin{choices}
        \wrongchoice{between 1 and 2 months}
        \wrongchoice{between 2 and 3 months}
        \wrongchoice{between 3 and 4 months}
        \wrongchoice{between 4 and 5 months}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t08-q03}
    In a random sample of 200 cars of a particular model,
        3 have a manufacturing defect.
    At this rate, how many of 10,000 cars of the same model will have a manufacturing defect.
    \begin{choices}
        \wrongchoice{150}
        \wrongchoice{200}
        \wrongchoice{250}
        \wrongchoice{300}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t08-q04}
    \begin{center}
    \begin{tikzpicture}
        %% pgfplots
    \end{tikzpicture}
    \end{center}
    The scatterplot above shows data collected on the lengths and widiths if \emph{Iris setosa} petals.
    A line of best fit for the data is shown.
    Based on the line of best fit,
        if the width of an /emph{Iris setosa} petal is 19 millimeters,
        what is the predicted length, in millimeters,
        of the petal?
    \begin{choices}
        \wrongchoice{21.10}
        \wrongchoice{31.73}
        \wrongchoice{52.83}
        \wrongchoice{55.83}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t08-q05}
    \begin{center}
    \begin{tikzpicture}
        %% diagrams
    \end{tikzpicture}
    \end{center}
    In the figure above, lines $l$ and $m$ are parallel,
        $y=20$, and $z=60$.
    What is the value of $x$?
    \begin{choices}
        \wrongchoice{120}
        \wrongchoice{100}
        \wrongchoice{90}
        \wrongchoice{80}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t08-q06}
    Two types of tickets were sold for a concert held at an amphitheater.
    Tickets to sit on a bench during the concert cost \$75 each,    
        and tickets to sit on the law during the concert cost \$40 each.
    Organizer of the concert annouced that 350 tickets had been sold and the \$19,250 has been raised through ticket sales alone.
    Which of teh following systems of equations could be used the find the number of tickets for bench sets, $B$,
        and the number of tickets for lawn seats, $L$, that were sold for the concert?
    \begin{choices}
        \wrongchoice{$\left(75B\right) \left(40L\right) = 1,9510$
                     $B + L = 350$
        }
        \wrongchoice{100}
        \wrongchoice{90}
        \wrongchoice{80}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t08-q07}
    In the $xy$-plane, the graph of which of the following equations is a line with a slope of 3?
    \begin{choices}
        \wrongchoice{$y=\dfrac{1}{3}x$}
        \wrongchoice{$y=x-3$}
        \wrongchoice{$y=3x+2$}
        \wrongchoice{$y=6x+3$}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t08-q08}
    \begin{equation}
        x+1 = \frac{1}{x+1}
    \end{equation}
    In the equation above,
        which of the following is a possible value of $x+1$?
    \begin{choices}
        \wrongchoice{$1-\sqrt{2}$}
        \wrongchoice{$\sqrt{2}$}
        \wrongchoice{$2$}
        \wrongchoice{$4$}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t08-q09}
    % \recyle command
    The glass pictures above can hold a maximum volume of 473 cubic centimeters,
        which is approximately 16 fluid ounces?
    % start questioid
    What is the value of $k$ in centimeter?
    \begin{choices}
        \wrongchoice{2.52}
        \wrongchoice{7.67}
        \wrongchoice{7.79}
        \wrongchoice{10.11}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t08-q10}
    % \recyle command
    % start questioid
    Water pours into the glass slowly and at a constant rate.
    Which of the following graphs best illustrates the height of the water level in the glass as it fills?
    \begin{choices}
        \wrongchoice{
        \begin{tikzpicture}
            %% PGFplogs
        \end{tikzpicture}
        }
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t08-q11}
    % \recyle command
    % start questioid
    Jenny has a pitchers that contains 1 gallon of water.
    How mnay times could Jenny completely fill the glass with 1 gallone of water?
    $( 1 gallone = 128 fluid ounces )
    \begin{choices}
        \wrongchoice{16}
        \wrongchoice{8}
        \wrongchoice{4}
        \wrongchoice{3}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t08-q12}
    Roberto is an insurance agent who sells two types of policies:
        a \%50,000 policy and a \$100,000 policy.
    Last month, his goal was to sell at least 57 insurance policies.
    While he did not meet his goal, the total value of the policies he sold was over \$3,000,000.
    Which of teh following systems of inequalities describes $x$,
        The possible number of \$50,000 policies, and $y$, the possible number of \$100,000 policies,
        that Roberto sold last month?
    \begin{choices}
        \wrongchoice{$x+x<50$}
        % format help
        \wrongchoice{$x+x<50$}
        \wrongchoice{$x+x<50$}
        \wrongchoice{$x+x<50$}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t08-q13}
    If $a^{-\dfrac{1}{2}} = x$, what $a>0$, what is $a$ in terms of $x$?
    \begin{choices}
        \wrongchoice{$sqrt{x}$}
        \wrongchoice{$-sqrt{x}$}
        \wrongchoice{$\dfrac{1}{x^2}$}
        \wrongchoice{$-1\dfrac{1}{x^2}$}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t08-q14}
    Which of the following is a value of $x$ for which the expression
        $\dfrac{-3}{x^2+3x-10}$ is undefined?
    \begin{choices}
        \wrongchoice{$-3$}
        \wrongchoice{$-2$}
        \wrongchoice{$0$}
        \wrongchoice{$2$}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t08-q15}
    A granite block in the shape of a right rectangular prism has dimensions 30 centimeters by 40 centimeters by 50 centimeters.
    The block has a density of 2.8 grams per cubic centimeter.
    What is the mass of the block, in grams?
    (Density is mass per unit volume.)
    \begin{choices}
        \wrongchoice{336}
        \wrongchoice{3,360}
        \wrongchoice{16,800}
        \wrongchoice{168,000}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t08-q16}
    \begin{center}
    \begin{tabu}{XXXX}
    \end{tabu}
    \end{center}
    The table shows the results of a research study that investigated the therapeurtic value of Vitamin C in preventing colds.
    A random sample of 300 adults received either a vitamin C pill or a sugar pill each day during a 2-week period,
        and the adults reported whether they contacted a cold during that time period.
    What proportion of adults who received a sugar pill reported contacting a cold? 
    \begin{choices}
        \wrongchoice{$\dfrac{11}{18}$}
        \wrongchoice{$\dfrac{11}{50}$}
        \wrongchoice{$\dfrac{9}{50}$}
        \wrongchoice{$\dfrac{11}{100}$}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t08-q17}
    \begin{center}
    \begin{tabu}{XXXX}
    \end{tabu}
    \end{center}
    The table above shows the distribution of ages of 20 students enrolled in a college class.
    Which of the following gives the correct order of the means,
        median, and mode of the ages?
    \begin{choices}
        \wrongchoice{mode < median < mean}
        \wrongchoice{mode < mean < median}
        \wrongchoice{median < mode < mean}
        \wrongchoice{mean < mode < median}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t08-q18}
    The figure below shows the relationship between the percent of leaf litter mass remaining after decomposing for 3 years and the mean annual temperature,
         in degrees Celesius (\si{\degreeCelsiu}),
         in 38 forests in Canada.
    A line of best fit is also shown.
    \begin{center}
    \begin{tabu}{XXXX}
    \end{tabu}
    \end{center}
    A particular forest in Canada, whose data is not included in the figure,
        has a mean annual tempetature of \SI{-2}{\degreeCelsius}.
    Based on the line of best fit,
        which of the following is closest to the predicted percent of leaf litter mass remaining in this particular forest after decomposing for 3 years?
    \begin{choices}
        \wrongchoice{50\%}
        \wrongchoice{63\%}
        \wrongchoice{70\%}
        \wrongchoice{82\%}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t08-q19}
    The range of the polynomial function $f$ is the set of real numbers less than or equal to 4.
    If the zeros of the $f$ are $-3$ and $1$,
        which of the following could be the graph of $y=f(x)$ in the $xy$-plane?
    \begin{choices}
        \wrongchoice{
            \begin{tikzpicture}
                %% PGFplots
            \end{tikzpicture}
        }
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t08-q20}
    The average annual energy cost for a certain home is \$4,334.
    The homeowner plans to spend \$25,000 to install a geothermal heating system.
    The homeowner estimates that the average annual energy cost will then be \$2,712.
    Which of the following inequalities can be solved to find $t$,
        The number of years after installation at which the total amount of energy cost saving will exceed the installation cost?
    \begin{choices}
        \wrongchoice{$25,000 > \left(4,334 - 2,712\right) t$}
        \wrongchoice{$25,000 < \left(4,334 - 2,712\right) t$}
        \wrongchoice{$25,000 - 4,334 > 2,712 t$}
        \wrongchoice{$25,000 > \dfrac{4,332}{2,712} t$}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t08-q21}
    Between 1985 and 2003, data were collected every three years on the amount of plastic produced annual in the Units States, in billion of pounds.
    The graph below shows the data and a line of best fit.
    The equation of the line of best fit is $y=3.39x + 46.89$,
        where $x$ is the number of years since 1985 and $y$ is the amount of plastic produced annually,
        in billion of pounds.
    \begin{center}
    \begin{tikzpicture}
        %% plot
    \end{tikzpicture}
    \end{center}
    %% Start problem
    Which of the following is the best interpretation of the number 3.39 in the context of the problem?
    \begin{choices}
        \wrongchoice{The amount of plastic, in billion of pound,
                produced in the United States during the year 1985}
        \wrongchoice{The number of years it took the United States to produce 1 billion pounds of plastic}
        \wrongchoice{The average annual plastic production, in billions of pounds, in the United States from 1985 to 2003}
        \wrongchoice{The average annual increase, in billion of pounds,
                of plastic product per year in the United States from 1985 to 2003}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{math-t08-q22}
    Between 1985 and 2003, data were collected every three years on the amount of plastic produced annual in the Units States, in billion of pounds.
    The graph below shows the data and a line of best fit.
    The equation of the line of best fit is $y=3.39x + 46.89$,
        where $x$ is the number of years since 1985 and $y$ is the amount of plastic produced annually,
        in billion of pounds.
    \begin{center}
    \begin{tikzpicture}
        %% plot
    \end{tikzpicture}
    \end{center}
    %% Start problem
    Which of the following is closest to the percent increase in the billions of pounds of plastic produce in the United States from 2000 to 2003?
    \begin{choices}
        \wrongchoice{10\%}
        \wrongchoice{44\%}
        \wrongchoice{77\%}
        \wrongchoice{110\%}
    \end{choices}
\end{question}
}



\endinput


