
%%--------------------------------------------------
%% Grammar Mastery Test
%%--------------------------------------------------


%% Grammar Multiple Choice Questions
%%--------------------------------------------------
\element{grammar-mc}{
\begin{question}{grammar-Q01}
    Choose the correct sentence.
    \begin{choices}
      \correctchoice{Some of the dessert was left by the end of the birthday party.}
        \wrongchoice{Some of the dessert were left by the end of the birthday party.}
        \wrongchoice{Some of the desserts was left by the end of the birthday party.}
        \wrongchoice{Some desserts was left by the end of the birthday party.}
    \end{choices}
\end{question}
}

\element{grammar-mc}{
\begin{question}{grammar-Q02}
    Choose the correct sentence.
    \begin{choices}
        \wrongchoice{The papa bear thought that all of his porridge were missing.}
        \wrongchoice{The papa bear thought that none of his porridge were missing.}
        \wrongchoice{The papa bear thought that some of his porridge were missing.}
      \correctchoice{The papa bear thought that some of his porridge was missing.}
    \end{choices}
\end{question}
}

\element{grammar-mc}{
\begin{question}{grammar-Q03}
    Choose the correct sentence.
    \begin{choices}
        \wrongchoice{Your brilliant excuses almost makes up for your tardiness.}
      \correctchoice{Your brilliant excuses almost make up for your tardiness.}
        \wrongchoice{Your brilliant excuses makes up for your tardiness.}
        \wrongchoice{Your brilliant excuses has made up for your tardiness.}
    \end{choices}
\end{question}
}

\element{grammar-mc}{
\begin{question}{grammar-Q04}
    Choose the correct sentence.
    \begin{choices}
        \wrongchoice{Neither Jackson nor Jenna have played hooky.}
        \wrongchoice{Neither Jackson nor Jenna are playing hooky.}
      \correctchoice{Neither Jackson nor Jenna is playing hooky.}
        \wrongchoice{Neither Jackson nor Jenna were playing hooky.}
    \end{choices}
\end{question}
}

\element{grammar-mc}{
\begin{question}{grammar-Q05}
    Choose the correct sentence.
    \begin{choices}
      \correctchoice{Neither Jackson nor I am playing hooky.}
        \wrongchoice{Neither Jackson nor I is playing hooky.}
        \wrongchoice{Neither Jackson nor I are playing hooky.}
        \wrongchoice{Neither Jackson nor I were playing hooky.}
    \end{choices}
\end{question}
}

\element{grammar-mc}{
\begin{question}{grammar-Q06}
    Choose the correct sentence.
    \begin{choices}
        \wrongchoice{Either of us were capable of winning.}
        \wrongchoice{Either of us are capable of winning.}
        \wrongchoice{Either of us have been capable of winning.}
      \correctchoice{Either of us is capable of winning.}
    \end{choices}
\end{question}
}

\element{grammar-mc}{
\begin{question}{grammar-Q07}
    Choose the correct sentence.
    \begin{choices}
      \correctchoice{All of the class is willing to take part in the prank.}
        \wrongchoice{All of the classes is willing to take part in the prank.}
        \wrongchoice{All of the class are willing to take part in the prank.}
        \wrongchoice{All of the classes has been willing to take part in the prank.}
    \end{choices}
\end{question}
}

\element{grammar-mc}{
\begin{question}{grammar-Q08}
    Choose the correct sentence.
    \begin{choices}
        \wrongchoice{Some of the candies is on the table.}
        \wrongchoice{Some of the candies has been on the table.}
        \wrongchoice{Some of the candies was on the table.}
      \correctchoice{Some of the candies are on the table.}
    \end{choices}
\end{question}
}

\element{grammar-mc}{
\begin{question}{grammar-Q09}
    Choose the correct sentence.
    \begin{choices}
      \correctchoice{One-third of the voters tend not to cast their ballots in national elections.}
        \wrongchoice{One-third of the voters tends not to cast their ballots in national elections.}
        \wrongchoice{One-third of the voters tends not to cast its ballots in national elections.}
        \wrongchoice{One-third of the voters tends not to cast its ballot in national elections.}
    \end{choices}
\end{question}
}

\element{grammar-mc}{
\begin{question}{grammar-Q10}
    Choose the correct sentence.
    \begin{choices}
        \wrongchoice{Here is the paper clips you requested.}
        \wrongchoice{Here's the paper clips you requested.}
      \correctchoice{Here are the paper clips you requested.}
        \wrongchoice{Here are the box of paper clips you requested.}
    \end{choices}
\end{question}
}

\element{grammar-mc}{
\begin{question}{grammar-Q11}
    Choose the correct sentence.
    \begin{choices}
        \wrongchioce{She is one of those doctors which make house calls.}
      \correctchioce{She is one of those doctors who make house calls.}
        \wrongchioce{She is one of those doctors who makes house calls.}
        \wrongchioce{She is one of those doctors that makes house calls.}
    \end{choices}
\end{question}
}

\element{grammar-mc}{
\begin{question}{grammar-Q12}
    Choose the correct sentence.
    \begin{choices}
        \wrongchoice{Dr. Cresta is one of those professors who does whatever it takes to get his point across to his students.}
        \wrongchoice{Dr. Cresta is one of those professors who does whatever it takes to get their point across to their students.}
      \correctchoice{Dr. Cresta is a professor who do whatever it takes to get his point across to his students.}
        \wrongchoice{Dr. Cresta is one of those professors who do whatever it takes to get their point across to their students.}
    \end{choices}
\end{question}
}

\element{grammar-mc}{
\begin{question}{grammar-Q13}
    Choose the correct sentence.
    \begin{choices}
      \correctchoice{She is the only one of the professors who does what it takes to help her students.}
        \wrongchoice{She is the only one of the professors who do what it takes to help her students.}
        \wrongchoice{She, along with her colleagues, are professors who do what it takes to help their students.}
        \wrongchoice{She is one of many professors who does what it takes to help her students.}
    \end{choices}
\end{question}
}

\element{grammar-mc}{
\begin{question}{grammar-Q14}
    Choose the correct sentence.
    \begin{choices}
      \correctchoice{She and he are always fighting.}
        \wrongchoice{She and him are always fighting.}
        \wrongchoice{Her and him are always fighting.}
        \wrongchoice{He and her are always fighting.}
    \end{choices}
\end{question}
}

\element{grammar-mc}{
\begin{question}{grammar-Q15}
    Choose the correct sentence.
    \begin{choices}
        \wrongchoice{When Toni and him come over, we always have a great time.}
      \correctchoice{When Toni and he come over, we always have a great time.}
        \wrongchoice{When Toni and himself come over, we always have a great time.}
        \wrongchoice{When him and Toni come over, we always have a great time.}
    \end{choices}
\end{question}
}

\element{grammar-mc}{
\begin{question}{grammar-Q16}
    Choose the correct sentence.
    \begin{choices}
        \wrongchoice{It is us who must decide whether to tax ourselves or cut spending.}
        \wrongchoice{It is us whom must decide whether to tax ourselves or cut spending.}
      \correctchoice{It is we who must decide whether to tax ourselves or cut spending.}
        \wrongchoice{It is we whom must decide whether to tax ourselves or cut spending.}
    \end{choices}
\end{question}
}

\element{grammar-mc}{
\begin{question}{grammar-Q17}
    Choose the correct sentence.
    \begin{choices}
      \correctchoice{Between you and me, this class is a joke.}
        \wrongchoice{Between you and I, this class is a joke.}
        \wrongchoice{Between yourself and I, this class is a joke.}
        \wrongchoice{Between you and myself, this class is a joke.}
    \end{choices}
\end{question}
}

\element{grammar-mc}{
\begin{question}{grammar-Q18}
    Choose the correct sentence.
    \begin{choices}
        \wrongchoice{Whom do you think you are to give me advice about dating?}
      \correctchoice{Who do you think you are to give me advice about dating?}
        \wrongchoice{Whom do you think you be to give me advice about dating?}
        \wrongchoice{Who do you think you be to give me advice about dating?}
    \end{choices}
\end{question}
}

\element{grammar-mc}{
\begin{question}{grammar-Q19}
    Choose the correct sentence.
    \begin{choices}
      \correctchoice{Who makes up these English rules anyway?}
        \wrongchoice{Whom makes up these English rules anyway?}
        \wrongchoice{Whomever makes up these English rules anyway?}
        \wrongchoice{Whom make up these English rules anyway?}
    \end{choices}
\end{question}
}

\element{grammar-mc}{
\begin{question}{grammar-Q20}
    Choose the correct sentence.
    \begin{choices}
        \wrongchoice{Whom do you think should win?}
        \wrongchoice{Whomever do you think should win?}
      \correctchoice{Who do you think should win?}
    \end{choices}
\end{question}
}

\element{grammar-mc}{
\begin{question}{grammar-Q21}
    Choose the correct sentence.
    \begin{choices}
      \correctchoice{Whom are you voting for?}
        \wrongchoice{Who are you voting for?}
        \wrongchoice{For who are you voting?}
    \end{choices}
\end{question}
}

\element{grammar-mc}{
\begin{question}{grammar-Q22}
    Choose the correct sentence.
    \begin{choices}
        \wrongchoice{Whomever has the keys get to be in the driver's seat.}
      \correctchoice{Whoever has the keys gets to be in the driver's seat.}
        \wrongchoice{Whoever has the keys get to be in the driver's seat.}
    \end{choices}
\end{question}
}

\element{grammar-mc}{
\begin{question}{grammar-Q23}
    Choose the correct sentence.
    \begin{choices}
        \wrongchoice{We are willing to work with whoever you recommend.}
        \wrongchoice{We are willing to work with who you recommend.}
      \correctchoice{We are willing to work with whomever you recommend.}
        \wrongchoice{We are willing to work with whoever yourself recommend.}
    \end{choices}
\end{question}
}

\element{grammar-mc}{
\begin{question}{grammar-Q24}
    Choose the correct sentence.
    \begin{choices}
        \wrongchoice{The company which Ted represented at the meeting had big plans.}
        \wrongchoice{The company who Ted represented at the meeting had big plans.}
      \correctchoice{The company that Ted represented at the meeting had big plans.}
        \wrongchoice{The company whom Ted represented at the meeting had big plans.}
    \end{choices}
\end{question}
}

\element{grammar-mc}{
\begin{question}{grammar-Q25}
    Choose the correct sentence.
    \begin{choices}
        \wrongchoice{The thoughts that Ted presented, that were about shifting national priorities, were well received.}
        \wrongchoice{The thoughts that Ted presented, were well received.}
        \wrongchoice{The thoughts, that Ted presented, were well received.}
      \correctchoice{The thoughts that Ted presented, which were about shifting national priorities, were well received.}
    \end{choices}
\end{question}
}

\element{grammar-mc}{
\begin{question}{grammar-Q26}
    Choose the correct sentence.
    \begin{choices}
        \wrongchoice{When you do a job so good, you can expect a raise.}
      \correctchoice{When you do a job so well, you can expect a raise.}
        \wrongchoice{When you do so well a job, you can expect a raise.}
    \end{choices}
\end{question}
}

\element{grammar-mc}{
\begin{question}{grammar-Q27}
    Choose the correct sentence.
    \begin{choices}
      \correctchoice{Bonnie was a good sport about losing the race.}
        \wrongchoice{Bonnie was a well sport about losing the race.}
        \wrongchoice{When Bonnie lost the race, she took it good.}
        \wrongchoice{When Bonnie lost the race, she was a well sport.}
    \end{choices}
\end{question}
}

\element{grammar-mc}{
\begin{question}{grammar-Q28}
    Choose the correct sentence.
    \begin{choices}
        \wrongchoice{Harry smells well. What aftershave is he wearing?}
        \wrongchoice{Harry smells good even though his nose is broken.}
      \correctchoice{Harry smells good. What aftershave is he wearing?}
    \end{choices}
\end{question}
}

\element{grammar-mc}{
\begin{question}{grammar-Q29}
    Choose the correct sentence.
    \begin{choices}
      \correctchoice{Lisa did so well on the test that she, as well as Juan, was allowed to accelerate to the next level.}
        \wrongchoice{Lisa did so well on the test that she, as well as Juan, were allowed to accelerate to the next level.}
        \wrongchoice{Lisa did so good on the test that she, as well as Juan, were allowed to accelerate to the next level.}
        \wrongchoice{Lisa did so good on the test that she, as well as Juan, was allowed to accelerate to the next level.}
    \end{choices}
\end{question}
}

\element{grammar-mc}{
\begin{question}{grammar-Q30}
    Choose the correct sentence.
    \begin{choices}
        \wrongchoice{Our puppy is much more sweeter than her brother.}
        \wrongchoice{Our puppy is definitely more sweeter than her brother.}
      \correctchoice{Our puppy is definitely sweeter than her brother.}
    \end{choices}
\end{question}
}

\element{grammar-mc}{
\begin{question}{grammar-Q31}
    Choose the correct sentence.
    \begin{choices}
      \correctchoice{When she smiled she looked happier.}
        \wrongchoice{When she smiled she looked more happily.}
        \wrongchoice{When she smiled she looked more happier.}
    \end{choices}
\end{question}
}

\element{grammar-mc}{
\begin{question}{grammar-Q32}
    Choose the correct sentence.
    \begin{choices}
        \wrongchoice{Karen should of known that her cheap umbrella would break in the storm.}
        \wrongchoice{Karen should of known that her cheap umbrella might break in the storm.}
      \correctchoice{Karen should have known that her cheap umbrella would break in the storm.}
        \wrongchoice{Karen shoulda known that her cheap umbrella would break in the storm.}
    \end{choices}
\end{question}
}

\element{grammar-mc}{
\begin{question}{grammar-Q33}
    Choose the correct sentence.
    \begin{choices}
        \wrongchoice{Sometimes the affects of our generosity make a difference.}
        \wrongchoice{Sometimes our generosity effects others and makes a difference.}
      \correctchoice{Sometimes the effects of our generosity affect others.}
        \wrongchoice{Sometimes the affects of our generosity effect others.}
    \end{choices}
\end{question}
}

\element{grammar-mc}{
\begin{question}{grammar-Q34}
    Choose the correct sentence.
    \begin{choices}
        \wrongchoice{Ben thought he had lain my jacket on that bench.}
      \correctchoice{Ben thought he had laid my jacket on that bench.}
        \wrongchoice{Ben thought he saw my jacket laying on that bench.}
        \wrongchoice{Ben thought he layed my jacket on that bench.}
    \end{choices}
\end{question}
}

\element{grammar-mc}{
\begin{question}{grammar-Q35}
    Choose the correct sentence.
    \begin{choices}
      \correctchoice{Our company policy will not allow me to accept a gift worth more than \$50.}
        \wrongchoice{Our company policy will not allow me to except a gift worth more than \$50.}
    \end{choices}
\end{question}
}

\element{grammar-mc}{
\begin{question}{grammar-Q36}
    Choose the correct sentence.
    \begin{choices}
        \wrongchioce{They thought we were late, but my wife and I were all ready at the restaurant.}
      \correctchioce{They thought we were late, but my wife and I were already at the restaurant.}
    \end{choices}
\end{question}
}

\element{grammar-mc}{
\begin{question}{grammar-Q37}
    Choose the correct sentence.
    \begin{choices}
        \wrongchoice{Irregardless of who was there first, we were all very hungry and ready to eat.}
      \correctchoice{Regardless of who was there first, we were all very hungry and ready to eat.}
    \end{choices}
\end{question}
}

\element{grammar-mc}{
\begin{question}{grammar-Q38}
    Choose the correct sentence.
    \begin{choices}
        \wrongchoice{We could hardly believe that the Giants could loose the game by that many runs.}
      \correctchoice{We could hardly believe that the Giants could lose the game by that many runs.}
    \end{choices}
\end{question}
}

\element{grammar-mc}{
\begin{question}{grammar-Q39}
    Choose the correct sentence.
    \begin{choices}
      \correctchoice{Isn’t it amazing how long that mime can remain completely stationary?}
        \wrongchoice{Isn’t it amazing how long that mime can remain completely stationery?}
    \end{choices}
\end{question}
}

\element{grammar-mc}{
\begin{question}{grammar-Q40}
    Choose the correct sentence.
    \begin{choices}
      \correctchoice{The department’s principal concern is the safety of all employees.}
        \wrongchoice{The department’s principle concern is the safety of all employees.}
    \end{choices}
\end{question}
}

\element{grammar-mc}{
\begin{question}{grammar-Q41}
    Choose the correct sentence.
    \begin{choices}
      \correctchoice{How did they manage to serve cold ice cream in the middle of the vast desert?}
        \wrongchoice{How did they manage to serve cold ice cream in the middle of the vast dessert?}
    \end{choices}
\end{question}
}

\element{grammar-mc}{
\begin{question}{grammar-Q42}
    Choose the correct sentence.
    \begin{choices}
        \wrongchoice{The boss complemented Ari on his excellent presentation.}
      \correctchoice{The boss complimented Ari on his excellent presentation.}
    \end{choices}
\end{question}
}

\element{grammar-mc}{
\begin{question}{grammar-Q43}
    Choose the correct sentence.
    \begin{choices}
      \correctchoice{The judge did not believe any of their stories.}
        \wrongchoice{The judge did not believe any of there stories.}
        \wrongchoice{The judge did not believe any of they're stories.}
    \end{choices}
\end{question}
}

\element{grammar-mc}{
\begin{question}{grammar-Q44}
    Choose the correct sentence.
    \begin{choices}
        \wrongchoice{Ilana said she wanted to become a FBI agent when she grew up.}
      \correctchoice{Ilana said she wanted to become an FBI agent when she grew up.}
    \end{choices}
\end{question}
}

\element{grammar-mc}{
\begin{question}{grammar-Q45}
    Choose the correct sentence.
    \begin{choices}
      \correctchoice{We knew those rascals were all together in this.}
        \wrongchoice{We knew those rascals were altogether in this.}
    \end{choices}
\end{question}
}

\element{grammar-mc}{
\begin{question}{grammar-Q46}
    Choose the correct sentence.
    \begin{choices}
        \wrongchoice{The store was further away than we thought.}
      \correctchoice{The store was farther away than we thought.}
    \end{choices}
\end{question}
}

\element{grammar-mc}{
\begin{question}{grammar-Q47}
    Choose the correct sentence.
    \begin{choices}
      \correctchoice{Paul should have known better than to act like that.}
        \wrongchoice{Paul should of known better than to act like that.}
    \end{choices}
\end{question}
}

\element{grammar-mc}{
\begin{question}{grammar-Q48}
    Choose the correct sentence.
    \begin{choices}
        \wrongchoice{The golf course at the resort is lovely, but I prefer it's swimming pool.}
      \correctchoice{The golf course at the resort is lovely, but I prefer its swimming pool.}
    \end{choices}
\end{question}
}

\element{grammar-mc}{
\begin{question}{grammar-Q49}
    Choose the correct sentence.
    \begin{choices}
        \wrongchoice{I paid the cab fair and Alejandro paid for dinner.}
      \correctchoice{I paid the cab fare and Alejandro paid for dinner.}
    \end{choices}
\end{question}
}

\element{grammar-mc}{
\begin{question}{grammar-Q50}
    Choose the correct sentence.
    \begin{choices}
      \correctchoice{Marta completed five fewer problems than I did in the same amount of time.}
        \wrongchoice{Marta completed five less problems than I did in the same amount of time.}
    \end{choices}
\end{question}
}


\endinput


