%% http://www.bestsamplequestions.com/gre-questions/sentence-completions/sentence-completions.html

%%--------------------------------------------------
%% GRE: Sentence Completion
%%--------------------------------------------------


%% Directions:
%% Every sentence given below has one or may be two blanks; every blank point out that there is something that has been erased. Beneath the sentence are set of words or five options given. Select the particular word or set of words from every blank that perfectly fits the meaning of the sentence as a whole.


%% GRE Multiple Choice Questions
%%--------------------------------------------------
\element{gre-mc}{
\begin{question}{gre-sentence-completion-q01}
    Hoping to \rule[-0.1pt]{4em}{0.1pt} the clash,
        negotiators suggest a negotiation that they felt would be \rule[-0.1pt]{4em}{0.1pt} to both policies and legislation.
    \begin{choices}
        \wrongchoice{Manage---Resolving}
        \wrongchoice{Solve---Divisive}
        \wrongchoice{Extend---Detrimental}
      \correctchoice{Resolve---Acceptable}
        \wrongchoice{End---Likely}
    \end{choices}
\end{question}
}

\element{gre-mc}{
\begin{question}{gre-sentence-completion-q02}
    In spite of her age, she has a childish and \rule[-0.1pt]{4em}{0.1pt} sense of humor.
    \begin{choices}
        \wrongchoice{Adolescent}
        \wrongchoice{Trivial}
        \wrongchoice{Mature}
      \correctchoice{Asinine}
        \wrongchoice{Youthful}
    \end{choices}
\end{question}
}

\element{gre-mc}{
\begin{question}{gre-sentence-completion-q03}
    At the cutting edge of research,
        scientists are developing new sunscreens to protect people from harmful \rule[-0.1pt]{4em}{0.1pt}.
    \begin{choices}
      \correctchoice{UV rays}
        \wrongchoice{Pollution}
        \wrongchoice{Environment}
        \wrongchoice{Atmosphere}
        \wrongchoice{None of the above}
    \end{choices}
\end{question}
}

\element{gre-mc}{
\begin{question}{gre-sentence-completion-q04}
    Knowing Julian was outshined by many other performers,
        she knew she was pampering in a bit of \rule[-0.1pt]{4em}{0.1pt} when she speculated whether Julian was the supreme living performer ever.
    \begin{choices}
        \wrongchoice{Hyperbole}
      \correctchoice{Injustice}
        \wrongchoice{Understatement}
        \wrongchoice{Irony}
        \wrongchoice{Overemphasis}
    \end{choices}
\end{question}
}

\element{gre-mc}{
\begin{question}{gre-sentence-completion-q05}
    In spite of mixed effusion to the divergent,
        there is no required link between technical skill and humanism, and quite probably,
        there may be a little of a \rule[-0.1pt]{4em}{0.1pt} between them.
    \begin{choices}
        \wrongchoice{Dichotomy}
        \wrongchoice{Congruity}
        \wrongchoice{Reciprocity}
        \wrongchoice{Union}
      \correctchoice{Generosity}
    \end{choices}
\end{question}
}

\element{gre-mc}{
\begin{question}{gre-sentence-completion-q06}
    Simply paying a judgment or tax won't \rule[-0.1pt]{4em}{0.1pt} improve your credit score. 
    It will however, start the clock ticking so that item will \rule[-0.1pt]{4em}{0.1pt} get removed.
    \begin{choices}
      \correctchoice{Likely---Eventually}
        \wrongchoice{Possible---Finally}
        \wrongchoice{Promising---Lastly}
        \wrongchoice{Capable---Last of all}
        \wrongchoice{Potentially---At last}
    \end{choices}
\end{question}
}

\element{gre-mc}{
\begin{question}{gre-sentence-completion-q07}
    Bankruptcy can offer a fresh start from debts it does not \rule[-0.1pt]{4em}{0.1pt} out the \rule[-0.1pt]{4em}{0.1pt} accounts that appeared on your report.
    \begin{choices}
         \wrongchoice{Wash---Unique}
       \correctchoice{Wipe---Original}
         \wrongchoice{Dab---Inventive}
         \wrongchoice{Blob---Creative}
         \wrongchoice{Splash---Artistic}
    \end{choices}
\end{question}
}

\element{gre-mc}{
\begin{question}{gre-sentence-completion-q08}
    Your credit cards however will be closed during the program so it will be \rule[-0.1pt]{4em}{0.1pt} you can get new loans.
    \begin{choices}
        \wrongchoice{Similarly}
        \wrongchoice{Likely}
        \wrongchoice{Probably}
      \correctchoice{Unlikely}
        \wrongchoice{Doubtful}
    \end{choices}
\end{question}
}

\element{gre-mc}{
\begin{question}{gre-sentence-completion-q09}
    There are lenders, though, that understand the value of credit counseling and will be willing to finance a loan once you have been \rule[-0.1pt]{4em}{0.1pt} paying on your program for \rule[-0.1pt]{4em}{0.1pt} one or two years, provided you meet their
    \begin{choices}
        \wrongchoice{Profitably---Slightest}
      \correctchoice{Successfully---At least}
        \wrongchoice{Beneficially---Least}
        \wrongchoice{Usefully---Smallest amount}
        \wrongchoice{None of the above}
    \end{choices}
\end{question}
}

\element{gre-mc}{
\begin{question}{gre-sentence-completion-q10}
    If you had joint accounts with \rule[-0.1pt]{4em}{0.1pt} who died, then you will be responsible for the bills
    \begin{choices}
      \correctchoice{Someone}
        \wrongchoice{Any one}
        \wrongchoice{Every one}
        \wrongchoice{Everybody}
        \wrongchoice{Each one }
    \end{choices}
\end{question}
}

%% page 2 11
\element{gre-mc}{
\begin{question}{gre-sentence-completion-q11}
    If you have an account that was charged off,
        it may show a balance \rule[-0.1pt]{4em}{0.1pt} it is paid or settled.
    \begin{choices}
        \wrongchoice{Pending}
        \wrongchoice{Unless}
        \wrongchoice{Except}
        \wrongchoice{If not}
      \correctchoice{Until}
    \end{choices}
\end{question}
}

\element{gre-mc}{
\begin{question}{gre-sentence-completion-q12}
    Don't be pressured into paying those bills directly,
        \rule[-0.1pt]{4em}{0.1pt} if it will hurt your family financially
    \begin{choices}
        \wrongchoice{Particularly}
      \correctchoice{Especially}
        \wrongchoice{Mainly}
        \wrongchoice{Mostly}
        \wrongchoice{Typically}
    \end{choices}
\end{question}
}

\element{gre-mc}{
\begin{question}{gre-sentence-completion-q13}
    It's feasible that during a bank merger or the sale of a few accounts,
        your account went to a latest lender and you just don't \rule[-0.1pt]{4em}{0.1pt} the name of the latest lender.
    \begin{choices}
      \correctchoice{Recognize}
        \wrongchoice{Distinguish}
        \wrongchoice{Discern}
        \wrongchoice{Discriminate}
        \wrongchoice{Classify }
    \end{choices}
\end{question}
}

\element{gre-mc}{
\begin{question}{gre-sentence-completion-q14}
    If your bankruptcies may be reported for ten years from the date you filed, \rule[-0.1pt]{4em}{0.1pt} credit bureaus will remove chapter 13 bankruptcies seven years from the filling date.
    \begin{choices}
        \wrongchoice{Minor}
        \wrongchoice{Small}
      \correctchoice{Major}
        \wrongchoice{Important}
        \wrongchoice{Particular }
    \end{choices}
\end{question}
}

\element{gre-mc}{
\begin{question}{gre-sentence-completion-q15}
    The students have been complaining about the assigned novel,
        which is hard to \rule[-0.1pt]{4em}{0.1pt}.
    \begin{choices}
      \correctchoice{Understand}
        \wrongchoice{Remember}
        \wrongchoice{Know}
        \wrongchoice{Consider}
        \wrongchoice{Believe}
    \end{choices}
\end{question}
}

\element{gre-mc}{
\begin{question}{gre-sentence-completion-q16}
    Some drugs are \rule[-0.1pt]{4em}{0.1pt} to children, and such medicines should be kept locked up.
    \begin{choices}
        \wrongchoice{Useful}
      \correctchoice{Harmful}
        \wrongchoice{Helpful}
        \wrongchoice{Valuable}
        \wrongchoice{Profitable}
    \end{choices}
\end{question}
}

\element{gre-mc}{
\begin{question}{gre-sentence-completion-q17}
    Physical needs are unsatisfied, they take first place, but when they are satisfied, emotions unconnected with them become \rule[-0.1pt]{4em}{0.1pt} in deciding whether a man is to be happy or unhappy.
    \begin{choices}
        \wrongchoice{Significant}
      \correctchoice{Important}
        \wrongchoice{Vital}
        \wrongchoice{Main}
        \wrongchoice{Major}
    \end{choices}
\end{question}
}

\element{gre-mc}{
\begin{question}{gre-sentence-completion-q18}
    Millions of people struggle for bare \rule[-0.1pt]{4em}{0.1pt} in every country and we don't have \rule[-0.1pt]{4em}{0.1pt} medical facilities in this hospital.
    \begin{choices}
      \correctchoice{Existence---Adequate}
        \wrongchoice{Life---Sufficient}
        \wrongchoice{Living---Ample}
        \wrongchoice{Livelihood---Plenty}
        \wrongchoice{Existing---Plenty}
    \end{choices}
\end{question}
}

\element{gre-mc}{
\begin{question}{gre-sentence-completion-q19}
    The master tells the upset workers that machines have \rule[-0.1pt]{4em}{0.1pt} their earning, buying power and hence, happiness.
    \begin{choices}
        \wrongchoice{Amplified}
      \correctchoice{Increased}
        \wrongchoice{Enlarged}
        \wrongchoice{Inflated}
        \wrongchoice{Magnified}
    \end{choices}
\end{question}
}

\element{gre-mc}{
\begin{question}{gre-sentence-completion-q20}
    Workers who operate the machines in dark, dirty and noisy work places \rule[-0.1pt]{4em}{0.1pt} that the machine \rule[-0.1pt]{4em}{0.1pt} their health badly.
    \begin{choices}
        \wrongchoice{Criticize---Distress}
      \correctchoice{Complain---Affect}
        \wrongchoice{Condemn---Sorrow}
        \wrongchoice{Attack---Grief}
        \wrongchoice{Harass---Influence}
    \end{choices}
\end{question}
}

%% page 3 21
\element{gre-mc}{
\begin{question}{gre-sentence-completion-q21}
    The people wish to be rich not in order to \rule[-0.1pt]{4em}{0.1pt} luxury goods so much as to feel superior to their neighbors.
    \begin{choices}
        \wrongchoice{Sell}
      \correctchoice{Buy}
        \wrongchoice{Advertise}
        \wrongchoice{Publicize}
        \wrongchoice{Announce}
    \end{choices}
\end{question}
}

\element{gre-mc}{
\begin{question}{gre-sentence-completion-q22}
    The master \rule[-0.1pt]{4em}{0.1pt} naturally admires the machines because they will serve him sincerely. But he admires their look \rule[-0.1pt]{4em}{0.1pt} they are actually operated
    \begin{choices}
      \correctchoice{Quiet---Before}
        \wrongchoice{Bit---Previous to}
        \wrongchoice{Little---Prior}
        \wrongchoice{Slight---Former}
        \wrongchoice{Minor---Past}
    \end{choices}
\end{question}
}

\element{gre-mc}{
\begin{question}{gre-sentence-completion-q23}
    The rich are \rule[-0.1pt]{4em}{0.1pt} fortunate than their neighbors or relations. 
    This is their competitive \rule[-0.1pt]{4em}{0.1pt} over others.
    \begin{choices}
      \correctchoice{More---Advantage}
        \wrongchoice{Less---Gain}
        \wrongchoice{Little---Profit}
        \wrongchoice{Slight---Yield}
        \wrongchoice{Small---Expand}
    \end{choices}
\end{question}
}

\element{gre-mc}{
\begin{question}{gre-sentence-completion-q24}
    The state can provide some \rule[-0.1pt]{4em}{0.1pt} sport facilities to satisfy men inherit ant desire for \rule[-0.1pt]{4em}{0.1pt} and action.
    \begin{choices}
        \wrongchoice{daring---Gratify}
      \correctchoice{Adventurous---Thrill}
        \wrongchoice{Bold---Indulge}
        \wrongchoice{Brave---Spoil}
        \wrongchoice{Heroic---Ruin}
    \end{choices}
\end{question}
}

\element{gre-mc}{
\begin{question}{gre-sentence-completion-q25}
    The two other factors which play \rule[-0.1pt]{4em}{0.1pt} part in \rule[-0.1pt]{4em}{0.1pt} poverty is density of population and political condition.
    \begin{choices}
      \correctchoice{Major---Increasing}
        \wrongchoice{Chief---Rising}
        \wrongchoice{Principle---Growing}
        \wrongchoice{Main---Budding}
        \wrongchoice{Important---Emergent}
    \end{choices}
\end{question}
}

\element{gre-mc}{
\begin{question}{gre-sentence-completion-q26}
    Machines demand regularity and they \rule[-0.1pt]{4em}{0.1pt} to be operated regularly and continually. But human emotions do not follow any set course and they are \rule[-0.1pt]{4em}{0.1pt} and spontaneous.
    \begin{choices}
        \wrongchoice{Required---Unequal}
        \wrongchoice{Compulsory---Imbalanced}
      \correctchoice{Need---irregular}
        \wrongchoice{Vital---Lopsided}
        \wrongchoice{Obligatory---Extreme}
    \end{choices}
\end{question}
}

\element{gre-mc}{
\begin{question}{gre-sentence-completion-q27}
    The \rule[-0.1pt]{4em}{0.1pt} praise given to a person who is a sincere tireless worker is that he has the qualities of a machine. 
    He is \rule[-0.1pt]{4em}{0.1pt}, punctual and accurate
    \begin{choices}
      \correctchoice{Highest---Dependable}
        \wrongchoice{Good---Silly}
        \wrongchoice{Bad---Stupid}
        \wrongchoice{Nice---Brainless}
        \wrongchoice{Polite---Mindless}
    \end{choices}
\end{question}
}

\element{gre-mc}{
\begin{question}{gre-sentence-completion-q28}
    The art collector \rule[-0.1pt]{4em}{0.1pt} pleasure from the thought that others know how much he has spent on \rule[-0.1pt]{4em}{0.1pt} painting
    \begin{choices}
        \wrongchoice{Attain---Every}
      \correctchoice{Derives---Each}
        \wrongchoice{Accomplish---All}
        \wrongchoice{Achieve---Everyone}
        \wrongchoice{Do---Everything}
    \end{choices}
\end{question}
}

\element{gre-mc}{
\begin{question}{gre-sentence-completion-q29}
    The author wants to \rule[-0.1pt]{4em}{0.1pt} those machines have the \rule[-0.1pt]{4em}{0.1pt} attraction for the young and the old alike
    \begin{choices}
        \wrongchoice{Show---Huge}
        \wrongchoice{Explain---Big}
      \correctchoice{Prove---Great}
        \wrongchoice{Establish---Vast}
        \wrongchoice{Found---Immense}
    \end{choices}
\end{question}
}

\element{gre-mc}{
\begin{question}{gre-sentence-completion-q30}
    Machines are worshipped because they are beautiful, and valued because they \rule[-0.1pt]{4em}{0.1pt} power; they are hated because they are hideous and loathed because they \rule[-0.1pt]{4em}{0.1pt} slavery.
    \begin{choices}
      \correctchoice{Confer---Impose}
        \wrongchoice{Grant---Impress}
        \wrongchoice{Allowance---Astonish}
        \wrongchoice{Payment---Daze}
        \wrongchoice{Contribution---Stun}
    \end{choices}
\end{question}
}

%% page 4 31
\element{gre-mc}{
\begin{question}{gre-sentence-completion-q31}
    The master of the machine, it is true, lives at a \rule[-0.1pt]{4em}{0.1pt} from it where he cannot hear its noise or see its unsightly heaps of slag or smell it's \rule[-0.1pt]{4em}{0.1pt} fumes.
    \begin{choices}
      \correctchoice{Distance---Noxious}
        \wrongchoice{Aloofness---Deadly}
        \wrongchoice{Coldness---Toxic}
        \wrongchoice{Iciness---Noxious}
        \wrongchoice{Frostiness---Injurious}
    \end{choices}
\end{question}
}

\element{gre-mc}{
\begin{question}{gre-sentence-completion-q32}
    David complains that his room is \rule[-0.1pt]{4em}{0.1pt} filled with tobacco smoke.
    \begin{choices}
        \wrongchoice{Frequently}
        \wrongchoice{Regularly}
        \wrongchoice{Habitually}
      \correctchoice{Often}
        \wrongchoice{Commonly}
    \end{choices}
\end{question}
}

\element{gre-mc}{
\begin{question}{gre-sentence-completion-q33}
    His hairs are cut too \rule[-0.1pt]{4em}{0.1pt}.
    It \rule[-0.1pt]{4em}{0.1pt} that he has been given a hair cut for the army.
    \begin{choices}
      \correctchoice{Short---Seems}
        \wrongchoice{Tiny---As if}
        \wrongchoice{Little---Since}
        \wrongchoice{Slight---When}
        \wrongchoice{Minor---While}
    \end{choices}
\end{question}
}

\element{gre-mc}{
\begin{question}{gre-sentence-completion-q34}
    The \rule[-0.1pt]{4em}{0.1pt} percentage for admission to this course is 95\%
    \begin{choices}
        \wrongchoice{Initial}
        \wrongchoice{Primary}
        \wrongchoice{Starting}
      \correctchoice{Cut off}
        \wrongchoice{Main}
    \end{choices}
\end{question}
}

\element{gre-mc}{
\begin{question}{gre-sentence-completion-q35}
    How did they \rule[-0.1pt]{4em}{0.1pt} the flight for California?
    \begin{choices}
      \correctchoice{Board}
        \wrongchoice{Took}
        \wrongchoice{Went}
        \wrongchoice{Taken}
        \wrongchoice{Gone}
    \end{choices}
\end{question}
}

\element{gre-mc}{
\begin{question}{gre-sentence-completion-q36}
    How many persons were to be hanged to \rule[-0.1pt]{4em}{0.1pt} and how did they behave before their death?
    \begin{choices}
        \wrongchoice{Decrease}
      \correctchoice{Death}
        \wrongchoice{Murder}
        \wrongchoice{Killed}
        \wrongchoice{Demise}
    \end{choices}
\end{question}
}

\element{gre-mc}{
\begin{question}{gre-sentence-completion-q37}
    The islands \rule[-0.1pt]{4em}{0.1pt} rains for more than six or seven months
    \begin{choices}
        \wrongchoice{Get}
        \wrongchoice{Obtain}
        \wrongchoice{Acquire}
      \correctchoice{Receive}
        \wrongchoice{Got}
    \end{choices}
\end{question}
}

\element{gre-mc}{
\begin{question}{gre-sentence-completion-q38}
    Poetry and Philosophy take \rule[-0.1pt]{4em}{0.1pt} forms in the times of struggle for freedom or revolution.
    \begin{choices}
        \wrongchoice{Recent}
        \wrongchoice{Latest}
        \wrongchoice{Fresh}
      \correctchoice{New}
        \wrongchoice{Modern}
    \end{choices}
\end{question}
}

\element{gre-mc}{
\begin{question}{gre-sentence-completion-q39}
    The author's mother died and his father \rule[-0.1pt]{4em}{0.1pt} lonely and sad.
    \begin{choices}
        \wrongchoice{Experienced}
        \wrongchoice{Feel}
        \wrongchoice{Feeling}
      \correctchoice{Felt}
        \wrongchoice{Touch}
    \end{choices}
\end{question}
}

\element{gre-mc}{
\begin{question}{gre-sentence-completion-q40}
    He didn't feel the \rule[-0.1pt]{4em}{0.1pt} of his mother because his father was both father and mother to him.
    \begin{choices}
        \wrongchoice{Lack}
      \correctchoice{Absence}
        \wrongchoice{Need}
        \wrongchoice{Want}
        \wrongchoice{Requirement}
    \end{choices}
\end{question}
}

%% page 5 41
\element{gre-mc}{
\begin{question}{gre-sentence-completion-q41}
    The lake was not a \rule[-0.1pt]{4em}{0.1pt} once but a man made reservoir.
    \begin{choices}
        \wrongchoice{Normal}
      \correctchoice{Natural}
        \wrongchoice{Ordinary}
        \wrongchoice{Usual}
        \wrongchoice{Normal}
    \end{choices}
\end{question}
}

\element{gre-mc}{
\begin{question}{gre-sentence-completion-q42}
    I \rule[-0.1pt]{4em}{0.1pt} a car the day after landing and brought a comprehensive book of maps, which I found most helpful on the cross country voyage, but which I did not believe I should \rule[-0.1pt]{4em}{0.1pt} on the last stage.
    \begin{choices}
        \wrongchoice{Brought---Require}
      \correctchoice{Hired---Need}
        \wrongchoice{Bring---Involve}
        \wrongchoice{Booked---Should}
        \wrongchoice{Taken---Requirement}
    \end{choices}
\end{question}
}

\element{gre-mc}{
\begin{question}{gre-sentence-completion-q43}
    We have been \rule[-0.1pt]{4em}{0.1pt} about the evils of child labor for the last 15 years in this country.
    \begin{choices}
      \correctchoice{Talking}
        \wrongchoice{Speaking}
        \wrongchoice{Communicating}
        \wrongchoice{Language}
        \wrongchoice{Talk}
    \end{choices}
\end{question}
}

\element{gre-mc}{
\begin{question}{gre-sentence-completion-q44}
    A successful man is able to \rule[-0.1pt]{4em}{0.1pt} his ideas in a way that he can sell them to others.
    \begin{choices}
        \wrongchoice{Speak}
        \wrongchoice{Talking}
        \wrongchoice{Telling}
      \correctchoice{Communicate}
        \wrongchoice{Communication}
    \end{choices}
\end{question}
}

\element{gre-mc}{
\begin{question}{gre-sentence-completion-q45}
    David knows how to influence people and win friends so as to \rule[-0.1pt]{4em}{0.1pt} them for a purpose.
    \begin{choices}
      \correctchoice{Motivate}
        \wrongchoice{Encourage}
        \wrongchoice{Knowledge}
        \wrongchoice{Training}
        \wrongchoice{Information}
    \end{choices}
\end{question}
}

\element{gre-mc}{
\begin{question}{gre-sentence-completion-q46}
    Education does not seem to have played a \rule[-0.1pt]{4em}{0.1pt} role in making our life successful.
    \begin{choices}
        \wrongchoice{Affective}
      \correctchoice{Great}
        \wrongchoice{Huge}
        \wrongchoice{Small}
        \wrongchoice{Little}
    \end{choices}
\end{question}
}

\element{gre-mc}{
\begin{question}{gre-sentence-completion-q47}
    After thirty years of work, Dr. John Gibbon of U.S.A had \rule[-0.1pt]{4em}{0.1pt} a machine that could take over temporarily from the heart and lungs.
    \begin{choices}
      \correctchoice{Developed}
        \wrongchoice{Invented}
        \wrongchoice{Made up}
        \wrongchoice{Urbanized}
        \wrongchoice{Imaginary}
    \end{choices}
\end{question}
}

\element{gre-mc}{
\begin{question}{gre-sentence-completion-q48}
    Medical experts have cautioned against \rule[-0.1pt]{4em}{0.1pt} use of aluminum cookware and foils, especially for acidic food preparations \rule[-0.1pt]{4em}{0.1pt} tamarind, tomatoes and green leafy vegetables which could lead to aluminum toxicity and consequent nerve disorders.
    \begin{choices}
        \wrongchoice{Wide---Have}
      \correctchoice{Extensive---Containing}
        \wrongchoice{Ample---Contain}
        \wrongchoice{Plentiful---Enclose}
        \wrongchoice{Abundant---Surround}
    \end{choices}
\end{question}
}

\element{gre-mc}{
\begin{question}{gre-sentence-completion-q49}
    Chronic exposure of high levels of aluminum \rule[-0.1pt]{4em}{0.1pt} food and water could lead to nerve and brain disorders such as Alzheimer's and Parkinson's disease, they say.
    \begin{choices}
      \correctchoice{Through}
        \wrongchoice{During}
        \wrongchoice{Throughout}
        \wrongchoice{All over}
        \wrongchoice{For the duration of}
    \end{choices}
\end{question}
}

\element{gre-mc}{
\begin{question}{gre-sentence-completion-q50}
    NIN Scientist says in a statement that they have also \rule[-0.1pt]{4em}{0.1pt} regular monitoring of aluminum in blood for dialysis victims. 
    Patients with kidney disorders are \rule[-0.1pt]{4em}{0.1pt} susceptible to aluminum toxicity as their excretion of aluminum is affected.
    \begin{choices}
        \wrongchoice{Suggested---Chiefly}
      \correctchoice{Advised---Particularly}
        \wrongchoice{Recommended---Mostly}
        \wrongchoice{Optional---Mainly}
        \wrongchoice{Not compulsory---Chiefly}
    \end{choices}
\end{question}
}

%% page 6 51
\element{gre-mc}{
\begin{question}{gre-sentence-completion-q51}
    With the exposure of human beings to aluminum increasing markedly in \rule[-0.1pt]{4em}{0.1pt} years, they are more prone to absorbing \rule[-0.1pt]{4em}{0.1pt} amount of this metal, the report warns.
    \begin{choices}
        \wrongchoice{Current---Too much}
      \correctchoice{Recent---Excessive}
        \wrongchoice{Modern---Extreme}
        \wrongchoice{Present---Severe}
        \wrongchoice{Fresh---Harsh}
    \end{choices}
\end{question}
}

\element{gre-mc}{
\begin{question}{gre-sentence-completion-q52}
    Aluminum is \rule[-0.1pt]{4em}{0.1pt} in water, spoil, plants and cooking utensils.
    It is added to drinking water as aluminum sulphate at the treatment plants, while soil contamination with it leads to its \rule[-0.1pt]{4em}{0.1pt} in vegetables.
    \begin{choices}
      \correctchoice{Present---Accumulation}
        \wrongchoice{There---Buildup}
        \wrongchoice{Nearby---Increase}
        \wrongchoice{Close by---Boost}
        \wrongchoice{Close at hand---Improve}
    \end{choices}
\end{question}
}

\element{gre-mc}{
\begin{question}{gre-sentence-completion-q53}
    Beggars almost sell themselves as human beings to \rule[-0.1pt]{4em}{0.1pt} the pity of passersby.
    \begin{choices}
        \wrongchoice{Stimulate}
      \correctchoice{Arouse}
        \wrongchoice{Kindle}
        \wrongchoice{Promote}
        \wrongchoice{Support}
    \end{choices}
\end{question}
}

\element{gre-mc}{
\begin{question}{gre-sentence-completion-q54}
    A tramp may ask you for money, but he will never ask you to feel \rule[-0.1pt]{4em}{0.1pt} for him.
    \begin{choices}
        \wrongchoice{Bad}
        \wrongchoice{Worst}
      \correctchoice{Sorry}
        \wrongchoice{Good}
        \wrongchoice{Best}
    \end{choices}
\end{question}
}

\element{gre-mc}{
\begin{question}{gre-sentence-completion-q55}
    Teachers sell knowledge, philosophers wisdom and priests \rule[-0.1pt]{4em}{0.1pt} comforts. 
    Value of material goods can be \rule[-0.1pt]{4em}{0.1pt} in terms of money but not the value of the services.
    \begin{choices}
        \wrongchoice{Religious---Calculated}
      \correctchoice{Spiritual---Measured}
        \wrongchoice{Dutiful---Planned}
        \wrongchoice{Loyal---Intended}
        \wrongchoice{Reliable---Projected}
    \end{choices}
\end{question}
}

\element{gre-mc}{
\begin{question}{gre-sentence-completion-q56}
    Continuity of purpose is one of the most \rule[-0.1pt]{4em}{0.1pt} ingredients of happiness and that come chiefly through their work.
    \begin{choices}
        \wrongchoice{Important}
        \wrongchoice{Particular}
        \wrongchoice{Significant}
      \correctchoice{Essential}
        \wrongchoice{Useless}
    \end{choices}
\end{question}
}

\element{gre-mc}{
\begin{question}{gre-sentence-completion-q57}
    Work, therefore is desirable first and \rule[-0.1pt]{4em}{0.1pt} as a preventive of boredom, for the boredom that a man feels when he is doing something out of \rule[-0.1pt]{4em}{0.1pt}, through uninteresting work is as boring as having nothing to do.
    \begin{choices}
      \correctchoice{Foremost---Compulsion}
        \wrongchoice{Primary---Obligation}
        \wrongchoice{Prime---Responsibility}
        \wrongchoice{Main---Blame}
        \wrongchoice{Chief---Duty}
    \end{choices}
\end{question}
}

\element{gre-mc}{
\begin{question}{gre-sentence-completion-q58}
    Clever advertising, aimed at chronic sufferers who will try anything because doctors have not been able to \rule[-0.1pt]{4em}{0.1pt} them, can induce such faith in a preparation, \rule[-0.1pt]{4em}{0.1pt} if sleepy priced that it will produce by suggestion a very real effect in some people.
    \begin{choices}
        \wrongchoice{Heal---Especially}
      \correctchoice{Cure---Particularly}
        \wrongchoice{Mend---Above all}
        \wrongchoice{Fix---Mainly}
        \wrongchoice{Make well---Chiefly}
    \end{choices}
\end{question}
}

\element{gre-mc}{
\begin{question}{gre-sentence-completion-q59}
    The topic of thought is one area of Psychology and many observers have considered these aspects in connection with robots and computers, some of the old worries about artificial intelligence were \rule[-0.1pt]{4em}{0.1pt} linked to the question of whether computers could think.
    \begin{choices}
        \wrongchoice{Directly}
      \correctchoice{Closely}
        \wrongchoice{Very much}
        \wrongchoice{Strongly}
        \wrongchoice{Honestly}
    \end{choices}
\end{question}
}

\element{gre-mc}{
\begin{question}{gre-sentence-completion-q60}
    Another disadvantage is that television \rule[-0.1pt]{4em}{0.1pt} causes people to become dissatisfied with their own lives.
    \begin{choices}
        \wrongchoice{Frequently}
      \correctchoice{Often}
        \wrongchoice{Regularly}
        \wrongchoice{Normally}
        \wrongchoice{Commonly}
    \end{choices}
\end{question}
}

%% page 7 61
\element{gre-mc}{
\begin{question}{gre-sentence-completion-q61}
    Penguin became a different company in the year 1936 and set up \rule[-0.1pt]{4em}{0.1pt} in the Crypt of the Holy Trinity Church on Marylebone Road, using a fairground glide to obtain deliveries from the street above.
    In twelve months, it had sold an incredible 3 million paperbacks.
    Customary publishers tended to view Penguin with misgiving and \rule[-0.1pt]{4em}{0.1pt}, as did some authors.
    \begin{choices}
      \correctchoice{Premises---Uncertainty}
        \wrongchoice{Ground---Doubt}
        \wrongchoice{Location---hesitation}
        \wrongchoice{Place---Indecision}
        \wrongchoice{Position---Hesitancy}
    \end{choices}
\end{question}
}

\element{gre-mc}{
\begin{question}{gre-sentence-completion-q62}
    The planets, the majority of the satellites of the planets and the asteroids \rule[-0.1pt]{4em}{0.1pt} around the Sun in the similar direction, in almost spherical orbits. When looking down from on top of the Sun's North Pole, the planets \rule[-0.1pt]{4em}{0.1pt} contradict in a clockwise direction.
    The planets orbit the Sun in or close to the similar plane, called the ecliptic.
    \begin{choices}
        \wrongchoice{Rotate---Track}
      \correctchoice{Revolve---Orbit}
        \wrongchoice{Spin---Path}
        \wrongchoice{Circle---Range}
        \wrongchoice{Encircle---Lane}
    \end{choices}
\end{question}
}

\element{gre-mc}{
\begin{question}{gre-sentence-completion-q63}
    The term volcano came from the Vulcano desert island, which had been named after Vulcan, the Roman god of fire. 
    There are many \rule[-0.1pt]{4em}{0.1pt} kinds of volcanoes as well as composite volcanoes, shelter volcanoes, clinker cones, splash cones, and compound or complex volcano. 
    These dissimilar types of volcanoes come in unusual shapes and \rule[-0.1pt]{4em}{0.1pt} in various ways.
    \begin{choices}
      \correctchoice{Dissimilar---Explode}
        \wrongchoice{Unlike---Blow up}
        \wrongchoice{Distinct---Burst}
        \wrongchoice{Disparate---Rapture}
        \wrongchoice{Unrelated---delight}
    \end{choices}
\end{question}
}

\element{gre-mc}{
\begin{question}{gre-sentence-completion-q64}
    Kiwifruit is the most vitamin and nutrient rich of the top 27 fruits eaten in the world nowadays. 
    It also has the \rule[-0.1pt]{4em}{0.1pt} compactness of any fruit which is rich in vitamin C and magnesium limited mineral in the food delivered of wealthy countries and a nutrient useful for cardiovascular physical condition. Amongst the top three high potassium low sodium fruits, kiwi fruit is regarded as the one of the \rule[-0.1pt]{4em}{0.1pt} fruit, having a large amount of potassium compared to banana or any other citrus fruits.
    \begin{choices}
      \correctchoice{Maximum---Best}
        \wrongchoice{Great---Most excellent}
        \wrongchoice{Grand---Finest}
        \wrongchoice{Impressive---Premium}
        \wrongchoice{Imposing---Quality}
    \end{choices}
\end{question}
}

\element{gre-mc}{
\begin{question}{gre-sentence-completion-q65}
    It's alluring to blame fruit growers, sellers and wholesalers for making the pear a substandard eating experience but in \rule[-0.1pt]{4em}{0.1pt}, pear is a very complicated fruit to trade. 
    They ripen from the inside out and the only sign that they are ready to eat is a slight give or smoothness around the stem. 
    Eat them \rule[-0.1pt]{4em}{0.1pt} and they will be dry and tasteless. 
    Leave them too long and they may become brown and soft in the middle.
    \begin{choices}
        \wrongchoice{Actually---Fast}
        \wrongchoice{Really---Quick}
        \wrongchoice{Truly---Speedy}
      \correctchoice{Reality---Quickly}
        \wrongchoice{Certainly---Rapid}
    \end{choices}
\end{question}
}

\element{gre-mc}{
\begin{question}{gre-sentence-completion-q66}
    Diamond is the strongest and hardest natural metal. 
    The Mohs solidity scale, on which diamond is 10 and sapphire is 9, doesn't sufficiently attest to this \rule[-0.1pt]{4em}{0.1pt} solidity, as diamond is exponentially stronger compared to corundum. 
    Diamond is very least compressible and \rule[-0.1pt]{4em}{0.1pt} substance.
    \begin{choices}
      \correctchoice{Unbelievable---Strongest}
        \wrongchoice{Incredible---Hard}
        \wrongchoice{Absurd---strong}
        \wrongchoice{Illogical---Stiff}
        \wrongchoice{Irrational---Rigid}
    \end{choices}
\end{question}
}

\element{gre-mc}{
\begin{question}{gre-sentence-completion-q67}
    More than \$50 billion of people are blown on cosmetics \rule[-0.1pt]{4em}{0.1pt} every year and hundreds of hours are spent using creams, powders and lotions. 
    Even with the current downturn in the country, makeup fans have basically turned to drugstores, instead of \rule[-0.1pt]{4em}{0.1pt} cosmetics boutiques, to holdup their tonics, wands and face cosmetics, according to a current consumer details by Euro monitor International.
    \begin{choices}
        \wrongchoice{Universal---Small}
        \wrongchoice{Widespread---Low-priced}
        \wrongchoice{Extensive---Posh}
        \wrongchoice{General---Cheap}
      \correctchoice{Worldwide---Expensive}
    \end{choices}
\end{question}
}

\element{gre-mc}{
\begin{question}{gre-sentence-completion-q68}
    Starfish are also \rule[-0.1pt]{4em}{0.1pt} as sea stars and are not actually fish in spite of the name been given to them because of its shape.
    These are known as echinoderms, which are found plentiful in the deep Oceans and low waters as well. 
    If you have ever bumped into a starfish and turned it over, you will find bulges on the base.
    These are called as tube feet, which have basically two functions---one being able to travel around the \rule[-0.1pt]{4em}{0.1pt} floor and the other to open up a clam or scallop.
    \begin{choices}
      \correctchoice{Identified---Deep Sea}
        \wrongchoice{Branded---Pond water}
        \wrongchoice{Famous---Shallow water}
        \wrongchoice{Famed---River water}
        \wrongchoice{Celebrated---Water}
    \end{choices}
\end{question}
}

\element{gre-mc}{
\begin{question}{gre-sentence-completion-q69}
    All stars starts from clouds of freezing molecular hydrogen that \rule[-0.1pt]{4em}{0.1pt} fall down.
    As they cloud crumples, it wreckage into many pieces that will go on to form alone stars.
    The objects collect into a ball that persists to fall down under its individual gravity until it can \rule[-0.1pt]{4em}{0.1pt} fire nuclear fusion at its main core. 
    This original gas was formed throughout the Big Bang, and is always about 75\% hydrogen gas and 24\% helium.
    \begin{choices}
      \correctchoice{Gravitationally---Catches}
        \wrongchoice{Automatically---Hold}
        \wrongchoice{Mechanically---Grab}
        \wrongchoice{Involuntarily---Clutch}
        \wrongchoice{Unwillingly---Grasp}
    \end{choices}
\end{question}
}

\element{gre-mc}{
\begin{question}{gre-sentence-completion-q70}
    Venus is like the Earth's wicked twin. 
    Although it's alike in \rule[-0.1pt]{4em}{0.1pt} and weight to the Earth, the environment of Venus sets it separately. 
    The mass of the environment is 95 times that of the Earth's environment. 
    If you could stand on the plane of Venus, you would actually \rule[-0.1pt]{4em}{0.1pt} 92 times the force you have on Earth. 
    This is the similar as going almost a kilometer beneath the surface of the ocean.
    \begin{choices}
        \wrongchoice{Dimension---Experience}
        \wrongchoice{Length---Feel}
        \wrongchoice{Height---Know}
      \correctchoice{Size---Experience}
        \wrongchoice{Altitude---Skill}
    \end{choices}
\end{question}
}

\endinput


