
%%--------------------------------------------------
%% GRE: Analytical Reasoning
%%--------------------------------------------------

%%--------------------------------------------------
%% References
%%--------------------------------------------------

%% http://www.bestsamplequestions.com/gre-questions/analytical-reasoning/analytical-reasoning.html


%% GRE Multiple Choice Questions
%%--------------------------------------------------

%% page 1 1--5
\element{gre-mc}{
    Questions 1 to 5 are based on the following:

    Five persons are sitting in a line. 
    One of the two persons, at the farthest ends, is sharp, the other one is fair.

    An overweight person is sitting to the right of a feeble person. 
    A tall person is to the left of the fair person and the feeble person is sitting between the sharp and overweight persons.

\begin{question}{gre-analytical-reasoning-q01}
    Tall person is at which place counting from right?
    \begin{choices}
        \wrongchoice{First}
        \wrongchoice{Second}
        \wrongchoice{Third}
        \wrongchoice{Fourth}
        \wrongchoice{Cannot be determined}
    \end{choices}
\end{question}

\begin{question}{gre-analytical-reasoning-q02}
    Tall person is at which place counting from right?
    \begin{choices}
        \wrongchoice{First}
        \wrongchoice{Second}
        \wrongchoice{Third}
        \wrongchoice{Fourth}
        \wrongchoice{Cannot be determined}
    \end{choices}
\end{question}
}

\begin{comment}

Question 2

Which of the following depicts the person to the left of feeble person?
(a) Sharp
(b) Overweight
(c) Fair
(d) Tall
(e) Cannot be determined

Question 3

Which of the following persons is sitting in the middle?
(a) Fair
(b) feeble
(c) sharp
(d) Tall
(e) Overweight

Question 4

To whose left is the overweight person sitting?
(a) Fair
(b) Sharp
(c) Tall
(d) feeble
(e) Cannot be determined

Question 5

If the fair person and overweight person swap their position, so also tall and feeble, then who will be sitting to the left of the feeble person?
(a) Tall
(b) Fair
(c) Overweight
(d) Sharp
(e) Cannot be determined

Answers: 1(b), 2(a), 3(e), 4(c) and 5(b)

Clarification: Let the fair person sit to the farthest right because it is given that a tall person is to his left. This signifies that the order Tall, Fair is followed.

Also, then the sharp person will be in the farthest left. An overweight person is to the right of a feeble person i.e. the order Feeble, Overweight is followed. The Feeble person is sitting in the middle of the Sharp and Overweight person means the order Sharp, Feeble, Overweight is followed. Sharp, Feeble, Overweight, Tall, and Fair.


%% page 2 6--10


Question 6

David ranks seventh from the top and 28th from the bottom in a class. How many students are there in the class?

(a) 36
(b) 35
(c) 34
(d) Cannot be determined
(e) None of the above

Answer: (c)

Question 7

Clorida is taller than Ivory. Emily is taller than Lovely. Lovely is taller than Enamol. To determine who among them is the tallest, which of the following further information, if any, is required?
(a) Clorida is taller than Enamol and Lovely
(b) No further information is needed
(c) Emily is taller Ivory
(d) Clorida is taller than Lovely
(e) Enamol is taller than Clorida

Answer: (e)

Question 8

Four of the following five are similar in a definite way and so form a group. Which one of them does not belong to the group?
(a) Umbrella
(b) Gloves
(c) Shirt
(d) Shoes
(e) Cap

Answer: (a)

Question 9

There are 26 steps in a Church. In the time Sandy comes down two steps, Plato goes one step. If they start simultaneously and keep their speed uniform, then at which step from bottom will they meet.
(a) 9th
(b) 12th
(c) 13th
(d) 8th
(e) None of the above

Answer: (a)

Clarification: Assume they meet at Xth step from the bottom, and this is equal to number of steps downward plus number of step upward minus common step (which will be added two times)
Therefore 2*2+2*1-1=26
Therefore X= 9

Question 10

In certain code Language the words ROUTINE is written as VMRGFLI. How will the word CRUELTY be written in that code language?
(a) VOCVZRL
(b) WPCVZRL
(c) VPCVZRL
(d) VPVCZRL
(e) None of the above

Answer: (c)

The first alphabet becomes the third alphabet, second alphabet is coded as -2, and the third alphabet becomes first after +1. A similar relationship exists between the last three alphabets. A for the center alphabet, it is coded as the same positioned alphabet from the right end of the letter.


%% page 3 11--15

Question 11 to 15: In each of the following questions, five groups of letters have been given, out of which four are alike in some way and one is different. Choose the odd one out.

Question 11
(a) Treat
(b) Great
(c) Tears
(d) Rates
(e) Heard

Answer: Heard

Clarification: All other groups have the letters T E A R.

Question 12
(a) Wear
(b) Fear
(c) Cear
(d) Bear
(e) Tear

Answer: Cear

Clarification: All the words except CEAR can be found in your Dictionary
Question 13

(a) Egg
(b) Acne
(c) Mother
(d) Defeat
(e) Giddy

Answer: Giddy

Clarification: All the other groups contain the alphabet E.

Question 14
(a) Great
(b) Treat
(c) Tears
(d) Table
(e) Later

Answer: Table

Clarification: All the other groups contain the letter T E A R.

Question 15
(a) Reap
(b) Rare
(c) Tore
(d) Tear
(e) Pear

Answer: Tore

Clarification: All the other groups have the letters “E, A, R”


%% page 4 16--20


Question 16 and 17

You are required to answer these questions referring to the symbol, alphabet or number sequence given below.

P Y 4 # A Q © K B 8 D 5 * E % 2 S ? 9 R U $ F @ 6 H M 3 W (X)

Question 16

If all the symbols are dropped from the sequence, then which element will be in the center in the new sequence?
(a) 5
(b) E
(c) 2
(d) S
(e) There is no center element

Answer: (e)

Clarification: P Y 4 A Q K B 8 D 5 E 2 S 9 R U F 6 H M 3 W. We can see that number of elements is even number (22), there is no center element possible.

Question 17

#8 is related to? W in the same way as BE is related to?
(a) S?
(b) 6M
(c) W(x)
(d) \$3
(e) None of the above

Answer: (e)

Clarification: Number of elements between the second pair of elements is double with respect to the number of elements between the first pair of elements.

Question 18
DELETED

Question 19
DELETED

Question 20 Joseph, Jackie and Ninda are the three mountaineers. Joseph is Jackie’s brother. Jackie is Ninda’s brother. Ninda is not Joseph’s brother. Therefore, Ninda is Joseph’s sister.
(a) Should be True
(b) May be False
(c) Should be False
(d) Cannot be determined

Answer: (a)

Clarification: From the above statement it clear that Ninda is Joseph’s sister


%% page 5 21--15


n each of the following questions, four groups of letters have been given, out of which four are alike in some way and one is different. Choose the odd one out.

Question 21
(a) Curtain
(b) Saree
(c) Shirt
(d) Petticoat

Answer: Curtain

Clarification: Except the word Curtain, all the others can be worn.

Question 22
(a) Ground
(b) Class
(c) Teacher
(d) Student

Answer: Ground

Question 23
(a) Inhabit
(b) Vacate
(c) Reside
(d) Dwell

Answer: Vacate

Clarification: Except the word Vacate, all other words mean to stay.
Question 24 (a) Cotton
(b) Nylon
(c) Silk
(d) Terylene

Answer: Cotton

Clarification: Only Cotton is grown in fields.

Question 25
(a) Joy
(b) Love
(c) Hate
(d) Toy

Answer: Toy
Clarification: Except toy, all other words describe emotions. 


%% page 6 26--30

n each of the following questions, four groups of letters have been given, out of which four are alike in some way and one is different. Choose the odd one out.

Question 26
(a) Rule
(b) Common
(c) Law
(d) Custom

Answer: Common

Clarification: All words except common are related to Law.

Question 27
(a) Brother
(b) Father
(c) Uncle
(d) Student

Answer: Student

Clarification: Except the word student, all other words come in relation.

Question 28
(a) Parrot
(b) Pigeon
(c) Sparrow
(d) Kiwi

Answer: Kiwi

Clarification: Except Kiwi, all other words are the names of birds.

Question 29
(a) Trickster
(b) Juggler
(c) Magician
(d) Musician

Answer: Musician

Clarification: All other words in the group, except Musician

Question 30
(a) Attachment
(b) Love
(c) Hatred
(d) Affection

Answer: Hatred

Clarification: Except the word Hatred, all the other words signify Love.


%% page 7 31--35

Question 31 to 35

Every sentence given under has one or two blanks. Every blank shows that something has been misplaced. Below every sentence five words are specified as option. Select one right word for every blank that perfectly fits the meaning of the sentences as a whole.
31. The fact that the-------of conflict is no longer as famous as it once was-----progress in race dealings.

(a) Insidiousness----repeated
(b) Practice----inculcates
(c) Shine----presages
(d) Technique----presages
(e) Caginess----indicates

Answer: (d)

32. A child should not be----as being either very shy or over aggressive.
(a) Categorized
(b) Instructed
(c) Intoned
(d) Unfocused
(e) abstained

Answer: (a)

33. President Farhaad sheikh of Egypt, ignoring----disapproval in the Alab world and in his own administration, ----accepted Prime Minister Zishan Khan Invitation to visit Iraq in order to address the Iraqi parliament.
a. Acrimonious----formally
b. Flawed----awkwardly
c. Definite----earlier
d. Spiteful----plaintively
e. Alluring----scrupulously

Answer: (a)

34. In his general----manner, he had covered himself against this type of loss.
a. thoughtful
b. fortunate
c. uncaring
d. circumspect
e. scathing

Answer: (d)

35. We not at all thought that he would way out to----in order to attain his aim; we always considered him as a----man.
a. Appeal----dishonest
b. Necromancy----pietistic
c. Reason----admirable
d. Prestidigitation----eloquent
e. Subterfuge----honest

Answer: (e)


%% page 8 36--40

Question 36 to 40

All the question given below has two words which have definite relationship to each other, followed by five alphabets pairs of associated words. Choose the alphabets pair of words.

36. Degree: Angle
a. area : square inch
b. milk : quart
c. civilization : classes
d. letter : alphabet
e. time : minutes

Answer: (a)

37. Confirmed : Ingrained
a. awareness : theoretical
b. financial : bankrupt
c. undeveloped : immature
d. believable : unbelievable
e. wary: grueling

Answer: (b)

38. Lullaby : Barcarole
a. birth : marriage
b. night : sunrise
c. cradle : gondola
d. song : verse
e. song : sonneteer

Answer: (c)

39. Zoology : Animals
a. ecology : pollution
b. botany : trees
c. chemistry : molecule
d. Past : public
e. mathematics : arithmetic

Answer: (a)

40. Dory : Van
a. dairy : buffalo
b. fish : bus
c. freighter : caisson
d. runners : bat
e. Danish : Dutch

Answer: (c)

%% page 9 41--50

In these particular questions there are given some statements, followed by the conclusion which appeals you to be the most correct.

41. Nitrogen gas is lighter than oxygen. Nitrogen gas is lighter than Helium. Therefore, oxygen is the heaviest of the three gases.
(a) Can’t say
(b) True
(c) False
(d) Probably true
(e) None of the above

Answer: (a)

42. The presence of calcium in milk makes it white. Rice too is white in color. Therefore, rice also contains calcium.
(a) Can’t say
(b) True
(c) False
(d) Probably true
(e) None of the above

Answer: (a)

43. Soap is used for washing because
(a) The advertising is powerful
(b) Its shape is convenient
(c) It dissolves dirt in water more easily
(d) The perfume is pleasant
(e) None of the above

Answer: (c)

44. Ice floats on water because
(a) It is spongy
(b) It is trans parent
(c) It is an element which melts easily
(d) Its weight is less than the weight of water of equal volume
(e) None of the above

Answer: (d)

45. At midnight, you heard the voice of several people shouting “fire”. Which of the following you would do?
(a) Ensure where the fire had taken place and to what extent
(b) Continue to sleep till you are called for
(c) Rush out of the room with buckets of water to extinguish the fire
(d) Rush to the fire brigade station and inform the officials about the fire
(e) None of the above

Answer: (a)

%% page 10 46--50

In these particular questions there are given some statements, followed by the conclusion which appeals you to be the most correct.

46. You have been asked to appoint a personal secretary. Which of the following quality would you consider as most important?
(a) She must have good experience
(b) She must have an imposing personality
(c) She must be highly educated
(d) She must be an efficient stenographer
(e) None of the above

Answer: (a)

47. While riding on a scooter, you find someone has been hurt by your scooter. Which of the following will be your responsibility?
(a) Pay compensation for the injury and try to dispose the matter
(b) Try to run away from the spot immediately
(c) Take him to the Doctor and arrange for the medical aid
(d) Stop your vehicle and say sorry
(e) None of the above

Answer: (c)

48. Generally a patient of tuberculosis visits the hill stations because
(a) They are advised by the Physicians to do so
(b) It is pleasure to enjoy the environment
(c) Atmospheric pressure decreases with the height from the sea level
(d) Cold weather is favorable for the patients of tuberculosis
(e) None of the above

Answer: (c)

49. Snakes and hawks are the predators of mice in the field. Dogs which also feed on mice are bought on the scene. What will be the immediate result?
(a) Increase in the number of snakes
(b) Decrease in the number of snakes and hawks
(c) Decrease in the number of mice
(d) Decrease in the number of dogs
(e) None of the above

Answer: (c)

50. Average family income in the cities has increased today as compared to the last few years, as in most families these days’ husbands and wives are working. This sentences implies all the following except
(a) Family income level was lower few years ago
(b) Wives earn more than husbands today
(c) It was more prevalent for one spouse to work earlier than today
(d) More husbands and wives are working today as compared to last few years
(e) None of the above

Answer: (b)

%% page 11 51--55

51. Team sports like cricket, display socialist tendencies in their requirements of individual subordination to the authority of coaches and managers.

Which of the following conclusion may not be inferred from the above information?
(a) All team sports have socialist tendencies
(b) All team sports are authoritarian
(c) Without employee subordination to managerial authority, production for profit would not be possible
(d) All team players are subordinate to their coaches
(e) None of the above

Answer: (c)

52. If in your college hostel mess, you find that the vegetable curry being served for the last ten days is having a lot of stones and you are fed up with it. What will you do?
(a) Buy your own vegetables and cook it in your room
(b) Leave consuming the vegetables altogether
(c) Speak with cook to change the vegetable
(d) Bring the matter to the notice of the mess in charge and if nothing is done by him, then inform the hostel administration
(e) None of the above

Answer: (d)

53. From 1940 to 1970, the amount of food production per worker and per hour increased two fold. From 1970 to 2000, food production per worker and per hour increased one and a half times.
Each of the following, if true, could help to account for this trend except (a) More workers were needed to produce the same unit of output
(b) The number of farm workers increased
(c) The number of hours worked per unit of output decreased
(d) The use of chemical fertilizers decreased
(e) None of the above

Answer: (b)

54. Starting in 1985, all drivers had to wear helmets if they have to drive a two wheeler. From which of the following can this statement be properly inferred?
(a) Some drivers may have worn helmets before 1985, but all two wheeler drivers were required to wear them beginning in 1985
(b) No drivers had to wear helmets before 1985
(c) Two wheelers drivers were the first to be required to wear helmets
(d) Two wheelers drivers had to wear helmets prior to 1985
(e) None of the above

Answer: (a)

55. In 1970, the average child visited the dentist once a year. By 1990 the number of visits increased to two. Today, the average child visits the dentist three times a year. Each of the following, if true, could explain this trend except.
(a) Better home care of teeth has reduced the number of cavities
(b) Dentist fee have declined over the period
(c) Parents are more aware of the importance of dental care
(d) Dental care has become less painful
(e) None of the above

Answer: (c)

%% page 12 56--60

56. Opposition of new anti terrorist legislation could defend themselves against the author’s strategy by arguing
(a) That India’s border partners have also passed similar legislation


(b) The fact that past such legislation improved the situation does not mean that the present bill will also do the same
(c) That the new law is not as strong as the earlier bill
(d) That the defense personnel are not always right
(e) None of the above

Answer: (c)

57. While returning from the night cinema show, you notice that some stupid people are chasing two young and beautiful girls going in a Cab. What will you do in such a situation?
(a) You will pass on your way quietly and take no notice of them
(b) You would ask the stupid people to run away or to go through the consequences
(c) You would seek the help of some passerby so as to make the girls out of the stupid people grip
(d) You would escort girls up to market place giving no chance to stupid people to play their nasty games
(e) None of the above

Answer: (b)

58. In 2002, according to a news poll, 36 % of the voters had leaning towards party “Y”. In 2004, this figure rose to 46%. But in another survey the percentage was down to 40%. Therefore, the party “Z” is likely to win the next election. Which of the following, if true, would seriously weaken the above conclusion?
(a) People tend to switch their votes at the last minute
(b) It has been shown that 85% of the voters belonging to the party “Y” vote in an election as compared to 50% of the voters belonging to party “Z”
(c) People vote for the best candidate, not for the party
(d) No one can predict how people will vote
(e) None of the above

Answer: (b)

59. Inflation rose by 4.5% over the second quarter, by 3.5% during the first quarter and higher than 2.5% recorded during the same time last year. However, the higher price index did not seem to alarm National stock index, as stock prices remained steady.
Which of the following, if true, could explain the reaction of National stock Index? (a) The Prime minister announced that he was concerned about the rising inflation
(b) Stock prices were steady because of a fear that inflation would continue
(c) Economist warned that inflation would continue
(d) Much of the quarterly increase in the price level was due to a summer drought effect on food price
(e) None of the above

Answer: (a)

60. During 2002, advertising expenditure on readymade garments increased by 20% while readymade garments consumption rose by 25%.
Each of the following, if true could help explain the increase in garments consumption except (a) Per capita consumption of unstitched garments declined
(b) Advertising effectiveness increased
(c) Serving machine production doubled
(d) Readymade garments were available in more shops
(e) None of the above

Answer: (a)

%% page 13 61--65

Question 61

Which of the following is different from the rest three?

(a) Shrub
(b) Flower
(c) Tree
(d) Herb
(e) None of the above

Answer (c)

Question 62

Which one of the following differs from the rest three?
(a) FHUJU
(b) YNHIA
(c) ISEPU
(d) SGRFI
(e) None of the above

Answer (a)

Clarification: The vowel U is repeated

Question 63

Find that pair of numbers which is not related to the other pairs of numbers due to lack of some common property.
(a) 57, 69
(b) 42, 29
(c) 47, 59
(d) 73, 61
(e) None of the above

Answer (b)

Clarification: Difference between the numbers must be 12

Question 64

Which one of the following differs from the rest of the three?
(a) TSGH
(b) ZAYB
(c) VEUF
(d) XCWD
(e) None of the above

Answer (a)

Clarification: (A) = ZA/YB. A and Z are the first and last alphabets. Y and B are the second alphabets from the end and from the beginning and so on, therefore TSGH differs.

Question 65

Which one is different from the rest three?
(a) Pointed-Blunt
(b) Hard-Soft
(c) Sweet-Sour
(d) Long-High
(e) None of the above

Answer (d)

%% page 14 66--70

Question 66

Four of the following five are alike in a certain way and so form a group. Which is the one that does not belong to that group?

(a) QOM
(b) CEG
(c) IKM
(d) UWY
(e) PRT

Answer (a)

Clarification: In the group (a), three alternative letters of the alphabet are in reverse order

In the Questions 67 to 70, select the word opposite in meaning of the given word.

Question 67

Repel
(a) Attract
(b) Concentrate
(c) Continue
(d) Attend
(e) None of the above

Answer (a)

Question 68

Violent
(a) Harmless
(b) Gentle
(c) Tame
(d) Humble
(e) None of the above

Answer (b)

Question 69

Malicious
(a) Indifferent
(b) Boastful
(c) Kind
(d) Generous
(e) None of the above

Answer (d)

Question 70

Frugal
(a) Ostentatious
(b) Copious
(c) Generous
(d) Extravagant
(e) None of the above

Answer (d)

%% page 15 70--77

Question 71

Barely had he arrived------ it started raining.
(a) When
(b) After
(c) Before
(d) Than

Answer (d)

Question 72

He tried to ------ himself against a group of ruffians
(a) Support
(b) Collect
(c) Defend
(d) Save

Answer (d)

Question 73

My aunty decided to take ------ and my sister to the market.
(a) Mine
(b) Myself
(c) I
(d) Me

Answer (d)

Question 74

Find the ------ of the news.
(a) Headings
(b) Topics
(c) Titles
(d) Captions

Answer (a)

Question 75

During Christmas the shops are ------ of people.
(a) Crowded
(b) Busy
(c) Bubbling
(d) Full

Answer (d)

%% page 17 76--80

Questions from 76 to 80, choose the one option which best expresses the meaning of the given word.

Question 76

Gratify
(a) Pacify
(b) Appreciate
(c) Indulge
(d) Frank

Answer (a)

Question 77

Extricate
(a) Complicate
(b) Pull
(c) Free
(d) Tie

Answer (c)

Question 78

Inexplicable
(a) Chaotic
(b) Unaccountable
(c) Confusing
(d) Unconnected

Answer (b)

Question 79

Insolvent
(a) Broke
(b) Poor
(c) Penniles
(d) Bankrupt

Answer (d)

Question 80

Stringent
(a) Shrill
(b) Dry
(c) Rigorous
(d) Strained

Answer (c)


%% page 17 80--85

ynonyms:

In each section you will find a number of sentences, in which you will find one word is ITALICISED. For each italicized word, find the word nearest in meaning to the italicized part.

Question 81

The weavers have to do monotonous work
(a) Exhausting
(b) Autonomous
(c) Irksome
(d) Repetitive

Answer: (d)

Question 82

The country’s economy is beginning to look up now.
(a) Improve
(b) Go down
(c) Remain static
(d) Look clear

Answer (a)

Question 83

There is not a single word that is redundant in the report.
(a) Flowery
(b) Bombastic
(c) Unimportant
(d) Not needed

Answer (d)

Question 84

Most of the politicians these days have a large number of toadies around them.
(a) Followers
(b) Professionals assistants
(c) Servants
(d) Sycophants

Answer (c)

Question 85

The old man shows no sign of infirmity even though he is eighty years old.
(a) Indolence
(b) Fickleness
(c) Lack of firmness
(d) Feebleness

Answer (d)

%% page 18 85--90

Questions from 86 to 90

Fill in the blanks with appropriate words

Question 86

As ice is related to coolness in the same way as Earth is related to ------
(a) Gravitation
(b) Weight
(c) Ocean
(d) Forest

Answer (a)

Question 87

As North Pole is related to Magnet, in the same way ------ is related to Battery.
(a) Terminal
(b) Power
(c) Energy
(d) Cell

Answer (d)

Question 88

Find the missing number in the following series.

6, 12, 21, ----, 48
(a) 40
(b) 33
(c) 38
(d) 45

Answer (d)

Clarification: +6, +9, +12, +15

Question 89

Which one is different from rest three?
(a) Scooter
(b) Cycle
(c) Car
(d) Tonga

Answer (c)

Question 90

Arrange the following words in a meaningful order:

Platinum, Gold, Iron, Diamond, Sand
(a) 5 4 3 2 1
(b) 2 4 3 5 1
(c) 4 5 1 3 2
(d) 3 2 1 5 4

Answer (d)


%% page 19 91--95

In the following questions, from 91 to 95, a group of words is given in each question. Below four words are given. Find the appropriate alternatives which can substitute the given words. Find the suitable options which can substitute the given words.

Question 91

Parts of a country behind the coast or a river’s banks
(a) Swamps
(b) Isthmus
(c) Archipelago
(d) Hinterland

(e) None of the above

Answer (d)

Question 92

A person who knows many languages
(a) Polyglot
(b) Grammarian
(c) Bilingual
(d) Linguist
(e) None of the above

Answer (d)

Question 93

That which cannot be read
(a) Negligible
(b) Incorrigible
(c) Illegible
(d) Ineligible
(e) None of the above

Answer (c)

Question 94

Study of the evolution of man as an animal
(a) Ethnology
(b) Anthropology
(c) Chronology
(d) Archaeology
(e) None of the above

Answer (b)

Question 95

To cause troops, etc. to plead out in readiness for battle
(a) Deploy
(b) Align
(c) Disperse
(d) Collocate
(e) None of the above

Answer (a)

%% page 20 96--100

From questions 96 to 100, one word in each sentence is italicized. Choose the correct word which may improve the sentence and if there is no improvement required then your sentence should be (e)

Question 96

He opened the letter without caring to read the address on envelop.
(a) Thinking
(b) Bothering
(c) Worrying
(d) Knowing
(e) No improvement

Answer (b)

Question 97

She gave most of her time to composition.
(a) Lent
(b) Devoted
(c) Spent
(d) Spend
(e) No improvement

Answer (b)

Question 98

The parents became very troubled when their son did not return by late night.
(a) Depressed
(b) Sad
(c) Anxious
(d) Worried
(e) No improvement

Answer (c)

Question 99

This particular matter must be regarded in every point of view.
(a) From
(b) With
(c) At
(d) By
(e) No improvement

Answer (a)

Question 100

She did not ask any questions to him.
(a) To him any question
(b) Any question from him
(c) Him any question
(d) Any question for him
(e) No improvement

Answer (c)
\end{comment}

\endinput



