
%%--------------------------------------------------
%% SAT Practice Test One
%%--------------------------------------------------

%% https://collegereadiness.collegeboard.org/pdf/sat-practice-test-1.pdf

%% Directions
%%--------------------------------------------------

%% Each passage below is accompanied by a number of questions. 
%% For some questions, you will consider how the passage might be revised to improve the expression of ideas. 
%% For other questions, you will consider how the passage might be edited to correct errors in sentence structure, usage, or punctuation. 
%% A passage or a question may be accompanied by one or more graphics (such as a table or graph) that you will consider as you make revising and editing decisions.

%% Some questions will direct you to an underlined portion of a passage. 
%% Other questions will direct you to a location in a passage or ask you to think about the passage as a whole.

%% After reading each passage, choose the answer to each question that most effectively improves the quality of writing in the passage or that makes the passage conform to the conventions of standard written English. 
%% Many questions include a “NO CHANGE” option.
%% Choose that option if you think the best choice is to leave the relevant portion of the passage as it is.


%% NOTE: Unauthorized copying or reuse of any part of this page is illegal.


%% SAT Writing and Language Test
%%--------------------------------------------------
\element{sat-mc}{
Whey to Go
Greek yogurt—a strained form of cultured
yogurt—has grown enormously in popularity in the
United States since it was first introduced in the country
in the late 1980s.
From 2011 to 2012 alone, sales of Greek yogurt in the
US increased by 50 percent. The resulting increase in
Greek yogurt production has forced those involved in the
business to address the detrimental effects that the
yogurt-making process may be having on the
environment. Fortunately, farmers and others in the

Greek yogurt business have found many methods of controlling and eliminating most environmental threats.
Given these solutions as well as the many health benefits
of the food, the advantages of Greek yogurt 1 outdo the
potential drawbacks of its production.
[1] The main environmental problem caused by the
production of Greek yogurt is the creation of acid whey
as a by-product. [2] Because it requires up to four times
more milk to make than conventional yogurt does, Greek
yogurt produces larger amounts of acid whey, which is
difficult to dispose of. [3] To address the problem of
disposal, farmers have found a number of uses for acid
whey. [4] They can add it to livestock feed as a protein
2 supplement, and people can make their own
Greek-style yogurt at home by straining regular yogurt.
[5] If it is improperly introduced into the environment,
acid-whey runoff 3 can pollute waterways, depleting
the oxygen content of streams and rivers as it
decomposes. [6] Yogurt manufacturers, food
4 scientists; and government officials are also
working together to develop additional solutions for
reusing whey. 5


Though these conservation methods can be costly and time-consuming, they are well worth the
effort. Nutritionists consider Greek yogurt to be a healthy
food: it is an excellent source of calcium and protein,
serves 7 to be a digestive aid, and 8 it contains few
calories in its unsweetened low- and non-fat forms.
Greek yogurt is slightly lower in sugar and carbohydrates
than conventional yogurt is. 9 Also, because it is more
concentrated, Greek yogurt contains slightly more
protein per serving, thereby helping people stay


\begin{question}{writing-t01-q01}
    \begin{choices}
        \wrongchoice{One character argues with another character who intrudes on her home.}
        \wrongchoice{One character receives a surprising request from another character.}
        \wrongchoice{One character reminisces about choices she has made over the years.}
        \wrongchoice{One character criticizes another character for pursuing an unexpected course of action.}
    \end{choices}
\end{question}
}

A) NO CHANGE
B) defeat
C) outperform
D) outweigh
2
Which choice provides the most relevant detail?
A) NO CHANGE
B) supplement and convert it into gas to use as fuel
in electricity production.
C) supplement, while sweet whey is more desirable
as a food additive for humans.
D) supplement, which provides an important
element of their diet.
3
A) NO CHANGE
B) can pollute waterway ’ s,
C) could have polluted waterways,
’
D) has polluted waterway’s,
4
A) NO CHANGE
B) scientists: and
C) scientists, and
D) scientists, and,
5
To make this paragraph most logical, sentence 5
should be placed
A) where it is now.
B) after sentence 1.
C) after sentence 2.
D) after sentence 3


The writer is considering deleting the underlined
sentence. Should the writer do this?
A) Yes, because it does not provide a transition
from the previous paragraph.
B) Yes, because it fails to support the main
argument of the passage as introduced in the
first paragraph.
C) No, because it continues the explanation of how
acid whey can be disposed of safely.
D) No, because it sets up the argument in the
paragraph for the benefits of Greek yogurt.
7
A) NO CHANGE
B) as
C) like
D) for
8
A) NO CHANGE
B) containing
C) contains
D) will contain
9
A) NO CHANGE
B) In other words,
C) Therefore,
D) For instance,





\endinput


