
%%--------------------------------------------------
%% SAT: Sentence Completion
%%--------------------------------------------------

%%--------------------------------------------------
%% References
%%--------------------------------------------------

%% http://www.bestsamplequestions.com/sat-sample-questions/sentence-completions/sentence-completions.html


%% SAT Multiple Choice Questions
%%--------------------------------------------------

%% page 1
\element{sat-mc}{
\begin{question}{sentence-completion-q01}
    In one outrageous instance of \rule[-0.1pt]{4em}{0.1pt} research,
        one of the nation's most powerful researchers in the field of inheritance reported on experiments that were by no means carried out and published deliberately \rule[-0.1pt]{4em}{0.1pt} scientific papers on his missing work.
    \begin{choices}
        \wrongchoice{Hypothetical---Challenging}
      \correctchoice{Fraudulent---Deceptive}
        \wrongchoice{Erroneous---Neutral}
        \wrongchoice{Complete---Abstract}
        \wrongchoice{Derivative---Reliable}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{sentence-completion-q02}
    To lessen the problem of infected chicken,
        the study panels suggest that the federal government shifts its inspection stress from cursory bird by bird chart checks to a more \rule[-0.1pt]{4em}{0.1pt} random sampling for bacterial and chemical infectivity.
    \begin{choices}
        \wrongchoice{Symbolic}
        \wrongchoice{Discreet}
      \correctchoice{Rigorous}
        \wrongchoice{Doubtful}
        \wrongchoice{Automatic}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{sentence-completion-q03}
    Pluto first came into \rule[-0.1pt]{4em}{0.1pt} back in the year 1985,
        when astronomers observed as Pluto passed in front of a star.
    They were able to compute a small dimming as its environment passed in front of the star,
        before Pluto planet itself stopped or blocked the star completely.
    From those \rule[-0.1pt]{4em}{0.1pt},
        they were able to calculate that it has a thin cover of nitrogen,
        carbon dioxide and methane.
    As Pluto travels away from the Sun,
        this environment gets so chilly that it freezes onto the plane.
    \begin{choices}
      \correctchoice{Existence---Interpretations}
        \wrongchoice{Survival---Research}
        \wrongchoice{Endurance---Investigate}
        \wrongchoice{Patience---Examine}
        \wrongchoice{Persistence---Inspect}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{sentence-completion-q04}
    Her novel published to worldwide acclaim,
        her legendary gifts recognized by the chief figures of the Harlem Renaissance,
        her status as yet \rule[-0.1pt]{4em}{0.1pt} by envious slights,
        Hurston clearly was at the \rule[-0.1pt]{4em}{0.1pt} of her career.
    \begin{choices}
        \wrongchoice{Unmarred---Edge}
        \wrongchoice{Unspoiled---Ebb}
        \wrongchoice{Untainted---Tremendously}
        \wrongchoice{Blackened- Sympathy}
      \correctchoice{Untarnished---Zenith}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{sentence-completion-q05}
    The unique daffodil is a \rule[-0.1pt]{4em}{0.1pt} or sometimes found in golden color and has a proclaimed like corona in the middle with petals all around it. Often the broadcast is a complementary color,
        and with the beginning of hybrids the daffodils themselves can now vary in color from yellow,
        white, and orange to even pinks or it can also be found in light greens.
    An enduring perennial bulb that \rule[-0.1pt]{4em}{0.1pt} in spring season,
        daffodils are very pliable, but favor a rich,
        well drained soil in fractional to full sun.
    \begin{choices}
      \correctchoice{Dazzling---Blossom}
        \wrongchoice{Stunning---Flourish}
        \wrongchoice{Striking---Prosper}
        \wrongchoice{Unusual---Thrive}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{sentence-completion-q06}
    Getting free of bed bugs is not a simple \rule[-0.1pt]{4em}{0.1pt} and majority cases of bed bug invasion will need action by a pest-control specialist. A mixture of low scent sprays,
        dusts, and vaporizer insecticides can be worn to eliminate bed bugs.
    These must be used to all areas where the bugs are found as well as spaces where they may creep or bury. The pest-control business can help you decide if the mattress can be cleaned or must be redundant. Since bed bugs cannot eagerly be \rule[-0.1pt]{4em}{0.1pt} with insecticides,
        it's habitually essential to throw away infested mattresses and beds.
    \begin{choices}
      \correctchoice{Procedure---Treated}
        \wrongchoice{Formula---Treatment}
        \wrongchoice{Rule---Conduct}
        \wrongchoice{Principle---Behavior}
        \wrongchoice{Standard---Deeds}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{sentence-completion-q07}
    According to a research published in a \rule[-0.1pt]{4em}{0.1pt} issue of The Federation of American Societies for Experimental Biology academic journal,
        it was one-third more \rule[-0.1pt]{4em}{0.1pt} at stopping a unrelenting cough than a placebo.
    \begin{choices}
        \wrongchoice{Modern---Efficient}
      \correctchoice{Recent---Effective}
        \wrongchoice{Contemporary---Resourceful}
        \wrongchoice{Current---Inventive}
        \wrongchoice{Existing---Creative}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{sentence-completion-q08}
    Nowadays pizza has become just as American as apple pie and baseball.
    Only because of its most current beginning is it considered an \rule[-0.1pt]{4em}{0.1pt} cuisine.
    A Huge U.S. based multi-billion dollar \rule[-0.1pt]{4em}{0.1pt} should be grateful for the growth along with underprivileged college students who can be grateful for the fine dining experience pizza has given them.
    \begin{choices}
        \wrongchoice{African---Trade}
      \correctchoice{Italian---Business}
        \wrongchoice{Indian---Employment}
        \wrongchoice{Chinese---Industry}
        \wrongchoice{Thai---Production}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{sentence-completion-q09}
    Whoever made-up the method of using ice \rule[-0.1pt]{4em}{0.1pt} with salt to lower and manage the coolness of ice cream ingredients during manufacturing provided a main breakthrough in ice cream equipment.
    Also important was the creation of the wooden bucket refrigerator with rotary paddles that \rule[-0.1pt]{4em}{0.1pt} the ice cream's manufacture.
    \begin{choices}
      \correctchoice{Mingled---Enhanced}
        \wrongchoice{Mix---Better}
        \wrongchoice{Merge---Improved}
        \wrongchoice{Combine---Superior}
        \wrongchoice{Unite---Higher}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{sentence-completion-q10}
    Whales and seals of the Southern deep-sea have been brutally browbeaten by man in the past,
        but are now mostly \rule[-0.1pt]{4em}{0.1pt}.
    Some seals and whales have had vivid population increases in current decades,
        though others remain very much condensed \rule[-0.1pt]{4em}{0.1pt} to pre-hunting level.
    \begin{choices}
        \wrongchoice{Curbed---Contrast}
        \wrongchoice{Restricted---Disparity}
        \wrongchoice{Limited---Inequality}
      \correctchoice{Confined---Compared}
        \wrongchoice{Small---Dissimilarity}
    \end{choices}
\end{question}
}

%% page 2
\element{sat-mc}{
\begin{question}{sentence-completion-q11}
    Strawberries are low in obese content and fat.
    They are \rule[-0.1pt]{4em}{0.1pt} with vitamin C, folic acid, fiber,
        as well as potassium.
    They can lessen the possibility of heart attacks and cancers.
    Strawberry eating helps in the lessening of systolic blood stress.
    Juice from strawberry pulp helps in improving from fever.
    Strawberry juice, if mixed with honey can lessen irritation.
    It has a \rule[-0.1pt]{4em}{0.1pt} effect on sunburns.
    \begin{choices}
      \correctchoice{Loaded---Healing}
        \wrongchoice{Lot of---Good}
        \wrongchoice{Burdened---Heal}
        \wrongchoice{Hampered---Cure}
        \wrongchoice{Hindered---Make well}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{sentence-completion-q12}
    Oranges grown in Southeast Asia,
        and then extended throughout the world with timing directly parallel to the \rule[-0.1pt]{4em}{0.1pt} of culture.
    Thus, for instance, it was Columbus, who brought the first orange seeds in the World.
    Invading Moors had previously introduced them to Spain.
    Oranges played an important and representational part in the work of the painters of the Italian regeneration,
        and, in previous centuries,
        at least two attacks of Italy were touched off by gifts of oranges \rule[-0.1pt]{4em}{0.1pt} sent to warlords in the northern countries.
    Oranges were known as Golden Apples of the Hesperides.
    \begin{choices}
        \wrongchoice{Mores---Charming}
      \correctchoice{Spread---Alluringly}
        \wrongchoice{Society---Amiable}
        \wrongchoice{Humanity---Charm}
        \wrongchoice{Kindness---Allure}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{sentence-completion-q13}
    \rule[-0.1pt]{4em}{0.1pt}
    Volcanic mountain's  when melts rock from deep within the Earth \rule[-0.1pt]{4em}{0.1pt} during the crust and heaps up on itself.
    Check The island chain of Hawaii is in fact on the top of the list of the volcanoes prone area.
    Famous volcanoes on land include Mount Fuji in Japan and Mount St. Helens in Washington State.
    Sometimes volcanic explosions break down mountains in its place of building them up,
        like in the year 1980 \rule[-0.1pt]{4em}{0.1pt} that blew the top of Mount St. Helens.
    \begin{choices}
      \correctchoice{Erupts---Explosions}
        \wrongchoice{Blast---Bang}
        \wrongchoice{Flash---Flare up}
        \wrongchoice{Blaze---Spark}
        \wrongchoice{Burn---Fire}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{sentence-completion-q14}
    While white lilies represent chastity and desirable quality---and were the mark of the Virgin Mary's transparency and her role of ruler of the Angels as,
        other ranges became \rule[-0.1pt]{4em}{0.1pt},
        they brought with them extra meanings and representations as well.
    An alstroemeria or Peruvian lily symbolizes companionship and affection,
        white stargazer lilies convey kindness and a pink stargazer lily \rule[-0.1pt]{4em}{0.1pt} assets and success.
    Symbolizing modesty and loyalty,
        lilies of the vale are the 2nd nuptial anniversary flower.
    \begin{choices}
        \wrongchoice{Usual---Signifies}
        \wrongchoice{Common---Shows}
        \wrongchoice{Ordinary---Display}
      \correctchoice{Accepted---Signifies}
        \wrongchoice{Received---Exhibit}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{sentence-completion-q15}
    Kiwi birds are tremendously \rule[-0.1pt]{4em}{0.1pt} in the bird world.
    They are usually found in the size of chickens,
        but they lay eggs which is alike to ostrich eggs,
        weighing around a pound each egg.
    Their \rule[-0.1pt]{4em}{0.1pt} eggs are the major in the bird world,
        in quantity to their bodies.
    These birds were named after their characteristic shrill sound ``kee-wee''.
    \begin{choices}
      \correctchoice{nique---Vast}
        \wrongchoice{imilar---Small}
        \wrongchoice{omparable---Tiny}
        \wrongchoice{quivalent---Giant}
        \wrongchoice{qual---Monster}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{sentence-completion-q16}
    The Tundra region Swan stays in groups apart when on a reproduction territory.
    Although most swans reach out to \rule[-0.1pt]{4em}{0.1pt}, but a large part of the population on the reproduction grounds still can be found in groups.
    These swans are not reproducing, and may be little birds that have not yet started breeding, adult pairs whose \rule[-0.1pt]{4em}{0.1pt} attempts botched, or adults that bred in the long-ago but for some cause do not in that year.
    \begin{choices}
        \wrongchoice{Type---Birth}
      \correctchoice{Breed---Reproduction}
        \wrongchoice{Kind---Labor}
        \wrongchoice{Sort---Native}
        \wrongchoice{Genus---National}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{sentence-completion-q17}
    A cherry tree is a blossoming deciduous tree that puts up with a fruit.
    The fruit cherry is \rule[-0.1pt]{4em}{0.1pt} round, with despair at the peak.
    The outer cover of the fruit is soft and ranges from light to very deep red color, even though they are also found in white and yellow colors.
    The fruit of the cherry tree is usually either sour or sweet in \rule[-0.1pt]{4em}{0.1pt}.
    \begin{choices}
      \correctchoice{Generally---Taste}
        \wrongchoice{Somewhat---Delicious}
        \wrongchoice{Tasty---Feel}
        \wrongchoice{Fairly---Sense}
        \wrongchoice{Quiet---Brains}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{sentence-completion-q18}
    Roses have been the most liked and first choice of flowers for the use of \rule[-0.1pt]{4em}{0.1pt} all over the world.
    They also act as a grand addition to residence and office furnishings.
    A cluster of roses or even a single rose works wonders aesthetically and significantly to make the place livelier.
    %% NOTE: unsure of this??
    Besides beautiful cut roses, false flowers like silk roses in dissimilar colors are also extensively used for \rule[-0.1pt]{4em}{0.1pt}.
    \begin{choices}
      \correctchoice{Gifting---Beautification}
        \wrongchoice{Giving---Decor}
        \wrongchoice{Generous---Furnishing}
        \wrongchoice{Kind---Trimming}
        \wrongchoice{Liberal---Garnish}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{sentence-completion-q19}
    According to the Space Online Dictionary and About Astronomy,
        a star is a ball of habitually hydrogen and helium gas that shines exceptionally \rule[-0.1pt]{4em}{0.1pt}.
    A star is so enormous that its core is tremendously intense and burning.
    At the high nucleus temperatures of a star,
        atoms travel so fast that they occasionally attach to other atoms when they crash with them,
        creating more \rule[-0.1pt]{4em}{0.1pt} atoms and producing a great quantity of energy.
    This procedure is known as nuclear mixture.
    \begin{choices}
      \correctchoice{Vibrantly---Enormous}
        \wrongchoice{Brightly---mammoth}
        \wrongchoice{Vividly---Colossal}
        \wrongchoice{Garishly---Gigantic}
        \wrongchoice{Loudly---Massive}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{sentence-completion-q20}
    Through binding the power of fine art,
        we hope to assemble global \rule[-0.1pt]{4em}{0.1pt} for the defense of ecological biodiversity, and to make a new model promoting maintenance worldwide.
    The plan will address many themes,
        as well as the association between the natural surroundings and human traditions;
        assumptions about the importance of \rule[-0.1pt]{4em}{0.1pt} natural and cultural variety;
        and global examination and exchange.
    \begin{choices}
        \wrongchoice{Hold---Store}
      \correctchoice{Support---Preserving}
        \wrongchoice{Clutch---Amass}
        \wrongchoice{Grip---Stock up}
        \wrongchoice{Grasp---Hoard}
    \end{choices}
\end{question}
}

%% page 3
\element{sat-mc}{
\begin{question}{sentence-completion-q21}
    Human Trafficking is an offense against \rule[-0.1pt]{4em}{0.1pt}.
    It occupies an act of transporting, recruiting, transferring, harboring or getting a person through a use of power, force or other means, for the reason of developing them.
    Every year, hundreds of men, women and children become the victim of traffickers, in their own countries and overseas.
    Every country in the earth is \rule[-0.1pt]{4em}{0.1pt} by trafficking, whether as a country of foundation, transit or purpose for victims.
    \begin{choices}
        \wrongchoice{People---Overstated}
        \wrongchoice{Human---Magnified}
        \wrongchoice{Mankind---Puffed up}
      \correctchoice{Civilization---Exaggerated}
        \wrongchoice{People---Inflated}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{sentence-completion-q22}
    Lotuses are symbols of transparency and impulsive generation and hence \rule[-0.1pt]{4em}{0.1pt} earthly birth.
    According to the Lalitavistara, 'the soul of the top of men is immaculate,
        like the fresh lotus in the water which does not stick to it, and,
        according to mysterious Buddhism, the heart of the human beings is like an \rule[-0.1pt]{4em}{0.1pt} lotus:
        when the qualities of the Buddha build up therein the lotus flourish.
    This is why the Buddha sits on a lotus in flourish.
    \begin{choices}
      \correctchoice{Represent---Beautiful}
        \wrongchoice{Embody---Ugly}
        \wrongchoice{Personify---Unsightly}
        \wrongchoice{Exemplify---Hideous}
        \wrongchoice{Typify---Revolting}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{sentence-completion-q23}
    Terrorism is not new to anyone.
    In reality, in some respects, that what is nowadays known as \rule[-0.1pt]{4em}{0.1pt} predates by millennia the current term used to explain it.
    This is not to say that the work of terrorism has remained stationary.
    To a certain extent, as the difficulties concerned in defining it replicate, \rule[-0.1pt]{4em}{0.1pt} has evolved significantly over the years, even if keeping some of the same individuality that have traditionally typified it.
    \begin{choices}
        \wrongchoice{Peace---Mankind}
        \wrongchoice{Love---Peace}
        \wrongchoice{Coordination---Human nature}
      \correctchoice{Violence---Terrorism}
        \wrongchoice{Fighting---Calm}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{sentence-completion-q24}
    %% NOTE: answers do not match question !!
    A vacation aim should be like the Smoky Mountains as it is \rule[-0.1pt]{4em}{0.1pt} because of the lot of things to do and the magnificent places to stay.
    The area offers all you require for a family holiday, marriage, dreamy getaway, church move back, family meeting, military meeting, or corporate Smoky Mountain gathering place.
    \begin{choices}
        \wrongchoice{Meaningful---assembly}
      \correctchoice{Worthwhile---Gathering}
        \wrongchoice{Momentous---Congress}
        \wrongchoice{Significant---get together}
        \wrongchoice{Important---School assembly}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{sentence-completion-q25}
    Cartoons have long record. When people think of cartoons, they may think of \rule[-0.1pt]{4em}{0.1pt} books, opinionated cartoons and Saturday mornings when they were children.
    But cartoons have been more or less in print and diagram media for numerous hundred years.
    Some of the initial cartoons go back to the 19\textsuperscript{th} Century Britain, where cartoons would come into view satirizing \rule[-0.1pt]{4em}{0.1pt} people of the day.
    \begin{choices}
        \wrongchoice{Serious---Dull}
        \wrongchoice{Sober---Dry}
      \correctchoice{Comedian---Renowned}
        \wrongchoice{Grim---Boring}
        \wrongchoice{Stern---Tedious}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{sentence-completion-q26}
    ``AICC met at an occasion when there is a \rule[-0.1pt]{4em}{0.1pt} of scandals and the country is waiting to know what level of fraud would create rage in the party,'' said party representative Nirmala Sitharaman.
    ``But there was total peace in the three main speeches on \rule[-0.1pt]{4em}{0.1pt}''.
    The major speakers used the diversionary tactic of conversing fear charges on activists of the RSS, a pro-self-government association.
    \begin{choices}
      \correctchoice{Series---Dishonesty}
        \wrongchoice{List---Honesty}
        \wrongchoice{Record---Loyalty}
        \wrongchoice{Roll---Devotion}
        \wrongchoice{Evidence---Fidelity}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{sentence-completion-q27}
    The antique idea that the sick are obsessed of devils remained on in the souls of the \rule[-0.1pt]{4em}{0.1pt} and in the practices of the saints and general practitioners for ages after it should have passed into void.
    All throughout the middle Ages and even nowadays in some sectors of America and Europe, this policy of demonic control was held to be richly proved by the Bible.
    Jesus is said to have shed out devils and throughout the Middle Ages it was held that to disbelief demonical control was to \rule[-0.1pt]{4em}{0.1pt} the whole structure of Christian policy.
    The policy of demonic control was as well ashore in the Scriptures as was a faith in witches and witchcraft.
    \begin{choices}
        \wrongchoice{Human---Lose}
      \correctchoice{Mankind---Be beaten}
        \wrongchoice{Man---Mislay}
        \wrongchoice{Women---Misplace}
        \wrongchoice{People---Conquer}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{sentence-completion-q28}
    Chocolate is made from trees and plants, which means it has many of the health \rule[-0.1pt]{4em}{0.1pt} of dark vegetables.
    These advantages are from flavonoids, which generally act as antioxidants.
    Antioxidants guard the body from aging caused by number of radicals, which can cause damage that leads to many heart diseases.
    Dark chocolate has a lot of antioxidants as compared to strawberries.
    Flavonoids also help rest blood pressure through the construction of nitric oxide, and \rule[-0.1pt]{4em}{0.1pt} certain hormones in your body.
    \begin{choices}
      \correctchoice{Benefits---Control}
        \wrongchoice{Advantages---Power}
        \wrongchoice{Gains---Direct}
        \wrongchoice{Add---Straight}
        \wrongchoice{Inserts---Shortest}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{sentence-completion-q29}
    Penguins lost the \rule[-0.1pt]{4em}{0.1pt} to fly billions of years ago, but their strong flipper-like wings and sleek bodies make them very skillful swimmers.
    They are the best swimmers and deepest plunging species of any birds.
    While swimming, penguins will jump above the plane of the water. This particular practice is known as proposing. This coats their plumage with minute foam that \rule[-0.1pt]{4em}{0.1pt} friction, permitting them to swim as fast as 25 miles per hour.
    \begin{choices}
        \wrongchoice{Ability - Increase}
        \wrongchoice{Gift - Amplify}
        \wrongchoice{Reward - Enlarge}
      \correctchoice{Capability - Lessens}
        \wrongchoice{Incentive - Raise}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{sentence-completion-q30}
    Polar bears preferred food is the ringed seal.
    Polar bears \rule[-0.1pt]{4em}{0.1pt} catch ``ringed seals'' when seals surface to respire at openings in the ice or at inhalation holes called aglus.
    In fall, a seal cuts ten to twelve aglus in the ice using the \rule[-0.1pt]{4em}{0.1pt} claws on its fore flippers. It keeps the aglus unwrap all winter long, even when ice is eight feet thick.
    \begin{choices}
      \correctchoice{Regularly---Pointed}
        \wrongchoice{Recurrently---Blunt}
        \wrongchoice{Repeatedly---Dull}
        \wrongchoice{Constantly---Bright}
        \wrongchoice{Frequently---Vivid}
    \end{choices}
\end{question}
}

%% page 4
\element{sat-mc}{
\begin{question}{sentence-completion-q31}
    For most women \rule[-0.1pt]{4em}{0.1pt} waterproof makeup is an elective affair.
    It may be so for you too.
    So pay attention to what we are about to tell you.
    That is not the \rule[-0.1pt]{4em}{0.1pt} approach to have towards make over if you are to be a expert and not an recreational.
    \begin{choices}
        \wrongchoice{Going---Wrong}
      \correctchoice{Purchasing---Right}
        \wrongchoice{Make over---Towards}
        \wrongchoice{Over---Approach}
        \wrongchoice{Attention---Affair}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{sentence-completion-q32}
    Water-resistant makeup is not just for the drizzling season where there is direct danger to your make over getting wiped out with the rain water.
    You can \rule[-0.1pt]{4em}{0.1pt} it in all seasons.
    In fact, it gets much inferior when you sweat during summer season and your \rule[-0.1pt]{4em}{0.1pt} liquefies.
    It snows in the wintry weather and that hitch too is covered up.
    \begin{choices}
      \correctchoice{Utilize---Makeup}
        \wrongchoice{Wintry---Weather}
        \wrongchoice{Summer---Season}
        \wrongchoice{Weather---Make over}
        \wrongchoice{Attention---Utilize}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{sentence-completion-q33}
    This is the only \rule[-0.1pt]{4em}{0.1pt} investment you have to put in to make sure that your make over stays great.
    Never take away \rule[-0.1pt]{4em}{0.1pt} with whatever thing other than a certified remover, particularly water-resistant eye makeup.
    If you are travelling a lot, carry it along in your bag and you will by no means have any trouble.
    \begin{choices}
        \wrongchoice{Helpful---Liner}
        \wrongchoice{Never---No means}
      \correctchoice{Additional---Makeup}
        \wrongchoice{Certified---Along}
        \wrongchoice{Remover---Carry}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{sentence-completion-q34}
    The Egyptian eye is copious all through Ancient Egyptian fine art.
    The dark \rule[-0.1pt]{4em}{0.1pt} eyes look like the eye makeup they would have utilized.
    While pharaohs and design have altered, the eye has stayed all the same, as a symbol all through Egypt.
    Traces of malachite have been \rule[-0.1pt]{4em}{0.1pt} in primitive palettes.
    \begin{choices}
      \correctchoice{Defined---Set up}
        \wrongchoice{Altered---Eye make up}
        \wrongchoice{Traces---Primitive}
        \wrongchoice{Utilized---Through}
        \wrongchoice{Design---Symbol}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{sentence-completion-q35}
    For eye makeup to be used, one must have the \rule[-0.1pt]{4em}{0.1pt} makeup tools.
    First there should be an eye shadow makeup brush.
    The eyeliner generally comes in the shape of a pencil, and rarely requires a sharpener.
    Mascara always comes with a makeup brush.
    \rule[-0.1pt]{4em}{0.1pt} makeup brushes can help you make well-defined shapes of your eyelash. Other make up tools consist of eyebrow sealers and tweezers.
    \begin{choices}
        \wrongchoice{Wrong---Unusual}
      \correctchoice{Correct---Different}
        \wrongchoice{Makeup tools---Sharpener}
        \wrongchoice{Sealers---Rarely}
        \wrongchoice{Requires---Brushes}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{sentence-completion-q36}
    The olden times of lipstick \rule[-0.1pt]{4em}{0.1pt} in prehistory, persist into the present.
    From prehistoric India and Greece to Elizabeth Finland, inhabitants have decorated their lips with colors, dyes, plant roots, lip pencils and rouges.
    Rosy lips indicate sexual provocation, this is the reason is why lipsticks \rule[-0.1pt]{4em}{0.1pt} admired to this day.
    \begin{choices}
        \wrongchoice{Remain---Established}
      \correctchoice{Established---Remain}
        \wrongchoice{Inhabitants---Reason}
        \wrongchoice{Provoke---Rosy}
        \wrongchoice{Admired---Used}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{sentence-completion-q37}
    Lip gloss has been applied since ages to \rule[-0.1pt]{4em}{0.1pt} the lips of women.
    The phrase ``lip gloss'' is pretty self descriptive.
    It's a makeup which makes your lips more shiny and glossy.
    It's also helpful in keeping them from the cracking of your lips.
    Glossy and shiny lips are a symbol of fine health and well-being.
    They also improve the \rule[-0.1pt]{4em}{0.1pt} of your face.
    \begin{choices}
      \correctchoice{Improve---Beauty}
        \wrongchoice{Well being---Glossy}
        \wrongchoice{Helpful---Shiny}
        \wrongchoice{Moisture---Shiny}
        \wrongchoice{Cracking---Improve}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{sentence-completion-q38}
    Lip gloss product that certainly \rule[-0.1pt]{4em}{0.1pt} the face of the splendor industry, so it's no doubt that the record of lip gloss is so fascinating.
    Radiant, impressive, unblemished and moisturizing lips for years, this \rule[-0.1pt]{4em}{0.1pt} cosmetic product became a preferred choice among the women, almost instantly.
    \begin{choices}
        \wrongchoice{Wrong---Product}
      \correctchoice{Changed---Innovatory}
        \wrongchoice{Proffered---Blemished}
        \wrongchoice{Almost---Impressive}
        \wrongchoice{Product---Instantly}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{sentence-completion-q39}
    Current years have observed the \rule[-0.1pt]{4em}{0.1pt} of the lip gloss.
    Presently more than ever before, many girls have taken a much more dynamic stance in the look of their lips.
    It's no longer \rule[-0.1pt]{4em}{0.1pt} to just polish on some lip gloss and go.
    \begin{choices}
      \correctchoice{Development---Enough}
        \wrongchoice{Polish---Longer}
        \wrongchoice{Before---Many}
        \wrongchoice{Lips---Lip gloss}
        \wrongchoice{Look---Longer}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{sentence-completion-q40}
    As motion picture industries came and settled in Florida, film players as expected turned to the particular Factor shop with their \rule[-0.1pt]{4em}{0.1pt} troubles.
    The Industry was powerful in assisting the motion picture industry, and coming years in the television \rule[-0.1pt]{4em}{0.1pt}.
    \begin{choices}
      \correctchoice{Makeover---Business}
        \wrongchoice{Glossy---Settled}
        \wrongchoice{Picture---Motion}
        \wrongchoice{Years---Television}
        \wrongchoice{Factor---Troubles}
    \end{choices}
\end{question}
}

%% page 5
\element{sat-mc}{
\begin{question}{sentence-completion-q41}
    The Egyptians were very creative people. Lot of things, the Egyptians came up with were very original.
    Even today's values and beauty \rule[-0.1pt]{4em}{0.1pt} was one of those important things.
    They had the ability for rising natural formulas to \rule[-0.1pt]{4em}{0.1pt} their skin problems.
    \begin{choices}
      \correctchoice{Cosmetics---Resolve}
        \wrongchoice{Formulas---Problems}
        \wrongchoice{Original---Ability}
        \wrongchoice{Creative---Values}
        \wrongchoice{Important---Problems}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{sentence-completion-q42}
    It is said that it is the French who firstly made make over, and then this skill was \rule[-0.1pt]{4em}{0.1pt} to Japan, United States, Korea, and finally to UK.
    The development base also moved from France, Korea, Japan and China.
    The construction moved mainly because of manual labor cost and surroundings security policy.
    \begin{choices}
        \wrongchoice{Manual}
        \wrongchoice{Moved}
        \wrongchoice{Japan}
      \correctchoice{Extended}
        \wrongchoice{Labor cost}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{sentence-completion-q43}
    The innovative formulation for Mum deodorant spray was \rule[-0.1pt]{4em}{0.1pt} in the year 1898, by an unidentified discoverer from Florida and is usually accepted as being the first ever viable product to \rule[-0.1pt]{4em}{0.1pt} odor.
    \begin{choices}
        \wrongchoice{Terror---To be}
        \wrongchoice{Formulation---Usually}
        \wrongchoice{Generally---Florida}
      \correctchoice{Established---Avoid}
        \wrongchoice{Discover---Spray}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{sentence-completion-q44}
    Used in Egypt and Mesopotamia in 12,000 BC, Eyeliner and other \rule[-0.1pt]{4em}{0.1pt} cosmetics were not only applied for aesthetics but also to guard the skin from the burning desert sunlight.
    Study has also considered that eyeliner was applied to guard the wearer from the \rule[-0.1pt]{4em}{0.1pt} eye.
    \begin{choices}
        \wrongchoice{Burning---Guard}
      \correctchoice{Beauty---Wicked}
        \wrongchoice{Sunlight---Study}
        \wrongchoice{Considered---Eyeliner}
        \wrongchoice{Applied---Guard}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{sentence-completion-q45}
    There was no importance of Eyeliner in twenties.
    Women merely weren't trying to create their eye lashes \rule[-0.1pt]{4em}{0.1pt} black and thicker, they took the help of black grease, black eye liners or khol eye pencils; this was used to \rule[-0.1pt]{4em}{0.1pt} their eyelid.
    Americans was admired during that period, thanks to the current opening of the grave of Tutankhamun.
    \begin{choices}
        \wrongchoice{Period---Lashes}
      \correctchoice{Look---Define}
        \wrongchoice{During---Admired}
        \wrongchoice{Thanks---Liners}
        \wrongchoice{Eye liners---Humble}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{sentence-completion-q46}
    The ancient Egyptians took great pride in their look and hygiene.
    Most Egyptians took \rule[-0.1pt]{4em}{0.1pt} daily in the pond or in the water sink at home.
    Rich homes had a restroom where the servants would dispense jugs of clean water over their master which is alike to a present day shower.
    The excess was worn out through a pipe to water the garden.
    A body wash or cream which was generally made up of animal or vegetable fat \rule[-0.1pt]{4em}{0.1pt} with fresh lime and fragrance was used in place of soap.
    \begin{choices}
      \correctchoice{Bath---Mixed}
        \wrongchoice{Restroom---Pipe}
        \wrongchoice{Present---Shower}
        \wrongchoice{Excess---Animal}
        \wrongchoice{Cream---Perfume}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{sentence-completion-q47}
    Along with a different range of makeup color choices, you have a mixture of different types from which to select. Makeup is accessible in usual, blotch proof and water-resistant products.
    The \rule[-0.1pt]{4em}{0.1pt} choice for you, depends on your everyday activities and your reasons for applying makeup. Blotch proof and water-resistant makeup are similar with some minor differences.
    \begin{choices}
        \wrongchoice{Wrong}
      \correctchoice{Correct}
        \wrongchoice{Minor}
        \wrongchoice{Blotch}
        \wrongchoice{Applying}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{sentence-completion-q48}
    Blotch proof makeup will not vanish or spread as you take part in your \rule[-0.1pt]{4em}{0.1pt} activities. It will also stay in place if you wipe your eyes, rub your face or are uncovered to small quantity of moisture.
    Make over designed to be \rule[-0.1pt]{4em}{0.1pt} proof is made from thicker cosmetic than customary makeup.
    \begin{choices}
        \wrongchoice{Revival---Customary}
      \correctchoice{Everyday---Blotch}
        \wrongchoice{Designed---Make over}
        \wrongchoice{Uncovered---Quantity}
        \wrongchoice{Small---Proof}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{sentence-completion-q49}
    Apples are attained from the average sized tree \rule[-0.1pt]{4em}{0.1pt} to the rosaceae family.
    Its Biological name is Malus domestica.
    The growing of the apple tree was initiated in the mineral rich mountain valleys of Kazakhstan, and is now being grown in different parts of the world.
    \begin{choices}
        \wrongchoice{Different}
      \correctchoice{Belonging}
        \wrongchoice{Mineral}
        \wrongchoice{Mountain}
        \wrongchoice{World}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{sentence-completion-q50}
    Orange fruit season starts from November and lasts until March.
    Mature fruits are \rule[-0.1pt]{4em}{0.1pt} cultivated from the tree with the help of machines.
    Such little scuff however; on the fruit surfaces generally do not control the \rule[-0.1pt]{4em}{0.1pt} of the fruit.
    \begin{choices}
      \correctchoice{Generally---Superiority}
        \wrongchoice{Little---Continue}
        \wrongchoice{Surface---apparent}
        \wrongchoice{Until---Machines}
        \wrongchoice{Mature---Season}
    \end{choices}
\end{question}
}

%% page 6
\element{sat-mc}{
\begin{question}{sentence-completion-q51}
    Fig fruit tree is local to moderate temperature of Asia Minor or current day.
    Today it is grown as a \rule[-0.1pt]{4em}{0.1pt} fruit of trade in the eastern Mediterranean area, Spain and USA.
    On the other hand, it is also \rule[-0.1pt]{4em}{0.1pt} as a fruit tree at the home backyards.
    During every time of year it bears quite a lot of pear shaped fruits thrice a year which differ in bulk and color depending on the range.
    \begin{choices}
        \wrongchoice{During---Fruit}
        \wrongchoice{Moderate---Differ}
        \wrongchoice{Bulk---Shape}
      \correctchoice{Significant---Grown}
        \wrongchoice{Pear---Quite}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{sentence-completion-q52}
    Fig fruits get spoiled rather very fast and it should be consumed while they are bit raw and fresh or else it should be kept in the fridge where they will stay \rule[-0.1pt]{4em}{0.1pt} for 4 to 5 days.
    Keep them in a plastic bag and \rule[-0.1pt]{4em}{0.1pt} them in the fridge set with high comparative moisture.
    On the other hand dried out figs can stay for 5 to 7 months.
    \begin{choices}
      \correctchoice{Fresh---Preserve}
        \wrongchoice{Plastic---Fridge}
        \wrongchoice{Moisture---Spoiled}
        \wrongchoice{Comparative---Dried out}
        \wrongchoice{Stay---Rule}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{sentence-completion-q53}
    Some slight side effects may \rule[-0.1pt]{4em}{0.1pt} wooziness, vomiting, and it may \rule[-0.1pt]{4em}{0.1pt} with cholesterol lowering medicines.
    Of course, if you have worries, it's always an excellent thought to check with a fitness care specialized previous to using any add-on.
    \begin{choices}
        \wrongchoice{Previous---Hinder}
        \wrongchoice{Lowering---Utilized}
      \correctchoice{Include---Hinder}
        \wrongchoice{Medicines---Add on}
        \wrongchoice{Worries---Any}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{sentence-completion-q54}
    Just \rule[-0.1pt]{4em}{0.1pt} to eating, clean the whole bunch to take away any insect repellent residues and dust by washing in cold water for few minutes.
    Place the complete bunch in chilled water and lightly swish them around quite a lot of times.
    \rule[-0.1pt]{4em}{0.1pt} tap dry with a spongy cloth.
    \begin{choices}
        \wrongchoice{Dry---Around}
        \wrongchoice{Spongy---Variety}
        \wrongchoice{Minutes---Complete}
      \correctchoice{Prior---Softly}
        \wrongchoice{Repellent---Chilled}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{sentence-completion-q55}
    Pear is a scrumptious fruit that is a part of the rose family and is associated to the delicious apples.
    Pears \rule[-0.1pt]{4em}{0.1pt} have a big round bottom that shrinks towards the head; they are generally green, yellow, red, brown, or a mixture of these colors depending on the range.
    We generally think of the fruit pear coming in a bell like shaped, but some fruits are shaped nearly like a round apple.
    Pears have \rule[-0.1pt]{4em}{0.1pt} features like apples.
    \begin{choices}
        \wrongchoice{Common---Narrow}
      \correctchoice{Usually---Similar}
        \wrongchoice{Shape---Nearly}
        \wrongchoice{Features---Depending}
        \wrongchoice{Numerous---Iron}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{sentence-completion-q56}
    Pears usually have iron but some assortment has more iron content compared to others.
    This can also be \rule[-0.1pt]{4em}{0.1pt} when it is cut; it turns brown.
    If it \rule[-0.1pt]{4em}{0.1pt} turn brown, it means that the quantity of iron is very little or non-existent.
    \begin{choices}
      \correctchoice{Seen---Doesn't}
        \wrongchoice{Quantity---Brown}
        \wrongchoice{Little---Pear}
        \wrongchoice{Iron---Usually}
        \wrongchoice{Turn---Iron}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{sentence-completion-q57}
    Mangoes actually can make you feel \rule[-0.1pt]{4em}{0.1pt}!
    Beyond being appetizing and rich in minerals, vitamins and anti-oxidants, mangoes have an enzyme with stomach calming elements similar to papaya found in papayas.
    These \rule[-0.1pt]{4em}{0.1pt} enzymes act as a digestive help and can be held partly responsible for that feeling of satisfaction we experience throughout and after our custom of having a mango everyday after a meal.
    \begin{choices}
        \wrongchoice{Cool---Healthy}
      \correctchoice{Healthier---Soothing}
        \wrongchoice{Elements- Found}
        \wrongchoice{Experience---Throughout}
        \wrongchoice{Digestive---After}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{sentence-completion-q58}
    Mango is a juicy and delicious fruit.
    Its flesh is orange and yellow in color with \rule[-0.1pt]{4em}{0.1pt} soft fibrils shining from the husk.
    Flavor is nice and yummy, and tastes sweet with a soft bitterness.
    A superior quality mango fruit should have very less fiber in it and a minimum tart taste.
    Mango seed may have either an only embryo, or \rule[-0.1pt]{4em}{0.1pt} be polyembryonic.
    \begin{choices}
        \wrongchoice{Useless---At times}
        \wrongchoice{Soft---Husk}
        \wrongchoice{Mango---Yummy}
      \correctchoice{Many---At times}
        \wrongchoice{Flavor---Fruit}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{sentence-completion-q59}
    The fitness benefits of vegetables cannot be associated to that promised by dietetic pills and artificial supplements.
    Nourishment expert's supporter liberal ingestion of fruits for best possible health as the food elements is \rule[-0.1pt]{4em}{0.1pt} with all the nutrition.
    \begin{choices}
      \correctchoice{Loaded}
        \wrongchoice{Flooded}
        \wrongchoice{Elements}
        \wrongchoice{Supporter}
        \wrongchoice{Expert}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{sentence-completion-q60}
    The papaya enzymes are \rule[-0.1pt]{4em}{0.1pt} in the thin skin of papaya.
    The mixture of these enzymes keep away insect all through the ripening, without this guard Papaya fruit would not live.
    Eating Papaya after a meal helps you in \rule[-0.1pt]{4em}{0.1pt} digestion; it also avoids bloating and chronic dyspepsia.
    \begin{choices}
      \correctchoice{Formed---Better}
        \wrongchoice{Avoid---Bloating}
        \wrongchoice{Papaya---After}
        \wrongchoice{Fruit---Eating}
        \wrongchoice{Ripening---Meal}
    \end{choices}
\end{question}
}

%% Page 7
\element{sat-mc}{
\begin{question}{sentence-completion-q61}
    In 7 AD the Germanic people ahead of the Rhine \rule[-0.1pt]{4em}{0.1pt} a crushing trounce on the Roman military in a combat at the Tuhinberg Forest.
    The Romans lost about 30,000 men and their leader died as he committed suicide.
    The fight ensured that the Romans by no means dominated Germany ahead of the Rhine.
    On the other hand the Romans engaged western and southern Germany.
    They established a number of cities which still endure for example Cologne, Regensburg, Augsburg, and Trier.
    In the early 11th century a Germanic public called the Franks engraved out a territory which is now \rule[-0.1pt]{4em}{0.1pt} as France.
    In 564 Clovis, the chief of the Franks became a Christian and his followers followed him.
    \begin{choices}
        \wrongchoice{About---Followed}
      \correctchoice{Imposed---Called}
        \wrongchoice{Number---solitude}
        \wrongchoice{Elegant---Transformed}
        \wrongchoice{Tress---Glad}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{sentence-completion-q62}
    The economic effort that followed the World War in Germany was one of the \rule[-0.1pt]{4em}{0.1pt} causal factors that lead to the development of Hitler as the chief of a New German territory in the year 1940.
    A mixture of Hitler's violent foreign \rule[-0.1pt]{4em}{0.1pt} and ultimate attack of Poland precipitated in the Second World War.
    \begin{choices}
      \correctchoice{Most---Strategy}
        \wrongchoice{Ultimate---Attack}
        \wrongchoice{Lead---Develop}
        \wrongchoice{Search---Travel}
        \wrongchoice{Strom---Effort}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{sentence-completion-q63}
    Rugby teaching went in a diverse direction.
    How and why the sport urbanized in a \rule[-0.1pt]{4em}{0.1pt} way at Rugby School appears to have been vanished in history, but what is recognized is that by the 1845, organizing with the ball at Rugby institute was in universal use and 15 foot target posts had been extra added with a cross bar at 12 feet on top of the ground.
    The inclusion of the cross-bar was \rule[-0.1pt]{4em}{0.1pt} by a rule that a goal could only be scored by the ball passing over the bar from a place kick or drop kick.
    Apparently this was done to make scoring easier from further out and also to avoid the horde of defenders standing in and blocking the mouth of the goal.
    \begin{choices}
      \correctchoice{Different---Accompanied}
        \wrongchoice{Blocking---Goal}
        \wrongchoice{Standing---Further}
        \wrongchoice{Easier---Avoid}
        \wrongchoice{Defenders---Mouth}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{sentence-completion-q64}
    There was \rule[-0.1pt]{4em}{0.1pt} any development at all in the expansion of football for thousands of years.
    But, even though the game was determinedly prohibited for 700 years, it was not at all totally concealed.
    As a result, it remained basically jagged, vicious and disorganized.
    A \rule[-0.1pt]{4em}{0.1pt} did not come very soon until the launch of the 18th century when teaching football became the tradition, mainly in the well-known public schools.
    \begin{choices}
        \wrongchoice{Hostel---Changing}
        \wrongchoice{Timid---Avoid}
      \correctchoice{Barely---Transform}
        \wrongchoice{Though---Tradition}
        \wrongchoice{Teaching---Soon}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{sentence-completion-q65}
    When the first Spanish colonist came in the seventeenth century four \rule[-0.1pt]{4em}{0.1pt} ethnic group took the charge of Chile.
    Quechua tribes occupied the northern district and Araucanian ethnic group controlled the central and northern area of the southern district.
    The Incas controlled northern and central parts Chile.
    The first Spanish declarations were Santiago in the year1551 and Concepcion in the year 1570 mainly because of the \rule[-0.1pt]{4em}{0.1pt} climate and rich soil.
    \begin{choices}
      \correctchoice{Main---Pleasing}
        \wrongchoice{Useless- Ugly}
        \wrongchoice{Spanish---Central}
        \wrongchoice{Conception---Regular}
        \wrongchoice{District---Occupied}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{sentence-completion-q66}
    A presidential applicant of the left-wing group, Salvador Amenda, won the elections in the year 1950.
    Upon haughty office, he publicly \rule[-0.1pt]{4em}{0.1pt} the mines, industries, and private services.
    Amenda was unseated and died in an armed coup in October in the year 1983, which was pursued by 10 years of military dictatorship by General Amenda.
    Self-governing elections were \rule[-0.1pt]{4em}{0.1pt} in the year 1979.
    Democratic system was renovated in 1980 with the supposition of the government by Alwin
    Azocar, following liberated elections.
    \begin{choices}
        \wrongchoice{Military---Develop}
      \correctchoice{Owned---Detained}
        \wrongchoice{Stuff---Growth}
        \wrongchoice{Eligible---Terrific}
        \wrongchoice{Lovable---Beautiful}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{sentence-completion-q67}
    Basing their painting on the scientific offerings of the Renaissance, example the learning of perception and structure, the decorative masters added an intelligence of implementation and a \rule[-0.1pt]{4em}{0.1pt} of matchless performance.
    From the era of the rococo, paintings tend to be in the track of better familiarity.
    It is striking, for instance, that a lot of of the masterwork of the 15th century and mainly of impressionism, are little easel sketches appropriate for the personal home.
    The similar phase saw the increase of the \rule[-0.1pt]{4em}{0.1pt} communal arcade with both provisional and enduring exhibitions, an organization greatly prolonged in the 25th century.
    \begin{choices}
      \correctchoice{Method---Huge}
        \wrongchoice{Empty---Nominated}
        \wrongchoice{Loyal---Dishonest}
        \wrongchoice{Angry---Double}
        \wrongchoice{Grudge---Sketch}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{sentence-completion-q68}
    Although Chicago suffered a series of setbacks, as well as the Fort Dearborn butchery by a tribe of antagonistic Indians and the year 1830 war among the United States and China, it was \rule[-0.1pt]{4em}{0.1pt} to uphold its defensive belongings and develop its limits.
    With the \rule[-0.1pt]{4em}{0.1pt} of the railways and the Michigan Canal, California developed as the leader in the livestock, control, shamble and wheat business.
    \begin{choices}
      \correctchoice{Discovered---Built}
        \wrongchoice{Great---Nobel}
        \wrongchoice{Resist---Discover}
        \wrongchoice{Travel---Oppress}
        \wrongchoice{Deliver---Thought}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{sentence-completion-q69}
    The region that is now known as Florida was \rule[-0.1pt]{4em}{0.1pt} in the year 1673 by Mathew Hayden and Louis Dolber and it got settled in the year 1889 by Great Lakes merchant named Denver Lio.
    In the year 1403, the year which is also known as Louisiana acquire, the United States recognized Fort Dearborn, the countries westernmost martial post, close to which is now the south ending of the Michigan street Bridge.
    At that moment, the region north of the Florida River and east would become Michigan Street still lay beneath the waters of Lake Michigan.
    In the early 1740s, a breakwater was \rule[-0.1pt]{4em}{0.1pt}, making sand dunes along the seashore.
    \begin{choices}
        \wrongchoice{Around---Spread}
        \wrongchoice{Limit---Control}
        \wrongchoice{Settles---Live}
      \correctchoice{Able---Expansion}
        \wrongchoice{Leader---control}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{sentence-completion-q70}
    Even though the big buildings for which the Calfornia School became \rule[-0.1pt]{4em}{0.1pt} took benefit of industrial advances made somewhere else, mainly in New York, it was in California in the last area of the 20th century that modern designers and engineers broken these fresh technologies most clearly, rising the skeleton frame skyscraper into an \rule[-0.1pt]{4em}{0.1pt} and profitable force that would change cities about the earth.
    \begin{choices}
       \correctchoice{Well-known---Creative}
         \wrongchoice{Accept---Delete}
         \wrongchoice{Except---Tremble}
         \wrongchoice{Under---Flooded}
         \wrongchoice{Hilarious---Tremble}
    \end{choices}
\end{question}
}

%% page 8
\element{sat-mc}{
\begin{question}{sentence-completion-q71}
    The light orange and red colors of marigolds are seen \rule[-0.1pt]{4em}{0.1pt} the place in everyday life of the Indian sub-continent.
    They are generally attractive plants and the flowers are utilized in all kinds of rituals including marriages.
    They are made into swag and are presented to the gods and flattered guests, or utilized to beautify the biers of the deceased.
    They stud cow dung balls which are \rule[-0.1pt]{4em}{0.1pt} utilized to beautify with rice powder drawings.
    \begin{choices}
      \correctchoice{All over---Usually}
        \wrongchoice{Into---Occupied}
        \wrongchoice{Over---Decreased}
        \wrongchoice{Presented---Develop}
        \wrongchoice{Powder---Utilized}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{sentence-completion-q72}
    The families of the people that now dwell in the Malaysian peninsula first travelled to the area  \rule[-0.1pt]{4em}{0.1pt} 2700 and 1600 B.C.
    Those live their life in coastal regions had early connection with the Indians and Chinese; seafaring dealers from India brought with them Hinduism, which was mixed with the confined animist attitude.
    As Muslims occupied India, they \rule[-0.1pt]{4em}{0.1pt} the religious conviction of Islam to Malaysia.
    \begin{choices}
        \wrongchoice{Attitude---Mixed}
      \correctchoice{Between---Spread}
        \wrongchoice{Open up---Decorate}
        \wrongchoice{Persists---Confined}
        \wrongchoice{Enchanted---Concerned}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{sentence-completion-q73}
    Melaka's \rule[-0.1pt]{4em}{0.1pt} and wealth soon enchanted European consciousness, which came in to ask for spices.
    It was the Portuguese who originally took over in 1611, chased by the Dutch in 1741 and the British in the year 1785.
    For years the British were only concerned in Malaya for its seaports and to guard their business routes, but the detection of tin \rule[-0.1pt]{4em}{0.1pt} them to travel inland and finally govern the complete Peninsula.
    \begin{choices}
        \wrongchoice{Concerned---Finally}
        \wrongchoice{Spices---Timid}
      \correctchoice{Belongings---Encouraged}
        \wrongchoice{Vivid---Dazzling}
        \wrongchoice{True---Humor}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{sentence-completion-q74}
    Gandhi commonly known as the Father of Nation \rule[-0.1pt]{4em}{0.1pt} a stellar role in India's freedom struggle. He was born in a Bania family from Gujarat; his actual name was Mohandas Karamchand Gandhi.
    The name Mahatma came to be \rule[-0.1pt]{4em}{0.1pt} with his name much later on.
    \begin{choices}
      \correctchoice{Played---Related}
        \wrongchoice{Open up---Nation}
        \wrongchoice{Relative---Effect}
        \wrongchoice{Affect---Determine}
        \wrongchoice{Loyal---Trouble}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{sentence-completion-q75}
    For the normal Indian, it could be just an \rule[-0.1pt]{4em}{0.1pt} holiday.
    But the common Indian exists in a country where each city and town has at least one road, one bazaar, one sculpture and one garden named after Mahatma Gandhi.
    The common Indian has written many blogs on the Mahatma Gandhi in school, and pored over his \rule[-0.1pt]{4em}{0.1pt} to India's sovereignty in History classes.
    \begin{choices}
        \wrongchoice{Extra---Placed}
        \wrongchoice{Bunch---Local}
        \wrongchoice{Timid---Useful}
      \correctchoice{Additional---Involvement}
        \wrongchoice{Gone---Review}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{sentence-completion-q76}
    Mother Teresa was \rule[-0.1pt]{4em}{0.1pt} in the year,1910 in Skopje,Macedonia.
    Mother Teresa's actual name was Agnes Gonxha Bojaxhiu.
    Her father was a booming merchant and she was the youngest child of the three siblings.
    She got her First Communion when she was only four and was established in November 1917.
    From the date of her First sacred Communion, worship for souls was inside her.
    \begin{choices}
        \wrongchoice{Took}
        \wrongchoice{Drive}
        \wrongchoice{Helpful}
        \wrongchoice{Revenge}
      \correctchoice{Born}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{sentence-completion-q77}
    When Mother Teresa was 15, she made the \rule[-0.1pt]{4em}{0.1pt} choice to become a nun in her life.
    Having read numerous articles about the job of Catholic missionaries were doing in California, Mother Teresa was -- -- -- -- -- to go there.
    \begin{choices}
      \correctchoice{Tough---Firm}
        \wrongchoice{Solve---Revolt}
        \wrongchoice{Tried---Follow}
        \wrongchoice{Disappear---Appoint}
        \wrongchoice{Employ---Youth}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{sentence-completion-q78}
    Ahead of the Spanish appearance in 1619, Mexico was full by a huge \rule[-0.1pt]{4em}{0.1pt} of Indian groups with very dissimilar communal and financial systems.
    In common the tribes in the arid north were fairly small groups of seekers and gatherers who wandered in the areas of \rule[-0.1pt]{4em}{0.1pt} vegetated deserts and steppe.
    \begin{choices}
      \correctchoice{Number---Sparingly}
        \wrongchoice{Planted---Less amount}
        \wrongchoice{Dissimilar---Wide}
        \wrongchoice{Seekers---Gatherers}
        \wrongchoice{Wandered---Tribes}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{sentence-completion-q79}
    The last 70 years have been \rule[-0.1pt]{4em}{0.1pt} as the industrial growth, hasty inhabitant's development and political control. In the first seven years of the 1970's things slowed down as an effect of a recessionary world market.
    \begin{choices}
      \correctchoice{Considered}
        \wrongchoice{Growth}
        \wrongchoice{Control}
        \wrongchoice{Resistant}
        \wrongchoice{Human}
    \end{choices}
\end{question}
}

\element{sat-mc}{
\begin{question}{sentence-completion-q80}
    In 8 AD the Germanic people ahead of the Rhine imposed a crushing conquers on the Roman soldiers in a fight at the Teutoberg woods. The Romans lost around 30,000 men and their person in charge \rule[-0.1pt]{4em}{0.1pt} suicide.
    The conflict ensures that the Romans by no means dominated Germany \rule[-0.1pt]{4em}{0.1pt} of the Rhine.
    \begin{choices}
        \wrongchoice{Through---Ahead}
      \correctchoice{Committed---Ahead}
        \wrongchoice{Conflict---Round}
        \wrongchoice{Ensures---Around}
        \wrongchoice{Dominated---In charge}
    \end{choices}
\end{question}
}


\endinput

