
%%--------------------------------------------------
%% Schaum's Outline of Applied Physics
%%--------------------------------------------------


%% Chapter 1: Useful Math
%%--------------------------------------------------


%% Schaum's Numberic Problems
%%--------------------------------------------------
\element{schaums-num}{
\begin{question}{ch01-num-Q01}
    In which of the following equations is $x$ not equal to $2$?
    \begin{choices}
        \wrongchoice{$x^2 + 4x = 12$}
      \correctchoice{$\sqrt{2x 3 + 5x} = 14$}
        \wrongchoice{$\sqrt{6x^2 + 25} = 7\left( 5 − x^2 \right)$}
        \wrongchoice{$\left(x^2 + 6\right)^2 = 50x$}
    \end{choices}
\end{question}
}


1.1. Remove the parentheses from the following, and combine like terms:
A-J

1.2. Evaluate the following:
A-J

1.3. Solve each of the following equations for x:


1.4. Evaluate the following:


1.5. Express the following numbers in powers-of-10 notation:


1.6. Express the following numbers in decimal notation:


1.7. Perform the following additions and subtractions:


1.8. Perform the following multiplications and divisions, using powers-of-10 notation:

1.9. Evaluate the following and express the results in powers-of-10 notation:

1.10: Evaluate the following and express the results in powers-of-10 notation.

1.11. The earth is an average of 9.3 × 10 7 mi from the sun. How far is this in kilometers? In meters?

1.12. How many cubic feet are there in a cubic meter?

1.13. The speed limit in many European towns is 60 km/h. How many miles per hour is this?

1.14. The speed of light is 3.00 × 10 8 m/s. What is this speed in feet per second? In miles per second? In miles per hour?

1.15. A nautical mile is 6076 ft, and 1 knot (kn) is a unit of speed equal to 1 nautical mile/h. 
How fast is an 8-kn boat going in miles per hour? 
In feet per second?

1.16. Use the proper number of significant figures to express the results of the following calculations:



\endinput


