
%%--------------------------------------------------
%% Schaum's Outline of Applied Physics
%%--------------------------------------------------


%% Chapter 3: Motion in a Straight Line
%%--------------------------------------------------


%% Schaum's Numeric Problems
%%--------------------------------------------------
\element{schaums-num}{
\begin{questionmultx}{ch02-num-Q01}
    Find the length, $l$, of the hypotenuse of a right triangle whose legs are \SI{483}{\meter} and \SI{620}{\meter} long.
    Report $l/\si{\meter}$ below.
    \AMCnumericChoices{785.93}{
        vertical=false,
        digits=5,decimals=2,sign=true,
        borderwidth=0pt,backgroundcol=white,approx=5
    }
\end{questionmultx}
}



3.1. A ship steams at a constant velocity of 30 km/h. (a) How far does it travel in a day? (b) How long does it take to travel
500 km?
3.2. A car moves at 50 km/h for
for the entire trip?
1
2
h and then at 60 km/h for 2 h. (a) How far did it go? (b) What was its average velocity
3.3. A woman jogs halfway home at 8 km/h and walks the rest of the way at 6 km/h. Find her average velocity for the
entire trip.
3.4. An airplane whose airspeed is 500 km/h covers a distance of 1000 km in 2 12 h. How strong was the headwind against
it?
3.5. A boat moving downstream (with the current) in a river takes 4 min 7 s to cover a measured mile according to marks
on shore, and 7 min 30 s to cover the same distance moving upstream (against the current). If the boat’s velocity
relative to the water is 11 mi/h, what is the velocity of the current in the river?
3.6. How long does it take an echo to return to a woman standing 300 m from a cliff? The velocity of sound in air is about
343 m/s.
3.7. A car moving at 100 km/h is 80 km behind another car moving at 60 km/h in the same direction. How far does the
first car travel before it overtakes the second car?
3.8. A pitcher takes 0.1 s to throw a baseball, which leaves his hand at a velocity of 30 m/s. What is the acceleration of
the baseball while it is being thrown?
3.9. A car comes to a stop in 6 s from a velocity of 30 m/s. (a) What is its acceleration? (b) At the same acceleration, how
long would it take the car to come to a stop from a velocity of 40 m/s?
3.10. The brakes of a car can slow it down from 60 to 40 km/h in 2 s. How long will it take to bring the car to a stop from
an initial velocity of 25 km/h at the same acceleration?
3.11. An object starts from rest with an acceleration of 10 m/s 2 . (a) How far does it go in 0.5 s? (b) What is its velocity
after 0.5 s?
3.12. A car has an initial velocity of 10 m/s when it begins to be accelerated at 2.5 m/s 2 . (a) How long does it take to reach
a velocity of 25 m/s? (b) How far does it go during this period?
3.13. The brakes of a car moving at 14 m/s are applied, and the car comes to a stop in 4 s. How far does the car go while it
is slowing down from 14 to 10 m/s?

3.14. A car whose velocity is 20 km/h is given an acceleration of 5 (km/h)/s. What is its velocity after it has gone 0.25 km?
3.15. A sports car has an acceleration of 3 m/s 2 . How much distance does it cover while its velocity is increased from 0 to
10 m/s? From 10 to 30 m/s?

3.16. Find the acceleration of a car that comes to a stop from a velocity of 60 m/s in a distance of 360 m.
3.17. A bus starts from rest and accelerates at 1.5 m/s 2 until it reaches a velocity of 9 m/s. The bus continues at this velocity
and then decelerates at −2 m/s 2 until it comes to a stop 400 m from its starting point. How much time did the bus
take to cover the 400 m?

3.1. (a) 720 km (b) 17.7 h
3.2. (a) 145 km (b) 58 km/h
3.3. 6.9 km/h
3.4. 100 km
3.5. 3 mi/h
3.6. 1.75 s
3.7. 200 km
3.8. 300 m/s 2
3.9. (a) 5 m/s 2 (b) 8 s
 
 3.10. 2.5 s
 3.11. (a) 1.25 m (b) 5 m/s
 3.12. (a) 6 s (b) 105 m
 3.13. 13.7 m
 3.14. 27 m/s = 97 km/h
 3.15. 17 m; 133 m
 3.16. −5 m/s 2
 3.17. 50 s




\endinput

