
%%--------------------------------------------------
%% Holt: Multiple Choice Questions
%%--------------------------------------------------


%% Chapter 01: The Science of Physics
%%--------------------------------------------------


%% Holt Multiple Choice Questions
%%--------------------------------------------------
\element{holt-mc}{
\begin{question}{holt-ch01-Q01}
    What area of physics deals with the subjects of heat and temperature?
    \begin{multicols}{2}
    \begin{choices}
        \wrongchoice{mechanics}
      \correctchoice{thermodynamics}
        \wrongchoice{electrodynamics}
        \wrongchoice{quantum mechanics}
    \end{choices}
    \end{multicols}
\end{question}
}

\element{holt-mc}{
\begin{question}{holt-ch01-Q02}
    What area of physics deals with the behavior of subatomic particles?
    \begin{multicols}{2}
    \begin{choices}
        \wrongchoice{mechanics}
        \wrongchoice{thermodynamics}
        \wrongchoice{electrodynamics}
      \correctchoice{quantum mechanics}
    \end{choices}
    \end{multicols}
\end{question}
}

\element{holt-mc}{
\begin{question}{holt-ch01-Q03}
    What term describes a set of particles or interacting
        components considered to be a distinct physical
        entity for the purpose of study?
    \begin{multicols}{2}
    \begin{choices}
      \correctchoice{system}
        \wrongchoice{model}
        \wrongchoice{hypothesis}
        \wrongchoice{controlled experiment}
    \end{choices}
    \end{multicols}
\end{question}
}

\element{holt-mc}{
\begin{question}{holt-ch01-Q04}
    What is the SI base unit for length?
    \begin{multicols}{2}
    \begin{choices}
        \wrongchoice{inch (\si{\inch})}
        \wrongchoice{foot (\si{\foot})}
      \correctchoice{meter (\si{\meter})}
        \wrongchoice{kilometer (\si{\kilo\meter})}
    \end{choices}
    \end{multicols}
\end{question}
}

\element{holt-mc}{
\begin{question}{holt-ch01-Q05}
    A light-year (ly) is a unit of distance defined as
        the distance light travels in one year.
    Numerically, \SI{1}{ly}=\SI{9 500 000 000 000}{\kilo\meter}.
    How many meters are in a light year?
    \begin{multicols}{2}
    \begin{choices}
        \wrongchoice{\SI{9.5e10}{\meter}}
        \wrongchoice{\SI{9.5e12}{\meter}}
      \correctchoice{\SI{9.5e15}{\meter}}
        \wrongchoice{\SI{9.5e18}{\meter}}
    \end{choices}
    \end{multicols}
\end{question}
}

\element{holt-mc}{
\begin{question}{holt-ch01-Q06}
    If you do not keep your line of sight directly over a length measurement,
        how will your measurement most likely be affected?
    \begin{choices}
        \wrongchoice{Your measurement will be less precise.}
      \correctchoice{Your measurement will be less accurate.}
        \wrongchoice{Your measurement will have fewer significant figures.}
        \wrongchoice{Your measurement will suffer from instrument error.}
    \end{choices}
\end{question}
}

%\element{holt-mc}{
%\begin{question}{holt-ch01-Q07}
%    If you measured the length of a pencil by using the meterstick shown in the figure below and you report your measurement in centimeters,
%        how many significant figures should your reported measurement have?  
%    \begin{center}
%        %% NOTE: 
%    \end{center}
%    If you do not keep your line of sight directly over a length measurement,
%        how will your measurement most likely be affected?
%    \begin{multicols}{2}
%    \begin{choices}
%        \wrongchoice{one}
%        \wrongchoice{two}
%        \wrongchoice{three}
%        \wrongchoice{four}
%    \end{choices}
%    \end{multicols}
%\end{question}
%}

\element{holt-mc}{
\begin{question}{holt-ch01-Q08}
    A room is measured to be \SI{3.6}{\meter} by \SI{5.8}{\meter}.
    What is the area of the room?
    (Keep significant figures in mind.)
    \begin{multicols}{2}
    \begin{choices}
        \wrongchoice{\SI{20.88}{\meter\squared}}
        \wrongchoice{\SI{2e1}{\meter\squared}}
        \wrongchoice{\SI{2.0e1}{\meter\squared}}
      \correctchoice{\SI{21}{\meter\squared}}
    \end{choices}
    \end{multicols}
\end{question}
}

\element{holt-mc}{
\begin{question}{holt-ch01-Q09}
    What technique can help you determine the power of 10
        closest to the actual numerical value of a quantity?
    \begin{choices}
        \wrongchoice{rounding}
      \correctchoice{order-of-magnitude estimation}
        \wrongchoice{dimensional analysis}
        \wrongchoice{graphical analysis}
    \end{choices}
\end{question}
}

\element{holt-mc}{
\begin{question}{holt-ch01-Q10}
    Which of the following statements is true of \emph{any} valid physical equation?
    \begin{choices}
      \correctchoice{Both sides have the same dimensions}
        \wrongchoice{Both sides have the same variables}
        \wrongchoice{There are variables but no numbers}
        \wrongchoice{There are numbers but no variables}
    \end{choices}
\end{question}
}

\newcommand{\holtChOneQEleven}{
\begin{tikzpicture}
    \begin{axis}[
        axis y line=left,
        axis x line=bottom,
        axis line style={->},
        xlabel={time},
        x unit=\si{\second},
        xtick={0.0,0.1,0.2,0.3},
        minor x tick num=4,
        ylabel={distance},
        y unit=\si{\centi\meter},
        ytick={0,20,40,60,80},
        minor y tick num=1,
        xmin=0,xmax=0.32,
        ymin=0,ymax=80,
        grid=both,
        width=0.85\columnwidth,
        height=0.40\columnwidth,
        very thin,
    ]
    \addplot[line width=1pt,dashed,domain=0:0.32]{500*x*x};
    \addplot[mark=*,only marks] plot coordinates{ (0.1,5) (0.15,11.25) (0.2,20) (0.25,31.25) (0.3,45) };
    \end{axis}
\end{tikzpicture}
}

\element{holt-mc}{
\begin{question}{holt-ch01-Q11}
    The graph below shows the relationship between
        time and distance for a ball dropped vertically from rest.
    \begin{center}
        \holtChOneQEleven
    \end{center}
    About how far has the ball fallen after \SI{0.200}{\second}?
    \begin{multicols}{2}
    \begin{choices}
        \wrongchoice{\SI{5.00}{\centi\meter}}
        \wrongchoice{\SI{10.00}{\centi\meter}}
      \correctchoice{\SI{20.00}{\centi\meter}}
        \wrongchoice{\SI{30.00}{\centi\meter}}
    \end{choices}
    \end{multicols}
\end{question}
}

\element{holt-mc}{
\begin{question}{holt-ch01-Q12}
    The graph below shows the relationship between
        time and distance for a ball dropped vertically from rest.
    \begin{center}
        \holtChOneQEleven
    \end{center}
    Which of the following statements best describes the relationship between the variables?
    \begin{choices}
      \correctchoice{For equal time intervals, the change in position is increasing.}
        \wrongchoice{For equal time intervals, the change in position is decreasing.}
        \wrongchoice{For equal time intervals, the change in position is constant.}
        \wrongchoice{There is no clear relationship between time and change in position.}
    \end{choices}
\end{question}
}


\endinput

