
%%--------------------------------------------------
%% Holt: Multiple Choice Questions
%%--------------------------------------------------


%% Chapter 14: Refraction
%%--------------------------------------------------


%% Holt Multiple Choice Questions
%%--------------------------------------------------
\element{holt-mc}{
\begin{question}{ch14-mc-Q01}
    How is light affected by an increase in the inex of refraction?
    \begin{choices}
        \wrongchoice{its frequency increases}
        \wrongchoice{its frequency decreases}
        \wrongchoice{its speed increases}
        \wrongchoice{its speed decreases}
    \end{choices}
\end{question}
}

\element{holt-mc}{
\begin{question}{ch14-mc-Q02}
    Which of the following conditions is \emph{not} necessary for refraction to occur?
    \begin{choices}
        \wrongchoice{Both the incident and refracting substances must be transparent.}
        \wrongchoice{Both substances must have different indices of refraction.}
        \wrongchoice{The light must have one wavelength.}
        \wrongchoice{The light must enter at an angle greater than \ang{0} with respect to the normal}
    \end{choices}
\end{question}
}

\element{holt-mc}{
\begin{question}{ch14-mc-Q03}
    What is the focal length of the lens?}
    \begin{multicols}{2}
    \begin{choices}
        \wrongchoice{\SI{-12.5}{\centi\meter}}
        \wrongchoice{\SI{-8.33}{\centi\meter}}
        \wrongchoice{\SI{8.33}{\centi\meter}}
        \wrongchoice{\SI{12.5}{\centi\meter}}
    \end{choices}
    \end{multicols}
\end{question}
}

\element{holt-mc}{
\begin{question}{ch14-mc-Q04}
    %% NOTE: questionmult? with six options
    What is true of the image formed by the lens?
    \begin{choices}
        \wrongchoice{real, inverted, and enlarged}
        \wrongchoice{real, inverted, and diminished}
        \wrongchoice{virtual, upright, and enlarged}
        \wrongchoice{virtual, upright, and diminished}
    \end{choices}
\end{question}
}

\element{holt-mc}{
\begin{question}{ch14-mc-Q05}
    A block of flint glass with an inex of refraction of \num{1.66}
        is immersed in oil with an index of refraction of \num{1.33}.
    How does the critical angle for a refracted light ray in the glass
        var yfrom when the glass is surrounded by air?
    \begin{choices}
        \wrongchoice{it remains unchanged}
        \wrongchoice{it increases}
        \wrongchoice{it decreases}
        \wrongchoice{No total internal reflection takes place when the glass is placed in the oil}
    \end{choices}
\end{question}
}

\element{holt-mc}{
\begin{question}{ch14-mc-Q06}
    Which color of light is most refracted during dispersion by a prism?
    \begin{multicols}{2}
    \begin{choices}
        \wrongchoice{red}
        \wrongchoice{yellow}
        \wrongchoice{green}
        \wrongchoice{violet}
    \end{choices}
    \end{multicols}
\end{question}
}

\element{holt-mc}{
\begin{question}{ch14-mc-Q07}
    If an object in air is viewed from beneath the surface of water below,
        where does the object appear to be?
    \begin{choices}
        \wrongchoice{The object appears above its true position.}
        \wrongchoice{The object appears exactly at its true position.}
        \wrongchoice{The object appears below its its true position.}
        \wrongchoice{The object cannot bbe viewed from beneath the water's surface.}
    \end{choices}
\end{question}
}

\element{holt-mc}{
\begin{question}{ch14-mc-Q08}
    The phenomenon called ``looming'' is similar to a mirage,
        except that the inverted image appears above the object instead of below it.
    What must be true if looming is to occur?
    \begin{choices}
        \wrongchoice{The temperature of the air must increase with distance above the surface.}
        \wrongchoice{The temperature of the air must decrease with distance above the surface.}
        \wrongchoice{The mass of the air must increase with distance above the surface.}
        %% NOTE: changed increase to decrease to avoid Duplicate
        \wrongchoice{The mass of the air must decrease with distance above the surface.}
    \end{choices}
\end{question}
}

\element{holt-mc}{
\begin{question}{ch14-mc-Q09}
    Light with a vacuum wavelength of \SI{500.0}{\nano\meter} passes into benzene,
        which has an index of refraction of \num{1.5}.
    What is the wavelength of the light within the benzene?
    \begin{multicols}{2}
    \begin{choices}
        \wrongchoice{\SI{0.0013}{\nano\meter}}
        \wrongchoice{\SI{0.0030}{\nano\meter}}
        \wrongchoice{\SI{330}{\nano\meter}}
        \wrongchoice{\SI{750}{\nano\meter}}
    \end{choices}
    \end{multicols}
\end{question}
}

\element{holt-mc}{
\begin{question}{ch14-mc-Q10}
    Which of the following is \emph{not} a necessary condition for seeing a magnified image with a lens?
    \begin{choices}
        \wrongchoice{The object and image are on the same side of the lens.}
        \wrongchoice{The lens must be convering.}
        \wrongchoice{The observer must be placed within the focal length of the lens.}
        \wrongchoice{The object must be placed within the focal length of the lens.}
    \end{choices}
\end{question}
}


\endinput

