
%%--------------------------------------------------
%% Holt: Multiple Choice Questions
%%--------------------------------------------------


%% Chapter 15: Interference and Diffraction
%%--------------------------------------------------


%% Holt Multiple Choice Questions
%%--------------------------------------------------
\element{holt-mc}{
\begin{question}{ch15-mc-Q01}
    In the equations for interference,
        what does the term $d$ represent?
    \begin{choices}
        \wrongchoice{the distance from the midpoint between the two slits to the viewing screen}
        \wrongchoice{the distance between the two slits through which a light wave passes}
        \wrongchoice{the distance between two bright interference fringes}
        \wrongchoice{the distance between two dark interference fringes}
    \end{choices}
\end{question}
}

\element{holt-mc}{
\begin{question}{ch15-mc-Q02}
    Which of the following must be true for two wavess with identical amplitudes and wavelengths to undergo complete destructive interference?
    \begin{choices}
        \wrongchoice{the distance from the midpoint between the two slits to the viewing screen}
        \wrongchoice{the distance between the two slits through which a light wave passes}
        \wrongchoice{the distance between two bright interference fringes}
        \wrongchoice{the distance between two dark interference fringes}
    \end{choices}
\end{question}
}

\element{holt-mc}{
\begin{question}{ch15-mc-Q03}
    Which equation correctly describes the condition for observing the third dark fringe in an interference pattern?
    \begin{choices}
        \wrongchoice{$d \sin\theta = \lambda/2$}
        \wrongchoice{$d \sin\theta = 3\lambda/2$}
        \wrongchoice{$d \sin\theta = 5\lambda/2$}
        \wrongchoice{$d \sin\theta = 3\lambda$}
    \end{choices}
\end{question}
}

\element{holt-mc}{
\begin{question}{ch15-mc-Q04}
    Why is the diffraction of sound easier to observe than
        the diffraction of visible light?
    \begin{choices}
        \wrongchoice{Sound waves are easier to detect than visible light waves}
        \wrongchoice{Sound waves have longer wavelengths than visible light waves and so bend more around barriers}
        \wrongchoice{Sound waves are longitudinal waves, which diffract more than transverse waves}
        \wrongchoice{Sound waves have greater amplitude than visible light}
    \end{choices}
\end{question}
}

\element{holt-mc}{
\begin{question}{ch15-mc-Q05}
    Monochromatic infrared waves with a wavelength of \SI{750}{\nano\meter} pass through two narrow slits.
    If the slits are \SI{25}{\micro\meter} apart,
        at what angle will the fourth order bright fringe appear on a viewing screen?
    \begin{multicols}{2}
    \begin{choices}
        \wrongchoice{\ang{4.3}}
        \wrongchoice{\ang{6.0}}
        \wrongchoice{\ang{6.9}}
        \wrongchoice{\ang{7.8}}
    \end{choices}
    \end{multicols}
\end{question}
}

\element{holt-mc}{
\begin{question}{ch15-mc-Q06}
    Monochromatic light with a wavelength of \SI{640}{\nano\meter} passes through a diffraction grating that has \SI{5.0e4}{lines\per\meter}.
    A bright line ona a screen appears at an angle of \ang{11.1} from the central bright fringe.
    What is the order of this bright fringe?
    \begin{multicols}{2}
    \begin{choices}
        \wrongchoice{$m=2$}
        \wrongchoice{$m=4$}
        \wrongchoice{$m=6$}
        \wrongchoice{$m=8$}
    \end{choices}
    \end{multicols}
\end{question}
}

\element{holt-mc}{
\begin{question}{ch15-mc-Q07}
    For observing the same object,
        how many times better is the resolution
        of the telescope shown on the left in the figure
        than that of the telescope shown on the right?
    \begin{center}
        %% NOTE: insert diagram
    \end{center}
    \begin{multicols}{2}
    \begin{choices}
        \wrongchoice{\num{4}}
        \wrongchoice{\num{2}}
        \wrongchoice{\num{1/2}}
        \wrongchoice{\num{1/4}}
    \end{choices}
    \end{multicols}
\end{question}
}

\element{holt-mc}{
\begin{question}{ch15-mc-Q08}
    What steps should you employ to design a telescope with a higher degree of resolution?
    \begin{choices}
        \wrongchoice{Widen the aperture, or design the telescope to detect light of short wavelength}
        \wrongchoice{Narrow the aperture, or design the telescope to detect light of short wavelength}
        \wrongchoice{Widen the aperture, or design the telescope to detect light of long wavelength}
        \wrongchoice{Narrow the aperture, or design the telescope to detect light of long wavelength}
    \end{choices}
\end{question}
}

\element{holt-mc}{
\begin{question}{ch15-mc-Q09}
    What is the property of a laser called that causes coherent light to be emitted?
    \begin{choices}
        \wrongchoice{different intensities}
        \wrongchoice{light amplification}
        \wrongchoice{monochromaticity}
        \wrongchoice{simulated emission}
    \end{choices}
\end{question}
}

\element{holt-mc}{
\begin{question}{ch15-mc-Q10}
    Which of the following is \emph{not} an essential component of a laser?
    \begin{choices}
        \wrongchoice{a partially transparent mirror}
        \wrongchoice{a fully reflecting mirror}
        \wrongchoice{a converging lens}
        \wrongchoice{an active medium}
    \end{choices}
\end{question}
}


\endinput

