

%% CAP High School Prize Examination
%%----------------------------------------


%% this section contains 40 problems


%% CAP Exam 2015
%%----------------------------------------


%% CAP Exam 2014
%%----------------------------------------
\element{cap}{ %% cap-A5
\begin{question}{CAP-A-2014-q05}
    What is the average horizontal force acting on a ball when it elastically bounces off a wall,
        assuming the collision time is \SI{0.1}{\second} and the momentum of the ball before the bounce was \SI{2}{\kilo\gram\meter\per\second},
        perpendicular to the wall?
    \begin{multicols}{2}
    \begin{choices}
        \wrongchoice{\SI{0.2}{\newton}}
        \wrongchoice{\SI{0.4}{\newton}}
      \correctchoice{\SI{40}{\newton}}
        \wrongchoice{\SI{20}{\newton}}
    \end{choices}
    \end{multicols}
\end{question}
}


%% CAP Exam 2013
%%----------------------------------------
\element{cap}{ %% cap-A5
\begin{question}{CAP-A-2013-q08}
    Two balls of different masses collide head-on. 
    After the collision, the balls remain at rest,
        and no external forces act on them. 
    Which statement is true about the speeds of the balls before the collision?
    \begin{choices}
      \correctchoice{They must have been different, and the collision was inelastic.}
        \wrongchoice{They must have been different, and the collision was elastic.}
        \wrongchoice{They must have been identical, and the collision was inelastic.}
        \wrongchoice{They must have been identical, and the collision was elastic.}
        \wrongchoice{No combination of speed values could have caused both balls to stop after the collision.}
    \end{choices}
\end{question}
}


%% CAP Exam 2010
%%----------------------------------------
\element{cap}{ %% cap-A5
\begin{question}{CAP-A-2010-q01}
    A ball is dropped from a height $h$. 
    It hits the ground and bounces back up with a momentum loss of \SI{10}{\percent} due to the impact. 
    The maximum height it will reach is:
    \begin{multicols}{2}
    \begin{choices}
        \wrongchoice{$0.90 h$}
      \correctchoice{$0.81 h$}
        \wrongchoice{$0.949 h$}
        \wrongchoice{$0.3 h$}
    \end{choices}
    \end{multicols}
\end{question}
}


%% CAP Exam 2009
%%----------------------------------------
\element{cap}{ %% cap-A5
\begin{question}{CAP-A-2009-q01}
    A ball falls to the earth from a height $h$ and bounces to a height $h^{\prime}$.
    Momentum is conserved in the ball-earth system:
    \begin{choices}
      \correctchoice{no matter what height $h^{\prime}$ the ball reaches.}
        \wrongchoice{only if $h^{\prime} < h$.}
        \wrongchoice{only if $h^{\prime} = h$.}
        \wrongchoice{only if $h^{\prime} > h$.}
        \wrongchoice{only if $h^{\prime} \geq h$.}
    \end{choices}
\end{question}
}


\endinput


