

%% CAP High School Prize Examination
%%----------------------------------------


%% this section contains 40 problems


%% CAP Exam 2015
%%----------------------------------------
\element{cap}{ %% cap-E3
\begin{question}{CAP-A-2015-q20}
    Unstable elementary particles are produced traveling at $v=0.6c$ with respect to an observer in a laboratory. 
    These particles have a typical intrinsic lifetime of \SI{100}{\nano\second}.
    In the frame of the observer,
        how long will the particles typically last before decaying?
    \begin{choices}
        \wrongchoice{They won't decay while moving}
        \wrongchoice{\SI{100}{\nano\second}}
      \correctchoice{\SI{125}{\nano\second}}
        \wrongchoice{\SI{175}{\nano\second}}
        \wrongchoice{\SI{80}{\nano\second}}
    \end{choices}
\end{question}
}

\element{cap}{ %% cap-E3
\begin{question}{CAP-A-2015-q25}
    Two objects, $A$ and $B$,
        appear to be the same length in a reference frame when $A$ is stationary and $B$ is moving with speed $\frac{3}{5} c$ along its length. 
    In the frame of reference where $B$ is stationary and $A$ is moving,
        what is the ratio of their lengths?
    \begin{choices}
        \wrongchoice{\num{49.3e-3} times as long.}
      \correctchoice{0.95 times as long.}
        \wrongchoice{1.05 times longer.}
        \wrongchoice{20.3 times longer.}
        \wrongchoice{The pendulum does not swing on the ISS.}
    \end{choices}
\end{question}
}


%% CAP Exam 2011
%%----------------------------------------
\element{cap}{ %% cap-E3
\begin{question}{CAP-A-2011-q08}
    A fast rocket travels directly upwards at 0.5c (half the speed of light). 
    There is an explosion directly below the rocket. 
    If astronauts manage to measure how fast the light produced by the explosion is moving relative to their spacecraft,
        they will find the light to be moving:
    \begin{choices}
        \wrongchoice{Upwards at speed $0.5 c$.}
      \correctchoice{Upwards at speed $c$.}
        \wrongchoice{Upwards at speed $1.5 c$.}
        \wrongchoice{Downwards at speed $0.5 c$.}
        \wrongchoice{Downwards at speed $c$.}
    \end{choices}
\end{question}
}

\element{cap}{ %% cap-E3
\begin{questionmult}{CAP-A-2011-q10}
    %For the statements:
    %\begin{enumerate}
    %    \item Mass can be directly converted into kinetic energy
    %    \item Kinetic energy can be directly converted into mass
    %\end{enumerate}
    Of the below statements, which are true?
    \begin{choices}
        \correctchoice{Mass can be directly converted into kinetic energy}
        \correctchoice{Kinetic energy can be directly converted into mass}
        %\wrongchoice{only first is true}
        %\wrongchoice{only second is true}
        %\correctchoice{both are true}
        %\wrongchoice{neither is true}
    \end{choices}
\end{questionmult}
}


\endinput


