
%%--------------------------------------------------
%% Glencoe: Physics Test Prep
%%--------------------------------------------------


%% Chapter 01: What is Physics
%%--------------------------------------------------


%% Glencoe: Multiple Choice Questions
%%--------------------------------------------------
\element{glencoe-mc}{
\begin{question}{glencoe-ch01-Q01}
    All of these are very important parts of studying physics \emph{except}:
    \begin{choices}
        \wrongchoice{describing the organization of the universe.}
        \wrongchoice{understanding natural laws.}
      \correctchoice{memorizing complicated explanations.}
        \wrongchoice{deducing and applying natural laws.}
    \end{choices}
\end{question}
}

1. The graph shows the velocity of a bicycle as
the rider moves away from a curb.
6.00
Velocity (m/s)
5.00
4.00
3.00
2.00 Objective: 1.04
Thinking Skill: Applying
1.00
0.00
1.00 2.00 3.00 4.00 5.00 6.00 7.00 8.00
Copyright © Glencoe/McGraw-Hill, a division of The McGraw-Hill Companies, Inc.
Time (s)
Based on the slope of the graph, what is the
average acceleration of the bicycle?
A 6.00 m/s 2
B 3.00 m/s 2
C 1.33 m/s 2
D 0.750 m/s 2
Objective: 1.05
Thinking Skill: Applying

2. A car’s velocity decreases from 22.0 m/s to
10.0 m/s over a period of 3.0 s. What is the
car’s average acceleration?
A 4.0 m/s 2
B 3.0 m/s 2
C 3.0 m/s 2
D 4.0 m/s 2


3. If a sprinter accelerates from rest at a
constant rate of 2.0 m/s 2 , how fast will she
be running after 4.0 s?
A 8.0 m/s
B 4.0 m/s
C 2.0 m/s
D 0.5 m/s

4. A graph shows position as a function of
time for an object moving with constant
acceleration. What does the slope of the
graph represent?
A acceleration
B displacement
C time
D velocity
Objective: 1.05
Thinking Skill: Analyzing

5. A pebble falls from a bridge into the river
below. If the pebble falls for 1.20 s, what is
its velocity when it hits the water?
A 8.17 m/s
B 8.40 m/s
C 11.0 m/s
D 11.8 m/s
Objective: 1.05
Thinking Skill: Applying




Which graph might represent the
acceleration of a jet plane moving down a
runway from a rest position?
%% NOTE: four graphs
A Graph 1
B Graph 2
B 31 km/h
C 23 km/h
D 140 m/s 2
Objective: 1.04
Thinking Skill: Applying
C Graph 3
D Graph 4
Objective: 1.05
Thinking Skill: Analyzing

7. Which graph might show the velocity of a
ball that is thrown straight up into the air
and allowed to fall freely to the ground?
A Graph 1
B Graph 2
C Graph 3
D Graph 4










\endinput

