

%% AAPT Physics Olympiad F=ma Questions
%%----------------------------------------


%% PhysicsOlympiad 2015
%%----------------------------------------



%% PhysicsOlympiad 1999
%%----------------------------------------
\element{aapt}{ %% Olympiad-A3
\begin{question}{olympiad-1999-q15}
    A \SI{4.0}{\kilo\gram} mass is attached to one end of a rope \SI{2}{\meter} long.
    If the mass is swung in a vertical circle from the free end of the rope,
        what is the tension in the rope when the mass is at its highest point if it is moving with a speed of \SI{5}{\meter\per\second}?
    \begin{multicols}{3}
    \begin{choices}
        \wrongchoice{\SI{5.4}{\newton}}
      \correctchoice{\SI{10.8}{\newton}}
        \wrongchoice{\SI{21.6}{\newton}}
        \wrongchoice{\SI{50}{\newton}}
        \wrongchoice{\SI{65.4}{\newton}}
    \end{choices}
    \end{multicols}
\end{question}
}


%% PhysicsOlympiad 1998
%%----------------------------------------
\element{aapt}{ %% Olympiad-C2
\begin{question}{olympiad-1998-q18}
    A gas contains a mixture of \ce{He^{4}} and \ce{Ne^{20}} atoms.
    If the average speed of the \ce{He^{4}} atoms is $v_0$,
        what is the average speed of the \ce{Ne^{20}} atoms?
    \begin{multicols}{3}
    \begin{choices}
        \wrongchoice{$\dfrac{1}{5} v_0$}
      \correctchoice{$\dfrac{1}{\sqrt{5}} v_0$}
        \wrongchoice{$v_0$}
        \wrongchoice{$\sqrt{5} v_0$}
        \wrongchoice{$5 v_0$}
    \end{choices}
    \end{multicols}
\end{question}
}


%% PhysicsOlympiad 1996
%%----------------------------------------
\element{aapt}{ %% Olympiad-C2
\begin{question}{olympiad-1996-q16}
    The root mean square velocity of oxygen gas (atomic mass 16) is $v$ at room temperature.
    What is the root mean square velocity of helium (atomic mass 4) at the same temperature?
    \begin{multicols}{3}
    \begin{choices}
        \wrongchoice{$4 v$}
      \correctchoice{$2 v$}
        \wrongchoice{$v$}
        \wrongchoice{$\dfrac{v}{2}$}
        \wrongchoice{$\dfrac{v}{4}$}
    \end{choices}
    \end{multicols}
\end{question}
}


%% PhysicsOlympiad 1994
%%----------------------------------------
\element{aapt}{ %% Olympiad-C2
\begin{question}{olympiad-1994-q19}
    The average translational kinetic energy of any ideal gas depends only on:
    \begin{choices}
      \correctchoice{the absolute (Kelvin) temperature.}
        \wrongchoice{the mass of the gas.}
        \wrongchoice{the pressure of the gas.}
        \wrongchoice{the amount of the gas.}
        \wrongchoice{whether the gas is monatomic or diatomic.}
    \end{choices}
\end{question}
}



\endinput


