

%% AAPT Physics Olympiad F=ma Questions
%%----------------------------------------


%% PhysicsOlympiad 2015
%%----------------------------------------


%% PhysicsOlympiad 1999
%%----------------------------------------
\element{aapt}{ %% Olympiad-B1
\begin{question}{olympiad-1999-q20}
    Given a wave produced by a simple harmonic oscillator whose displacement in meters is given by the equation:
        $y = 0.3\sin\left(3\pi x + 24\pi t\right)$, what is the frequency of the wave in hertz?
    \begin{multicols}{3}
    \begin{choices}
        \wrongchoice{\SI{3}{\hertz}}
        \wrongchoice{\SI{7.2}{\hertz}}
        \wrongchoice{\SI{8}{\hertz}}
      \correctchoice{\SI{12}{\hertz}}
        \wrongchoice{\SI{24}{\hertz}}
    \end{choices}
    \end{multicols}
\end{question}
}

\element{aapt}{ %% Olympiad-B1
\begin{question}{olympiad-1999-q21}
    Which of the following wave properties cannot be demonstrated by all kinds of waves?
    \begin{multicols}{2}
    \begin{choices}
      \correctchoice{Polarization}
        \wrongchoice{Diffraction}
        \wrongchoice{Superposition}
        \wrongchoice{Refraction}
        \wrongchoice{Frequency}
    \end{choices}
    \end{multicols}
\end{question}
}


%% PhysicsOlympiad 1997
%%----------------------------------------
\element{aapt}{ %% Olympiad-B1
\begin{question}{olympiad-1997-q18}
    A wave is described by the equation: $y(x,t) = 0.030 \sin\left(5\pi x + 4\pi t\right)$ where $x$ and $y$ are in meters and $t$ is in seconds.
    The $+x$ direction is to the right.
    What is the velocity of the wave?
    \begin{choices}
      \correctchoice{\SI{0.80}{\meter\per\second} to the left}
        \wrongchoice{\SI{1.25}{\meter\per\second} to the left}
        \wrongchoice{\SI[parse-numbers=false]{0.12\pi}{\meter\per\second} to the right}
        \wrongchoice{\SI{0.80}{\meter\per\second} to the right}
        \wrongchoice{\SI{1.25}{\meter\per\second} to the right}
    \end{choices}
\end{question}
}


%% PhysicsOlympiad 1996
%%----------------------------------------
\element{aapt}{ %% Olympiad-B1
\begin{question}{olympiad-1996-q18}
    String $A$ and String $B$ have the same mass and length.
    String $A$ is under tension $T$ and string $B$ is under tension $2T$.
    The speed of waves in $B$ is \rule[-0.1pt]{4em}{0.1pt} times the speed of waves in $A$.
    \begin{multicols}{3}
    \begin{choices}
        \wrongchoice{0.50}
        \wrongchoice{0.71}
        \wrongchoice{1.00}
      \correctchoice{1.4}
        \wrongchoice{2.0}
    \end{choices}
    \end{multicols}
\end{question}
}


%% PhysicsOlympiad 1995
%%----------------------------------------
\element{aapt}{ %% Olympiad-B1
\begin{question}{olympiad-1995-q19}
    Two interfering waves have the same wavelength, frequency, and amplitude.
    They are traveling in the same direction but are 90ยบ out of phase.
    Compared to the individual waves, the resultant wave will have the same:
    \begin{choices}
        \wrongchoice{amplitude and velocity but different wavelength.}
        \wrongchoice{amplitude and wavelength but different velocity.}
      \correctchoice{wavelength and velocity but different amplitude.}
        \wrongchoice{amplitude and frequency but different velocity.}
        \wrongchoice{frequency and velocity but different wavelength.}
    \end{choices}
\end{question}
}

\element{aapt}{ %% Olympiad-B1
\begin{question}{olympiad-1995-q20}
    An organ pipe which is open at both ends resonates with fundamental frequency \SI{300}{\hertz}.
    If one end of the pipe is closed,
        it will resonate with a fundamental frequency of:
    \begin{multicols}{3}
    \begin{choices}
        \wrongchoice{\SI{75}{\hertz}}
      \correctchoice{\SI{150}{\hertz}}
        \wrongchoice{\SI{300}{\hertz}}
        \wrongchoice{\SI{600}{\hertz}}
        \wrongchoice{\SI{1200}{\hertz}}
    \end{choices}
    \end{multicols}
\end{question}
}


%% PhysicsOlympiad 1994
%%----------------------------------------



\endinput


